% +------------------------------------------------------------------------+
% | CGAL Reference Manual: Reference manual for Qt_widget.tex
% +------------------------------------------------------------------------+
% |
% | 20.12.2001	Radu Ursu
% | 
% | \RCSdef{\qtwidgetRev}{$Revision$}
% | \RCSdefDate{\qtwidgetDate}{$Date$}
% +------------------------------------------------------------------------+

% +-----------------------------------------------------+

\ccHeading{Manipulators for Qt\_widget}


A \ccc{manipulator} is an object which can be inserted in the Qt\_widget 
stream, via the operator \(<<\), to change the context for further
drawing.

Here, we simply document the use of these operators which is all the
user needs to know to modify the state of a stream. The design of
\ccc{manipulators} and \ccc{manipulator-creator} being given after.

\ccFunction{Qt_widget& operator<<(Qt_widget& win, BackgroundColor(const
Color& c));}{Sets the color used for backgroundcolor.}
\ccGlue

\ccFunction{Qt_widget& operator<<(Qt_widget& win, FillColor(const
Color& c));}{Sets the color used for filling the objects.}
\ccGlue

\ccFunction{Qt_widget& operator<<(Qt_widget& win, LineWidth(const
unsigned int i));}{Sets the width of the line for drawing objects.}
\ccGlue

\ccFunction{Qt_widget& operator<<(Qt_widget& win, PointSize(const
unsigned int i));}{Sets the size of the points.}
\ccGlue

\ccFunction{Qt_widget& operator<<(Qt_widget& win, noFill());}{Sets the state 
of Qt\_widget concerning filling the objects to be false.}
\ccGlue

\ccFunction{Qt_widget& operator<<(Qt_widget& win, const Color& c);}{Sets the 
color used as the Qt\_widget fillColor.}
\ccGlue

\ccFunction{Qt_widget& operator<<(Qt_widget& win, const PointStyle& ps);}{Sets
 the point style for Qt\_widget. \ccc{PointStyle} is a global enumeration declared in Qt\_widget.h.}
\ccGlue


% +-----------------------------------------------------+
% EOF







