\begin{ccRefConcept}{FractionTraits}

\ccDefinition

A model of \ccRefName\ is associated with a type \ccc{Type}.

It first of all indicates whether the associated type can be considered as 
a fraction. In this case it provides a generic mechanism to access numerator and 
denominator of this type. 


Motivation: Beyond the need for performing algebraic operations on objects as a 
whole, there are also number types which one would like to decompose into 
numerator and denominator. This does not only hold for rational numbers 
as \ccc{Quotient}, \ccc{Gmpq}, \ccc{mpq_class} or \ccc{leda_rational}, but 
also compound objects as \ccc{Sqrt_extension} or \ccc{Polynomial} 
which may decompose into a (scalar) 
denominator and a compound numerator with a simpler coefficient type 
(e.g. integer instead of rational). Often operations can be performed faster on 
these denominator-free multiples. \\


\ccInclude{CGAL/Fraction_traits.h}

\ccTypes

\ccNestedType{Type}{the associated type}
\ccNestedType{Is_fraction}{ 
        Tag indicating whether the associated type is a fraction and can be 
        decomposed into a numerator and denominator. \\
        This is either \ccc{CGAL::Tag_true} or \ccc{CGAL::Tag_false}.}
\ccNestedType{Numerator_type  }{The type to represent the numerator. 
        This is undefined in case the associated type is not a fraction. }
\ccNestedType{Denominator_type}{The (simpler) type to represent the denominator.
        This is undefined in case the associated type is not a fraction. }

\ccHeading{Functors}

\ccNestedType{Decompose}{If \ccc{Type} is decomposable this is a model of \ccc{FractionTraits::Decompose} otherwise this is \ccc{CGAL::Null_functor}.}
\ccNestedType{Compose}{If \ccc{Type} is decomposable this is a model of \ccc{FractionTraits::Compose} otherwise this is \ccc{CGAL::Null_functor}.}
\ccNestedType{Common_factor}{If \ccc{Type} is decomposable this is a model of \ccc{FractionTraits::CommonFactor} otherwise this is \ccc{CGAL::Null_functor}.}


\ccSeeAlso
\ccRefIdfierPage{CGAL::Fraction_traits<Type>}\\
\ccRefConceptPage{FractionTraits::Decompose}\\
\ccRefConceptPage{FractionTraits::Compose}\\
\ccRefConceptPage{FractionTraits::CommonFactor}\\

\end{ccRefConcept}
