\begin{ccRefConcept}{RealEmbeddable}

\ccDefinition

A model of this concepts represents numbers that embeddable on the real 
axis. The type obeys the algebraic structure and compares two values according 
to the total order of the real numbers.


Remark:\\
If a number type is a model of both IntegralDomainWithoutDiv and 
RealComparable, the number an object of that type represents for the 
algebraic operations must be the same real number it represents for 
comparison. It follows that the ring represented by such a number type 
is a subring of the real numbers and hence has characteristic zero 
( see http://mathworld.wolfram.com/CharacteristicField.html ).


\ignore{
In addition to the comparison operators, the template class 
NiX::NT_traits<NT> provides three adaptable functors for number types 
NT that are a model of RealComparable.

    * NiX::NT_traits::Abs ()(x) is an AdaptableUnaryFunction that accepts 
a number x and computes its absolute value.

    * NiX::NT_traits::Sign ()(x) is an AdaptableUnaryFunction that accepts
 a number x and computes its three-valued sign.

    * NiX::NT_traits::Compare ()(x,y) is an AdaptableBinaryFunction that
 accepts two numbers x and y and computes a three-valued comparison result.

    * NiX::NT_traits::To_double ()(x) is an AdaptableUnaryFunction that 
accepts a number x and computes a double approximation of x.

    * NiX::NT_traits::To_Interval ()(x) is an AdaptableUnaryFunction that 
accepts a number x and computes a double Interval approximation of x. It 
is guaranteed that x is contained in the interval. 
}

\ccRefines
\ccc{LessThanComparable}

\ccOperations
\ccFunction{bool operator< (const RealEmbeddable &a, 
                            const RealEmbeddable &b);}{}
\ccGlue
\ccFunction{bool operator<=(const RealEmbeddable &a, 
                            const RealEmbeddable &b);}{}
\ccGlue
\ccFunction{bool operator> (const RealEmbeddable &a, 
                            const RealEmbeddable &b);}{}
\ccGlue
\ccFunction{bool operator>=(const RealEmbeddable &a, 
                            const RealEmbeddable &b);}{}
\ccGlue



\ccSeeAlso

\ccRefIdfierPage{RealEmbeddableTraits}\\

\ccHasModels

\end{ccRefConcept}