% +------------------------------------------------------------------------+
% | Reference manual page: Event.tex
% +------------------------------------------------------------------------+
% | 20.03.2005   Author
% | Package: Kinetic_data_structures
% | 
\RCSdef{\RCSEventRev}{$Id$}
\RCSdefDate{\RCSEventDate}{$Date$}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+

\ccDefGlobalScope{CGAL::}
\begin{ccRefClass}[Kinetic::]{Event_base<KDS>}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries

\ccDefinition
  
This class provides a base to use for implementing events. The base provides default implementations of several methods and stores a pointer to the KDS.

\ccCreationVariable{a}  %% choose variable name

\ccConstructor{Event_base(KDS *kds)}{Construct the object and store the pointer to the KDS.}

\ccConstructor{Event_base()}{Use a \ccc{NULL} pointer as the KDS pointer.}

\ccOperations

\ccMethod{KDS* kds();}{Returns the stored pointer to the KDS.}

\ccMethod{CGAL::Comparison_result compare_concurrent(Key a, Key b) const;}{This returns \ccc{CGAL::compare(a,b)}.}

\ccMethod{bool merge_concurrent(Key a, Key b);}{ This does nothing and returns false.}

\ccMethod{void audit(Key this_key);}{Audit that this is a valid event.}

\ccMethod{std::ostream& write(std::ostream&) const;}{Write ``Event base'' to the stream.}

%\ccMethod{void degenerate_events(Event_key this_event, Event_key other_event);}{This event and the event referenced by \ccc{k} belong to the same KDS and occur simultaneously. This function call gives the KDS a chance to handle } 

\ccIsModel

\ccc{Kinetic::Event}.

\ccSeeAlso

\ccc{Kinetic::EventQueue}

\ccExample

All of the kinetic data structures provided have models of
\ccRefName. Here is the code implementing a swap event from the
sorting kinetic data structure.

\begin{ccExampleCode}
template <class Certificate, class Id, class Root_enumerator> 
class Swap_event: CGAL::Kinetic::Event_base<Sort> {
  typedef CGAL::Kinetic::Event_base<Sort> P;
public:
  Swap_event(Id o, Sort* sorter, 
	     const Certificate &s): P(sorter),
	                            left_object_(o),
                                    s_(s){}
  void process(){
    P::kds()->swap(left_object_, s_);
  }
  Id left_object_; 
  Certificate s_;
};
\end{ccExampleCode}


\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

