% +------------------------------------------------------------------------+
% | Reference manual page: Triangulation_simplex_3.tex
% +------------------------------------------------------------------------+
% | 27.09.2005   Nico Kruithof
% | Package: Skin_surface
% | 
\RCSdef{\RCSTriangulationsimplexRev}{$Id$}
\RCSdefDate{\RCSTriangulationsimplexDate}{$Date$}
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefClass}{Triangulation_simplex_3<Triangulation_3>}
\label{refTriangulationSimplex}

\ccDefinition The class \ccRefName\ stores a simplex of any dimension
defined by the \ccc{Triangulation_3} class. It also makes two
simplices comparable which is necessary to create a \ccc{map} or
\ccc{set} of simplices. The simplex is invalidated by any change in
the simplex it points to.

\ccInclude{CGAL/Triangulation_simplex_3.h}

\ccParameters 
%
It is parameterized by the triangulation it derives the simplices
from. 

\ccTypes
\ccThree{typedef Triangulation_3::Vertex_handle}{Triangulated}{}
\ccThreeToTwo

\ccTypedef{typedef Triangulation_3::Vertex_handle Vertex_handle;}{}
\ccGlue
\ccTypedef{typedef Triangulation_3::Edge Edge;}{}
\ccGlue
\ccTypedef{typedef Triangulation_3::Facet Facet;}{}
\ccGlue
\ccTypedef{typedef Triangulation_3::Cell_handle Cell_handle;}{}


\ccCreation
\ccCreationVariable{simplex}  %% choose variable name
\ccThree{Point }{Point}{}
\ccThreeToTwo

\ccConstructor{Triangulation_simplex_3();}{Initialises the simplex to
  an invalid simplex.}
\ccConstructor{Triangulation_simplex_3(Vertex_handle vh);}{Initialises
  the simplex with the vertex pointed to by \ccc{vh}.}
\ccConstructor{Triangulation_simplex_3(Edge e);}{Initialises the
  simplex with the edge \ccc{e}.}
\ccConstructor{Triangulation_simplex_3(Facet f);}{Initialises the
  simplex with the facet \ccc{f}.}
\ccConstructor{Triangulation_simplex_3(Cell_handle ch);}{Initialises
  the simplex with the cell pointed to by \ccc{ch}.}

\ccOperations
\ccThree{Vertex_han}{Vertex_handle(simplex)xx}{}
\ccThreeToTwo

\ccMethod{int dimension () const;}{returns the dimension of the
  simplex.}
%
\ccMethod{operator Vertex_handle () const;}{Returns the \ccc{Vertex_handle}
  stored in the simplex. \ccPrecond{dimension() == 0}}
\ccGlue
\ccMethod{operator Edge () const;}{Returns the \ccc{Edge}
  stored in the simplex. \ccPrecond{dimension() == 1}}
\ccGlue
\ccMethod{operator Facet () const;}{Returns the \ccc{Facet}
  stored in the simplex. \ccPrecond{dimension() == 2}}
\ccGlue
\ccMethod{operator Cell_handle () const;}{Returns the \ccc{Cell_handle}
  stored in the simplex. \ccPrecond{dimension() == 3}}


%NGHK: check
\ccMethod{bool operator==(const Triangulation_simplex_3 &s1);}{Test
  whether two simplices are equal.}
\ccGlue
%NGHK: check
\ccMethod{bool operator< (const Triangulation_simplex_3 &s1);}{Defines
  a partial ordering on the simplices.}

\ccSeeAlso
\ccRefIdfierPage{CGAL::Triangulation_3<TriangulationTraits_3,TriangulationDataStructure_3>}

\end{ccRefClass}
