% +------------------------------------------------------------------------+
% | Reference manual page: Triangulation_incremental_builder_3.tex
% +------------------------------------------------------------------------+
% | 27.09.2005   Nico Kruithof
% | Package: Skin_surface
% | 
\RCSdef{\RCSTriangulationincrementalbuilderRev}{$Id$}
\RCSdefDate{\RCSTriangulationincrementalbuilderDate}{$Date$}
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefClass}{Triangulation_incremental_builder_3<Triangulation_3>}
\label{refTriangulationincrementalbuilder}
\ccDefinition
  
The \ccRefName\ supports the incremental construction of a
triangulation from a set of vertices and cells. First the vertices of
the triangulation are inserted. Then the cells are inserted as
quadruples of four vertices. The orientation of each cell is supposed
to be positive.

\ccInclude{CGAL/Triangulation_incremental_builder_3.h}


\ccThree{typedef T::Vertex_handle}{Triang}{}
\ccThreeToTwo

\ccTypes

\ccTypedef{typedef Triangulation_3 T;}{}

\ccTypedef{typedef T::Vertex_handle Vertex_handle;}{}
\ccGlue
\ccTypedef{typedef T::Cell_handle Cell_handle;}{}
\ccGlue
\ccTypedef{typedef T::Facet Facet;}{}

\ccThree{Vertex_handle}{Triang}{}
\ccThreeToTwo


\ccCreation
\ccCreationVariable{observer}

\ccConstructor{Triangulation_incremental_builder_3( T &t, bool verbose
  = false);}{}

\ccOperations

\ccMethod{void begin_triangulation(int dim);}{Initializes the
  triangulation and sets the dimension to \ccc{dim}.}

\ccMethod{void end_triangulation();}{Finalizes the triangulation.}

\ccMethod{Vertex_handle add_vertex();}{Adds a vertex to the
  triangulation and returns a pointer to the vertex.}

\ccMethod{Cell_handle add_cell(Vertex_handle vh0, Vertex_handle vh1,
  Vertex_handle vh2, Vertex_handle vh3);}{Adds a cell to the
  triangulation with the given vertices. Only finite cells have to be
  specified.}

\end{ccRefClass}
