\begin{ccRefClass}{tree_point_traits}

\ccDefinition
\ccStyle{tree_point_traits} is a template class
that provides an interface to data items.

\ccInclude{CGAL/Tree_traits.h}\\

\ccTypes
\gdef\ccPureClassName{Point_traits}
\gdef\ccPureTemplateClassName{Point_traits}
\ccStyle{typedef}\\
\ccStyle{tree_point_traits<Data, Window, Key,
         Data_func, Window_left_func, Window_right_func,
         Compare> Point_traits;}

\ccNestedType{Data}{the container
  \ccStyle{Data} --- defines the Data type. It may consist of
         several data slots. One of these data slots has to be of
         type \ccStyle{Key}.}
\ccNestedType{Window}{the container
  \ccStyle{Window} --- defines the type of the query rectangle. It
  may consist of
         several data slots. Two of these data slots has to be of
         type \ccStyle{Key}}

\ccNestedType{Key}{the type
  \ccStyle{Key} of the data
  slot this  traits class provides access to.}

\ccNestedType{Data_func}{
  \ccStyle{Data_func} is a
         function object  providing an
  \ccc{operator()} that takes an argument of type \ccc{Data} and returns
  a component of type \ccc{Key}.}
\ccNestedType{Window_left_func}{
  \ccStyle{Window_left_func}  is a function objects that
         allow to access the
         left data slot of container
         \ccStyle{Window} which has type \ccStyle{Key}}
\ccNestedType{Window_right_func}{
  \ccStyle{Window_right_func}  is a function objects that
         allow to access the
         right data slot of container
         \ccStyle{Window} which has type \ccStyle{Key}}
\ccNestedType{Compare}{ defines a comparison relation which must
         define a strict ordering of the objects of type
         \ccStyle{Key}. If defined, \ccStyle{less<Key>}
         is sufficient.}


\ccCreation
\ccStyle{tree_point_traits<Data, Window, Key,
         Data_func, Window_left_func,
         Window_right_func, Compare> d();}\\
\ccCreationVariable{d}
%\renewcommand{\ccAlternateThreeColumn}{\ccFalse}
\hspace*{0.2\linewidth}\parbox{0.8\linewidth}{
 Generation of a \ccStyle{tree\_point\_traits} instance. It is a template class
that provides an interface to data items.}


\ccOperations
\ccMethod{Key get_key(Data d);}{The data slot of
  the data item of \ccStyle{d} of type \ccStyle{Key} is
  accessed by function object \ccStyle{Data_func}.}
\ccMethod{Key get_left(Window w);}{The data slot of
  the data item of \ccStyle{w} of type \ccStyle{Key} is
  accessed by function object
  \ccStyle{Window_left_func}.}
\ccMethod{Key get_right(Window w);}{The data slot of
  the data item of \ccStyle{w} of type \ccStyle{Key} is
  accessed by function object \ccStyle{Window_right_func}.}
\ccMethod{bool comp(Key& key1, Key&
  key2);}{returns \ccStyle{Compare(key1, key2)}.}
\ccMethod{bool key_comp(Data& data1, Data&
  data2);}{returns \ccStyle{Compare(get_key(data1), get_key(data2))}.}

\end{ccRefClass}
