\begin{ccRefClass}{tree_interval_traits}

\ccDefinition
\ccStyle{tree_interval_traits} is a template class
that provides an interface to data items. It is similar to
\ccStyle{tree_point_traits}, except that it provides
access to two data slots of the same type of each container class
(\ccStyle{Data, Window}) instead of providing access to one
data slot of container class \ccStyle{Data} and two data slots
of class  \ccStyle{Window}.

\ccInclude{CGAL/Tree_traits.h}\\

\ccTypes
\ccStyle{typedef}\\
\ccc{tree_interval_traits<Data, Window, Key,
         Data_left_func, Data_right_func, Window_left_func,
         Window_right_func, Compare> Interval_traits;}
\gdef\ccPureClassName{Interval_traits}
\gdef\ccPureTemplateClassName{Interval_traits}

\ccNestedType{Data}{the container \ccStyle{Data} ---
  the data type. It may consist of
         several data slots. Two of these data slots have to be of
         type \ccStyle{Key}.}
\ccNestedType{Window}{the container
  \ccStyle{Window} --- the query window type. It may consist of
         several data slots. Two of these data slots have to be of
         type \ccStyle{Key}.}
\ccNestedType{Key}{the type
  \ccStyle{Key} of the data
  slot this traits class provides access to.}
\ccNestedType{Data_left_func}{
  \ccStyle{Data_left_func} is a
         function object  providing an
  \ccc{operator()} that takes an argument of type \ccc{Data}
  and returns
  a (the left) component of type \ccc{Key}.}
\ccNestedType{Data_right_func}{
  \ccStyle{Data_right_func} is a
         function object  providing an
  \ccc{operator()} that takes an argument of type \ccc{Data}
  and returns
  a (the right) component of type \ccc{Key}.}
\ccNestedType{Window_left_func}{
  \ccStyle{Window_left_func}  is a function objects that
         allow to access the
         left data slot of container
         \ccStyle{Window} which has type \ccStyle{Key}}
\ccNestedType{Window_right_func}{
  \ccStyle{Window_right_func}  is a function objects that
         allow to access the
         right data slot of container
         \ccStyle{Window} which has type \ccStyle{Key}}
\ccNestedType{Compare}{ defines a comparison relation which must
         define a strict ordering of the objects of type
         \ccStyle{Key}. If defined, \ccStyle{less<Key>}
         is sufficient.}

\ccCreation
\ccCreationVariable{d}

\ccStyle{tree_interval_traits<Data, Window, Key,
         Data_left_func, Data_right_func,
         Window_left_func,
         Window_right_func, Compare> d();}\\
\hspace*{0.2\linewidth}\parbox{0.8\linewidth}{Generation of a \ccStyle{tree\_point\_traits} instance. It is a template class
that provides an interface to data items.}

\ccOperations
\ccMethod{Key get_left(Data d);}{The data slot of
  the data item of \ccStyle{d} of type \ccStyle{Key} is
  accessed by function object
  \ccStyle{Data_left_func}.}
\ccMethod{Key get_right(Data d);}{The data slot of
  the data item of \ccStyle{d} of type \ccStyle{Key} is
  accessed by function object
  \ccStyle{Data_right_func}.}
\ccMethod{Key get_left_win(Window w);}{The data slot of
  the data item of \ccStyle{w} of type \ccStyle{Key} is
  accessed by function object
  \ccStyle{Window_left_func}.}
\ccMethod{Key get_right_win(Window w);}{The data slot of
  the data item of \ccStyle{w} of type \ccStyle{Key} is
  accessed by function object \ccStyle{Window_right_func}.}
\ccMethod{bool comp(Key& key1, Key& key2);}{returns Compare(key1, key2).}

\end{ccRefClass}
