% +------------------------------------------------------------------------+
% | Reference manual page: Ovl_dcel.tex (Map_overlay)
% +------------------------------------------------------------------------+
% | 
% | Package: ovl (Map_Overlay_2)
% | 
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+

\begin{ccRefClass}{Map_overlay_default_dcel<Traits,V,H,F>}

\ccDefinition

    The \ccClassTemplateName\ is a model of the \ccc{MapOverlayDcel_2} concept. 
    Its template parameters are the Traits, the vertex, halfedge and face
    types. The Traits type conforms to the requirements of the 
    \ccc{SweepLineTraits_2} concept, and the three latter types
    conform to the requirements of the \ccc{PlanarMapDcelVertex_2} concept,
    the \ccc{PlanarMapDcelHalfedge_2} concept and the \ccc{PlanarMapDcelFace_2}
    concept respectively.

\ccInclude{CGAL/Map_overlay_default_dcel.h}

\ccIsModel
    \ccc{MapOverlayDcel_2}

\ccHeading{Models for Dcel Vertex, Halfedge and Face}
The \ccStyle{Vertex_overlay<Vertex_base>} is a model for the 
\ccc{MapOverlayDcelVertex_2} concept. 
The \ccStyle{Halfedge_overlay<Halfedge_base>} is a
model for the \ccc{MapOverlayDcelHalfedge_2} concept.
The \ccStyle{Face_overlay<Face_base>} is a
model for the \ccc{MapOverlayDcelFace_2} concept. 

\ccHeading{Requirements}
\ccc{Traits} is a model for the \ccc{SweepLineTraits_2} concept.
\ccc{Vertex_base} is a model for the \ccc{PlanarMapDcelVertex_2} concept.
\ccc{Halfedge_base} is a model for the \ccc{PlanarMapDcelHalfedge_2} concept.
\ccc{Face_base} is a model for the \ccc{PlanarMapDcelFace_2} concept.


\ccInclude{CGAL/Map_overlay_default_dcel.h}

\ccHeading{The Default Dcel Structure}
The 
\ccStyle{Map_overlay_default_dcel<Traits,Vertex_base=Pm_vertex_base<Traits::Point>,
Halfedge_base=Pm_halfedge_base<Traits::X_curve>,
Face_base=Pm_face_base>} 
is a model of the \ccc{MapOverlayDcel_2} concept. 
Its template parameters are the traits class, 
and the basic vertex, halfedge and face which the overlay components inherit.
The default template parameters for the three basic components are the 
\ccc{Planar_Map_2} basic components.
The overlay default DCEL is a wrapper for \ccStyle{Pm_dcel} instantiated 
with \ccStyle{Vertex_overlay<Vertex_base>},
\ccStyle{Halfedge_overlay<Halfedge_base>} and 
\ccStyle{Face_overlay<Fase_base>}.


\end{ccRefClass}
% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+
