\begin{ccRefClass}{Circle_3<SphericalKernel>}

\ccInclude{CGAL/Circle_3.h}

\ccIsModel

\ccc{SphericalKernel::Circle_3}

\ccCreation
\ccCreationVariable{c}

\ccThree{Circular_arc_point_3}{ca.is_x_monotone()}{}
\ccThreeToTwo

\ccConstructor{Circle_3(const SphericalKernel::Point_3& center, 
	const SphericalKernel::FT& sr, const SphericalKernel::Plane_3& p)}
{Constructs the circle of center \ccc{c} and squared radius \ccc{sr} in plane \ccc{p}.
\ccPrecond{$sr>0$.}}

\ccConstructor{Circle_3(const SphericalKernel::Sphere_3& s1, 
	const SphericalKernel::Sphere_3& s2)}
{Constructs the circle along which the two spheres intersect.
\ccPrecond{The two spheres intersect along a circle.}}

\ccConstructor{Circle_3(const SphericalKernel::Sphere_3& s, 
	const SphericalKernel::Plane_3& p)}
{Constructs the circle along which the sphere and the plane intersect.
\ccPrecond{The sphere and the plane intersect along a circle.}}

\ccConstructor{Circle_3(const SphericalKernel::Plane_3& p, 
	const SphericalKernel::Sphere_3& s)}
{Constructs the circle along which the sphere and the plane intersect.
\ccPrecond{The sphere and the plane intersect along a circle.}}

\ccAccessFunctions

\ccThree{SphericalKernel::Circular_arc_point_3}{ca.is_x_monotone()}{}
\ccThreeToTwo

\ccMethod{SphericalKernel::Point_3 center();}{}
\ccGlue
\ccMethod{SphericalKernel::FT squared_radius();}{}

\ccMethod{SphericalKernel::Plane_3 supporting_plane();}{}

\ccMethod{SphericalKernel::Bbox_3 bbox();}{}

\ccOperations

\ccFunction{bool operator==(const Circle_3<SphericalKernel> &p,
		           const Circle_3<SphericalKernel> &q);}
{Test for equality.}

\ccHeading{I/O}

\ccFunction{istream& operator>> (std::istream& is, Circle_3 & c);}
{Reads a plane and a sphere defining the circle.}
\ccGlue
\ccFunction{ostream& operator<< (std::ostream& os, const Circle_3 &c);}
{Outputs the supporting plane and the diametral sphere of the circle.}

\end{ccRefClass}
