\lcTex{\chapter*{Preface}}
\lcHtml{\chapter{Preface}}


\cgal\ is a {\em Computational Geometry Algorithms Library} written in \CC, 
developed by a consortium consisting of
\ccAnchor{http://www.inf.ethz.ch/}{ETH Z\"urich} (Switzerland), 
\ccAnchor{http://www.inf.fu-berlin.de/}{Freie Universit{\"a}t Berlin} (Germany), 
\ccAnchor{http://www.inria.fr/recherche/equipes/geometrica.en.html}{{\sc Inria} 
Sophia-Antipolis} (France),
\ccAnchor{http://www.informatik.uni-halle.de/}{Martin-Luther-Universit{\"a}t 
Halle-Wittenberg} (Germany),
\ccAnchor{http://www.mpi-sb.mpg.de/}{Max-Planck Institut f{\"u}r Informatik},
Saarbr\"ucken (Germany),
\ccAnchor{http://info.risc.uni-linz.ac.at/}{{\sc Risc}} Linz (Austria)
\ccAnchor{http://www.cs.tau.ac.il/}{Tel-Aviv University} (Israel), and
\ccAnchor{http://www.cs.uu.nl/}{Utrecht University} (The Netherlands). 
You can find more information about the project on the 
\ccAnchor{http://www.cgal.org}{\cgal\ home page}
\ccTexHtml{at URL {\tt http://www.cgal.org}}{}.




\section*{Editorial Committee}

\input{Manual/editors}



\section*{Authors Basic Library}

\noindent
Chapter~\ref{chap:convex_hull_2}: Susan Hert and Stefan Schirra 
(\ccHtmlNoLinksFrom{Max-Planck Institut f\"ur Informatik}).

\noindent
Chapter~\ref{chap:convex_hull_3}: Susan Hert and Stefan Schirra 
(\ccHtmlNoLinksFrom{Max-Planck Institut f\"ur Informatik}).

\noindent
Chapter~\ref{chap:convex_hull_d}: Susan Hert and Michael Seel 
(\ccHtmlNoLinksFrom{Max-Planck Institut f\"ur Informatik}).

\noindent
Chapter~\ref{Polygon}: Geert-Jan Giezeman and Wieger Wesselink 
(Utrecht University).

\noindent
Chapter~\ref{chap:polygon_partition}: Susan Hert 
(\ccHtmlNoLinksFrom{Max-Planck Institut f\"ur Informatik}).

\noindent
Chapter~\ref{chap:nef_2}: Michael Seel 
(\ccHtmlNoLinksFrom{Max-Planck Institut f\"ur Informatik}).

\noindent
Chapter~\ref{I1_ChapterTopologicalMap}: Iddo Hanniel, Shai Hirsch 
(Tel-Aviv University).

\noindent
Chapter~\ref{I1_ChapterPlanarMap}: Ester Ezra, Eyal Flato, Dan Halperin, 
Iddo Hanniel, Sariel Har-Peled, Shai Hirsch, Oren Nechushtan 
(Tel-Aviv University).

\noindent
Chapter~\ref{I1_ChapterPmwx}: Eyal Flato, Dan Halperin, Shai Hirsch,
(Tel-Aviv University).

\noindent
Chapter~\ref{I1_ChapterArrangement_2}: Ester Ezra, Eyal Flato, 
Iddo Hanniel, Shai Hirsch, Ron Wein (Tel-Aviv University).


\noindent
Chapter~\ref{chapterPolyhedron}: Lutz Kettner (ETH Z\"urich).

\noindent
Chapter~\ref{chapterHalfedgeDS}: Lutz Kettner (ETH Z\"urich).

\noindent
Chapter~\ref{Chapter_2D_Triangulations}: 
Herv\'e Br\"onnimann, Olivier Devillers, Andreas Fabri,
Monique Teillaud, Mariette Yvinec ({\sc Inria} Sophia-Antipolis).

\noindent
Chapter~\ref{user_chapter_2D_Triangulation_Data_Structure}"
Herv\'e Br\"onnimann, Olivier Devillers, Andreas Fabri,
Monique Teillaud, Mariette Yvinec ({\sc Inria} Sophia-Antipolis).


\noindent
Chapter~\ref{chapter-Triangulation3}: 
Andreas Fabri, Sylvain Pion, Monique Teillaud ({\sc Inria} Sophia-Antipolis).

\noindent
Chapter~\ref{chapter-TDS3}: 
Sylvain Pion, Monique Teillaud ({\sc Inria} Sophia-Antipolis).

\noindent
Chapter~\ref{I1_ChapterAlphashapes2D}: 
Tran Kai Frank Da ({\sc Inria} Sophia-Antipolis).

\noindent
Chapter~\ref{I1_ChapterAlphashapes3D}: 
Tran Kai Frank Da ({\sc Inria} Sophia-Antipolis).

\noindent
Chapter~\ref{chapter-apollonius2}: Menelaos Karavelas, Mariette Yvinec ({\sc Inria} Sophia-Antipolis).



\noindent
Chapter~\ref{Optimisation}: Bernd G\"artner, Thomas Herrmann, Michael Hoffmann,
Sven Sch\"onherr (ETH Z\"urich).

\noindent
Chapter~\ref{chapter_Interval_skip_list} : Andreas Fabri ({\sc Geometry Factory}).

\noindent
Chapter~\ref{chapterPoint_set_2} : Matthias B\"asken (Martin-Luther-Universit{\"a}t Halle-Wittenberg).

\noindent
Chapter~\ref{Trees}: Gabriele Neyer (ETH Z\"urich).

\noindent
Chapter~\ref{ChapterUserSpatialSearching}: Hans Tangelder (Utrecht University).

\section*{Authors Support Library}

Chapter~\ref{Numbertype}: 
Olivier Devillers, Sylvain Pion ({\sc Inria} Sophia-Antipolis),
Lutz Kettner (ETH Z\"urich),
Susan Hert, Stefan Schirra (\ccHtmlNoLinksFrom{Max-Planck-Institut f\"ur Informa
tik}).

Chapter~\ref{chapterStlExtensions}: 
Michael Hoffmann, Lutz Kettner (ETH Z\"urich).

Chapter~\ref{chap:Handles_and_Circs}:
Olivier Devillers, Mariette Yvinec ({\sc Inria} Sophia-Antipolis),
Michal Seel (\ccHtmlNoLinksFrom{Max-Planck-Institut f\"ur Informatik}),
Lutz Kettner (ETH Z\"urich).

Chapter~\ref{chapterGenerators}: 
Susan Hert (\ccHtmlNoLinksFrom{Max-Planck-Institut f\"ur Informatik}),
Michael Hoffmann, Lutz Kettner, Sven Sch\"onherr (ETH Z\"urich).

Chapter~\ref{chap:Miscellany}:
Michal Seel (\ccHtmlNoLinksFrom{Max-Planck-Institut f\"ur Informatik}).
Lutz Kettner (ETH Z\"urich).

Chapter~\ref{Chapter_operator_for_IO_streams}: 
Andreas Fabri ({\sc Inria} Sophia-Antipolis),
Geert-Jan Giezeman (Utrecht University),
Lutz Kettner (ETH Z\"urich).

Chapter~\ref{chapterWin}:
Matthias B\"asken (Martin-Luther-Universit{\"a}t Halle-Wittenberg),
Andreas Fabri ({\sc Inria} Sophia-Antipolis),
Lutz Kettner (ETH Z\"urich),
Stefan Schirra (\ccHtmlNoLinksFrom{Max-Planck-Institut f\"ur Informatik}).

Chapter~\ref{chapterGeoWin}:
Matthias B\"asken (Martin-Luther-Universit{\"a}t Halle-Wittenberg).

Chapter~\ref{ChapterGeomview}:
Andreas Fabri, Mariette Yvinec ({\sc Inria} Sophia-Antipolis).

Chapter~\ref{chapterQtwidget}:
Radu Ursu ({\sc Inria} Sophia-Antipolis),
Laurent Rineau (ENS Paris).



\section*{Acknowledgement}


This work was partially supported by the ESPRIT IV Long Term Research
Projects No.~21957 (CGAL) and No.~28155 (GALIA), and by the IST
Programme of the EU as a Shared-cost RTD (FET Open) Project No
IST-2000-26473 (ECG - Effective Computational Geometry for Curves and
Surfaces).


