% +------------------------------------------------------------------------+
% | Reference manual page: CellAttribute.tex
% +------------------------------------------------------------------------+
% | 04.02.2010   Guillaume Damiand
% | Package: Combinatorial_map
% +------------------------------------------------------------------------+
\ccRefPageBegin
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+
\begin{ccRefConcept}{CellAttribute}
%\ccRefLabel{CGAL::CellAttribute}

\ccDefinition
  
The concept \ccRefName\ represents a non void attribute associated
with a cell of a combinatorial map. It can keep a handle to one
dart of its associated cell, and can contain any information.

% . The attribute keeps a handle to one dart
% of its associated cell when the template parameter \ccc{Tag} is
% \ccc{Tag_true} (bi-directional association between darts and
% attributes). If \ccc{Tag} is \ccc{Tag_false}, the attribute does not
% know a dart of its associated cell (uni-directional association from
% darts to attributes).

% \ccParameters
% \ccc{Refs} must be a model of the \ccc{CombinatorialMap} concept defining
%    \ccc{Dart_handle} and \ccc{Dart_const_handle} types.\\
% \ccc{Tag} \ccc{Tag_true} to enable the storage of a
% \ccc{Dart_handle} of the associated cell, \ccc{Tag_false} otherwise.\\
% \ccc{FunctorOnMerge} functor called when two attributes are merged. 
% Must be a model of the \ccc{AttributeFunctor} concept.\\
% \ccc{FunctorOnSplit} functor called when one attribute is split in two. 
% Must be a model of the \ccc{AttributeFunctor} concept.

\ccTypes
\ccNestedType{Dart_handle}{Dart handle type.}
\ccGlue
\ccNestedType{Dart_const_handle}{Dart const handle type.}

\ccNestedType{Info}{Type of the information contained in the attribute. 
   If \ccc{void}, the cell attribute does not have any information.}

\ccNestedType{Supports_cell_dart}
    {Equals to \ccc{Tag_true} to enable the storage of a
      \ccc{Dart_handle} of the associated cell, \ccc{Tag_false} otherwise.}

\ccNestedType{On_merge}{Functor called before merging two attributes. Must be 
  a model of the \ccc{Binary Function} concept having two references
  to a model of \ccc{CellAttribute} as type of both arguments and \ccc{void} as
  return type.} 
\ccGlue
\ccNestedType{On_split}{Functor called after an attribute was split in two.
  Must be a model of the \ccc{Binary Function} concept having two references
  to a model of \ccc{CellAttribute} as type of both arguments and \ccc{void} as
  return type.} 
%the \ccc{AttributeFunctor} concept

% +-----------------------------------+
\ccCreation
\ccCreationVariable{ca}

\ccConstructor{CellAttribute();}{}

\ccConstructor{Cell_attribute(const Info& info);}
 {Constructor initializing the information of \ccc{ca} by the 
   copy contructor \ccc{Info(info)}.
   Defined only if \ccc{Info} is different from \ccc{void}.}

% +-----------------------------------+
\ccHeading{Access Member Functions}

\ccMethod{Dart_handle dart();} 
    {Returns one dart of the cell associated to attribute \ccc{ca}. 
     NULL if \ccc{Supports_cell_dart} is equal to \ccc{Tag_false}.}
\ccGlue
\ccMethod{Dart_const_handle dart() const;} 
   {Returns one dart of the cell associated to attribute \ccc{ca}, 
    when \ccc{ca} is const. 
    NULL if \ccc{Supports_cell_dart} is equal to \ccc{Tag_false}.}

\ccMethod{void set_dart(Dart_handle ahandle);}
    {Sets the dart of the cell associated to attribute \ccc{ca} to \ccc{ahandle}, 
      if \ccc{Supports_cell_dart} is equal to \ccc{Tag_true}.
      Otherwise, this method does nothing.
     \ccPrecond{\ccc{ahandle} belongs to the cell associated to \ccc{ca}.}
}

\ccMethod{Info& info();}
  {Returns the information of \ccc{ca}. 
    Defined only if \ccc{Info} is different from \ccc{void}.}

\ccMethod{const Info& info() const;}
  {Returns the information of \ccc{ca}, when \ccc{ca} is const.
    Defined only if \ccc{Info} is different from \ccc{void}.}

\ccHasModels
\ccRefIdfierPage{CGAL::Cell_attribute<CMap,Info_,Tag,OnMerge,OnSplit>}
%\ccRefIdfierPage{CGAL::Cell_attribute_with_info}\\

% \ccRefIdfierPage{CGAL::Cell_with_point}\\
% \ccRefIdfierPage{CGAL::Cell_with_point_and_attribute}\\


\ccSeeAlso
%\ccRefConceptPage{CGAL::AttributeFunctor}\\
\ccRefConceptPage{CombinatorialMap}\\
\ccRefConceptPage{CombinatorialMapItems}

\end{ccRefConcept}
% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+
