% +------------------------------------------------------------------------+
% | Reference manual page: Dart.tex
% +------------------------------------------------------------------------+
% | 04.02.2010   Guillaume Damiand
% | Package: Combinatorial_map
% +------------------------------------------------------------------------+
\ccRefPageBegin
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+
\begin{ccRefConcept}{Dart}
%\ccRefLabel{CGAL::Dart}

\ccDefinition
  
The concept \ccRefName\ defines a \emph{d}-dimensional dart.  A dart mainly
stores handles to the darts linked with itself by \betai{}, \myforall{}\emph{i}, 
0\myleq{}\emph{i}\myleq{}\emph{d}. Moreover, it stores also handles to each
non void attribute associated with itself.

% \ccParameters
% \ccc{d} is the dimension of the combinatorial map.\\
% \ccc{CMap} must be a model of the \ccc{CombinatorialMap} concept.

\ccCreation 
\ccCreationVariable{d0} 
A dart \ccc{d0} is never constructed directly, but always created
within a combinatorial map \ccc{cm} by using the method
\ccc{cm.create_dart();} A new dart is initialized to be \emph{i}-free,
\myforall{}\emph{i}: 0\myleq{}\emph{i}\myleq{}\emph{dimension}, and having all 
its attribute handles initialized to NULL, for each non void attribute.

\ccConstants
\ccVariable{static unsigned int dimension;}{The dimension of \ccc{d0}.}

\ccTypes
\ccTwo{Dart:: Dart_const_handle_}{}{}
%
\ccNestedType{Dart_handle}{Dart handle type.}
\ccGlue
\ccNestedType{Dart_const_handle}{Dart const handle type.}

\ccNestedType{template<unsigned int i> Attribute_handle<i>::type}
    {Handle to \emph{i}-attributes, with 0\myleq{}\emph{i}\myleq{}\emph{dimension}.}
\ccGlue
\ccNestedType{template<unsigned int i> Attribute_const_handle<i>::type}
    {Const handle to \emph{i}-attributes, with 0\myleq{}\emph{i}\myleq{}\emph{dimension}.}

\ccHeading{Access Member Functions}
\ccThree{Dart_const_handle}{beta(unsigned int i) const}{}
%
\ccMethod{Dart_handle beta(unsigned int i);}
         {Returns \betai{}(\ccc{d0}).
          \ccPrecond{0\myleq{}\emph{i}\myleq{}\emph{dimension}.}}
\ccGlue
\ccMethod{Dart_const_handle beta(unsigned int i) const;}
         {Returns \betai{}(\ccc{d0}) when \ccc{d0} is const.
          \ccPrecond{0\myleq{}\emph{i}\myleq{}\emph{dimension}.}}

\ccMethod{Dart_handle beta_inv(unsigned int i);}
         {Returns \betaiinv{}(\ccc{d0}).
          \ccPrecond{0\myleq{}\emph{i}\myleq{}\emph{dimension}.}}
\ccGlue
\ccMethod{Dart_const_handle beta_inv(unsigned int i) const;}
         {Returns \betaiinv{}(\ccc{d0}) when \ccc{d0} is const.
          \ccPrecond{0\myleq{}\emph{i}\myleq{}\emph{dimension}.}}

\ccMethod{bool is_free(unsigned int i) const;} 
         {Returns true iff \ccc{d0} is \emph{i}-free.
          \ccPrecond{0\myleq{}\emph{i}\myleq{}\emph{dimension}.}}

\ccMethod{int highest_nonfree_dimension() const;} 
         {Returns the highest dimension \emph{i} such that \ccc{d0} is not \emph{i}-free.
          -1 if \ccc{d0} is free for any dimension.}

\ccMethod{Dart_handle opposite();}
         {Returns a handle to a dart belonging to the same edge 
          than \ccc{d0}, and not to the same vertex.
          NULL if such a dart does not exist.}
\ccGlue
\ccMethod{Dart_const_handle opposite() const;}
         {Returns a handle to a dart belonging to the same edge 
          than \ccc{d0}, and not to the same vertex, when \ccc{d0} is const.
          NULL if such a dart does not exist.}

\ccMethod{Dart_handle other_extremity();}
         {Returns a handle to a dart belonging to the other vertex of
          the edge containing \ccc{d0} (but contrary to \ccc{opposite()} not 
          necessarily to the same edge). NULL if such a dart does not exist.}
\ccGlue
\ccMethod{Dart_const_handle other_extremity() const;}
         {Returns a \ccc{Dart_const_handle} to a dart belonging to the other vertex of
          the edge containing \ccc{d0}, when \ccc{d0} is const (but contrary to
          \ccc{opposite()} not necessarily to the same edge). 
          NULL if such a dart does not exist.}

\ccMethod{template <unsigned int i> Attribute_handle<i>::type attribute();}
         {Returns the \emph{i}-attribute associated to \ccc{d0}.
           \ccPrecond{0\myleq{}\emph{i}\myleq{}\emph{dimension}, and \emph{i}-attributes are non void.}}
\ccGlue
\ccMethod{template <unsigned int i> 
          Attribute_const_handle<i>::type attribute() const;}
         {Returns the \emph{i}-attribute associated to \ccc{d0},
           when  \ccc{d0} is const.
           \ccPrecond{0\myleq{}\emph{i}\myleq{}\emph{dimension}, and \emph{i}-attributes are non void.}}

\ccHasModels
\ccRefIdfierPage{CGAL::Dart<d,CMap>}

\end{ccRefConcept}
% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+
