\section{Todo}

\subsection{General thoughts}

\begin{itemize}

\item The name NotifyingTable is not very good. One possibility is
ActiveObjectTable.

\item The other trajectory modification events need to be documented
(Set\_moving\_point)

\item There is no 2d regular triangulation. This is not too much work,
but a bit (since I will need to refactor my 2d delaunay)

\item the FunctionKernel is not documented much (the options are never
explained)

\item The is some confusion about where a KDS should get a
FunctionKernel. Currently they mostly get them from the Simulator
(which directly provides the RootStack). I am not sure that this is
the right solution. The better solution may just be to have the
FunctionKernel (and RootStack) be fetched from the SimulationTraits.

\item I use TNT which is currently put in a include/TNT (parallel to
include/CGAL). Exposing it like this is a bit problematic. I could
modify the headers to nest TNT in the CGAL namespace and hide it in
include/CGAL.

\item The FunctionKernel numeric solver I implemented is not as good
as the one provided by GSL which is shipped on most linux boxes. It is
GPL, so the user does have to make a decision about using it. One
option would be to have a set of headers GSL\_numeric\_solver,
GSL\_inexact\_simulation\_traits, etc. which the user could choose to use
and to pull all the GSL stuff into the headers. I don't think we can
keep it in the library and still have the dynamic libraries link.

\item The 3d visualizion uses Coin. It is currently all in headers so
there is really no problem with the user only using it if they have
coin. It is pretty simple to port it to any other 3d viewer if CGAL
picks one.

\item The whole SimulationTraits is a bit funny since it allows you to
a) fetch a bunch of kernels and b) fetch pointers to the
movingpointtable and simulator. I don't see an obvious way to keep its
simplicity and have it make more sense.

\item the bib entries has not been added yet

\item the Qt stuff is broken since no one has figured out how to add
my files to CGALQt (or has told me how)


\end{itemize}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
