
\subsection{Implementing a Trivial Kinetic Data Structure}
\label{sec:trivial_kds_example}

 This kinetic data structure maintains one event in the queue which
has a list of the coordinates of all the known moving objects.  Two
classes are defined, the \ccc{Trivial_event}, and the
\ccc{Trivial_kds}. The event classes must be declared outside of the
kinetic data structure so that the \ccc{operator<<} can be defined for
them. 

The kinetic data structure maintains one event containing a list of
the trajectories of all objects in the the simulation. This
event must updated whenever any objects change, in addition, it is
always created to fail one time unit in the future, so it must be
recreated when it fails. As a result, the kinetic data structure has
the main parts of a real one--it responds to changes in trajectories
of the objects and certificate failures (when the event expires).

 The public methods can be grouped into three sets which are shared
 with almost all other kinetic data structures:
\begin{itemize}
\item \ccc{has_certificates} and \ccc{set_has_certificates} which
  checks/sets whether the kinetic data structure is currently
  maintaining certificates.
\item \ccc{insert}, \ccc{set}, \ccc{erase} which are called by the
  \ccc{CGAL::KDS::Notifying_table_listener_helper} in response to the
  addition, modification, or deletion of an object to, in or from the
  simulation.
\item \ccc{audit} which is called periodically by the
  \ccc{CGAL::KDS::Simulator_kds_listener} when kinetic data structures can
  easily audit themselves.
\end{itemize} 

In addition, it has one method which is called when a certificate
fails. The name/existence of such methods depend on the nature of the
kinetic data structure in question.

Like many kinetic data structures, it takes a \ccc{SimulationTraits}
as a template argument. This traits class defines the types needed for
the simulation and is responsible for instantiating them.

 \label{fig:trivial_usage_program}
\ccIncludeExampleCode{Kinetic_data_structures/trivial_kds.cc}
%../../examples/Kinetic_data_structures/ % LocalWords: CGAL
