% +------------------------------------------------------------------------+
% | Reference manual page: Triangulation_data_structure_3.tex
% +------------------------------------------------------------------------+
% | 29.3.2000   Monique Teillaud
% | Package: Triangulation3
% | 
\RCSdef{\RCSTriangulationdatastructureRev}{$Id$}
\RCSdefDate{\RCSTriangulationdatastructureDate}{$Date$}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefClass}{Triangulation_data_structure_3<TriangulationDSVertexBase_3,TriangulationDSCellBase_3>}

\ccDefinition
The class \ccc{Triangulation_data_structure_3} stores a 3D-triangulation data
structure and provides the optional
geometric functionalities to be used as a parameter for a 
3D-geometric triangulation (see Chapter~\ref{chapter-Triangulation3}). 

The vertices and cells are stored in two nested containers, which are
implemented using \ccc{CGAL::Compact_container}.  The class may offer some
flexibility for the choice of container in the future, in the form of
additional template parameters.

\ccInclude{CGAL/Triangulation_data_structure_3.h}

\ccParameters
It is parameterized by base classes for vertices and cells which have to match
the requirements for the concepts \ccc{TriangulationDSCellBase_3} and
\ccc{TriangulationDSVertexBase_3} respectively
\lcTex{(see \ccRefPage{TriangulationDSCellBase_3} 
and \ccRefPage{TriangulationDSVertexBase_3})}.

They have the default values \ccc{Triangulation_ds_vertex_base_3<>} and
\ccc{Triangulation_ds_cell_base_3<>} respectively.

\ccIsModel \ccc{TriangulationDataStructure_3}

\ccInheritsFrom{\ccc{CGAL::Triangulation_utils_3}}

The class \ccc{Triangulation_utils_3} defines basic computations on
indices of vertices and neighbors of cells. 

\begin{ccAdvanced}

\ccCreationVariable{tds}

In addition to the interface documented in the concept, the class offers the
following types and functions.

\ccTypes

\ccTypedef{typedef CGAL::Compact_container<Vertex> Vertex_range;}{Vertex container type.}
\ccGlue
\ccTypedef{typedef CGAL::Compact_container<Cell>   Cell_range;}{Cell container type.}

\ccOperations

\ccMethod{Cell_range & cells() const;}
{Returns a reference to the container of cells.}
\ccGlue
\ccMethod{Cell_range & cells();}
{Returns a reference to the container of cells.}
\ccGlue
\ccMethod{Vertex_range & vertices() const;}
{Returns a reference to the container of vertices.}
\ccGlue
\ccMethod{Vertex_range & vertices();}
{Returns a reference to the container of vertices.}

\end{ccAdvanced}

\ccSeeAlso

\ccc{CGAL::Triangulation_ds_vertex_base_3}\\
\ccc{CGAL::Triangulation_ds_cell_base_3}\\
\ccc{CGAL::Triangulation_vertex_base_with_info_3}\\
\ccc{CGAL::Triangulation_cell_base_with_info_3}

\end{ccRefClass}
