% =============================================================================
% The CGAL Developers' Manual
% Chapter: Submitting Packages
% -----------------------------------------------------------------------------
% file   : submission_process.tex
% authors: Geert-Jan Giezeman <geert@cs.uu.nl> & Susan Hert <hert@mpi-sb.mpg.de>
% -----------------------------------------------------------------------------
% $Id$
% $Date$
% =============================================================================

\InternalOnly{
\chapter{Submitting Packages\label{chap:submission}}
\ccChapterRelease{Chapter Version: 1.0}
\ccChapterAuthor{Geert-Jan Giezeman ({\tt geert@cs.uu.nl})\\
Susan Hert ({\tt hert@mpi-sb.mpg.de})}

\section{Editorial committee\label{sec:editorial_board}}
}

\ExternalOnly{
\chapter{Editorial Committee}
}
\ccIndexMainItemBegin{editorial committee}


The editorial committee is in charge of approving the inclusion of new packages
in the library.  This means that they assure that new contributions
\begin{itemize}
   \item are in keeping with the philosophy of \cgal\ (Chapter~\ref{chap:intro});
   \item are generic and fit seamlessly with other parts of the library;
   \item satisfy the coding conventions of \cgal\ (Chapter~\ref{chap:code_format});
   \item carefully and efficiently treat robustness issues
         (Chapter~\ref{chap:robustness});
   \item are designed in a flexible, extensible, and easy-to-use fashion;
   \item and are designed to be technically feasible for the platforms
         supported by \cgal.
\end{itemize}

Software specifications and implementations should be submitted to the
editorial committee for approval.  This can be done by sending mail to
the \ccAnchor{mailto:cgal-editorial-board@lists-sop.inria.fr}{committee}
\lcTex{(\texttt{cgal-editorial-board@lists-sop.inria.fr})} indicating
where the (PDF) documentation and code can be found.  After
some reasonable amount of time, you should receive feedback from
the committee about the specification and what, if anything, needs to
be changed. The usual procedure is that someone from the committee is
assigned to be (or volunteers to be) the primary reviewer and sends
comments on the submitted package to the committee and to the authors of
the package.  Discussion then proceeds among the committee members and the
authors until a consensus is reached about how the package should be
modified before being accepted.  When the package has been modified,
the authors should again notify the editorial committee to let them
know what has changed so a decision about acceptance of the package
can be taken.

One should write a specification for a new package
\InternalOnly{(Chapter~\ref{chap:specification})}
and submit it to the editorial committee for
approval before submitting the package for inclusion in the internal
releases (and ideally before implementation of the package).  This
ensures that time is not wasted in fixing code that may later be changed
due to the recommendations of the committee.
However, since it can take some time for the committee to process
submissions, packages that are to become part of the library
can be submitted
\InternalOnly{as detailed in
Section~\ref{sec:electronic_submission}} before approval.
Inclusion in an internal release does not ensure inclusion in a public
release.  Only after approval by the committee will packages be included in new
public releases and then only if they pass the test suite, of course.

The current list of members of the editorial committee can be found on the web site.

\InternalOnly{
\section{Electronic submission\label{sec:electronic_submission}}
\ccIndexMainItemBegin{submitting}

Whether you produce library code, demos, documentation or something else,
if you want it to become part of \cgal, you'll have to submit it in the form
of a package which has to be a folder under SVN trunk.
The directory structure required for a package is described in
Chapter~\ref{chap:directory_structure}.

Here we focus on how to submit a package.

\ccIndexSubitem{naming scheme}{package}
A package has a name, which identifies it.  This name should obey the same
rules as for C identifiers: it consists of letters, digits and underscores and
it does not start with a digit.  Choose a name that is descriptive, yet not
too long (under 25 characters).  If a package deals with objects of a
particular dimension, then use the suffixes \_2, \_3, and \_d, especially if
there exists (or may exist in the future) a package with similar
functionality in different dimensions.  Examples of good package names are
\texttt{Triangulation\_2} for a package dealing with triangulations of points
in the plane and \texttt{Min\_ellipse\_2}, which contains an algorithm that
finds the minimal enclosing ellipse of a set of points in the plane. The
package names \texttt{pm} and \texttt{arr} are a bit too terse.
\texttt{Planar\_map} and \texttt{Arrangement} (or
\texttt{Arrangement\_2}) are better.

Make sure your package does not have any file clashing with any other packages.
Please also make sure the information such as the maintainer email adress is
up to date under the \texttt{package\_info} directory.
\ccIndexSubitem{submitting}{file for}

\ccIndexMainItemEnd{submitting}


\section{Requirements and recommendations\label{sec:submission_req_and_rec}}

\noindent
Requirements:
\begin{itemize}
   \item Submit specifications to the editorial committee before submitting
         packages for internal releases.
   \item Obey the directory structure outlined in Chapter~\ref{chap:directory_structure}.
\end{itemize}

\noindent
Recommendations:
\begin{itemize}
    \item Wait for approval from the editorial committee before submitting packages
          for internal releases.
\end{itemize}
}
