%% Copyright (c) 2004  SciSoft.  All rights reserved.
%%
%% This file is part of CGAL (www.cgal.org); you may redistribute it under
%% the terms of the Q Public License version 1.0.
%% See the file LICENSE.QPL distributed with CGAL.
%%
%% Licensees holding a valid commercial license may use this file in
%% accordance with the commercial license agreement provided with the software.
%%
%% This file is provided AS IS with NO WARRANTY OF ANY KIND, INCLUDING THE
%% WARRANTY OF DESIGN, MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE.
%%
%% $Name$
%%
%% Author(s)     : Fernando Cacciola <fernando_cacciola@hotmail.com>

\chapter{2D Straight Skeleton}
\label{ref-chapter-straightskeleton2}

\ccHeading{Definition}

The straight skeleton of a polygon is a partitioning of the polygon interior into faces corresponding to the monotone areas traced by a continuous offsetting of the polygon's edges.
These faces are bounded by angular bisectors of the lines supporting the polygon edges; they are non-convex straight-line polygons themselves.

The concept \ccc{StraightSkeleton_2} is a refinement of the \ccc{HalfedfeDS} concept.
Halfedges represent both polygon edges (borders) and bisectors, while Vertices represent both polygon vertices and skeleton nodes.

\cgal\ provides the class \ccc{CGAL::Straight_skeleton_builder_2<Gt,Ssds>} for
computing the 2D straight skeleton of a simple polygon.
The two template parameters must be models of the \ccc{StraightSkeletonBuilderTraits_2} and \ccc{StraightSkeleton_2} concepts.\\
The first concept is related to the geometric objects and predicates associated with
the straight skeleton construction process. The class \ccc{Straight_skeleton_builder_traits_2<K,Ssds>} is a model of this concept.\\
The second concept refers to the data structure used to represent the straight skeleton.
Any instance of the class \ccc{CGAL_HALFEDGEDS_DEFAULT} with items modeling the right concepts: \ccc{StraightSkeletonVertex_2} and \ccc{StraightSkeletonHalfedge_2}, is a model of this concept (i.e. there is no explicit class for the \ccc{StraightSkeleton_2} concept).

\ccHeading{Concepts}
\ccRefConceptPage{StraightSkeleton_2} \\
\ccRefConceptPage{StraightSkeletonVertex_2} \\
\ccRefConceptPage{StraightSkeletonHalfedge_2} \\
\ccRefConceptPage{StraightSkeletonBuilderTraits_2} \\

\ccHeading{Classes}
\ccRefIdfierPage{CGAL::Straight_skeleton_vertex_base_2<Refs,Point,RT>}\\
\ccRefIdfierPage{CGAL::Straight_skeleton_halfedge_base_2<Refs,Segment>}\\
\ccRefIdfierPage{CGAL::Straight_skeleton_builder_traits_2<Kernel,Ssds>}\\
\ccRefIdfierPage{CGAL::Straight_skeleton_builder<Gt,Ssds>}\\

\lcHtml{\ccHeading{Links to the Reference Sections}}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+
