% +------------------------------------------------------------------------+
% | Reference manual page: Map_overlay_DCEL_vertex.tex (Map_overlay)
% +------------------------------------------------------------------------+
% | 
% | Package: ovl (Map_overlay_2)
% | 
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+

\begin{ccRefConcept}{MapOverlayDcelVertex_2}
\ccRefLabel{Ovl_Dcel_Vertex}
%\ccDefinition{A vertex $v$ 
%stores %a point and 
%   a reference to an incident 
%   halfedge that has $v$ as its %source.}
%   target.}

  \ccCreationVariable{v}

The \ccRefName\ concpet is a refinement of the \ccc{PlanarMapDcelVertex_2} concept. 
The requirements of the latter are the requirements of the former.
In addition the \ccRefName\ should contain the following methods.

  \ccOperations
  \ccMethod{void set_first_vertex_above(const void* v);}
  {set $v$ to be the pointer to the vertex of the first creator laying above the current vertex of the overlay.}
  
  \ccMethod{void set_second_vertex_above(const void* v);}
  {set $v$ to be the pointer to the vertex of the second creator laying above the current vertex of the overlay.}
  
  \ccMethod{void set_first_halfedge_above(const void* h);}
  {set $h$ to be the pointer to the halfedge of the first creator laying above the current vertex of the overlay.}

  \ccMethod{void set_second_halfedge_above(const void* h);}
  {set $h$ to be the pointer to the halfedge of the second creator laying above the current vertex of the overlay.}

  \ccMethod{void set_first_face_above(const void* f);}
  {set $f$ to be the pointer to the face of the first creator laying above the current vertex of the overlay.}
  
  \ccMethod{void set_second_face_above(const void* f);}
  {set $f$ to be the pointer to the face of the second creator laying above the current vertex of the overlay.}
  
  \ccMethod{const void* get_first_vertex_above();}
  {return the vertex pointer of the first creator laying above the current vertex of the overlay.}
  
  \ccMethod{const void* get_second_vertex_above();}
  {return the vertex pointer of the second creator laying above the current vertex of the overlay.}
  
  \ccMethod{const void* get_first_halfedge_above();}
  {return the halfedge pointer of the first creator laying above the current vertex of the overlay.}

  \ccMethod{const void* get_second_halfedge_above();}
  {return the halfedge pointer of the second creator laying above the current vertex of the overlay.}

  \ccMethod{const void* get_first_face_above();}
  {return the face pointer of the first creator laying above the current vertex of the overlay.}

  \ccMethod{const void* get_second_face_above();}
  {return the face pointer of the second creator laying above the current vertex of the overlay.}
  
\end{ccRefConcept} % MapOverlayDcelVertex_2

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+
