% +------------------------------------------------------------------------+
% | Reference manual page: Ovl_dcel.tex (Map_overlay)
% +------------------------------------------------------------------------+
% | 
% | Package: ovl (Map_Overlay_2)
% | 
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+

\begin{ccRefClass}{Ovl_dcel<Traits,V,H,F>}

\ccDefinition

    The \ccClassTemplateName\ is a model of the Dcel concept
    defined above. Its template parameters are the vertex, halfedge and face
    classes which conform to the requirements given above.

\ccInclude{CGAL/Map_overlay_default_dcel.h}

\ccIsModel
    \ccc{MapOverlayDcel_2}

\ccHeading{Models for Dcel Vertex, Halfedge and Face}
The \ccStyle{Vertex_overlay<Vertex_base>} is a model for the 
Dcel vertex concept defined above. 
The \ccStyle{Halfedge_overlay<Halfedge_base>} is a
model for the Dcel halfedge concept defined above.
The \ccStyle{Face_overlay<Face_base>} is a
model for the Dcel face concept defined above. 

\ccHeading{Requirements}
\ccc{Vertex_base} is a model for the \ccc{PlanarMapDcelVertex_2} concept.
\ccc{Halfedge_base} is a model for the \ccc{PlanarMapDcelHalfedge_2} concept.
\ccc{Face_base} is a model for the \ccc{PlanarMapDcelFace_2} concept.


\ccInclude{CGAL/Map_overlay_default_dcel.h}

\ccHeading{The Default Dcel Structure}
The \ccStyle{Map_overlay_default_dcel<Traits,Vertex_base=Pm_vertex_base<Traits::Point>,
   Halfedge_base=Pm_halfedge_base<Traits::X_curve>,
   Face_base=Pm_face_base>} 
is a model of the Dcel concept
defined above. Its template parameters are the traits class defined below, 
and the basic vertex, halfedge and face the overlay components inherit.
The default template parameters for the three basic components are the 
\ccc{Planar_map} basic components.
The overlay default DCEL is a wrapper for \ccStyle{Pm_dcel} instantiated 
with \ccStyle{Vertex_overlay<Vertex_base>},
\ccStyle{Halfedge_overlay<Halfedge_base>} and 
\ccStyle{Face_overlay<Fase_base>}.

\ccInclude{CGAL/Map_overlay_default_dcel.h}

\end{ccRefClass}
% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+
