\begin{ccRefConcept}{Kernel}
The concept of a {\em kernel} is defined by a set of requirements on
the provision of certain types.  The types are function object classes to be
used within the algorithms and data structures of \cgal.

A kernel provides types, construction objects, and generalized predicates.
The former replace constructors of the kernel classes and constructive
procedures in the kernel. There are also function objects replacing operators,
especially for equality testing.

Types and functors are identified by tags, which may be any type (like \ccc{CGAL::Segment_tag}). As a special case, the construction functor of a type identified by \ccc{Some_tag} is identified by the tag \ccc{Construct_ttag<Some_tag>}, and the conversion functor by \ccc{Convert_ttag<Some_tag>}.

Depending on \ccc{Default_ambient_dimension}, a kernel has 2 constructors, a default constructor and a constructor that takes as argument an \ccc{int} for the dimension.

\ccTypes

\ccNestedType{Default_ambient_dimension}{\ccc{Dimension_tag<d>} where \ccc{d} is the ambient dimension or \ccc{Dynamic_dimension_tag} if the dimension is unknown.}
\ccGlue
\ccNestedType{Max_ambient_dimension}{\ccc{Dimension_tag<d>} where \ccc{d} is an upper bound on the ambient dimension or \ccc{Dynamic_dimension_tag}.}

% Replace with Type<FT_tag>::type?
\ccNestedType{FT}{a model of \ccc{FieldNumberType}}
\ccGlue
\ccNestedType{RT}{a model of \ccc{RingNumberType}}

% Not documented in the first version
\ccNestedType{LA}{a model of \ccc{LinearAlgebraSomething} using \ccc{RT}}

The following types describe the return types of predicates.  They typically
map to \ccc{bool} and \cgal\ kernel enum types, except when an interval arithmetic
number type is used such as within the filtering kernels, in which case it is
\ccc{Uncertain<bool>} or similar.

\ccNestedType{Boolean}{\ccc{bool} or \ccc{Uncertain<bool>}}
\ccGlue
\ccNestedType{Sign}{\ccc{CGAL::Sign} or \ccc{Uncertain<CGAL::Sign>}}
\ccGlue
\ccNestedType{Comparison_result}{\ccc{CGAL::Comparison_result} or \ccc{Uncertain<CGAL::Comparison_result>}}
\ccGlue
\ccNestedType{Orientation}{\ccc{CGAL::Orientation} or \ccc{Uncertain<CGAL::Orientation>}}
\ccGlue
\ccNestedType{Oriented_side}{\ccc{CGAL::Oriented_side} or \ccc{Uncertain<CGAL::Oriented_side>}}
\ccGlue
\ccNestedType{Bounded_side}{\ccc{CGAL::Bounded_side} or \ccc{Uncertain<CGAL::Bounded_side>}}
\ccGlue
\ccNestedType{Angle}{\ccc{CGAL::Angle} or \ccc{Uncertain<CGAL::Angle>}}

\ccNestedType{template <class Tag> struct Type<Tag>}{This nested template class defines an object type \ccc{type}. For instance, \ccc{Type<Point_tag>::type} is the type of points.}

\ccNestedType{template <class Tag, class Option> struct Functor<Tag,Option=Default>}{This nested template class defines a functor type \ccc{type}. For instance, \ccc{Functor<Orientation_tag>::type} is the orientation predicate. Functors that are not provided should all be \ccc{Null_functor}.}

\ccNestedType{Object_list}{A typedef for \ccc{typeset<Point_tag,...>} with the list of tags that can be passed to the \ccc{Type} template.}

\end{ccRefConcept}

