%% Copyright (c) 2003,2004  INRIA Sophia-Antipolis (France) and
%% Notre Dame University (U.S.A.).  All rights reserved.
%%
%% This file is part of CGAL (www.cgal.org); you may redistribute it under
%% the terms of the Q Public License version 1.0.
%% See the file LICENSE.QPL distributed with CGAL.
%%
%% Licensees holding a valid commercial license may use this file in
%% accordance with the commercial license agreement provided with the software.
%%
%% This file is provided AS IS with NO WARRANTY OF ANY KIND, INCLUDING THE
%% WARRANTY OF DESIGN, MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE.
%%
%% $Source$
%% $Revision$ $Date$
%% $Name$
%%
%% Author(s)     : Menelaos Karavelas <mkaravel@cse.nd.edu>



\begin{ccRefConcept}{SegmentVoronoiDiagramVertexBase_2}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries
\ccCreationVariable{vb}
\ccDefinition

The concept \ccc{SegmentVoronoiDiagramVertexBase_2} describes the
requirements for the vertex base class of the
\ccc{SegmentVoronoiDiagramDataStructure_2} concept. A vertex stores a
site of the segment Voronoi diagram and provides access to one of its
incident faces through a \ccc{Face_handle}.

\ccRefines
\ccc{DefaultConstructible}\\
\ccc{CopyConstructible}\\
\ccc{Assignable}

\ccTypes
%\ccTwo{SegmentVoronoiDiagramVertexBase_2::Point_container+}{}
\ccThree{typedef typename Point_container::iterator+}{Point_handle+}{}
\ccThreeToTwo
\ccNestedType{Geom_traits}{A type for the geometric traits that defines
the site. \ccPrecond{The type \ccc{Geom_traits} must
define the type \ccc{Site_2}.}}
%
%\ccGlue
%\ccNestedType{Point_container}{A type for a container of points.}
%  \ccPrecond{This type must satisfy the requirements of the concept
%   \ccc{SimpleContainer}.}}
%
%\ccGlue
%\ccTypedef{typedef typename Point_container::iterator Point_handle;}
%{A handle type for the points in the point container.}
%
\ccGlue
\ccNestedType{Site_2}{A type for the site. This type must coincide
  with the type \ccc{Geom_traits::Site_2}.}
%
\ccGlue
\ccNestedType{Storage_site_tag}{A type that indicates what kind of
  storage type to use. \ccc{Storage_site_tag} must either be
    \ccc{CGAL::Tag_true} or \ccc{CGAL::Tag_false}.}
%
\ccGlue
\ccNestedType{Storage_site_2}{A type for the internal representation
  of sites. This type must satisfy the requirements of the concept
\ccc{SegmentVoronoiDiagramStorageSite_2}.}
%
\ccGlue
\ccNestedType{Segment_Voronoi_diagram_data_structure_2}{A type for the
  segment Voronoi diagram data structure, to which the vertex belongs to.}
%
\ccGlue
\ccNestedType{Vertex_handle}{A type for the vertex handle of the
  segment Voronoi diagram data structure.}
%
\ccGlue
\ccNestedType{Face_handle}{A type for the face handle of the
  segment Voronoi diagram data structure.}
%

\ccCreation
\ccCreationVariable{v}  %% choose variable name

\ccTwo{SegmentVoronoiDiagramVertexBase_2 v(Storage_site_2 ss);++}{}
%
%\ccConstructor{SegmentVoronoiDiagramVertexBase_2();}{Default constructor.}
%\ccGlue

In addition to the default and copy constructors and following
constructors are required:

\ccConstructor{SegmentVoronoiDiagramVertexBase_2(Storage_site_2 ss);}
{Constructs a vertex associated with the site represented by the
  storage site \ccc{ss}.}
\ccGlue
\ccConstructor{SegmentVoronoiDiagramVertexBase_2(Storage_site_2 ss,
  Face_handle f);}{Constructs a vertex associated with
  the site represented by the storage site \ccc{ss},
  and pointing to the face associated with the face handle \ccc{f}.}





\ccAccessFunctions
\ccThree{Storage_site_2}{v.storage_site()+}{}
%
\ccMethod{Storage_site_2 storage_site();}
{Returns  the storage site representing the site.}
\ccGlue
\ccMethod{Site_2 site();}
{Returns  the site.}
\ccGlue
\ccMethod{Face_handle face();}{Returns a handle to an incident face.}



\ccHeading{Setting}
\ccThree{void}{v.set_site(Storage_site_2 ss)+}{}
\ccMethod{void set_site(Storage_site_2 ss);}
{Sets the storage site.}
\ccGlue
\ccMethod{void set_face(Face_handle f);}{Sets the incident face.}

\ccThree{bool}{v.is_valid(bool verbose, int level)+}{}
\ccHeading{Checking}
\ccMethod{bool is_valid(bool verbose, int level) const;}
{Performs any required tests on a vertex.}


\ccHasModels

\ccc{CGAL::Segment_Voronoi_diagram_vertex_base_2<Gt>}.


\ccSeeAlso

\ccc{SegmentVoronoiDiagramDataStructure_2}\\
\ccc{SegmentVoronoiDiagramTraits_2}\\
\ccc{SegmentVoronoiDiagramSite_2}\\
\ccc{SegmentVoronoiDiagramStorageSite_2}\\
\ccc{CGAL::Segment_Voronoi_diagram_vertex_base_2<Gt>}\\
\ccc{CGAL::Segment_Voronoi_diagram_site_2<K>}\\
\ccc{CGAL::Segment_Voronoi_diagram_storage_site_2<Gt,SSTag>}\\
\ccc{CGAL::Segment_Voronoi_diagram_data_structure_2<Vb,Fb>}

\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+
