%% Copyright (c) 2003,2004  INRIA Sophia-Antipolis (France) and
%% Notre Dame University (U.S.A.).  All rights reserved.
%%
%% This file is part of CGAL (www.cgal.org); you may redistribute it under
%% the terms of the Q Public License version 1.0.
%% See the file LICENSE.QPL distributed with CGAL.
%%
%% Licensees holding a valid commercial license may use this file in
%% accordance with the commercial license agreement provided with the software.
%%
%% This file is provided AS IS with NO WARRANTY OF ANY KIND, INCLUDING THE
%% WARRANTY OF DESIGN, MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE.
%%
%% $Source$
%% $Revision$ $Date$
%% $Name$
%%
%% Author(s)     : Menelaos Karavelas <mkaravel@cse.nd.edu>


\begin{ccRefConcept}{SegmentVoronoiDiagramHierarchyVertexBase_2}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries
\ccCreationVariable{hvb}


\ccDefinition 
The vertex of a segment Voronoi diagram
included in a segment Voronoi diagram hierarchy has to provide
some pointers to the corresponding vertices in the
graphs of the next and preceeding levels.
Therefore, the concept \ccc{SegmentVoronoiDiagramHierarchyVertexBase_2}
refines the concept \ccc{SegmentVoronoiDiagramVertexBase_2}, by
adding two vertex handles to the correponding vertices for the
next and previous level graphs.


\ccRefines
\ccc{SegmentVoronoiDiagramVertexBase_2}


\ccTypes
\ccc{SegmentVoronoiDiagramHierarchyVertexBase_2} does not introduce
any types in addition to those of
\ccc{SegmentVoronoiDiagramVertexBase_2}.


\ccCreation
\ccCreationVariable{v}  %% choose variable name
\ccTwo{SegmentVoronoiDiagramHierarchyVertexBase_2 v;+++}{}
%

The \ccc{SegmentVoronoiDiagramHierarchyVertexBase_2} concept does not
introduce any constructors in addition to those of the
\ccc{SegmentVoronoiDiagramVertexBase_2} concept.

%% In addition to the default and copy constructors the following
%% constructors must be defined.

%% \ccConstructor{ApolloniusGraphHierarchyVertexBase_2(Storage_site_2 ss);}
%% {Constructs a vertex associated with the site represented by the
%%   storage site \ccc{ss}.}
%% %
%% \ccGlue
%% \ccConstructor
%% {segmentVoronoiDiagramHierarchyVertexBase_2(Storage_site_2 s,
%%   Face_handle f);}
%% {Constructs a vertex associated with
%% the site represented by the storage site \ccc{ss} and pointing to the
%% face associated with the face handle \ccc{f}.}


\ccOperations
\ccThree{Vertex_handle}{v.set_down(Vertex_handle d)+}{}
%
\ccMethod{Vertex_handle up();}{Returns a handle to the corresponding
  vertex of the next level segment Voronoi diagram. If such a vertex
  does not exist \ccc{Vertex_handle()} is returned.}
%
\ccGlue
\ccMethod{Vertex_handle down();}{Returns a handle to the corresponding
  vertex of the previous level segment Voronoi diagram. If such a
  vertex does not exist \ccc{Vertex_handle()} is returned.}
%
\ccGlue
\ccMethod{void set_up(Vertex_handle u);}{Sets the handle for the
  vertex of the next level segment Voronoi diagram.} 
%
\ccGlue 
\ccMethod{void set_down(Vertex_handle d);}{Sets the handle for the
  vertex of the previous level segment Voronoi diagram;}




\ccHasModels

\ccc{CGAL::Segment_Voronoi_diagram_hierarchy_vertex_base_2<CGAL::Segment_Voronoi_diagram_vertex_base_2<Gt,SSTag> >}


\ccSeeAlso

\ccc{SegmentVoronoiDiagramDataStructure_2} \\
\ccc{SegmentVoronoiDiagramVertexBase_2}\\
\ccc{CGAL::Segment_Voronoi_diagram_hierarchy_2<Gt,DS>}\\
\ccc{CGAL::Segment_Voronoi_diagram_data_structure_2<Vb,Fb>}\\
\ccc{CGAL::Segment_Voronoi_diagram_vertex_base_2<Gt,SSTag>}\\
\ccc{CGAL::Segment_Voronoi_diagram_hierarchy_vertex_base_2<Vbb>}

\end{ccRefConcept}


% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+
