%% Copyright (c) 2003,2004  INRIA Sophia-Antipolis (France) and
%% Notre Dame University (U.S.A.).  All rights reserved.
%%
%% This file is part of CGAL (www.cgal.org); you may redistribute it under
%% the terms of the Q Public License version 1.0.
%% See the file LICENSE.QPL distributed with CGAL.
%%
%% Licensees holding a valid commercial license may use this file in
%% accordance with the commercial license agreement provided with the software.
%%
%% This file is provided AS IS with NO WARRANTY OF ANY KIND, INCLUDING THE
%% WARRANTY OF DESIGN, MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE.
%%
%% $Source$
%% $Revision$ $Date$
%% $Name$
%%
%% Author(s)     : Menelaos Karavelas <mkaravel@cse.nd.edu>



\begin{ccRefConcept}{SegmentVoronoiDiagramStorageSite_2} 
%% add template arg's if necessary

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[class]{} %% add further index entries

\ccDefinition
  
The concept \ccc{SegmentVoronoiDiagramStorageSite_2} provides the
requirements for the storage sites of a segment Voronoi diagram. The
storage sites are sites that are used to store the information of a
site in a more compact form (that uses less storage). This is achieved
by storing handles to points instead of points.


\ccTwo{SegmentVoronoiDiagramStorageSite_2::Point_handle+}{}
\ccTypes
\ccNestedType{Site_2}{The site type.}
\ccGlue
\ccNestedType{Point_handle;}{The type for a handle to a point.}



\ccCreation
\ccTwo{SegmentVoronoiDiagramStorageSite_2 ss()+}{}


\ccCreationVariable{ss}  %% choose variable name
\ccConstructor{SegmentVoronoiDiagramStorageSite2 ss()}{Default constructor}
%
\ccGlue
\ccConstructor{SegmentVoronoiStorageSite2(Point_handle hp)}{Constructor from a
  point handle.}
%
\ccGlue
\ccConstructor{SegmentVoronoiStorageSite2(Point_handle hp1,
  Point_handle hp2)}{Constructor from two point handles.}
%
\ccGlue
\ccConstructor{SegmentVoronoiStorageSite2(Point_handle hp1,
  Point_handle hp2, Point_handle hq1, Point_handle hq2)}{Constructor
  from four point handles.}
%
\ccGlue
\ccConstructor{SegmentVoronoiStorageSite2(Point_handle hp1,
  Point_handle hp2, Point_handle hq1, Point_handle hq2, bool
  b)}{Constructor from four point handles and a boolean.}
%
\ccGlue
\ccConstructor{SegmentVoronoiStorageSite2(Point_handle hp1,
  Point_handle hp2, Point_handle hq1, Point_handle hq2, Point_handle
  hr1, Point_handle hr2)}{Constructor from six
  point handles.}
%
\ccGlue
\ccConstructor{SegmentVoronoiDiagramStorageSite_2(SegmentVoronoiDiagramStorageSite_2
  other)}{Copy constructor.}

\ccPredicates
\ccThree{bool}{ss.is_exact(unsigned int i)+}{}
\ccMethod{bool is_defined();}{Returns \ccc{true} if the storage site
  represents a valid point or segment.}
%
\ccGlue
\ccMethod{bool is_point();}{Returns \ccc{true} if the storage site
  represents a point.}
%
\ccGlue
\ccMethod{bool is_segment();}{Returns \ccc{true} if the storage site
  represents a segment.}
%
\ccGlue
\ccMethod{bool is_exact();}{Returns \ccc{true} if the storage site
  represents an input point or an input segment. Returns \ccc{false}
  if it represents a point of intersection of two segments, or if it
  represents a segment, at least one endpoint of which is a point of
  intersection of two segments.}
%
\ccGlue
\ccMethod{bool is_exact(unsigned int i);}{Returns \ccc{true} if the
  \ccc{i}-th endpoint of the corresponding site is an input
  point. Returns \ccc{false} if the \ccc{i}-th endpoint of the
  corresponding site is the intersection of two segments.
  \ccPrecond{\ccc{i} must be at most $1$, and \ccc{ss.is_segment()}
    must be \ccc{true}.}}




\ccAccessFunctions
%\ccThree{Point_handle}{ss.handle(unsigned int i)+}{}
\ccThree{SegmentVoronoiDiagramStorageSite_2}{}{}
\ccMethod{Point_handle handle(unsigned int i) const;}{
  Returns the \ccc{i}-th point handle of the site's
  representation. The valid values for \ccc{i} are $0$ through the
  number of points in the constructor or the
  \ccc{set_point}/\ccc{set_segment} methods used to
  construct or define, respectively the site.
  \ccPrecond{\ccc{i} must be at most $5$. The storage site must be of
    the correct type in order to access the corresponding point handle.}}
%
\ccGlue
\ccMethod{SegmentVoronoiDiagramStorageSite_2 supporting_site();}
	 {Returns a storage site object representing the exact segment
	   that supports the segment represented by the storage site.
  \ccPrecond{\ccc{ss.is_segment()} must be \ccc{true}.}
  \ccPostcond{The returned storage site represents an exact site.}}
%
\ccGlue
\ccMethod{SegmentVoronoiDiagramStorageSite_2 supporting_site(unsigned int i);}
	 {Returns a storage site object representing the \ccc{i}-th
	   exact segment that supports the point of intersection represented
	   by the storage site.
  \ccPrecond{\ccc{i} must be at most $1$, \ccc{ss.is_point()} must be
    \ccc{true} and \ccc{ss.is_exact()} must be \ccc{false}.}
  \ccPostcond{The returned storage site represents an exact site.}}
%
\ccGlue
\ccMethod{SegmentVoronoiDiagramStorageSite_2 crossing_site(unsigned int i);}
	 {Returns a storage site object representing the \ccc{i}-th exact
	   segment that supports the $i$-th endpoint of the site
	   which is not the supporting segment of the site.
	   \ccPrecond{\ccc{i} must be at most $1$,
	     \ccc{ss.is_segment()} must be \ccc{true} and
	     \ccc{ss.is_exact(i)} must be \ccc{false}.}
	   \ccPostcond{The returned site represents and exact site.}}
%
\ccGlue
\ccMethod{Site_2 site();}{Returns the site represented by the storage
  site.}


\ccHeading{Set methods}
\ccThree{void}{s.set_point(Point_handle hp)+}{}
%\ccThree{void}{s.set_segment(Point_2 p1, Point_2 p2)+}{}
\ccMethod{void set_point(Point_handle hp);}{}
%
\ccGlue
\ccMethod{void set_point(Point_handle hp1, Point_handle hp2,
  Point_handle hq1, Point_handle hq2);}{}
%
\ccGlue
\ccMethod{void set_segment(Point_handle hp1, Point_handle hp2);}{}
%
\ccGlue
\ccMethod{void set_segment(Point_handle hp1, Point_handle hp2,
  Point_handle hq1, Point_handle hq2, bool b);}{}
%
\ccGlue
\ccMethod{void set_segment(Point_handle hp1, Point_handle hp2,
  Point_handle hq1, Point_handle hq2, Point_handle hr1,
  Point_handle hr2);}{}



\ccHasModels
\ccc{CGAL::Segment_Voronoi_diagram_storage_site_2<Gt>}


\ccSeeAlso
\ccc{SegmentVoronoiDiagramTraits_2}\\
\ccc{CGAL::Segment_Voronoi_diagram_site_2<K>}\\
\ccc{CGAL::Segment_Voronoi_diagram_storage_site_2<Gt>}\\
\ccc{CGAL::Segment_Voronoi_diagram_traits_2<K,MTag>}\\
\ccc{CGAL::Segment_Voronoi_diagram_traits_without_intersections_2<K,MTag>}\\
\ccc{CGAL::Segment_Voronoi_diagram_filtered_traits_2<CK,CM,EK,EM,FK,FM>}\\
\ccc{CGAL::Segment_Voronoi_diagram_filtered_traits_without_intersections_2<CK,CM,EK,EM,FK,FM>}

\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

