%% Copyright (c) 2003,2004  INRIA Sophia-Antipolis (France) and
%% Notre Dame University (U.S.A.).  All rights reserved.
%%
%% This file is part of CGAL (www.cgal.org); you may redistribute it under
%% the terms of the Q Public License version 1.0.
%% See the file LICENSE.QPL distributed with CGAL.
%%
%% Licensees holding a valid commercial license may use this file in
%% accordance with the commercial license agreement provided with the software.
%%
%% This file is provided AS IS with NO WARRANTY OF ANY KIND, INCLUDING THE
%% WARRANTY OF DESIGN, MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE.
%%
%% $Source$
%% $Revision$ $Date$
%% $Name$
%%
%% Author(s)     : Menelaos Karavelas <mkaravel@cse.nd.edu>



\begin{ccRefConcept}{TriangulationFaceBaseWithEdges_2}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries
\ccDefinition
The \ccc{SegmentVoronoiDiagramFaceBase_2} refines the
\ccc{TriangulationFaceBase_2} concept by adding three edges (three
face handles and three integers). These triplets are intended to
support an in-place edge list. Since edges are not represented
explicitly, but rather as pairs of a \ccc{Face_handle} and an integer,
the only way to support this in-place edge list is by adding this
functionality in the face base of the triangulation data structure.

\ccRefines
\ccc{TriangulationFaceBase_2}

\ccTypes
\ccTwo{TriangulationFaceBaseWithEdges_2::Vertex_handle+}{}
\ccNestedType{Geom_traits}{A type for the geometric traits.}
%
\ccGlue
\ccNestedType{Triangulation_data_structure_2}{A type for the
  triangulation data structure, to which the face belongs to.}
%
\ccGlue
\ccNestedType{Vertex_handle}{A type for the vertex handle of the
  triangulation data structure.}
%
\ccGlue
\ccNestedType{Face_handle}{A type for the face handle of the
  triangulation data structure.}
%
\ccGlue
\ccNestedType{Edge}{A type for the edge of the triangulation data
  structure.}


\ccCreation
\ccCreationVariable{fbwe}
\ccTwo{TriangulationFaceBaseWithEdge_2 fbwe()+}{}
%
\ccConstructor{TriangulationFaceBaseWithEdges_2();}{Default constructor.}
%\ccGlue
\ccConstructor{TriangulationFaceBaseWithEdges_2(Vertex_handle v0,
  Vertex_handle v1, Vertex_handle  v2);}
{Initializes the vertices of the face with \ccc{v0}, \ccc{v1} and
\ccc{v2}. Neighbors are initialized to \ccc{Face_handle()}.}
%\ccGlue
\ccConstructor{TriangulationFaceBaseWithEdges_2(Vertex_handle v0,
  Vertex_handle v1, Vertex_handle v2,
  Face_handle n0, Face_handle n1, Face_handle n2);}
	      {Initializes the vertices of the face with \ccc{v0},
		\ccc{v1} and \ccc{v2}. Initializes the neighbors of
		the face with \ccc{n0}, \ccc{n1} and \ccc{n2}.}


\ccHeading{Operations}
We only cite the additional operations with respect to those of the
\ccc{TriangulationFaceBase_2} concept.

%
\ccThree{Edge}{fbwe.set_previous(int i, Edge prev)+}{}
%
\ccMethod{bool is_in_list(int i);}
{Checks if the edge corresponding to the pair (\ccc{fbwe}, \ccc{i})
is currently in the in-place edge list. Returns \ccc{true} if
(\ccc{fbwe}, \ccc{i}) is in the list, \ccc{false} otherwise.
\ccPrecond{\ccc{i} must be either \ccc{0}, \ccc{1} or \ccc{2}.}}
%
\ccGlue
\ccMethod{void set_next(int i, Edge next);}
{Sets the edge \ccc{next} as the successor of
(\ccc{fbwe}, \ccc{i}) in the list.
\ccPrecond \ccc{next} must correspond to a valid edge, and \ccc{i}
must be either \ccc{0}, \ccc{1} or \ccc{2}.}
%
\ccGlue
\ccMethod{void set_previous(int i, Edge prev);}
{Sets the edge \ccc{prev} as the predecessor of
(\ccc{fbwe}, \ccc{i}) in the list.
\ccPrecond{\ccc{prev} must correspond to a valid edge, and \ccc{i}
must be either \ccc{0}, \ccc{1} or \ccc{2}.}}
%
\ccGlue
\ccMethod{Edge next(int i);}
{Returns the successor of (\ccc{fbwe}, \ccc{i}) in the list.
\ccPrecond{\ccc{i} must be either \ccc{0}, \ccc{1} or \ccc{2}.}}
%
\ccGlue
\ccMethod{Edge previous(int i);}
{Returns the predecessor of (\ccc{fbwe}, \ccc{i}) in the list.
\ccPrecond{\ccc{i} must be either \ccc{0}, \ccc{1} or \ccc{2}.}}


\ccHasModels
\ccc{CGAL::Triangulation_face_base_with_edges_2<Fbb>}


\ccSeeAlso
\ccc{TriangulationFaceBase_2}\\
\ccc{TriangulationDataStructure_2}\\
\ccc{CGAL::Triangulation_face_base_2<Gt>}\\
\ccc{CGAL::Triangulation_face_base_with_edges_2<Fbb>}

\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+
