% +------------------------------------------------------------------------+
% | Reference manual page: Nef_polyhedron_S2_SVertex.tex
% +------------------------------------------------------------------------+
% | 14.05.2004   Peter Hachenberger
% | Package: Nef_S2
% | 
\RCSdef{\RCSNefS2SVertexeRev}{$Id$}
\RCSdefDate{\RCSNefS2SVertexDate}{$Date$}
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefClass}[Nef_polyhedron_S2<Traits>::]{SVertex}

\ccDefinition
 
Figure~\ref{figureNefS2SVertexIncidences} illustrates the incidence of a svertex on a sphere map. 

The member function 
\ccc{out_sedge} returns the first outgoing shalfedge, and \ccc{incident_sface}
returns the incident sface.

\ccInclude{CGAL/Nef_polyhedron_S2.h}

\ccTypes
\ccThree{SHalfedge_const_handle}{h.halfedge() const;;}{}
\ccThreeToTwo

The following types are the same as in \ccc{Nef_polyhedron_S2<Traits>}.

\ccNestedType{Mark}{type of mark.}

\ccNestedType{Sphere_point}{sphere point type stored in SVertex.}

\ccNestedType{SVertex_const_handle}{const handle to SVertex.}
\ccGlue
\ccNestedType{SHalfedge_const_handle}{const handle to SHalfedge.}
\ccGlue
\ccNestedType{SFace_const_handle}{const handle to SFace.}

\ccCreation
\ccCreationVariable{e}

There is no need for a user to create a \ccc{SVertex} explicitly. The
class \ccc{Nef_polyhedron_S2<Traits>} manages the needed svertices internally.

\ccOperations

\ccMethod{const Mark& mark() const;}{the mark of \ccVar\ .}

\ccMethod{const Sphere_point& point() const;}{the sphere point of \ccVar\ .}

\ccMethod{bool is_isolated() const;}
{returns |true| if \ccVar\ has no adjacent sedges.}

\ccMethod{SVertex_const_handle twin() const;}{the twin of \ccVar\ .}

\ccMethod{SHalfedge_const_handle out_sedge() const;}
{the first out sedge of \ccVar\ .}

\ccMethod{SFace_const_handle incident_sface() const;}
{the incident sface of \ccVar\ .}

\ccSeeAlso

\ccRefIdfierPage{CGAL::Nef_polyhedron_S2<Traits>::SHalfedge}\\
\ccRefIdfierPage{CGAL::Nef_polyhedron_S2<Traits>::SFace} \\
\ccRefIdfierPage{CGAL::Nef_polyhedron_S2<Traits>::Sphere_point}

\ccTagDefaults
\end{ccRefClass}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+
