\begin{ccRefFunctionObjectConcept}{AlgebraicStructureTraits::DivMod}

\ccDefinition

\ccc{AdaptableFunctor} computes both integral quotient and remainder
of division with remainder. The quotient $q$ and remainder $r$ are computed 
such that $x = q*y + r$ and $|r| < |y|$ with respect to the proper integer norm of 
the represented ring.
\footnote{
For integers this norm is the absolute value.\\ 
For univariate polynomials this norm is the degree.} 
In particular, $r$ is chosen to be $0$ if possible.
Moreover, we require $q$ to be minimized with respect to the proper integer norm.  

\ccIgnore{
For types representing \Z, this is round $q$ towards zero.
For univariate polynomials this has no effect at all.
MP_Float Z[1/2] is not clear yet.
}


Note that the last condition is needed to ensure a unique computation of the 
pair $(q,r)$. However, an other option is to require minimality for $|r|$, 
with the advantage that
a {\em mod(x,y)} operation would return the unique representative of the 
residue class of $x$ with respect to $y$, e.g. $mod(2,3)$ should return $-1$. 
But this conflicts with nearly all current implementation 
of integer types. From there, we decided to stay conform with common 
implementations and require $q$ to be computed as $x/y$ rounded towards zero. 

\ccIgnore{
Note that in general the above definition does not force a unique computation 
of the pair $(q,r)$. This could be solved by requiring $|r|$ to be minimal, 
in particular a {\em mod} operation would return the unique representative of 
its residue class. But this conflicts with nearly all current implementation 
of integer types. From there, we decided to stay conform with common 
implementation and require $q$ to be computed as $x/y$ rounded towards zero, 
for \ccc{RealEmbeddable} \ccc{EuclideanRing}s. 
}

The following table illustrates the behavior for integers: 

\begin{tabular}{ccc}
\begin{tabular}{|c|c|c|c|}
\hline
 $\ x\ $ & $\ y\ $ & $\ q\ $ & $\ r\ $\\
\hline
 3  &  3  &  1  &  0\\
 2  &  3  &  0  &  2\\
 1  &  3  &  0  &  1\\
 0  &  3  &  0  &  0\\
-1  &  3  &  0  & -1\\
-2  &  3  &  0  & -2\\
-3  &  3  & -1  &  0\\
\hline
\end{tabular}
& - & 
\begin{tabular}{|c|c|c|c|}
\hline
 $\ x\ $ & $\ y\ $ & $\ q\ $ & $\ r\ $\\
\hline
 3  & -3  & -1  &  0\\
 2  & -3  &  0  &  2\\
 1  & -3  &  0  &  1\\
 0  & -3  &  0  &  0\\
-1  & -3  &  0  & -1\\
-2  & -3  &  0  & -2\\
-3  & -3  &  1  &  0\\
\hline
\end{tabular}\\
\end{tabular}




\ccRefines 

\ccc{AdaptableFunctor} 

\ccTypes
\ccNestedType{result_type}
        { Is void.}
\ccGlue
\ccNestedType{first_argument_type}
        { Is \ccc{AlgebraicStructureTraits::Type}.}
\ccGlue
\ccNestedType{second_argument_type}
        { Is \ccc{AlgebraicStructureTraits::Type}.}
\ccGlue
\ccNestedType{third_argument_type}
        { Is \ccc{AlgebraicStructureTraits::Type&}.}
\ccGlue
\ccNestedType{fourth_argument_type}
        { Is \ccc{AlgebraicStructureTraits::Type&}.}

\ccOperations
\ccCreationVariable{div_mod}
\ccThree{xxxxxxxxxxx}{xxxxxxxxxxx}{}
\ccMethod{result_type operator()( first_argument_type  x, 
                                  second_argument_type y,
                                  third_argument_type  q,
                                  fourth_argument_type r);}{ 
        computes the quotient $q$ and remainder $r$, such that $x = q*y + r$ 
        and $r$ minimal with respect to the Euclidean Norm on   
        \ccc{Type}. }

\ccMethod{template <class NT1, class NT2> result_type 
        operator()(NT1  x, NT2  y, third_argument_type q, fourth_argument_type r);}
         {This operator is well defined if \ccc{NT1} and \ccc{NT2} are \ccc{ExplicitInteroperable} 
          with coercion type \ccc{AlgebraicStructureTraits::Type}. }

%\ccHasModels

\ccSeeAlso

\ccRefIdfierPage{AlgebraicStructureTraits}\\
\ccRefIdfierPage{AlgebraicStructureTraits::Mod}\\
\ccRefIdfierPage{AlgebraicStructureTraits::Div}\\

\end{ccRefFunctionObjectConcept} 
