% +------------------------------------------------------------------------+
% | Reference manual page: TDS_2::Face.tex
% +------------------------------------------------------------------------+
% | 07.04.2000   Author
% | Package: Package
% | 
\RCSdef{\RCSTdsFace}{$Id$}
\RCSdefDate{\RCSTdsFaceDate}{$Date$}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefConcept}{TriangulationDataStructure_2::Face}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries

\ccDefinition
  
The concept \ccRefName\  describes the types used to store the faces
face class of a 
\ccc{TriangulationDataStructure_2}\lcTex{, see 
\ccRefPage{TriangulationDataStructure_2}}.
A \ccRefName\ stores three pointers to its three vertices
and three pointers to its three neighbors.
The vertices are indexed 0,1, and 2 in counterclockwise order.
The  neighbor indexed $i$ lies
opposite to vertex i.

In degenerate cases,
when the triangulation data structure  stores a
simplicial complex of dimension $0$ and $1$,
the type \ccRefName\  is used to store the faces 
of maximal dimension of the complex 
: i.e. a vertex in dimension $0$, an edge in dimension $1$.
Only vertices and neighbors with index $0$ are set in the first case,
only vertices and neighbors with index $0$ or $1$ are set in the second case.


\ccTypes
The class \ccRefName\ defines the same types as 
the triangulation data structure 
except the iterators and the circulators.

\ccCreationVariable{f}  %% choose variable name

\ccCreation

The methods \ccc{create_face} and
\ccc{delete_face()}
have to be used to 
define new faces and  to delete non longer used faces.


\ccHeading{Vertex Access Functions}
\ccThree{Vertex_handle}{f.has_neighbors((Face_handle n);}{}

\ccMethod{Vertex_handle vertex(int i) const;}
{returns  the vertex \ccc{i} of \ccVar.
\ccPrecond{$0\leq i \leq 2$.}}
\ccGlue
\ccMethod{int index(Vertex_handle v) const;}
{returns the index of vertex \ccc{v} in \ccVar. \ccPrecond{\ccc{v} is
a vertex of \ccVar.}}
\ccGlue
\ccMethod{bool has_vertex(Vertex_handle v) const;}
{returns \ccc{true} if  \ccc{v} is a vertex of \ccVar.}
\ccGlue
\ccMethod{bool has_vertex(Vertex_handle v, int& i) const;}
{returns \ccc{true} if  \ccc{v} is a vertex of \ccVar, and
 computes the index \ccc{i} of \ccc{v} in \ccc{f}.}


\ccHeading{Neighbor Access Functions}

The neighbor with index \ccc{i} is the neighbor which is opposite
to the vertex with index \ccc{i}.


\ccMethod{Face_handle neighbor(int i) const;}
{returns  the neighbor \ccc{i} of \ccVar. 
\ccPrecond{$0\leq i \leq 2$}.
}
\ccGlue
\ccMethod{int index(Face_handle n) const;}
{returns the index of face \ccc{n}.
\ccPrecond{\ccc{n} is a neighbor of \ccVar.}}
\ccGlue
\ccMethod{bool has_neighbor(Face_handle n) const;}
{returns \ccc{true} if \ccc{n} is a neighbor of \ccVar.}
\ccGlue
\ccMethod{bool has_neighbor(Face_handle n, int& i) const;}
{returns \ccc{true} if \ccc{n} is a neighbor of \ccVar,  and
compute the index \ccc{i} of \ccc{n}.}



\begin{ccAdvanced}
\ccHeading{Setting}

\ccThree{Vertex_handle}{f.has_vertex( Vertex_handle v, int& i)x}{}
\ccMethod{void set_vertex(int i, Vertex_handle v);}
{sets vertex \ccc{i} to be \ccc{v}.
\ccPrecond{$0\leq i \leq 2$.}
}
\ccGlue
\ccMethod{void set_neighbor(int i, Face_handle n);}
{sets neighbor \ccc{i} to be \ccc{n}.
\ccPrecond{$0\leq i \leq 2$.}
}
\ccGlue
\ccMethod{ void set_vertices();}{sets the vertices pointers to \ccc{NULL}.}
\ccGlue
\ccMethod{void set_vertices(Vertex_handle v0,
		    Vertex_handle v1,
		    Vertex_handle v2);}{sets the vertices pointers.}
\ccGlue
\ccMethod{void set_neighbors();} {sets the neighbors pointers to \ccc{NULL}.}
\ccGlue
\ccMethod{void set_neighbors(Face_handle n0,
		     Face_handle n1,
		     Face_handle n2);}{sets the neighbors pointers.}


\ccHeading{Checking}

\ccMethod{bool is_valid() const;}
{returns \ccc{true} if  the function 
\ccc{is_valid()} of the base class
returns \ccc{true} and if, for each index $i$, $0 \le i < 3$,
face $f$ is a neighbor of its neighboring face \ccc{neighbor(i)}
and shares with this neighbor the  vertices \ccc{cw(i)} and \ccc{ccw(i)}
in correct reverse order.}

\end{ccAdvanced}

\ccHeading{Miscellaneous} 

\ccMethod{int ccw(int i) const;}
{Returns $i+1$ modulo 3.\ccPrecon{$0\leq i \leq 2$.}}

\ccMethod{int cw(int i) const;}
{Returns $i+2$ modulo 3.\ccPrecond{$0\leq i \leq 2$.}}

\ccHeading{I/O}

\ccFunction{istream& operator>> (istream& is, TriangulationDataStructure_2::Face & f);}
{Inputs any non combinatorial information possibly stored in  the face.}
\ccGlue
\ccFunction{ostream& operator<< (ostream& os, const TriangulationDataStructure_2::Face & f);}
{Outputs any non combinatorial information possibly stored in  the face.}


\ccSeeAlso
\ccc{TriangulationDataStructure_2}, \\
\ccc{TriangulationDataStructure_2::Vertex}, \\
\ccc{TriangulationFaceBase_2}.


\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

