% +------------------------------------------------------------------------+
% | Reference manual page: TriangulationDSFaceBase_2.tex
% +------------------------------------------------------------------------+
% | 13.08.2003   Author
% | Package: Package
% | 
\RCSdef{\RCSTriangulationDSFaceBaseRev}{$Id$}
\RCSdefDate{\RCSTriangulationDSFaceBaseDate}{$Date$}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefConcept}{TriangulationDSFaceBase_2}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries

\ccDefinition
The concept \ccRefName\ describes the requirements for
the base face of a \ccc{Triangulation_data_structure_2<Vb,Fb>}.

Note that if  the \ccc{Triangulation_data_structure_2} 
is plugged  into a triangulation class, 
the face base class may have  additional geometric
requirements depending on the triangulation class.

At the base level, 
(see Sections~\ref{Section_2D_Triangulations_Software_Design} 
and~\ref{2D_TDS_default}),
a  face stores handles
 on  its three vertices  and on  the three neighboring faces.
The vertices and neighbors are indexed 0,1 and 2.
Neighbor $i$ lies opposite to vertex $i$.

Since the \ccc{Triangulation_data_structure_2} is the class 
which defines the handle
types, the face base class has to be somehow 
parameterized by the triangulation
data structure.  But since the \ccc{Triangulation_data_structure_2}
itself is parameterized by the face and vertex
base classes, there is a cycle in the definition of these classes.  
In order
to break the cycle, the base classes for faces and vertices
 which are plugged in to instantiate a
\ccc{Triangulation_data_structure_2}
use a \ccc{void} as triangulation
data structure parameter. Then, 
the \ccc{Triangulation_data_structure_2}
 uses a {\it rebind}  mechanism (similar to the one specified in
\ccc{std::allocator}) in order to plug itself 
as parameter in the face and vertex  base classes. 
This mechanism requires that the base class  provides
a templated nested class \ccc{Rebind_TDS} that
itself provides 
 the subtype \ccc{Rebind_TDS<TDS2>::Other}
which is the {\it rebound} version of the base class.
 This {\it rebound} base class is  the class
that the   \ccc{Triangulation_data_structure_2}
 actually  uses  as a base class for the class
\ccc{Triangulation_data_structure_2::Face}.


\ccTypes
\ccThree{typedef TriangulationDataStructure_2::Vertex_handle}{}{}
\ccThreeToTwo
The concept \ccRefName\ has to provide the following types.

\ccNestedType{
  template <typename TDS2>
  struct Rebind_TDS}
{This nested template class has to define a type \ccc{Other} which is the
{\it rebound} face base, where  the 
\ccc{Triangulation_data_structure_2} is actually  plugged in.
This type  \ccc{Other}  will be the actual  base 
of the class \ccc{Triangulation_data_structure_2::Face}.}

\ccTypedef{typedef TriangulationDataStructure_2 Triangulation_data_structure;}{}
\ccGlue
\ccTypedef{typedef TriangulationDataStructure_2::Vertex_handle Vertex_handle;}{}
\ccGlue
\ccTypedef{typedef TriangulationDataStructure_2::Face_handle Face_handle;}{}




\ccCreation
\ccCreationVariable{f}  %% choose variable name
\ccTwo{TriangulationDSFaceBase_2( Vertex_handle v0,}{}
\ccConstructor{TriangulationDSFaceBase_2();}{default constructor.}
\ccGlue
\ccConstructor{TriangulationDSFaceBase_2(Vertex_handle v0, 
                                         Vertex_handle v1,
                                         Vertex_handle v2);}
{Initializes the vertices with \ccc{v0, v1, v2} and the neighbors 
with \ccc{Face_handle()}.} 
\ccGlue
\ccConstructor{TriangulationDSFaceBase_2(Vertex_handle v0, 
                                       Vertex_handle v1,
                                       Vertex_handle v2,
                                       Face_handle n0, 
                                       Face_handle n1,
                                       Face_handle n2);}
{initializes the vertices with \ccc{ v0,v1, v2} and the neighbors with
\ccc{n0, n1, n2}.}


\ccAccessFunctions
\ccThree{Vertex_handlex}{has_neigbor(const Face_handle n, int& i);}{}
\ccMethod{ int dimension();}{returns the dimension.}
\ccMethod{Vertex_handle vertex(int i) const;}
{returns the vertex \ccc{i} of \ccVar\ .
\ccPrecond{$0\leq i \leq 2$.}}
\ccGlue
\ccMethod{bool has_vertex(Vertex_handle v);}
{returns true if \ccc{v} is a vertex of \ccVar\ .}
\ccGlue
\ccMethod{bool has_vertex(Vertex_handle v, int& i) const;}
{as above, and sets \ccc{i} to the index of \ccc{v} in \ccVar\ .}
\ccGlue
\ccMethod{int index(Vertex_handle v) const;}
{returns the index of \ccc{v} in \ccVar\ .}
\ccGlue
\ccMethod{Face_handle neighbor(int i) const;}
{{returns the neighbor \ccc{i} of \ccVar\ .
\ccPrecond{$0\leq i \leq 2$.}}}
\ccGlue
\ccMethod{bool has_neighbor(Face_handle n);}
{returns true if \ccc{n} is a neighbor of \ccVar\ .}
\ccGlue
\ccMethod{bool has_neigbor(Face_handle n, int& i) const;}
{as above, and sets i to the index of \ccc{n} in \ccVar\ .}
\ccGlue
\ccMethod{int index(const Face_handle n) const;}
{returns the index of neighbor \ccc{n} in \ccVar\ .}

\ccHeading{Setting}
\ccMethod{void set_vertex(int i, Vertex_handle v);}
{sets vertex \ccc{i} to \ccc{v}.
{\ccPrecond{$0\leq i \leq 2$.}}}
\ccGlue
\ccMethod{ void set_vertices();}
{sets the vertices to \ccc{Vertex_handle()}.}
\ccGlue
\ccMethod{void set_vertices(Vertex_handle v0,
		    Vertex_handle v1,
		    Vertex_handle v2);}
{sets the vertices.}
\ccGlue
\ccMethod{void set_neighbor(int i, Face_handle n);}
{sets neighbors \ccc{i} to \ccc{n}.
{\ccPrecond{$0\leq i \leq 2$.}}}
\ccGlue
\ccMethod{void set_neighbors();} 
{sets the neighbors to \ccc{Face_handle()}.}
\ccGlue
\ccMethod{void set_neighbors(Face_handle n0,
		     Face_handle n1,
		     Face_handle n2);}{sets the neighbors.}

\ccHeading{Orientation}
\ccMethod{void reorient();}
{Changes the orientation of \ccVar\  by exchanging \ccc{vertex(0)}
with \ccc{vertex(1)} and \ccc{neighbor(0)} with \ccc{neighbor(1)}.}
\ccGlue
\ccMethod{void ccw_permute();}
{preforms a counterclockwise permutation of the
 vertices and neighbors of \ccVar.}
\ccGlue
\ccMethod{ void cw_permute();}
{preforms a clockwise permutation of the
 vertices and neighbors of \ccVar.}

\ccHeading{Checking}
\ccMethod{bool is_valid(bool verbose = false) const;}
{performs any required test on a face. \\
If \ccc{verbose} is set to \ccc{true}, messages are printed to give
a precise indication of the kind of invalidity encountered.}

\ccHeading{Various}

\ccMethod{void * for_compact_container() const;}{}
\ccGlue
\ccMethod{void * & for_compact_container();}{}
{ These member functions are required by \ccc{Triangulation_data_structure_2}
  because it uses \ccc{Compact_container} to store its faces.  See the
  documentation of \ccc{Compact_container} for the exact requirements.}




\ccHasModels
\ccc{CGAL::Triangulation_ds_face_base_2<Tds>}\\
\ccc{CGAL::Triangulation_face_base_2<Traits,Fb>}\\
\ccc{CGAL::Regular_triangulation_face_base_2<Traits,Fb>}\\
\ccc{CGAL::Constrained_triangulation_face_base_2<Traits,Fb>}\\
\ccc{CGAL::Triangulation_face_base_with_info_2<Info,Traits,Fb>}

\ccSeeAlso
\ccc{TriangulationDSVertexBase_2}\\
\ccc{TriangulationDataStructure_2::Face} \\
\ccc{TriangulationFaceBase_2} \\
\ccc{Triangulation_data_structure_2<Vb,Fb>} 

%% \ccIncludeExampleCode{Package/TriangulationDSFaceBase_2_prog.C}

\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

