\ccSetThreeColumns{CGAL_Color }{}{\hspace*{8cm}}
\ccSetTwoColumns{}{\hspace*{8cm}}

\cleardoublepage
\chapter{Colors} \label{colors}

\medskip

\begin{ccClass} {CGAL_Color}
\ccSection{Colors}

\ccDefinition
An object of the class \ccClassName\ is a color available
for drawing operations in \cgal\ output streams.
Each color is defined by a triple of integers $(r,g,b)$ with
$0\le r,g,b \le 255$, the so-called {\em rgb-value} of the color.


\ccCreation
\ccCreationVariable{c}

\ccThree{CGAL_Color &}{c(int red, int green, int blue);}{}
\ccThreeToTwo

\ccConstructor{CGAL_Color();}
             {creates a color with rgb-value $(0,0,0)$, i.e.\ black.}

\ccConstructor{CGAL_Color(int red, int green, int blue);}
             {creates a color with rgb-value \ccStyle{(red,green,blue)}.}


\ccOperations

\ccHidden \ccMethod{CGAL_Color & operator=(const CGAL_Color &q);}
        {Assignment.}

\ccMethod{bool operator==(const CGAL_Color &q) const;}
       {Test for equality: Two colors are equal, iff their 
        rgb-values are equal.}
\ccGlue
\ccMethod{bool operator!=(const CGAL_Color &q) const;}
       {Test for inequality.}

\ccMethod{int red() const;}
       {returns the  red component of \ccVar.}
\ccGlue
\ccMethod{int green() const;}
       {returns the  green component of \ccVar.}
\ccGlue
\ccMethod{int blue() const;}
       {returns the blue component of \ccVar.}

\ccConstants

The following constants are predefined:

\newpage

\ccThree{const CGAL_Color &}{CGAL_WHITE = CGAL_Color(255, 255, 255);}{}

\ccVariable{const CGAL_Color CGAL_BLACK  = CGAL_Color(0, 0, 0);}{Black.}
\ccGlue
\ccVariable{const CGAL_Color CGAL_WHITE  = CGAL_Color(255, 255, 255);}{White.}
\ccGlue
\ccVariable{const CGAL_Color CGAL_RED    = CGAL_Color(255, 0, 0);}{Red.}
\ccGlue
\ccVariable{const CGAL_Color CGAL_GREEN  = CGAL_Color(0, 255, 0);}{Green.}
\ccGlue
\ccVariable{const CGAL_Color CGAL_BLUE   = CGAL_Color(0, 0, 255);}{Blue.}
\ccGlue
\ccVariable{const CGAL_Color CGAL_VIOLET = CGAL_Color(255, 0, 255);}{Violet.}
\ccGlue
\ccVariable{const CGAL_Color CGAL_ORANGE = CGAL_Color(255, 170, 0);}{Orange.}
\end{ccClass} 
