% =============================================================================
% The CGAL Developers' Manual
% Chapter: Mailing Lists and Addresses
% -----------------------------------------------------------------------------
% file   : addresses.tex
% authors: Susan Hert <hert@mpi-sb.mpg.de>
% -----------------------------------------------------------------------------
% $Revision$
% $Date$
% =============================================================================

\chapter{Mailing Lists and Addresses}
\label{chap:addresses}
\ccChapterRelease{Chapter Version: 1.0} \\
\ccChapterAuthor{Susan Hert ({\tt hert@mpi-sb.mpg.de})} 
\ccIndexMainItemBegin{email addresses}
\ccIndexMainItemBegin{mailing lists}

There are a number of mailing lists and email addresses that have been set 
up to communicate with various subsets of the \cgal\ community.  The 
addresses that should be of interest to \cgal\ developers are as follows:

\begin{description}
\item[\ccAnchor{mailto:cgal-develop-l@postino.mpi-sb.mpg.de}{{\tt cgal-develop-l@postino.mpi-sb.mpg.de}}] 
     (a.k.a. \texttt{cgal-develop@cgal.org})
     \index{cgal_develop mailing list@{\tt cgal-develop} mailing list}
     This list is intended for discussing detailed matters 
     about implementation and development issues.  All developers should 
     subscribe to this list by sending a message to
     \ccAnchor{mailto:kettner@mpi-sb.mpg.de}{kettner@mpi-sb.mpg.de}.
     An \ccAnchor{http://postino.mpi-sb.mpg.de/cgi-bin/lyris.pl?enter=cgal-develop-l}{archive} 
     of this mailing list is maintained%
     \begin{ccTexOnly}
     at \nonlinkedpath|http://postino.mpi-sb.mpg.de/cgi-bin/lyris.pl?enter=cgal-develop-l|
     \end{ccTexOnly}.  To enter this archive, use your email address and
     password (if you have one) or
     \texttt{member1@cgal.org} and the usual password.  

\item[\ccAnchor{mailto:cgal-discuss-l@postino.mpi-sb.mpg.de}{{\tt cgal-discuss-l@postino.mpi-sb.mpg.de}}] 
     \index{cgal-discuss-l mailing list@{\tt cgal-discuss-l} mailing list}
     Users of \cgal\ post questions and discuss issues
     related to \cgal\ on this list.  All developers should subscribe to this 
     list so they can answer questions relevant to their packages and monitor 
     the input from the users provided here. 
     To subscribe to the list, send a message to
     \ccAnchor{mailto:cgal-discuss-l-request@postino.mpi-sb.mpg.de}%
     {\nonlinkedpath|cgal-discuss-l-request@postino.mpi-sb.mpg.de|}
     with the content ``\texttt{subscribe cgal-discuss-l}''.
     An \ccAnchor{http://postino.mpi-sb.mpg.de/cgi-bin/lyris.pl?enter=cgal-discuss-l}{archive} 
     of this mailing list is maintained%
     \begin{ccTexOnly}
     at \nonlinkedpath|http://postino.mpi-sb.mpg.de/cgi-bin/lyris.pl?enter=cgal-discuss-l|
     \end{ccTexOnly}.

\item[\ccAnchor{mailto:cgal-announce-l@postino.mpi-sb.mpg.de}{{\tt cgal-announce-l@postino.mpi-sb.mpg.de}}] 
     \index{cgal-announce-l mailing list@{\tt cgal-announce-l} mailing list}
     Announcements of new releases, bug fixes, special courses, etc. are posted
     to this list.  The list is moderated (meaning every message posted needs
     to be approved) to keep the traffic low.
     To subscribe to the list, send a message to
     \ccAnchor{mailto:cgal-announce-l-request@postino.mpi-sb.mpg.de}%
     {\nonlinkedpath|cgal-announce-l-request@postino.mpi-sb.mpg.de|}
     with the content ``\texttt{subscribe cgal-announce-l}''.
     An \ccAnchor{http://postino.mpi-sb.mpg.de/cgi-bin/lyris.pl?enter=cgal-announcw-l}{archive} 
     of this mailing list is maintained%
     \begin{ccTexOnly}
     at \nonlinkedpath|http://postino.mpi-sb.mpg.de/cgi-bin/lyris.pl?enter=cgal-announce-l|
     \end{ccTexOnly}.

\item[\ccAnchor{mailto:cgal-editor-l@postino.mpi-sb.mpg.de}{{\tt cgal-editor-l@postino.mpi-sb.mpg.de}}] 
     \index{editor address@{\tt editor} address}
     (a.k.a. \texttt{editor@cgal.org})
     This is the email address to which you should
     send proposed design specifications (Chapter~\ref{chap:specification})
     for approval by the editorial 
     board (Section~\ref{sec:editorial_board}). Anyone can do that 
     at any time about any \cgal\ design issues. 

     This list is also
     \ccAnchor{http://postino.mpi-sb.mpg.de/cgi-bin/lyris.pl?enter=cgal-editor-l}{archived}%
     \lcTex{
     at \path|http://postino.mpi-sb.mpg.de/cgi-bin/lyris.pl?enter=cgal-editor-l|}, and members of the list should use their own
     email addresses and passwords (if you have one) to enter the archive.

\item[\ccAnchor{mailto:cgal-submit@cs.uu.nl}{{\tt cgal-submit@cs.uu.nl}}] 
     (a.k.a. \texttt{cgal-submit@cgal.org})
     \index{cgal-submit address@{\tt cgal-submit} address}
     This is the address to which electronic
     submissions of packages, documentation, bug fixes, \etc\ are
     sent by the \texttt{cgal\_submit} script
     \index{cgal_submit script@{\tt cgal\_submit} script}
     (Section~\ref{sec:electronic_submission}).

\item[\ccAnchor{mailto:galia-board-l@postino.mpi-sb.mpg.de}{{\tt galia-board-l@postino.mpi-sb.mpg.de}}] 
     \index{galia-board-l address@{\tt galia-board-l} address}
     This list contains all \galia\ consortium board members and certain 
     members of the editorial board who coordinate development at their 
     respective sites.
     This group discusses global policy decisions about the library (such
     as licensing).  This list is closed, which means only members of the list 
     may post to it.

\item[\ccAnchor{mailto:cgal-internal-l@postino.mpi-sb.mpg.de}{{\tt cgal-internal-l@postino.mpi-sb.mpg.de}}] 
     \index{cgal-internal-l address@{\tt cgal-internal-l} address}
     This mailing list contains all members of the \texttt{galia-board-l} and
     \texttt{cgal-editor-l} mailing lists and a few other key developers.
     It is intended as a forum for discussion among developers and board 
     members.  The list is also closed, but developers interested in 
     discussing global policy issues can send a request to 
     \ccAnchor{mailto:kettner@mpi-sb.mpg.de}{kettner@mpi-sb.mpg.de} to be included
     on the list.
\end{description}

The mailing lists at \texttt{postino.mpi-sb.mpg.de} 
are currently
maintained by \ccAnchor{mailto:kettner@mpi-sb.mpg.de}{Lutz Kettner}. 
\ccIndexMainItemEnd{email addresses}
\ccIndexMainItemEnd{mailing lists}
