\begin{ccRefClass} {Line_3<Kernel>}

\ccDefinition
An object \ccStyle{l} of the data type \ccRefName\ is a directed
straight line in the three-dimensional Euclidean space $\E^3$.

\ccCreation
\ccCreationVariable{l}

\ccHidden \ccConstructor{Line_3();}
             {introduces an uninitialized variable \ccVar.}

\ccHidden \ccConstructor{Line_3(const Line_3<Kernel> &h);}
 	    {copy constructor.}

\ccConstructor{Line_3(const Point_3<Kernel> &p, const Point_3<Kernel> &q);}
            {introduces a line \ccVar\ passing through the points $p$ and $q$. 
             Line \ccVar\ is directed from $p$ to $q$.}


\ccConstructor{Line_3(const Point_3<Kernel> &p, const Direction_3<Kernel>&d)}
            {introduces a line \ccVar\ passing through point $p$ with 
             direction $d$.}

\ccConstructor{Line_3(const Point_3<Kernel> &p, const Vector_3<Kernel>&v)}
            {introduces a line \ccVar\ passing through point $p$ and
             oriented by $v$.}

\ccConstructor{Line_3(const Segment_3<Kernel> &s);}
            {returns the line supporting the segment $s$,
	    oriented from source to target.}

\ccConstructor{Line_3(const Ray_3<Kernel> &r);}
            {returns the line supporting the ray $r$, with the
	    same orientation.}

\ccOperations
\ccSetThreeColumns{Direction_3<Kernel> }{}{\hspace*{8.5cm}}

\ccHidden \ccMethod{Line_3<Kernel> & operator=(const Line_3<Kernel> &h);}
        {Assignment.}

\ccMethod{bool operator==(const Line_3<Kernel> &h) const;}
       {Test for equality: two lines are equal, iff they have a non 
        empty \ccHtmlNoLinksFrom{intersection} and the same direction.}

\ccMethod{bool operator!=(const Line_3<Kernel> &h) const;}
       {Test for inequality.}

\ccMethod{Point_3<Kernel>    projection(const Point_3<Kernel> &p) const;}
       {returns the orthogonal \ccHtmlNoLinksFrom{projection} of $p$ on \ccVar.}

\ccMethod{Point_3<Kernel> point(int i) const;}
       {returns an arbitrary point on \ccVar. It holds 
        \ccStyle{point(i) = point(j)}, iff \ccStyle{i=j}.}

\ccPredicates

\ccMethod{bool is_degenerate() const;}
       {returns \ccc{true} iff line \ccVar\ is degenerated to a point.}

\ccMethod{bool has_on(const Point_3<Kernel> &p) const;}
       {returns \ccc{true} iff \ccc{p} lies on \ccVar.}

\ccHeading{Miscellaneous}

\ccMethod{Plane_3<Kernel>      perpendicular_plane(const Point_3<Kernel> &p) const;}
       {returns the plane perpendicular to \ccVar\ passing through $p$.}

\ccMethod{Line_3<Kernel>      opposite() const;}
       {returns the line with opposite direction.}

\ccMethod{Vector_3<Kernel>    to_vector() const;}
       {returns a vector having the same direction as \ccVar.}

\ccMethod{Direction_3<Kernel> direction() const;}
       {returns the direction of \ccVar.}

\ccMethod{Line_3<Kernel>  transform(const Aff_transformation_3<Kernel> &t) const;}
       {returns the line obtained by applying $t$ on a point on \ccVar\ 
        and the direction of \ccVar.}

\ccSeeAlso
\ccRefConceptPage{Kernel::Line_3}

\end{ccRefClass} 
