% +------------------------------------------------------------------------+
% | Reference manual page: MeshFacetCriteria_3.tex
% +------------------------------------------------------------------------+
% | 13.02.2009   Author
% | Package: Mesh_3
% |
\RCSdef{\RCSMeshFacetCriteriaRev}{$Id$}
\RCSdefDate{\RCSMeshFacetCriteriaDate}{$Date$}
% |
\ccRefPageBegin
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefFunctionObjectConcept}{MeshFacetCriteria_3}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries

\ccDefinition
  
The Delaunay refinement process involved in the 
template functions \ccc{make_mesh_3} and \ccc{refine_mesh_3}
is guided by a set of elementary refinement criteria
that concern either mesh tetrahedra or surface facets.
The concept \ccRefName\ describes the types that
handle the refinement criteria for surface facets.


\ccTypes

\ccNestedType{Facet}{Type for the facets of the
  triangulation. Must match the \ccc{Facet} type in the
  triangulation type used by the mesh generation function.}

\ccNestedType{Cell_handle}{Handle type for the cells of the
  triangulation. Must match the \ccc{Cell_handle} type in the
  triangulation type used by the mesh generation function.}

\ccNestedType{Facet_quality}{Type representing the quality of a
  facet. Must be a model of CopyConstructible and
  LessThanComparable. Between two facets, the one which has the lower
  quality must have the lower \ccc{Facet_quality}.}

\ccNestedType{Is_facet_bad}{Type representing if a facet is bad or not. This type
must be convertible to \ccc{bool}. If it converts to \ccc{true} then the facet is bad, otherwise
the facet is good with regard to the criteria.

In addition, an object of this type must contain an object of type
\ccc{Facet_quality} if it represents
a bad facet. \ccc{Facet_quality} must be accessible by
\ccc{operator*()}. Note that \ccc{boost::optional<Facet_quality>} is 
a natural model of this concept} % boost::optional

\ccCreationVariable{facet_criteria}

\ccOperations

\ccMethod{Is_facet_bad operator()(Facet f);}
{Returns \ccc{Is_facet_bad} value of facet \ccc{f}.}
\ccMethod{Is_facet_bad operator()(Cell_handle c, int i);}
{Same as above with \ccc{f=(c,i)}.}


\ccHasModels
\ccc{Mesh_facet_criteria_3<Tr>}

\ccSeeAlso
\ccRefConceptPage{MeshCellCriteria_3}\\
\ccRefConceptPage{MeshEdgeCriteria_3} \\
\ccRefConceptPage{MeshCriteria_3} \\
\ccRefIdfierPage{CGAL::make_mesh_3} \\
\ccRefIdfierPage{CGAL::refine_mesh_3}\\


\end{ccRefFunctionObjectConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+
