% +------------------------------------------------------------------------+
% | Reference manual page: Mesh_cell_criteria_3.tex
% +------------------------------------------------------------------------+
% | 16.02.2009   Author
% | Package: Package
% |
\RCSdef{\RCSMeshcellcriteriaRev}{$Id: header.tex 40270 2007-09-07 15:29:10Z lsaboret $}
\RCSdefDate{\RCSMeshcellcriteriaDate}{$Date: 2007-09-07 17:29:10 +0200 (Ven, 07 sep 2007) $}
% |
\ccRefPageBegin
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefFunctionObjectClass}{Mesh_cell_criteria_3<Tr>}  %% add template arg's if necessary

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[class]{} %% add further index entries

\ccDefinition
  
The class \ccRefName\ is a model of \ccc{MeshCellCriteria_3}. It provides,
for the  mesh tetrahedra,
 a uniform shape criteria 
and a sizing field which may be a uniform or variable field.

\ccInclude{CGAL/Mesh_cell_criteria_3.h}

\ccParameters
The parameter \ccc{Tr} must be identical to the nested type
\ccc{Triangulation} of the instance used as model of
\ccc{MeshComplex_3InTriangulation_3}.

\ccIsModel
\ccc{MeshCellCriteria_3}


\ccTypes

\ccTypedef{typedef Tr::FT FT;}{Numerical type}

\ccCreation
\ccCreationVariable{mcc}  %% choose variable name

\ccConstructor{Mesh_cell_criteria_3(
  FT radius_edge_bound,
  FT radius_bound);}
{Returns an object to serve as default criteria  for cells. The argument 
\ccc{radius_edge_bound} is the  upper bound for the radius-edge ratio
of the tetrahedra. The argument \ccc{radius_bound} is a uniform upper bound
for the circumradii of the tetrahedra in the mesh. See
section~\ref{introsec:param} for further details.
Note that if one parameter is set to 0, then its corresponding criteria is ignored.}

\ccConstructor{
  template<class SizingField>
  Mesh_cell_criteria_3(
  FT radius_edge_bound,
  SizingField radius_bound);}
{Returns an object to serve as default criteria for facets. The type \ccc{SizingField} must
be a model of the concept \ccc{MeshDomainField_3}. The behavior and semantic of the arguments are the same 
as above, except that the radius bound parameter is a functional instead of a constant.}



\ccSeeAlso

\ccRefConceptPage{MeshCriteria_3} \\
\ccRefConceptPage{MeshCellCriteria_3} \\
\ccRefIdfierPage{Mesh_criteria_3<Tr>} \\
\ccRefIdfierPage{CGAL::make_mesh_3}




\end{ccRefFunctionObjectClass}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+

