% +------------------------------------------------------------------------+
% | Reference manual page: MeshDomainWithFeatures_3.tex
% +------------------------------------------------------------------------+
% | 28.07.2009   Stephane Tayeb
% | Package: Mesh_3
% |
\RCSdef{\RCSMeshDomainWithFeaturesRev}{$Id$}
\RCSdefDate{\RCSMeshDomainWithFeaturesDate}{$Date$}
% |
\ccRefPageBegin
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefConcept}{MeshDomainWithFeatures_3}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries

\ccDefinition
  
The concept \ccRefName\ refines the concept \ccc{MeshDomain_3}. 
While the concept
\ccc{MeshDomain_3} only exposes the 2-dimensional and 3-dimensional features of
the domain through different queries, the concept \ccRefName{} also exposes 0 and
1-dimensional features.  The  exposed features  of the domain are respectively called 
subdomains, surface patches, curve segments 
and corners according to their respective dimensions 3,2,1 and 0.

\ccRefines

\ccc{MeshDomain_3} \\

\ccTypes
\ccTypedef{ typedef CGAL::Tag_true  Has_features;} {A type to distinguish
\ccc{MeshDomain_3} models from \ccc{MeshDomainWithFeatures_3} models.}

\ccNestedType{FT}{Numerical type.}
\ccNestedType{Curve_segment_index}{Type of indices for curve segments ($1$-dimensional features)
  of the input domain.
  Must be a model of CopyConstructible, Assignable, DefaultConstructible and
  LessThanComparable. The default constructed value must be the value of an edge which
  does not approximate a 1-dimensional feature of the input domain.}
%  Each curve should have a starting point and an ending point (which could be
%  the same). This type must also permit to represent the orientation of the curve,
%  i.e. if the curv}
\ccNestedType{Corner_index}{Type of indices for corners (i.e. 0-dimensional features)
  of the input domain.
  Must be a model of CopyConstructible, Assignable, DefaultConstructible and
  LessThanComparable.}



\ccCreationVariable{md}  %% choose variable name

\ccOperations

Each connected component of a curve segment is assumed 
 to be oriented. The orientation is defined by the ordering 
of the two incident corners at the origin and endpoint.
Therefore it is possible
to defined the signed geodesic distance between two ordered
points on the same connected component of a curve segment.
A cycle is a connected component of a curve segment incident to
0 or 1 corner.

\ccMethod{Point_3 construct_point_on_curve_segment(
  const Point_3& p, const Curve_segment_index& ci, FT d) const;}{
  Returns a point on the curve segment with index \ccc{ci}
  at signed geodesic distance \ccc{d} from point \ccc{p}.
\ccPrecond{ Point \ccc{p} is supposed to be on curve segment \ccc{ci}.
 If \ccc{ d > 0}, the signed
  geodesic distance from \ccc{p} to the endpoint
 of the connected  component
of  \ccc{ci} including $p$, should be greater than $d$. 
If \ccc{ d < 0}, the signed
  geodesic distance from \ccc{p} to the origin of the connected component should be 
less than $d$ from the origin of the connected component. }}

Note that \ccc{construct_point_on_curve segment} is assumed to return
a uniquely defined point. Therefore it is not possible to handle as a single 
curve segment,  a singular curve with several branches incident
to the same point.

\ccHeading{Queries}

\ccMethod{FT geodesic_distance(const Point_3& p,
  const Point_3& q, const Curve_segment_index& ci) const;}{Returns the signed geodesic distance
  between points \ccc{p} and \ccc{q} along the input curve segment
  with index \ccc{ci}.
\ccPrecond{Points \ccc{p} and \ccc{q} belong to the same connected
  component
of the curve segment with index \ccc{ci}. }}

%\ccMethod{Curve_segment_index canonicalize(const Curve_segment_index& ci) const;}{
%  Returns the canonical (i.e. unordered) \ccc{Curve_segment_index} associated to \ccc{ci}.}
%\ccGlue
%\ccMethod{Curve_segment_index uncanonicalize(const Point_3& p, const Point_3& q,
%  const Curve_segment_index& ci) const;}{Returns the \ccc{Curve_segment_index} associated
%  to \ccc{ci} ordered from \ccc{p} to \ccc{q}.}
%\ccGlue
%\ccMethod{Curve_segment_index opposite(const Curve_segment_index& ci) const;}{
%  Returns the opposite \ccc{Curve_segment_index} of \ccc{ci}.}

\ccMethod{CGAL::Sign distance_sign_along_cycle(const Point_3& p, const Point_3& q,
  const Point_3& r, const Curve_segment_index& ci) const;}{
  Returns \ccc{CGAL::POSITIVE} if the signed geodesic distance from
  \ccc{p}
to \ccc{q}  on the way through $r$ 
   along cycle with index \ccc{ci}
  is positive, \ccc{CGAL::NEGATIVE} if the distance is negative, and \ccc{CGAL::ZERO} if \ccc{(p = q = r)}.
  \ccPrecond{Points \ccc{p}, \ccc{q} and \ccc{r} belongs to the
 same  connected component of  curve segment \ccc{ci} and this
 component is a cycle.}}
  
  
\ccMethod{bool is_cycle(const Point_3& p, const Curve_segment_index& ci) const;}{
	Returns \ccc{true} if the connected component of curve segment
        \ccc{ci} including point \ccc{p} is a cycle.}

\ccHeading{Retrieval of the input features and their incidences}

\ccMethod{template <typename OutputIterator>
  OutputIterator
  get_corners(OutputIterator corners) const;}{Fills \ccc{corners} with
  the  corners of the
  input domain. \ccc{corners} value type must be \ccc{std::pair<Corner_index,Point_3>}.}

\ccMethod{template <typename OutputIterator>
  OutputIterator
  get_curve_segments(OutputIterator curves) const;}{
  Fills \ccc{curves} with the  curve segments
  of the input domain. 
\ccc{curves} value type must be 
  \ccc{CGAL::cpp0x::tuple<Curve_segment_index,std::pair<Point_3,Index>,std::pair<Point_3,Index> >}.
  If the curve segment  corresponding to an entry
  in curves is not a cycle, the pair of associated points should
  belong to
  two corners  incident on the curve segment.
  If it is a cycle, then the same \ccc{Point_3} should be given twice and must be any
  point on the cycle.
  The \ccc{Index} values associated to the points are their indices w.r.t. their dimension.}

%\ccMethod{template <typename OutputIterator>
%  OutputIterator
%  incident_curve_segments(const Point_3& p, OutputIterator curves) const;}{
%  Fills \ccc{curves} with the 
%  curve segments  of the input domain incident to corner \ccc{p}. 
%It also returns the ending corner, named
%  \ccc{q}, of each curve segment(\ccc{p} is considered as the starting point). \ccc{curves} value type 
%  should be \ccc{std::pair<Curve_segment_index,Point_3>}.
%  \ccPrecond{\ccc{p} is a corner of the input domain.}}

\ccMethod{bool are_incident_surface_patch_curve_segment(Surface_patch_index spi, Curve_segment_index csi);}
{Returns \ccc{true} if the curve segment with index \ccc{csi} is incident to the surface patch with index \ccc{spi}.}

\ccMethod{bool are_incident_surface_patch_corner(Surface_patch_index spi, Corner_index ci);}
{Returns \ccc{true} if the corner with index \ccc{ci} is incident to the surface patch with index \ccc{spi}.}


\ccHeading{Indices converters}

\ccMethod{Index index_from_curve_segment_index(const Curve_segment_index& curve_segment_index) const;}{
  Returns the index to be stored at a vertex lying on the curve segment identified
  by \ccc{curve_segment_index}.}
\ccGlue
\ccMethod{Curve_segment_index curve_segment_index(const Index& index) const;}{
  Returns the \ccc{Curve_segment_index} of the curve segment where lies a vertex with
  dimension 1 and index \ccc{index}.}

\ccMethod{Index index_from_corner_index(const Corner_index& corner_index) const;}{
  Returns the index to be stored at a vertex lying on the corner identified
  by \ccc{corner_index}.}
\ccGlue
\ccMethod{Corner_index corner_index(const Index& index) const;}{
  Returns the \ccc{Corner_index} of the corner where lies a vertex with
  dimension 0 and index \ccc{index}.} 


\ccHasModels

\ccc{Mesh_domain_with_polyline_features_3<MeshDomain_3>} \\
\ccc{Polyhedral_mesh_domain_with_features_3<IGT>}

\ccSeeAlso

\ccRefConceptPage{MeshDomain_3}

\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+

