% +------------------------------------------------------------------------+
% | Reference manual page: Mesh_constant_domain_field_3.tex
% +------------------------------------------------------------------------+
% | 28.07.2009   Stephane Tayeb
% | Package: Mesh_3
% |
\RCSdef{\RCSMeshconstantdomainfieldRev}{$Id$}
\RCSdefDate{\RCSMeshconstantdomainfieldDate}{$Date$}
% |
\ccRefPageBegin
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefFunctionObjectClass}{Mesh_constant_domain_field_3<Gt,Index>}  %% add template arg's if necessary

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[class]{} %% add further index entries

\ccDefinition
  
The class \ccRefName\ is a model of concept \ccc{MeshDomainField_3}. It provides
a constant field accessible using queries on 3D-points.

The class \ccRefName\ can also be customized through \ccc{set_size()} operations to become
a piecewise constant field, i.e. a sizing field with a constant size on each subpart
of the domain.


\ccInclude{CGAL/Mesh_constant_domain_field_3.h}

\ccParameters

The parameter \ccc{Gt} is the geometric traits class. It must match the type \ccc{Triangulation::Geom_traits},
where \ccc{Triangulation} is the nested type of the model of \ccc{MeshComplex_3InTriangulation_3} used
in the meshing process.

The parameter \ccc{Index} is the type of index of the vertices of the triangulation.
It must match the type \ccc{Index} of the model of \ccc{MeshDomain_3} used in the meshing process.

\ccIsModel

\ccc{MeshDomainField_3}

\ccTypes

\ccTypedef{typedef Gt::FT FT;}{Numerical type.}\ccGlue
\ccTypedef{typedef Gt::Point_3 Point_3;}{Point type.}
\ccTypedef{typedef Index Index;}{Type of index of the vertices of the triangulation.}

\ccCreation
\ccCreationVariable{mcf}  %% choose variable name

\ccConstructor{Mesh_constant_domain_field_3(FT size);}{
Builds a constant domain field with size \ccc{size}.}

\ccOperations
\ccMethod{void set_size(FT size, int dimension, const Index& index);}{
  Sets the size such as \ccc{operator()} will return size \ccc{size}
  at any query point of dimension \ccc{dimension} and index \ccc{index}.}


\ccSeeAlso

\ccRefConceptPage{MeshDomainField_3} \\

\end{ccRefFunctionObjectClass}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+

