% +------------------------------------------------------------------------+
% | Reference manual page: MeshCellCriteria_3.tex
% +------------------------------------------------------------------------+
% | 13.02.2009   Author
% | Package: Mesh_3
% |
\RCSdef{\RCSMeshCellCriteriaRev}{$Id: MeshCellsCriteria_3.tex 49286 2009-05-11 12:42:33Z lrineau $}
\RCSdefDate{\RCSMeshCellCriteriaDate}{$Date: 2009-05-11 14:42:33 +0200 (Mon, 11 May 2009) $}
% |
\ccRefPageBegin
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefFunctionObjectConcept}{MeshCellCriteria_3}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries

\ccDefinition
  
The Delaunay refinement process involved in the 
template functions \ccc{make_mesh_3} and \ccc{refine_mesh_3}
is guided by a set of elementary refinement criteria
that concern either mesh tetrahedra or surface facets.
The concept \ccRefName\ describes the types  that
handle the refinement criteria for mesh  tetrahedra.


\ccTypes

\ccNestedType{Cell_handle}{Handle type for the cells of the
  triangulation. Must match the \ccc{Cell_handle} type in the
  triangulation type used by the mesh generation function.}

\ccNestedType{Cell_quality}{Type representing the quality of a
  cell. Must be a model of CopyConstructible and
  LessThanComparable. Between two cells, the one which has the lower
  quality must have the lower \ccc{Cell_quality}.}

\ccNestedType{Is_cell_bad}{Type representing if a cell is bad or not. Must
be convertible to \ccc{bool}. If it converts to \ccc{true} then the cell is bad, otherwise
the cell is good with regard to the criteria.

In addition, an object of this type must contain an object of type
\ccc{Cell_quality} if it represents
a bad cell. \ccc{Cell_quality} must be accessible by \ccc{operator*()}.
Note that \ccc{boost::optional<Cell_quality>} is a natural model of this concept.}% boost::optional


\ccCreationVariable{cell_criteria}

\ccOperations


\ccMethod{Cell_badness operator()(Cell_handle c);}
{Returns \ccc{Cell_badness} value of cell \ccc{c}.}


\ccHasModels
\ccc{Mesh_cell_criteria_3<Tr>}

\ccSeeAlso
\ccRefConceptPage{MeshEdgeCriteria_3}\\
\ccRefConceptPage{MeshFacetCriteria_3}\\
\ccRefConceptPage{MeshCriteria_3} \\
\ccRefIdfierPage{CGAL::make_mesh_3} \\
\ccRefIdfierPage{CGAL::refine_mesh_3}\\


\end{ccRefFunctionObjectConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+

