% +------------------------------------------------------------------------+
% | Reference manual page: ArrangementTraits.tex
% +------------------------------------------------------------------------+
% | 
% | Package: Arrangement_2
% | 
% +------------------------------------------------------------------------+

\ccRefPageBegin

\begin{ccRefConcept}{ArrangementTraits_2}

\ccDefinition

The refined arrangement-traits concept allows the construction of arrangement
of {\sl general} planar curves. Models of this concept are used
by the free \ccc{insert()} functions of the arrangement package and
by the \ccc{Arrangement_with_history_2} class.

A model of this concept must define nested \ccc{Curve_2} types, which
represents a general planar curve that is not necessarily $x$-monotone
and not necessarily connected. Such curves are eventually subdivided into
$x$-monotone subcurves and isolated points (represented by the \ccc{Point_2}
and \ccc{X_monotone_curve_2} types, defined in the basic traits concept).

\ccRefines
\ccc{ArrangementXMonotoneTraits_2}

\ccTypes
%=======

\ccNestedType{Curve_2}{represents a general planar curve.}

\ccHeading{Functor Types}
%========================

\ccThree{Compare_y_at_x_2~~~}{}{\hspace*{12cm}}
\ccThreeToTwo

\ccNestedType{Make_x_monotone_2}
{provides the operator (templated by the \ccc{OutputIterator} type)~: \\
 \ccc{OutputIterator operator() (Curve_2 c, OutputIterator oi)} \\
 which subdivides the input curve \ccc{c} into $x$-monotone subcurves and
 isolated points, and outputs the results using the output iterator.
 The value-type of \ccc{OutputIterator} is \ccc{CGAL::Object}, where each
 \ccc{Object} either wraps an \ccc{X_monotone_curve_2} instance or a
 \ccc{Point_2} instance. The operator returns a past-the-end iterator
 for the output sequence.}

\ccCreation
\ccCreationVariable{traits}
%==========================

\ccThree{Construct_x_monotone_curve_2~~~}{}{\hspace*{7cm}}
\ccThreeToTwo

\ccConstructor{ArrangementTraits_2();}{default constructor.}
\ccGlue
\ccConstructor{ArrangementTraits_2(ArrangementTraits_2 other);}
{copy constructor}
\ccGlue
\ccMethod{ArrangementTraits_2  operator=(other);}{assignment operator.}


\ccHeading{Accessing Functor Objects}
%====================================

\ccMethod{Make_x_monotone_2 make_x_monotone_2_object();} {}

\ccHasModels
%===========

\ccc{CGAL::Arr_segment_traits_2<Kernel>} \\
\ccc{CGAL::Arr_non_caching_segment_traits_2<Kernel>} \\
\ccc{CGAL::Arr_polyine_traits_2<SegmentTraits>} \\
\ccc{CGAL::Arr_conic_traits_2<RatKernel,AlgKernel,NtTraits>} \\
\ccc{CGAL::Arr_rational_arc_traits_2<AlgKernel,NtTraits>} \\

\ccSeeAlso
%=========

\ccc{ArrangementBasicTraits_2}\lcTex{ 
      (\ccRefPage{ArrangementBasicTraits_2})} \\
\ccc{ArrangementXMonotoneTraits_2}\lcTex{ 
      (\ccRefPage{ArrangementXMonotoneTraits_2})}

\end{ccRefConcept}

\ccRefPageEnd
