% +------------------------------------------------------------------------+
% | Reference manual page: Arr_dcel_base.tex
% +------------------------------------------------------------------------+
% | 
% | Package: Arrangement_2
% | 
% +------------------------------------------------------------------------+

\ccRefPageBegin

\begin{ccRefClass}{Arr_dcel_base<V,H,F>}
\label{arr_ref:arr_dcel_base}
    
\ccDefinition
%============

The base \dcel\ class for instatiating the \ccc{Arrangement_2} template.
The \ccClassTemplateName\ serves as a basis for extending the basic vertex,
halfedge or face types and attaching auxiliary data to them.

\ccInclude{CGAL/Arr_dcel_base.h}
 
\ccIsModel
    \ccc{ArrangementDcel}

\end{ccRefClass}

%--------------------------------------------------------------------------

\begin{ccRefClass}{Arr_vertex_base<Point>}
\label{arr_ref:arr_vertex_base}

\ccDefinition
%============

The basic \dcel\ vertex type. Serves as a basis for extending the basic
vertex record with auxiliary data fields. The \ccc{Point} parameter is used
to instantiate the type of points associated with the vertices.

\ccIsModel
    \ccc{ArrangementDcelVertex}

\end{ccRefClass}

%--------------------------------------------------------------------------

\begin{ccRefClass}{Arr_halfedge_base<Curve>}
\label{arr_ref:arr_halfedge_base}

\ccDefinition
%============

The basic \dcel\ halfedge type. Serves as a basis for extending the basic
halfedge record with auxiliary data fields. The \ccc{Curve} parameter is used
to instantiate the type of $x$-monotone curves associated with the vertices.

\ccIsModel
    \ccc{ArrangementDcelHalfedge}

\end{ccRefClass}

%--------------------------------------------------------------------------

\begin{ccRefClass}{Arr_face_base}
\label{arr_ref:arr_face_base}

\ccDefinition
%============

The basic \dcel\ face type. Serves as a basis for extending the basic
face record with auxiliary data fields.

\ccIsModel
    \ccc{ArrangementDcelFace}

\end{ccRefClass}

\ccRefPageEnd
