% +------------------------------------------------------------------------+
% | Reference manual page: Arr_dcel_vertex.tex
% +------------------------------------------------------------------------+
% | 
% | Package: Arrangement_2
% | 
% +------------------------------------------------------------------------+

\ccRefPageBegin

\begin{ccRefConcept}{ArrangementDcelVertex}

\ccDefinition

A vertex record in a \dcel\ data structure. A vertex is always associated
with a point. However, the vertex record only sotres a pointer to the
associated point, and the actual \ccc{Point} object is stored elsewhere.

\ccCreationVariable{v}

\ccTypes
%=======

\ccNestedType{Halfedge}{the corresponding \dcel\ halfedge type.}
\ccGlue
\ccNestedType{Face}{the corresponding \dcel\ face type.}

\ccNestedType{Point}{the point type associated with the vertex.} 

\ccCreation
%==========

\ccConstructor{Arr_dcel_vertex();}
   {default constructor.}

\ccMethod{void assign (const Self& other);}
   {assigns \ccVar{} with the contents of the \ccc{other} vertex.}

\ccHtmlNoLinksFrom{   % to avoid linkage of Vertex, etc to HDS::Vertex

\ccAccessFunctions
%=================

All functions below also have \ccc{const} counterparts, returning non-mutable
pointers or references:

\ccMethod{bool is_isolated() const;}
    {returns whether the vertex is isolated (has no incident halfedges).}

\ccMethod{Halfedge* halfedge();}
    {returns an incident halfedge that has \ccVar{} as its target.
     \ccPrecond{\ccVar{} is {\em not} an isolated vertex.}}

\ccMethod{Face* face();}
    {returns the face that conatins \ccVar{} in its interior.
     \ccPrecond{\ccVar{} is an isolated vertex.}}

\ccMethod{Point& point();}
    {returns the associated point.}

\ccModifiers
%===========

\ccMethod{void set_halfedge (Halfedge* e);}
    {sets the incident halfedge, marking \ccVar{} as a regular vertex.}

\ccMethod{void set_face (Face* f);}
    {sets the face that contains \ccVar{} in its interior, marking \ccVar{}
     as an isolated vertex.}

\ccMethod{void set_point (Point* p);}
    {sets the associated point.}

} % ccHtmlNoLinksFrom

\ccSeeAlso

\ccc{ArrangementDcel}\lcTex{ 
     (\ccRefPage{ArrangementDcel})}\\
\ccc{ArrangementDcelHalfedge}\lcTex{
     (\ccRefPage{ArrangementDcelHalfedge})}\\
\ccc{ArrangementDcelFace}\lcTex{
     (\ccRefPage{ArrangementDcelFace})}

\end{ccRefConcept}  

\ccRefPageEnd

