% +------------------------------------------------------------------------+
% | Reference manual page: Object_color_map.tex
% +------------------------------------------------------------------------+
% | 
% | Package: Arrangement_2
% | 
% +------------------------------------------------------------------------+

\ccRefPageBegin

\begin{ccRefClass}{Object_color_map<Handle>}
    
\ccDefinition
%============

The class implements the \boost\ \ccc{ReadWritePropertyMap} concept for 
\cgal\ handles to returnstore and retrieve a value of type 
\ccc{boost::default_color_type} given a handle refferencing some object. The 
color is stored or retrieved directly from the refferenced object.

The \ccClassTemplateName\ template has is parameterized with
the \ccc{Handle} template-parameter. It should be instantiated with
a class that is a handle to the colored object.

The object refferenced by the handle must have these two functions:
\begin{itemize}
\item data() --- return a value of type \ccc{boost::default_color_type} that 
is the color of the object.
\item \ccc{set_data(boost::default_color_type)} --- set the color of the 
object.
\end{itemize}

This object can be used in conjunction with the \ccc{Arr_face_graph_adator}
to utilize various \boost\ algorithms, such as BFS and DFS, and
apply them on \ccc{Arrangement_2} instances.

\ccInclude{CGAL/Object_color_map.h}

\ccCreation
\ccCreationVariable{arr}
%=======================
    
\ccConstructor{Object_color_map();}
    {default constructor.}
    
\ccAccessFunctions
%=================

\ccMethod{boost::default_color_type get(Handle handle) const;}
    {returns the color of the object refferenced by the given handle.}
    
\ccModifiers
%===========

\ccMethod{void put(Handle& handle, const boost::default_color_type &color);}
   {sets the given color to be the color of the object refferenced by the 
handle.}
    
\ccSeeAlso
    \ccc{Arr_face_graph_adator}\lcTex{ 
      (\ccRefPage{Arr_face_graph_adator})}

\end{ccRefClass}

\ccRefPageEnd
