% +------------------------------------------------------------------------+
% | Reference manual page: Fair.tex
% +------------------------------------------------------------------------+
% | 1.07.2001   Johan W.H. Tangelder
% | Package: ASPAS
% | 
\RCSdef{\RCSFairRev}{$Revision$}
\RCSdefDate{\RCSFairDate}{$Date$}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefFunctionObjectClass}{Fair<PointTraits, PointContainer, SpatialSeparator>}  %% add template arg's if necessary

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[class]{} %% add further index entries

\ccDefinition
Implements the {\bf fair} splitting rule.  

\ccParameters

Expects for the first template argument a model of
the concept \ccc{SpatialPoint}, 
for example \ccc{CGAL::Kd_tree_traits_point_d< Cartesian_d<double> >}. 

Expects for the second argument a model of the concept \ccc{PointContainer}. 
It has as default value the type \ccc{CGAL::Point_container<PointTraits>}.

Expects for the third template argument a model of the concept \ccc{Separator}. 
It has as default value the type, \ccc{CGAL::Plane_separator<PointTraits::NT>}.

\ccInclude{CGAL/Splitters.h}

\ccInheritsFrom \ccc{CGAL::Splitter_base}

\ccIsModel

Splitter

\ccTypes

\ccTypedef{PointTraits::NT NT;}{Number type.} 
\ccTypedef{PointContainer Container;}{Point container.}
\ccTypedef{SpatialSeparator Separator;}{Separator.}

\ccCreationVariable{s}  %% choose variable name

\ccConstructor{Fair();}{Default constructor.}
\ccConstructor{ Fair(unsigned int bucket_size, 
                     NT aspect_ratio=NT(3))}{Constructor.}

\ccOperations

\ccMethod{
void operator()(Separator& s, Container& c0, Container& c1);} 
{Modifies the separator $s$ by the fair splitting rule, 
and splits \ccc{c0} into \ccc{c0} and \ccc{c1},
using the splitting dimension and the splitting value of the modified separator.}

\ccSeeAlso

Splitter, PointContainer, SpatialSeparator.

\end{ccRefFunctionObjectClass}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

