% +------------------------------------------------------------------------+
% | Reference manual page: General_priority_search::iterator.tex
% +------------------------------------------------------------------------+
% | 1.07.2001   Johan W.H. Tangelder
% | Package: ASPAS
% |
\RCSdef{\RCSGeneralprioritysearch::iteratorRev}{$Revision$}
\RCSdefDate{\RCSGeneralprioritysearch::iteratorDate}{$Date$}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefClass}{General_priority_search<Traits, Query_item, Distance>::iterator}  %% add template arg's if necessary

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[class]{} %% add further index entries

\ccDefinition

The class \ccRefName\ implements an input iterator
for the computation of approximate neighbours.

\ccInclude{CGAL/Priority_search.h}

\ccParameters

Expects for the parameter \ccc{Traits} an implementation of the concept TreeTraits.
Expects for the parameter \ccc{Query_item}  an implementation of the
\ccc{Point} concept, for example \ccc{CGAL::Point_d}.
or an implementation of aspatial object, for
example \ccc{Kd_tree_rectangle} implementing iso-rectangles.
Expects for the parameter \ccc{Distance} an implementation of the concept OrthogonalDistance if extended
nodes are used. Otherwise it expects for the parameter \ccc{Distance} an implementation of the
concept GeneralDistance.

\ccCreation
\ccCreationVariable{i}  %% choose variable name

\ccConstructor{iterator();}{Default constructor. Constructs an past-the-end iterator.}
\ccConstructor{iterator(iterator& Iter);}{Copy constructor.}
\ccConstructor{iterator(Tree& tree, Item& q, Traits tr, Distance& d, int k, NT Eps,
bool Search_nearest=true);}
{Creates an iterator for searching approximately neighbours of the query item \ccc{q}
in the items stored in the $k$-$d$ tree \ccc{tree}.}

\ccHeading{Member Functions}

\ccMethod{Item_with_distance* operator*();}
{Returns a pointer to the pair consisting of the next neighbour and its distance
to the query item.}

\ccMethod{
iterator& operator++();}
{Prefix operator.}

\ccMethod{
std::auto_ptr<Item_with_distance> iterator& operator++(int);}
{Postfix operator.}

\ccMethod{
bool operator==(const iterator& It);}
{The equality operator.}

\ccMethod{
bool operator!=(const iterator& It);}
{The inequality operator.}

{\bf Non-Member functions related to \ccc{General_priority_search<Traits,Query_item,Distance>::iterator}}

\ccGlueBegin
\ccGlobalFunction{ template <class Traits, Query_item, Distance>
void swap(General_priority_search<Traits, Query_item, Distance>::iterator& x,
General_priority_search<Traits, Query_item, Distance>::iterator& y);}
{Swaps the contents of \ccc{x} and \ccc{y}.}
\ccGlueEnd

\ccSeeAlso

\ccc{General_priority_search}.


\end{ccRefClass}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

