\RCSdef{\RCSSurfaceMeshEdgesCriteriaRev}{$Id$}
\RCSdefDate{\RCSSurfaceMeshEdgesCriteriaDate}{$Date$}

\begin{ccRefConcept}{PiecewiseSmoothSurfaceMeshEdgesCriteria_3}

\ccDefinition
  
The Delaunay refinement process involved in the 
function template \ccc{make_piecewise_smooth_surface_mesh} 
is guided by a set of refinement criteria.
The concept \ccRefName\ describes the type  which
handles the criteria that apply to the marked edges of the 2D
complex. Those marked edges are a 1D mesh corresponding to the 1D curves of
a piecewise smooth surface.

The concept \ccRefName\ corresponds to the requirements for the template
parameter \ccc{EdgesCriteria} of the piecewise smooth surface mesher function
\ccc{make_piecewise_smooth_surface_mesh<SurfaceMeshC2T3,Surface,FacetsCriteria,
  EdgesCriteria,Tag>}.

Typically the meshing criteria are a set
of elementary criteria, each of which
has to be met by  the marked edges of the final mesh.
The meshing algorithm eliminates in turn  {\em bad} edges, i.e.,
marked edges that do not meet all the criteria.

\ccTypes

\ccNestedType{Edge}{The type of edges. This type has to match
the \ccc{Edge} type in  the triangulation type used  by 
the mesher function. (This triangulation type
is the type \ccc{SurfaceMeshC2T3::Triangulation} 
provided by the model of
\ccc{PiecewiseSmoothSurfaceMeshComplex_2InTriangulation_3} plugged 
 as first template parameter of
 \ccc{make_piecewise_smooth_surface_mesh}).}

\ccNestedType{Point_3}{The type of points. This has to match the
  \ccc{Point} type of the underlying triangulation as well.}

\ccOperations
\ccCreationVariable{criteria}

\ccMethod{bool is_bad (const Edge& e, const Point_3& p);}
{Returns \ccc{true} is \ccc{e} does not meet the criteria. \ccc{p} is the
  point that is candidate for insertion if \ccc{e} is to be eliminated.}

\ccHasModels

\ccc{Piecewise_smooth_surface_mesh_default_edges_criteria_3<Tr>}

\ccSeeAlso
\ccc{make_piecewise_smooth_surface_mesh<SurfaceMeshC2T3,Surface,FacetsCriteria,
  EdgesCriteria,Tag>}


\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

