% +------------------------------------------------------------------------+
% | Reference manual page: LinearCellComplexTraits.tex
% +------------------------------------------------------------------------+
% | 04.02.2010   Guillaume Damiand
% | Package: Combinatorial_map
% +------------------------------------------------------------------------+
\ccRefPageBegin
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+

\begin{ccRefConcept}{LinearCellComplexTraits}

Required types and functors for the \ccRefName\ concept. This
geometric traits concept is used in the \ccc{Linear_cell_complex}
class.  

% \ccRefines
% A model of the concept \ccc{Kernel} if \ccc{Ambiant_dimension==2} or 
% \ccc{Ambiant_dimension==3}; a model of the concept \ccc{Kernel_d} otherwise.

% \ccc{CopyConstructable}, \ccc{Assignable}.

\ccConstants
\ccVariable{static unsigned int ambient_dimension;}
{The ambient dimension, must be \mygt{}1.}

\ccTypes

% \ccNestedType{Kernel}{kernel type.}

\ccNestedType{FT}{a number type that is a model of FieldNumberType.}
\ccGlue
\ccNestedType{Point}{point type.}
\ccGlue
\ccNestedType{Vector}{vector type.}
\ccGlue
\ccNestedType{Direction}{direction type.}
% \ccGlue
% \ccNestedType{Iso_cuboid}{iso cuboid type.}

\ccHeading{Constructions}

\ccNestedType{Construct_translated_point}{Functor with operator to construct the translation of a Point by a given Vector.}
\ccGlue
\ccNestedType{Construct_vector}{Functor with operator to construct a vector going from the origin (given by \ccc{CGAL::Origin}) to a given point.}
\ccGlue
\ccNestedType{Construct_vector}{Functor with operator to construct a vector as the difference of two given points.}
\ccGlue
\ccNestedType{Construct_sum_of_vectors}{Functor with operator to construct a vector wich is the sum of the two given vectors.}
\ccGlue
\ccNestedType{Construct_scaled_vector}{Functor with operator to construct a vector which is equal to a given Vector scaled by a given number.}
\ccGlue
\ccNestedType{Construct_midpoint}{Functor with operator to construct a point equal to the midpoint of the two given points.}
\ccGlue
\ccNestedType{Construct_direction}{Functor with operator returning a direction corresponding to the given vector.}

% \ccGlue
% \ccNestedType{Construct_iso_cuboid}{Functor with operator returning an iso cuboid created from two points (min and max points of the iso cuboid).}

\ccHeading{Generalized Predicates}

\ccNestedType{Collinear}{Functor with operator returning true iff the three given points are collinear.}

\textbf{If \ccc{ambient_dimension==3}}

\ccTypes
\ccNestedType{Construct_normal_3}{a model of \ccc{ConstructNormal_3}}

\ccHasModels

\ccRefIdfierPage{CGAL::Linear_cell_complex_traits<d,K>}.

\ccSeeAlso

\ccRefIdfierPage{CGAL::Linear_cell_complex<d,d2,Traits_,Items_,Alloc_>}\\
%\ccRefConceptPage{LinearCellComplex}\\
\ccRefConceptPage{LinearCellComplexItems}\\

\end{ccRefConcept}
% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+

