\documentclass[a4paper,10pt]{article}
\usepackage[scale=0.7,vmarginratio={1:2},heightrounded]{geometry}

\usepackage{doc-setting}


\title{Arrangement of Polylines Traits Class - Upgrade}
\author{Dror Atariah}

\begin{document}
\maketitle

\begin{abstract}
  Outline the projects goals and progress.
\end{abstract}

\begin{queframe}
  Its seems like the out put of computation of an arrangement is very sensitive to the input.
  For example, consider the vertices \(p_1 = (0,2), p_2 = (-1,-1)\) and \(p_3 = (1,-1)\).
  The optimal result would be one vertex, one edge and two cells.
  In this case, the triangle defined by \(\overline{p_2 p_1 p_3 p_2}\) yields \((2,2,2)\) as the \(f\)-vector.
  However, the triangle \(\overline{p_1 p_2 p_3 p_1}\) yields the \(f\)-vector \((3,3,2)\).
  Note that the number of face is correct, but the other elements of the vector are not stable.
  Is this the expected behavior?
  Can it be improved?
  Is \((1,1,2)\) the ``real'' or ``optimal'' answer?
\end{queframe}


\section{Definitions}
\label{sec:definitions}

In this document we use the following conventions:
\begin{itemize}
%
\item \href{http://doc.cgal.org/4.2/CGAL.CGAL.2D-Arrangements/html/classCGAL_1_1Arr__polyline__traits__2.html}{\polytr} is the polyline traits class which currently models the following concepts:
  \begin{itemize}
  \item \concept{ArrangementTraits\_2}
  \item \concept{ArrangementLandmarkTraits\_2}
  \end{itemize}
  Its implementation can be found in \file{Arr\_polyline\_traits\_2.h}.
  This traits class has two nested types \poly and \xpoly which are the \type{Curve\_2} and \type{X\_monotone\_curve\_2} of the traits class.
  These curves are the representations of piecewise linear (PL) curves and x-monotone PL curves respectively.
  Together, \polytr is the component of the arrangement on surfaces package of \cgal which handles the construction and computations of arrangements of  sets of polylines.
  The actual implementations of \poly and \xpoly can be found in \file{Polyline\_2.h}.
%
\item \segtr is substituting the template parameter when instantiating \polytr and it should be a model of \concept{ArrangementTraits\_2}.
  In practice, currently, there are two implementations of segment traits classes that can be used
  \begin{itemize}
  \item \model{Arr\_segment\_traits\_2}
  \item \model{Arr\_non\_caching\_segment\_traits\_2}
  \end{itemize}
  In both cases \segtr is the traits class of segments (that is finite, linear segments), and they model the concepts:
  \begin{itemize}
  \item \concept{ArrangementTraits\_2}
  \item \concept{ArrangementLandmarkTraits\_2}
  \item \concept{ArrangementDirectionalXMonotoneTraits\_2}
  \end{itemize}
  The first one, for example, is implemented in \file{Arr\_segment\_traits\_2.h}.
  Let \seg be the \type{Curve\_2} and \type{X\_monotone\_curve\_2} types that are nested in \segtr.
\end{itemize}

\section{Implementation of \poly and \xpoly}
\label{sec:implementation-poly}

The implementations of \poly and \xpoly are the building blocks of the polyline traits class and the way we could compute arrangement of polylines.
In particular, this implementation has to be revised in order to support the computation of arrangements of unbounded polylines as well.
Furthermore, the code implementing these two classes is rather old and no longer meets the standards of \cgal.
In this section we shall list the elements of the implementation that have to be modified/updated/corrected/etc.

\subsection{Design and General Issues}
\label{sec:design-gener-issu-poly}

\begin{itemize}
\item Forbid the construction of degenerated \poly's and \xpoly's.
  Here \emph{degenerated} means that the polyline cannot reduce to an isolated vertex nor can it contain degenerated \seg's.
\item In general the segments of a given polyline may not be oriented, they merely have to concatenate properly and form a PL curve.
  \begin{center}
    \begin{tikzpicture}
      \begin{scope}[thick,decoration={%
          markings,
          mark=at position 0.5 with {\arrow{>}}%
        }]
        \draw[postaction={decorate}] (-2,0) coordinate (a1) -- (-1,1) coordinate (a2);
        \draw[postaction={decorate}] (0,0) coordinate (a3) -- (a2);
        \draw[postaction={decorate}] (1,1) coordinate (a4) -- (a3);
        \draw[postaction={decorate}] (a4) -- (-0.25,0.75) coordinate (a5);
        \foreach \i in {1,2,3,4,5}
        \fill (a\i) circle (2pt);
      \end{scope}
    \end{tikzpicture}
  \end{center}
  In turn, this means that ideally the \seg's constituting a \poly may not be oriented, or in other words that the \segtr may not provide the notion of neither \emph{source} nor \emph{target} nor any equivalent notion of the constituting \seg's.
  However the current implementation of \polytr and its \poly and \xpoly nested types uses the functions \code{source()} and \code{target()} which are provided by \segtr.
  But these functions are \emph{not} defined by any of the concepts that \segtr models.
  As the existing implementations of \segtr's models the concept \concept{ArrangementDirectionalXMonotoneTraits\_2} we can mimic functions like \code{source()} and \code{target()} using a combination of
  \begin{itemize}
  \item \functor{Construct\_min\_vertex\_2}
  \item \functor{Construct\_max\_vertex\_2}
  \end{itemize}
  which are provided by \concept{ArrangementTraits\_2}, and by the functors
  \begin{itemize}
  \item \functor{Compare\_endpoints\_xy\_2}
  \item \functor{Construct\_opposite\_2}
  \end{itemize}
  which are provided by \concept{ArrangementDirectionalXMonotoneTraits\_2}.

  In order to keep the efficiency benefits of the usage of \code{source()} and \code{target()} on one hand and consistency with the documentation on the other, \textbf{{we add a requirement that \segtr should be model of the \concept{ArrangementDirectionalXMonotoneTraits\_2}.}}
  Once \segtr models this concept we can remove all occurrences of \code{source()} and \code{target()}.
  Note that this assumption implies only a conceptual restriction, since in practice the available implementations that can be used models this concept anyway.
  In this case we also assert that \polytr itself will be a model of this concept.

  As a result, we can also provide the following invariant: \textbf{\poly and \xpoly will be \emph{well oriented}.}\marginpar{\footnotesize{\emph{well oriented}}}
  That is, the \emph{source} of the \(n\)-th \seg should be the \emph{target} of the \((n-1)\)-th \seg.
  In particular the polyline plotted above could be either of the following:
  \begin{center}
    \begin{tikzpicture}
      \begin{scope}[thick,decoration={%
          markings,
          mark=at position 0.5 with {\arrow{>}}%
        }]
        \coordinate (a1) at (-2,0);
        \coordinate (a2) at (-1,1);
        \coordinate (a3) at (0,0);
        \coordinate (a4) at (1,1);
        \coordinate (a5) at (-0.25,0.75);
        \draw[postaction={decorate}] (a1) -- (a2);
        \draw[postaction={decorate}] (a2) -- (a3);
        \draw[postaction={decorate}] (a3) -- (a4);
        \draw[postaction={decorate}] (a4) -- (a5);
        \foreach \i in {1,2,3,4,5}
        \fill (a\i) circle (2pt);
      \end{scope}
      %
      \begin{scope}[xshift=4cm,thick,decoration={%
          markings,
          mark=at position 0.5 with {\arrow{>}}%
        }]
        \coordinate (a1) at (-2,0);
        \coordinate (a2) at (-1,1);
        \coordinate (a3) at (0,0);
        \coordinate (a4) at (1,1);
        \coordinate (a5) at (-0.25,0.75);
        \draw[postaction={decorate}] (a2) -- (a1);
        \draw[postaction={decorate}] (a3) -- (a2);
        \draw[postaction={decorate}] (a4) -- (a3);
        \draw[postaction={decorate}] (a5) -- (a4);
        \foreach \i in {1,2,3,4,5}
        \fill (a\i) circle (2pt);
      \end{scope}
    \end{tikzpicture}
  \end{center}
  and only one of them!
  %

  An \xpoly is x-monotone regardless of its representation.
  X-monotonicity is determined by the geometrical image of the polyline, and not by its internal representation.
  Currently, an \xpoly maintains a \emph{direction invariant}\marginpar{\footnotesize{\emph{direction invariant}}} that it is oriented \emph{left-to-right}.
  That is, its vertices should be given in an increasing lexicographic order.
  However, in general an \xpoly should merely be x-monotone, and its vertices (or segments) may be oriented from left-to-right \emph{or} from right-to-left.
  %
  \begin{queframe}
    What about \xpoly?
    \begin{itemize}
    \item Given our assumption that \segtr models \concept{ArrangementDirectionalXMonotoneTraits\_2}, an \xpoly should be well oriented just like the general \poly.
      Should it also be directed from \emph{left-to-right}?
      Is this decision depends on what \segtr models?
      Does there any connection exists between a direction invariant of \xpoly and the concepts modeled by \segtr?
    \item In general, obviously this should not be the case (see above).
      Actually, it make sense not to have this invariant just like the segments themselves are not maintaining a similar invariant.
    \end{itemize}
  \end{queframe}

\begin{queframe}
  Is there some concept in the package which provides source and target?
  Maybe as functors?
\end{queframe}
%
\begin{queframe}
  Why using the \functor{Compare\_xy\_2} from \segtr and not the global function \code{CGAL::compare\_xy} (when comparing points of course)?
\end{queframe}

\item According to \cgal's style there should be no instances of usage of functors from traits classes (also if they occur in \emph{pre-condition} code) inside \poly and \xpoly.
In particular, remove all calls to construction of functors from the traits class.
%
\item Method of accessing the \seg's of a \poly: Currently the \code{operator[]} is used to access the segments of a given polygon.
\begin{queframe}
  Do we want to change this method?
\end{queframe}
\item Name-spaces changes\todo{TBA}.
\end{itemize}

\subsection{Construction and Iteration}
\label{sec:constr+iter-poly}

Currently in \file{Polyline\_2.h} the implementation of the \poly{'s} is \emph{relaying on their vertices}.
The possible constructors get as inputs ranges of \emph{points}.
Furthermore, given either a \poly or \xpoly, it is only possible to iterate over its vertices.
There is no way to iterate over its constituting \seg{'s}.
This design limits the possibilities of extending the traits class' support, for example handling unbounded polylines.

\paragraph{Has to be done:}
\subparagraph{Construction.}
In order to enable construction of unbounded polylines, we have to add the possibility of construction from ranges of \seg's.
Ultimately, there will be \emph{only} one constructor of either \poly's or \xpoly's.
This construction will construct the polyline \emph{only} from ranges of \seg's.
For the sake of backwards compatibility, the current constructor, namely the one from a range of points, will be kept as deprecated\footnote{In the next version it will be removed completely.}.

The user should be encouraged to use the construction functors from \polytr (see \cref{sec:constr-funct-polytr}) and not the direct constructor of the class.
The functors provide the construction from two points, one segment, range of points and range of segments.

\subparagraph{Iteration.}
As we pointed out, iteration over the vertices of the polyline is restrictive.
We thus replace the iterators over the vertices which are currently defined in \poly with iterators over the segments of the \poly.
The iterators over the segments are obtained directly from the container of the \seg's in \poly.

\subsection{Augmenting a polyline}
\label{sec:augmenting-poly}

Currently, a polyline can be augmented using a \emph{push-back} function.
This function works as follows:
\begin{enumerate}
\item Gets a vertex as its input.
\item Obtains the last vertex of the polyline using \code{target()} function.
\item Generates a new \seg and pushes it to the range of segments representing the \poly.
\end{enumerate}
The use of \code{target()} is problematic as it implicitly assume that the \segtr class provides orientation of the \seg's.

\paragraph{Has to be done:}
All \code{push\_back()} should be deprecated and removed.
The functionality of augmenting a \poly (or an \xpoly) should be handled by \polytr.
See \cref{sec:augmenting-poly-in-polytr} for further details.

\section{Implementation of \polytr}
\label{sec:impl-polytr}

Ultimately, the \polytr should be in charge of all the operations which deal with \poly's and \xpoly's.
To that end, the traits class should provide functors which construct, augment, split etc. polylines.

\subsection{Construction Functors}
\label{sec:constr-funct-polytr}

As we leave only one constructor (which handles a range of \seg's) in the class of \poly and \xpoly we have to provide other needed construction methods in the traits class, namely in \polytr.
To that end we provide several construction functors which can handle various types of inputs.
Here is a list of the various overloads of the parentheses operator of the construction functors:
\begin{pyglist}[language=c++]
  Curve_2 operator()(const Point_2& p, const Point_2& q) const
  Curve_2 operator()(const Segment_2& seg) const
  Curve_2 operator()(ForwardIterator begin, ForwardIterator end) const
\end{pyglist}
\noindent
The last functor dispatches the given range to the corresponding implementation depending on the \emph{type} of the elements of the range.
Similar functors are provided for the construction of \xpoly.
All validity tests of the input should be done in \code{CGAL\_precondition} blocks.

\subsection{Augmenting a \poly or \xpoly}
\label{sec:augmenting-poly-in-polytr}

Add a functor to the traits class which will provide the user an interface to augment \poly (and \xpoly if needed).
This functor should be able to append vertices or segments to an \emph{existing} \poly.
Note that one the polyline will be unbounded augmentation will not be always possible.

\subsection{Output of \functor{Intersect\_2}}
\label{sec:outp-funct-intersect-2}

In the concept \concept{ArrTraits::Intersect\_2} it is defined that the output iterator should contain the elements in an ascending \(xy\)-lexicographic order.
Thus, obviously, the implementation of \functor{Intersect\_2} should meet this requirement as well.
\begin{queframe}
  If indeed the \xpoly may not maintain left-to-right direction invariant (see Section~\ref{sec:design-gener-issu-poly}), meeting this requirement can be hard, isn't it?

  Furthermore, the current implementation of \functor{Intersect\_2} seems to fail if the given \xpoly's are not oriented from left-to-right.
  \begin{pyglist}[language=c++]
    Traits_2::Intersect_2 int_2 = traits.intersect_2_object();
    std::vector<CGAL::Object> out;
    int_2(poly1,poly2,back_inserter(out));
    std::cout << "Number of intersection elements: " << out.size() << std::endl;
    for (
    std::vector<CGAL::Object>::iterator it = out.begin() ;
    it!=out.end() ; ++it)
    {
      typedef std::pair<Point_2,Traits_2::Multiplicity> pt_int;
      const pt_int p =
      CGAL::object_cast<pt_int>(*it);
      std::cout << "Intersection element: " << p.first << std::endl;
    }
  \end{pyglist}
\end{queframe}

\subsection{Changes Derived from \poly}
\label{sec:changes-derived-from-polytr}

As a result of the changes in \poly and \xpoly (cf. \cref{sec:implementation-poly}), updates and modifications are needed also in \polytr.
In particular the following functors have to be updated:
\begin{itemize}
\item \functor{Make\_x\_monotone\_2}:
  \begin{itemize}
  \item Assumes iteration over the vertices of the given \poly.
  \item When constructing the \xpoly's, this functor should use the construction functors provided in \polytr.
  \end{itemize}
\end{itemize}


\subsection{Relation to the \segtr Parameter}
\label{sec:relat-segtr-param-polytr}

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
