\ccRefPageBegin

\begin{ccRefFunction}{locate}

\ccDefinition

The function \ccRefName{} performs a batched point-location operation on a
given arrangement. It accepts a range of query points, and locates each
point in the arrangement. The query results are returned through the output
iterator. Each query result is given as a pair of the query point and an
object representing the arrangement feature that contains it, namely a
discriminated union container of the bounded types\ccc{Face_const_handle},
\ccc{Halfedge_const_handle}, and \ccc{Vertex_const_hanlde}. The resulting
pairs in the output sequence are sorted in increasing $xy$-lexicographical
order of the query points. The function returns a past-the-end iterator of
the output sequence.

\paragraph{A note on Backwards compatibility}
The function \ccRefName{} used to return \ccc{CGAL::Object} up to
\cgal{} version~3.9. Starting with \cal{} version~4.0 the return type
is determined by a metafunction. To preserve backwards compatibility
\ccc{CGAL::Object} can be constructed from the new return types
implicitly, but switching to the new style is recommended. To enable
the old style without any overhead, the macro
\ccc{CGAL_ARR_POINT_LOCATION_VERSION} can be defined to 1 before any
\cgal{} header is included.

\ccInclude{CGAL/Arr_batched_point_location.h}

\ccGlobalFunction{template<typename Traits, typename Dcel,
                           typename inputIterator, typename OutputIterator>
                  OutputIterator locate (const Arrangement_2<Traits,Dcel>& arr,
                                         inputIterator points_begin,
                                         inputIterator points_end,
                                         OutputIterator oi);}

\ccRequirements
\begin{itemize}
\item \ccc{InputIterator::value_type} must be \ccc{Arrangement_2::Point_2}.
\item \ccc{*OutputIterator} must be convertible to
  \ccc{std::pair<Arrangement_2::Point_2,Arr_point_location_result<Arrangement_2>::Type>}.
\end{itemize}

\ccSeeAlso
%============
\ccRefIdfierPage{CGAL::Arr_point_location_result<Arrangement>}\\
\ccRefIdfierPage{CGAL_ARR_POINT_LOCATION_VERSION}

\end{ccRefFunction}

\ccRefPageEnd
