% +------------------------------------------------------------------------+
% | Reference manual page: Arr_out_formatter.tex
% +------------------------------------------------------------------------+
% | 
% | Package: Arrangement_2
% | 
% +------------------------------------------------------------------------+

\ccRefPageBegin

\begin{ccRefConcept}{ArrangementOutputFormatter}

A model for the \ccRefName\ concept supports a set of functions that enable
writing an arrangement to an output stream using a specific format.

\ccTypes
%=======

\ccNestedType{Arrangement_2}{the type of arrangement to output.}

\ccTypedef{typedef typename Arrangement_2::Point_2 Point_2;}
    {the point type.}
\ccGlue
\ccTypedef{typedef typename Arrangement_2::X_monotone_curve_2 X_monotone_curve_2;}
    {the $x$-monotone curve type.}

\ccTypedef{typedef typename Arrangement_2::Size Size;}{}
\ccGlue
\ccTypedef{typedef typename Arrangement_2::Vertex_const_handle Vertex_const_handle;}{}
\ccGlue
\ccTypedef{typedef typename Arrangement_2::Halfedge_const_handle Halfedge_const_handle;}{}
\ccGlue
\ccTypedef{typedef typename Arrangement_2::Face_const_handle Face_const_handle;}{}

\ccCreation
\ccCreationVariable{outf}
%========================
    
\ccConstructor{Arr_out_formatter();}
   {default constructor.}

\ccConstructor{Arr_out_formatter (std::ostream& os);}
   {constructs a formatter that writes to \ccc{os}.}

\ccMethod{void set_out (std::ostream& os);}
   {directs \ccVar\ to write to \ccc{os}.}

\ccAccessFunctions
%=================

\ccMethod{std::ostream& out ();}
   {returns the stream that \ccVar\ writes to.
    \ccPrecond{\ccVar\ is directed to a valid output stream.}}

\ccHeading{Formatted Output Functions}
%=====================================

\ccMethod{void write_arrangement_begin ();}
    {writes a message indicating the beginning of the arrangement.}
\ccGlue
\ccMethod{void write_arrangement_end ();}
    {writes a message indicating the end of the arrangement.}

\ccMethod{void write_size (const char *label, Size size);}
    {writes a size value, preceded by a given label.}

\ccMethod{void write_vertices_begin();}
    {writes a message indicating the beginning of the vertex records.}
\ccGlue
\ccMethod{void write_vertices_end();}
    {writes a message indicating the end of the vertex records.}

\ccMethod{void write_edges_begin();}
    {writes a message indicating the beginning of the edge records.}
\ccGlue
\ccMethod{void write_edges_end();}
    {writes a message indicating the end of the edge records.}

\ccMethod{void write_faces_begin();}
    {writes a message indicating the beginning of the face records.}
\ccGlue
\ccMethod{void write_faces_end();}
    {writes a message indicating the end of the face records.}

\ccMethod{void write_vertex_begin();}
    {writes a message indicating the beginning of a single vertex record.}
\ccGlue
\ccMethod{void write_vertex_end();}
    {writes a message indicating the end of a single vertex record.}

\ccMethod{void write_vertex_index (std::size_t idx);}
    {writes a vertex index.}

\ccMethod{void write_point (const Point_2& p);}
    {writes a point.}

\ccMethod{void write_vertex_data (Vertex_const_handle v);}
    {writes the auxiliary data associated with the vertex.}

\ccMethod{void write_edge_begin();}
    {writes a message indicating the beginning of a single edge record.}
\ccGlue
\ccMethod{void write_edge_end();}
    {writes a message indicating the end of a single edge record.}

\ccMethod{void write_halfedge_index (std::size_t idx);}
    {writes a halfedge index.}

\ccMethod{void write_x_monotone_curve (const X_monotone_curve_2& c);}
    {writes an $x$-monotone curve.}

\ccMethod{void write_halfegde_data (Halfedge_const_handle he);}
    {writes the auxiliary data associated with the halfedge.}

\ccMethod{void write_face_begin();}
    {writes a message indicating the beginning of a single face record.}
\ccGlue
\ccMethod{void write_face_end();}
    {writes a message indicating the end of a single face record.}

\ccMethod{void write_outer_ccb_begin();}
    {writes a message indicating the beginning of the outer CCB of the current face.}
\ccGlue
\ccMethod{void write_outer_ccb_end();}
    {writes a message indicating the end of the outer CCB of the current face.}

\ccMethod{void write_holes_begin();}
    {writes a message indicating the beginning of the container of holes inside the
     current face.}
\ccGlue
\ccMethod{void write_holes_end();}
    {writes a message indicating the end of the container of holes inside the
     current face.}

\ccMethod{void write_ccb_halfedges_begin();}
    {writes a message indicating the beginning a connected component's boundary.}
\ccGlue
\ccMethod{void write_ccb_halfedges_end();}
    {writes a message indicating the end of a connected component's boundary.}

\ccMethod{void write_isolated_vertices_begin();}
    {writes a message indicating the beginning of the container of isolated vertices
     inside the current face.}
\ccGlue
\ccMethod{void write_isolated_vertices_end();}
    {writes a message indicating the end of the container of isolated vertices inside
     the current face.}

\ccMethod{void write_face_data (Face_const_handle f);}
    {writes the auxiliary data associated with the face.}

\ccHasModels
%===========

\ccc{Arr_text_formatter<Arrangement>}\lcTex{
        (\ccRefPage{CGAL::Arr_text_formatter<Arrangement>})}\\
\ccc{Arr_face_extended_text_formatter<Arrangement>}\lcTex{
        (\ccRefPage{CGAL::Arr_face_extended_text_formatter<Arrangement>})}\\
\ccc{Arr_extended_dcel_text_formatter<Arrangement>}\lcTex{
        (\ccRefPage{CGAL::Arr_extended_dcel_text_formatter<Arrangement>})}

\end{ccRefConcept}

\ccRefPageEnd

