% +------------------------------------------------------------------------+
% | Reference manual page: Arr_dcel_base.tex
% +------------------------------------------------------------------------+
% | 
% | Package: Arrangement_2
% | 
% +------------------------------------------------------------------------+

\ccRefPageBegin

\begin{ccRefClass}{Arr_dcel_base<V,H,F>}
\label{arr_ref:arr_dcel_base}
    
\ccDefinition
%============

The \ccClassTemplateName\ class is an important ingredient in the
definition of \dcel\ data structures. It serves as a basis class for
any instance of the \ccc{Dcel} template parameter of the
\ccc{Arrangement_2} template. In particular it is the basis class of
the default \ccc{Dcel} template parameter, and the basis class of any
extended \dcel. The template parameters \ccc{V}, \ccc{H}, and \ccc{F}
must be instantiated with models of the concepts
\ccc{ArrangementDcelVertex}, \ccc{ArrangementDcelHalfedge},
and \ccc{ArrangementDcelFace} respectively.

\ccInclude{CGAL/Arr_dcel_base.h}
 
\ccIsModel
    \ccc{ArrangementDcel}

%--------------------------------------------------------------------------

\subsection*{Class Arr\_vertex\_base$<$Point$>$}
%===============================================

\begin{ccClass}{Arr_vertex_base<Point>}

\ccDefinition
%============

The basic \dcel\ vertex type. Serves as a basis class for an extended
vertex record with auxiliary data fields. The \ccc{Point} parameter is
the type of points associated with the vertices.

\ccIsModel
    \ccc{ArrangementDcelVertex}

\end{ccClass}

%--------------------------------------------------------------------------

\subsection*{Class Arr\_halfedge\_base$<$Curve$>$}
%=================================================

\begin{ccClass}{Arr_halfedge_base<Curve>}

\ccDefinition
%============

The basic \dcel\ halfedge type. Serves as a basis class for an
extended halfedge record with auxiliary data fields. The \ccc{Curve}
parameter is the type of $x$-monotone curves associated with the vertices.

\ccIsModel
    \ccc{ArrangementDcelHalfedge}

\end{ccClass}

%--------------------------------------------------------------------------

\subsection*{Class Arr\_face\_base}
%==================================

\begin{ccClass}{Arr_face_base}

\ccDefinition
%============

The basic \dcel\ face type. Serves as a basis class for an extended
face record with auxiliary data fields.

\ccIsModel
    \ccc{ArrangementDcelFace}

\end{ccClass}

%--------------------------------------------------------------------------

\end{ccRefClass}

\ccRefPageEnd
