\ccHtmlNoClassLinks
\begin{ccRefFunction}{operator<<}
\label{ref_arr_operator_leftshift}

\ccDefinition

The function \ccRefName{} inserts an object into a given output stream.

%%%%

\ccInclude{CGAL/IO/Arr_iostream.h}

\ccGlobalFunction{template<typename Traits, typename Dcel>
            std::ostream& operator<< (std::ostream& os,
                                      const Arrangement_2<Traits,Dcel>& arr);}
Inserts the arrangement object \ccc{arr} into the output stream
\ccc{os} using the output format defined by the
\ccc{Arr_text_formatter} class. Only the basic geometric and
topological features of the arrangement are inserted. Auxiliary data
that may be attached to the \dcel\ features is ignored.

%%%%

\ccInclude{CGAL/IO/Arr_with_history_iostream.h}

\ccGlobalFunction{template<typename Traits, typename Dcel>
            std::ostream& operator<< (std::ostream& os,
                         const Arrangement_with_history_2<Traits,Dcel>& arr);}
Inserts the arrangement-with-history object \ccc{arr} into the output
stream \ccc{os} using the output format defined by the
\ccc{Arr_with_history_text_formatter} class. Only the basic geometric
and topological features of the arrangement are inserted. Auxiliary
data that may be attached to the \dcel\ features is ignored.

%%%%

%% Inserts an arrangement into a given Postscript stream.
%% Only the basic geometric and topological features of the arrangement are
%% written. Auxiliary data that might be attached to the \dcel\ features is
%% lost.

%% \ccInclude{CGAL/IO/Arr_postscript_file_stream.h}

%% \ccGlobalFunction{template<typename Traits, typename Dcel>
%% Arr_postscript_file_stream& operator<< (std::ostream& os,
%%                                       const Arrangement_2<Traits,Dcel>& arr);}

%%%%

%% Inserts a polyline into a given Postscript stream.
%% Only the basic geometric and topological features of the polylines are
%% written. Auxiliary data that might be attached is lost.
    
%% \ccInclude{CGAL/IO/Polyline_2_postscript_file_stream.h}

%% \ccGlobalFunction{template<typename SegmentTraits>
%% Postscript_file_stream& operator<< (std::ostream& os,
%%                                   const Polyline_2<SegmentTraits>& polyline);}

%%%%

Inserts a polyline into a given \ccc{Qt_widget} stream.
Only the basic geometric and topological features of the polylines are
written. Auxiliary data that might be attached is lost.
    
\ccInclude{CGAL/IO/Qt_widget_Polyline_2.h}

\ccGlobalFunction{template<typename SegmentTraits>
          Qt_widget& operator<< (std::ostream& os,
                                 const Polyline_2<SegmentTraits>& polyline);}

%%%%

Inserts a conic arc into a given \ccc{Qt_widget} stream.
Only the basic geometric and topological features of the conic arcs are
written. Auxiliary data that might be attached is lost.
    
\ccInclude{CGAL/IO/Qt_widget_Conic_arc_2.h}

\ccGlobalFunction{template<typename ConicArc>
         Qt_widget& operator<< (std::ostream& os,
                                const _Conic_x_monotone_arc_2<ConicArc>& cv);}

\ccSeeAlso
  \ccc{read}\lcTex{(\ccRefPage{CGAL::read})}\\
  \ccc{write}\lcTex{(\ccRefPage{CGAL::write})}\\
  \lcTex{\ccc{operator>>} page~\pageref{ref_arr_operator_rightshift}}
  \lcRawHtml{<I><A HREF="Function_operator--.html">operator&gt;&gt;</A></I>}

\end{ccRefFunction}
\ccRefPageEnd
