% +------------------------------------------------------------------------+
% | Reference manual page: Arrangement_2.tex
% +------------------------------------------------------------------------+
% | 
% | Package: Arrangement_2
% | 
% +------------------------------------------------------------------------+

\ccRefPageBegin

\begin{ccRefClass}{Arrangement_2<Traits,Dcel>}
\label{arr_ref:arr}

\ccDefinition
%============

An object \ccc{arr} of the class \ccClassTemplateName\ represents the
planar subdivision induced by a set of $x$-monotone curves and isolated
points into maximally connected cells. The arrangement is represented as
a doubly-connected edge-list ({\sc Dcel}) such that each {\sc Dcel} vertex
is associated with a point of the plane and each edge is
associated with an $x$-monotone curve whose interior is disjoint from all
other edges and vertices. Recall that an arrangement
edge is always comprised of a pair of twin {\sc Dcel} halfedges.

The \ccClassTemplateName\ template has two parameters:
\begin{itemize}
\item The \ccc{Traits} template-parameter should be instantiated with
a model of the \ccc{ArrangementBasicTraits_2} concept. The traits
class defines the types of $x$-monotone curves and two-dimensional
points, namely \ccc{X_monotone_curve_2} and \ccc{Point_2},
respectively, and supports basic geometric predicates on them.
\item The \ccc{Dcel} template-parameter should be instantiated with
a class that is a model of the \ccc{ArrangementDcel} concept. The
value of this parameter is by default
\ccc{Arr_default_dcel<Traits>}.
\end{itemize}
The available traits classes and {\sc Dcel} classes are described below. 

\ccInclude{CGAL/Arrangement_2.h}

\ccTypes
%=======

\ccThree{typedef typename Traits_2::X_monotone_curve_2}{X_monotone_2;}{}
\ccThreeToTwo
\ccTypedef{typedef Arrangement_2<Traits_2,Dcel> Self;}
  {a private type used as an abbreviation of the \ccRefName\ type hereafter.}
  
\ccNestedType{Traits_2}{the traits class in use.}
\ccGlue
\ccNestedType{Dcel}{the {\sc Dcel} representation of the arrangement.}

\ccTypedef{typedef typename Traits_2::Point_2 Point_2;}
  {the point type, as defined by the traits class.}
\ccGlue
\ccTypedef{typedef typename Traits_2::X_monotone_curve_2 X_monotone_curve_2;}
  {the $x$-monotone curve type, as defined by the traits class.}

\ccTypedef{typedef typename Dcel::Size Size;}
  {the size type (equivalent to \ccc{size_t}).}

\ccThree{Arrangement_2<Traits,Dcel>::Halfedge_iterator}{}{}
\ccThreeToTwo
\ccNestedType{Vertex}{represents a $0$-dimensional cell in the subdivision.
                      A vertex is always associated with a point.}
\ccGlue
\ccNestedType{Halfedge}{represents (together with its twin --- see below)
                   a $1$-dimensional cell in the subdivision.
                   A halfedge is always associated with an $x$-monotone curve.}
\ccGlue
\ccNestedType{Face}{represents a $2$-dimensional cell in the subdivision.}

The following handles, iterators, and circulators all have respective
constant counterparts (for example, in addition to \ccc{Vertex_iterator}
the type \ccc{Vertex_const_iterator} is also defined).
See~\cite{cgal:ms-strg-96} for a discussion of constant versus mutable
iterator types. The mutable types are assignable to their constant
counterparts. 

\ccc{Vertex_iterator}, \ccc{Halfedge_iterator}, and
\ccc{Face_iterator} are equivalent to the respective handle types (namely,
\ccc{Vertex_handle}, \ccc{Halfedge_handle}, and \ccc{Face_handle}). Thus,
wherever the handles appear in function parameter lists, the respective
iterators can be passed as well.
   
\ccNestedType{Vertex_handle}{a handle for an arrangement vertex.}
\ccGlue
\ccNestedType{Halfedge_handle}{a handle for a halfedge.
          The halfedge and its twin form together an arrangement edge.}
\ccGlue
\ccNestedType{Face_handle}{a handle for an arrangement face.}

\ccNestedType{Vertex_iterator}{a bidirectional iterator over the
       vertices of the arrangement. Its value-type is \ccc{Vertex}.}
\ccGlue
\ccNestedType{Halfedge_iterator}{a bidirectional iterator over the
       halfedges of the arrangement.  Its value-type is \ccc{Halfedge}.}
\ccGlue    
\ccNestedType{Edge_iterator}{a bidirectional iterator over the
       edges of the arrangement. (That is, it skips every other halfedge.)
       Its value-type is \ccc{Halfedge}.}
\ccGlue    
\ccNestedType{Face_iterator}{a bidirectional iterator over the
       faces of arrangement.  Its value-type is \ccStyle{Face}.}
\ccGlue    
\ccNestedType{Unbounded_face_iterator}{a bidirectional iterator over the
       unbounded faces of arrangement.  Its value-type is \ccStyle{Face}.}
    
\ccNestedType{Halfedge_around_vertex_circulator}{a bidirectional circulator
       over the halfedges that have a given vertex as their target.  
       Its value-type is \ccStyle{Halfedge}.}
\ccGlue
\ccNestedType{Ccb_halfedge_circulator}{a bidirectional circulator over the
       halfedges of a CCB (connected component of the boundary).
       Its value-type is \ccStyle{Halfedge}. Each
       bounded face has a single CCB representing it outer boundary, and may
       have several inner CCBs representing its holes.}
\ccGlue
\ccNestedType{Hole_iterator}{a bidirectional iterator over the holes 
       (i.e., inner CCBs) contained inside a given face.
       Its value type is \ccStyle{Ccb_halfedge_circulator}.}
\ccGlue
\ccNestedType{Isolated_vertex_iterator}{a bidirectional iterator over the
       isolated vertices contained inside a given face.
       Its value type is \ccStyle{Vertex}.}

\ccCreation
\ccCreationVariable{arr}
%=======================
    
\ccConstructor{Arrangement_2<Traits, Dcel>();} 
    {constructs an empty arrangement containing one unbounded face,
     which corresponds to the entire plane.}
    
\ccConstructor{Arrangement_2<Traits, Dcel>(const Self& other);}
    {copy constructor.}
        
\ccConstructor{Arrangement_2<Traits, Dcel>(const Traits_2 *traits);}
    {constructs an empty arrangement that uses the given \ccc{traits}
     instance for performing the geometric predicates.}


\ccThree{Halfedge_iterator}{arr.number_of_halfedges()~}{}
\ccThreeToTwo
\ccHeading{Assignment Methods}
%=============================

\ccMethod{Self& operator= (other);}
    {assignment operator.}

\ccMethod{void assign (const Self& other);}
    {assigns the contents of another arrangement.}

\ccMethod{void clear ();}
    {clears the arrangement.}


\ccAccessFunctions
%=================

\ccMethod{Traits_2* get_traits();}
    {returns the traits object used by the arrangement instance.
    A \ccc{const} version is also available.}

\ccMethod{bool is_empty() const;}
    {determines whether the arrangement is empty (contains only the unbounded
     face, with no vertices or edges).}

All \ccc{_begin()} and \ccc{_end()} methods listed below also have \ccc{const}
counterparts, returning constant iterators instead of mutable ones:

$\bullet$ {\sl Accessing the Arrangement Vertices:}
%----------------------------------------------

\ccMethod{Size number_of_vertices() const;}
    {returns the number of vertices in the arrangement.}

\ccMethod{Size number_of_isolated_vertices() const;}
    {returns the total number of isolated vertices in the arrangement.}

\ccMethod{Vertex_iterator vertices_begin();}
    {returns the begin-iterator of the vertices in the arrangement.}
    
\ccMethod{Vertex_iterator vertices_end();}
    {returns the past-the-end iterator of the vertices in the arrangement.}

\ccMethod{Size number_of_vertices_at_infinity() const;}
    {returns the number of arrangement vertices that lie at infinity and
     are not associated with valid points. Such vertices are not considered
     to be regular arrangement vertices and \ccVar\ccc{.number_of_vertices()}
     does not count them.}

$\bullet$ {\sl Accessing the Arrangement Edges:}
%-------------------------------------------

\ccMethod{Size number_of_halfedges() const;}
    {returns the number of halfedges in the arrangement.}

\ccMethod{Halfedge_iterator halfedges_begin();}
    {returns the begin-iterator of the halfedges in the arrangement.}
 
\ccMethod{Halfedge_iterator halfedges_end();}
    {returns the past-the-end iterator of the halfedges in the arrangement.}

\ccMethod{Size number_of_edges() const;}
    {returns the number of edges in the arrangement (equivalent to
     \ccc{arr.number_of_halfedges() / 2}).}

\ccMethod{Edge_iterator edges_begin();}
    {returns the begin-iterator of the edges in the arrangement.}
 
\ccMethod{Edge_iterator edges_end();}
    {returns the past-the-end iterator of the edges in the arrangement.}

$\bullet$ {\sl Accessing the Arrangement Faces:}
%-------------------------------------------

\ccMethod{Face_handle unbounded_face();}
    {returns a handle for an unbounded face of the arrangement.
     In case the arrangement comprises only bounded curves, there is a single
     unbounded face and the function returns a handle to it. Otherwise, a
     handle to an arbitrary unbounded face is returned.}

\ccMethod{Size number_of_faces() const;}
    {returns the number of faces in the arrangement.}

\ccMethod{Face_iterator faces_begin();}
    {returns the begin-iterator of the faces in the arrangement.}
    
\ccMethod{Face_iterator faces_end();}
    {returns the past-the-end iterator of the faces in the arrangement.}

\ccMethod{Size number_of_unbounded_faces() const;}
    {returns the number of unbounded faces in the arrangement.
     Note \ccVar\ccc{.number_of_faces()} also counts the unbounded faces
     of the arrangement.}

\ccMethod{Unbounded_face_iterator unbounded_faces_begin();}
    {returns the begin-iterator of the unbounded faces in the arrangement.}
    
\ccMethod{Unbounded_face_iterator unbounded_faces_end();}
    {returns the past-the-end iterator of the unbounded faces in the
     arrangement.}

\ccMethod{Face_handle fictitious_face();}
    {returns a handle to the fictitious face of the arrangement.
    If the arrangement is not unbounded, there is no fictitious
    face. In this case the result is not deterministic. A const
    version is also available.}
     
\begin{ccAdvanced}

\ccHeading{Casting away Constness}
%=================================

It is sometime necessary to convert a constant (non-mutable) handle to
a mutable handle. For example, the result of a point-location query is
a non-mutable handle for the arrangement cell containing the query point.
Assume that the query point lies on a edge, so we obtain a
\ccc{Halfedge_const_handle}; if we wish to use this handle and remove the
edge, we first need to cast away its ``constness''.
 
\ccMethod{Vertex_handle non_const_handle (Vertex_const_handle v);}
    {casts the given constant vertex handle to an equivalent mutable handle.}

\ccMethod{Halfedge_handle non_const_handle (Halfedge_const_handle e);}
    {casts the given constant halfedge handle to an equivalent mutable handle.}

\ccMethod{Face_handle non_const_handle (Face_const_handle f);}
    {casts the given constant face handle to an equivalent mutable handle.}

\end{ccAdvanced}

\ccModifiers
%===========

$\bullet$ {\sl Specialized Insertion Methods:}
%------------------------------------------

\ccMethod{Vertex_handle insert_in_face_interior (const Point_2& p,
                                                 Face_handle f);}
   {inserts the point \ccc{p} into the arrangement as an isolated vertex in
    the interior of the face \ccc{f} and returns a handle for the newly
    created vertex.
    \ccPrecond{\ccc{p} lies in the interior of the face \ccc{f}.}}

\ccMethod{Halfedge_handle insert_in_face_interior
                                      (const X_monotone_curve_2& c, 
                                       Face_handle f);}
   {inserts the curve \ccc{c} that is entirely contained in the interior
    of a given face \ccc{f}. If \ccc{c} is a bounded curve two new vertices
    that correspond to \ccc{c}'s endpoints are created and connected with a
    newly created halfedge pair, which forms a new hole (inner component)
    in the face \ccc{f}. If \ccc{c} is unbounded, at least one of the two
    vertices that represents its end lies at infinity, and its creation
    modifies the outer boundary of \ccc{f}.
    The function returns a handle for one of the new halfedges
    corresponding to the inserted curve, directed in lexicographic
    increasing order (from left to right).
    \ccPrecond{\ccc{c} lies entirely in the interior of the face \ccc{f} and
    is disjoint from all existing arrangement vertices and edges (in
    particular, both its endpoints are not already associated with existing
    arrangement vertices).}
    \ccPrecond{In case \ccc{c} is an unbounded curve, \ccc{f} must be an
    unbounded face.}}

\ccMethod{Halfedge_handle insert_from_left_vertex
                                      (const X_monotone_curve_2& c,
                                       Vertex_handle v);}
  {inserts the curve \ccc{c} into the arrangement, such that its left
   endpoint corresponds to a given arrangement vertex. As a result, a new
   vertex that correspond to \ccc{c}'s right endpoint is created and
   connected to \ccc{v} with a newly created halfedge pair. If \ccc{c} has
   an unbounded right end, the new vertex lies at infinity and the
   unbounded face that contains the interior of the curve is split. 
   The function returns a handle for one of the new halfedges corresponding
   to the inserted curve, directed towards the newly created vertex ---
   that is, directed in lexicographic increasing order (from left to right).
   \ccPrecond{The interior of \ccc{c} is disjoint from all existing arrangement
   vertices and edges.}
   \ccPrecond{\ccc{v} is associated with the left endpoint of \ccc{c}.}
   \ccPrecond{The right endpoint of \ccc{c} is not already associated with
   an existing arrangement vertex.}}

\ccMethod{Halfedge_handle insert_from_right_vertex
                                      (const X_monotone_curve_2& c,
                                       Vertex_handle v);}
  {inserts the curve \ccc{c} into the arrangement, such that its right
   endpoint corresponds to a given arrangement vertex. As a result, a new
   vertex that correspond to \ccc{c}'s left endpoint is created and
   connected to \ccc{v} with a newly created halfedge pair.  If \ccc{c} has
   an unbounded left end, the new vertex lies at infinity and the
   unbounded face that contains the interior of the curve is split.
   The function returns a handle for one of the new halfedges corresponding
   to the inserted curve, directed to the newly created vertex ---
   that is, directed in lexicographic decreasing order (from right to left).
   \ccPrecond{The interior of \ccc{c} is disjoint from all existing arrangement
   vertices and edges.}
   \ccPrecond{\ccc{v} is associated with the right endpoint of \ccc{c}.}
   \ccPrecond{The left endpoint of \ccc{c} is not already associated with
   an existing arrangement vertex.}}

\ccMethod{Halfedge_handle insert_at_vertices (const X_monotone_curve_2& c,
                                              Vertex_handle v1, 
                                              Vertex_handle v2);}
  {inserts the curve \ccc{c} into the arrangement, such that both \ccc{c}'s
   endpoints correspond to existing arrangement vertices, given by \ccc{v1}
   and \ccc{v2}. The function creates a new halfedge pair that connects the
   two vertices, and returns a handle for the halfedge directed from \ccc{v1}
   to \ccc{v2}.
   \ccPrecond{The interior of \ccc{c} is disjoint from all existing arrangement
   vertices and edges.}
   \ccPrecond{\ccc{c} must not be an unbounded curve.}
   \ccPrecond{\ccc{v1} and \ccc{v2} are associated with \ccc{c}'s endpoints.} 
   \ccPrecond{If \ccc{v1} and \ccc{v2} are already
              connected by an edge, this edge represents an $x$-monotone
              curve that is interior-disjoint from \ccc{c}).}}

\begin{ccAdvanced}

\ccMethod{Halfedge_handle insert_in_face_interior
                            (const X_monotone_curve_2& c,
                             Halfedge_handle fict_pred1,
                             Halfedge_handle fict_pred2 = Halfedge_handle());}
  {inserts an unbounded curve \ccc{c} into the arrangement, such that \ccc{c}
   is entirely contained within a single unbounded face of the arrangement.
   \ccc{fict_pred1} specifies the fictitious halfedge that should contain the
   vertex at infinity that corresponds to the unbounded end of \ccc{c}. If
   both ends of \ccc{c} are unbounded, \ccc{fict_pred1} indicated the place
   for its left end and \ccc{fict_pred2} indicated a place for its right end.  
   The function returns a handle for one of the new halfedges directed
   (lexicographically) from left to right.
   \ccPrecond{\ccc{c} is an unbounded curve disjoint from all existing
   arrangement vertices and edges.}
   \ccPrecond{\ccc{fict_pred1} (and \ccc{fict_pred2}) are fictitious halfedges
   that contains the unbounded end(s) of \ccc{c}. If both halfedges are given
   they must be both incident to the same unbounded face.}}

\ccMethod{Halfedge_handle insert_from_left_vertex
                                      (const X_monotone_curve_2& c,
                                       Halfedge_handle pred);}
  {inserts the curve \ccc{c} into the arrangement, such that its left
   endpoint corresponds to a given arrangement vertex. This vertex is the
   target vertex of the halfedge \ccc{pred}, such that \ccc{c} is inserted
   to the circular list of halfedges around \ccc{pred->target()} right
   between \ccc{pred} and its successor. The function returns a handle for
   one of the new halfedges directed (lexicographically) from left to right.
   \ccPrecond{The interior of \ccc{c} is disjoint from all existing arrangement
   vertices and edges.}
   \ccPrecond{\ccc{pred->target()} is associated with the left endpoint
   of \ccc{c}, and \ccc{c} should be inserted after \ccc{pred} in a
   clockwise order around this vertex.} 
   \ccPrecond{The right endpoint of \ccc{c} is not already associated with
   an existing arrangement vertex.}}

\ccMethod{Halfedge_handle insert_from_left_vertex
                                      (const X_monotone_curve_2& c,
                                       Halfedge_handle pred,
                                       Halfedge_handle fict_pred);}
  {inserts an unbounded curve \ccc{c} into the arrangement, such that its left
   endpoint is bounded and corresponds to a given arrangement vertex. This
   vertex is the target vertex of the halfedge \ccc{pred}, such that \ccc{c}
   is inserted to the circular list of halfedges around \ccc{pred->target()}
   right between \ccc{pred} and its successor. Similarly, \ccc{fict_pred}
   specifies the fictitious halfedge that should contain the vertex at infinity
   that corresponds to the unbounded right end of \ccc{c}.
   The function returns a handle for one of the new halfedges directed
   (lexicographically) from left to right.
   \ccPrecond{The interior of \ccc{c} is disjoint from all existing arrangement
   vertices and edges. \ccc{c} must have a bounded left endpoint and an
   unbounded right end.}
   \ccPrecond{\ccc{pred->target()} is associated with the left endpoint
   of \ccc{c}, and \ccc{c} should be inserted after \ccc{pred} in a
   clockwise order around this vertex.} 
   \ccPrecond{\ccc{fict_pred} is a fictitious halfedge that contains the
   unbounded right end of \ccc{c}.}}

\ccMethod{Halfedge_handle insert_from_right_vertex
                                      (const X_monotone_curve_2& c,
                                       Halfedge_handle pred);}
  {inserts the curve \ccc{c} into the arrangement, such that its right
   endpoint corresponds to a given arrangement vertex. This vertex is the
   target vertex of the halfedge \ccc{pred}, such that \ccc{c} is inserted
   to the circular list of halfedges around \ccc{pred->target()} right
   between \ccc{pred} and its successor. The function returns a handle for
   one of the new halfedges directed (lexicographically) from right to left.
   \ccPrecond{The interior of \ccc{c} is disjoint from all existing arrangement
   vertices and edges.}
   \ccPrecond{\ccc{pred->target()} is associated with the right endpoint
   of \ccc{c}, and \ccc{c} should be inserted after \ccc{pred} in a
   clockwise order around this vertex.}
   \ccPrecond{The left endpoint of \ccc{c} is not already associated with
   an existing arrangement vertex.}}

\ccMethod{Halfedge_handle insert_from_right_vertex
                                      (const X_monotone_curve_2& c,
                                       Halfedge_handle pred,
                                       Halfedge_handle fict_pred);}
  {inserts an unbounded curve \ccc{c} into the arrangement, such that its right
   endpoint is bounded and corresponds to a given arrangement vertex. This
   vertex is the target vertex of the halfedge \ccc{pred}, such that \ccc{c}
   is inserted to the circular list of halfedges around \ccc{pred->target()}
   right between \ccc{pred} and its successor. Similarly, \ccc{fict_pred}
   specifies the fictitious halfedge that should contain the vertex at infinity
   that corresponds to the unbounded left end of \ccc{c}.
   The function returns a handle for one of the new halfedges directed
   (lexicographically) from right to left.
   \ccPrecond{The interior of \ccc{c} is disjoint from all existing arrangement
   vertices and edges. \ccc{c} must have a bounded right endpoint and an
   unbounded left end.}
   \ccPrecond{\ccc{pred->target()} is associated with the right endpoint
   of \ccc{c}, and \ccc{c} should be inserted after \ccc{pred} in a
   clockwise order around this vertex.} 
   \ccPrecond{\ccc{fict_pred} is a fictitious halfedge that contains the
   unbounded left end of \ccc{c}.}}

\ccMethod{Halfedge_handle insert_at_vertices (const X_monotone_curve_2& c,
                                              Halfedge_handle pred1, 
                                              Vertex_handle v2);}
  {inserts the curve \ccc{c} into the arrangement, such that both \ccc{c}'s
   endpoints correspond to existing arrangement vertices, given by
   \ccc{pred1->target()} and \ccc{v2}. The function creates a new halfedge
   pair that connects the two vertices (where the corresponding halfedge is
   inserted right between \ccc{pred1} and its successor around \ccc{pred1}'s
   target vertex) and returns a handle for the halfedge directed from
   \ccc{pred1->target()} to \ccc{v2}.
   \ccPrecond{The interior of \ccc{c} is disjoint from all existing arrangement
   vertices and edges.}
   \ccPrecond{\ccc{pred1->target()} and \ccc{v2} are associated with 
   \ccc{c}'s endpoints.} 
   \ccPrecond{If \ccc{pred1->target} and \ccc{v2} are already connected
              by an edge, this edge represents an $x$-monotone curve that
              is interior-disjoint from \ccc{c}).}}

\ccMethod{Halfedge_handle insert_at_vertices (const X_monotone_curve_2& c,
                                              Halfedge_handle pred1, 
                                              Halfedge_handle pred2);}
  {inserts the curve \ccc{c} into the arrangement, such that both \ccc{c}'s
   endpoints correspond to existing arrangement vertices, given by
   \ccc{pred1->target()} and \ccc{pred2->target()}. The function creates a
   new halfedge pair that connects the two vertices (with \ccc{pred1} and
   \ccc{pred2} indicate the exact place for these halfedges around the two
   target vertices) and returns a handle for the halfedge directed from
   \ccc{pred1->target()} to \ccc{pred2->target()}.
   \ccPrecond{The interior of \ccc{c} is disjoint from all existing arrangement
   vertices and edges.}
   \ccPrecond{\ccc{pred1->target()} and \ccc{pred2->target()} are associated
   with \ccc{c}'s endpoints.} 
   \ccPrecond{If \ccc{pred1->target} and \ccc{pred2->target()} are already
              connected by an edge, this edge represents an $x$-monotone
              curve that is interior-disjoint from \ccc{c}).}}

\end{ccAdvanced}

$\bullet$ {\sl Modifying Vertices and Edges:}
%-----------------------------------------

\ccMethod{Vertex_handle modify_vertex (Vertex_handle v,
                                       const Point_2& p);}
   {sets \ccc{p} to be the point associated with the vertex \ccc{v}.
    The function returns a handle for the modified vertex (same as \ccc{v}).
    \ccPrecond{\ccc{v} is not a vertex at infinity and \ccc{p} is
               geometrically equivalent to the point currently associated
               with \ccc{v}.}}

\ccMethod{Face_handle remove_isolated_vertex (Vertex_handle v);}
   {removes the isolated vertex \ccc{v} from the arrangement. The function
    returns the face \ccc{f} that used to contain the isolated vertex.
    \ccPrecond{\ccc{v} is an isolated vertex (has no incident edges).}}

\ccMethod{Halfedge_handle modify_edge (Halfedge_handle e,
                                       const X_monotone_curve_2& c);}
   {sets \ccc{c} to be the $x$-monotone curve associated with the edge \ccc{e}.
    The function returns a handle for the modified edge (same as \ccc{e}).
    \ccPrecond{\ccc{c} is geometrically equivalent to the curve currently
               associated with \ccc{e}.}}

\ccMethod{Halfedge_handle split_edge (Halfedge_handle e,
                                      const X_monotone_curve_2& c1, 
                                      const X_monotone_curve_2& c2);}
  {splits the edge \ccc{e} into two edges (more precisely, into two halfedge
   pairs), associated with the given subcurves \ccc{c1} and \ccc{c2}, and
   creates a vertex that corresponds to the split point. 
   The function returns a handle for the halfedge, whose source is the same
   as \ccc{e->source()} and whose target vertex is the split point.
   \ccPrecond{Either \ccc{c1}'s left endpoint and \ccc{c2}'s right endpoint
   correspond to \ccc{e}'s end-vertices such that \ccc{c1}'s right endpoint
   and \ccc{c2}'s left endpoint are equal and define the split point ---
   or vice-versa (with change of roles between \ccc{c1} and \ccc{c2}).}}

\ccMethod{Halfedge_handle merge_edge (Halfedge_handle e1,
                                      Halfedge_handle e2, 
                                      const X_monotone_curve_2& c);}
  {merges the edges represented by \ccStyle{e1} and \ccStyle{e2} into
   a single edge, associated with the given merged curve \ccc{c}.
   Denote \ccc{e1}'s end-vertices as $u_1$ and $v$, while \ccc{e2}'s
   end-vertices are denoted $u_2$ and $v$. The function removes the
   common vertex $v$ returns a handle for one of the merged halfedges,
   directed from $u_1$ to $u_2$.
   \ccPrecond{\ccc{e1} and \ccc{e2} share a common end-vertex, such that the
   two other end-vertices of the two edges are associated with \ccc{c}'s
   endpoints.}}

\ccMethod{Face_handle remove_edge (Halfedge_handle e,
                                   bool remove_source = true,
                                   bool remove_target = true);}
  {removes the edge \ccStyle{e} from the arrangement. Since the \ccc{e} may
   be the only edge incident to its source vertex (or its target vertex),
   this vertex can be removed as well. The flags \ccc{remove_source} and
   \ccc{remove_target} indicate whether the endpoints of \ccc{e} should be
   removed, or whether they should be left as isolated vertices in the
   arrangement.
   If the operation causes two faces to merge, the merged face is returned.
   Otherwise, the face to which the edge was incident is returned.}

\ccHeading{Miscellaneous}
% =======================

\ccMethod{bool is_valid () const;}
   {returns \ccc{true} if \ccVar\ represents a valid instance of 
   \ccClassTemplateName. In particular, the functions checks the topological 
    structure of the arrangement and assures that it is valid. In addition, 
    the function performs several simple geometric tests to ensure the 
    validity of some of the geometric properties of the arrangement. Namely, 
    it checks that all arrangement vertices are associated with distinct
    points, and that the halfedges around every vertex are ordered clockwise.}

\ccSeeAlso
\ccc{ArrangementDcel}\lcTex{(\ccRefPage{ArrangementDcel})}\\
\ccc{Arr_default_dcel<Traits>}
  \lcTex{(\ccRefPage{CGAL::Arr_default_dcel<Traits>})}\\
\ccc{ArrangementBasicTraits_2}\lcTex{(\ccRefPage{ArrangementBasicTraits_2})}\\
\ccc{CGAL::is_valid}\lcTex{(\ccRefPage{CGAL::is_valid})}\\
Insertion functions\lcTex{ 
  (\ccRefPage{CGAL::insert}, 
   \ccRefPage{CGAL::insert_non_intersecting_curve}, 
   \ccRefPage{CGAL::insert_non_intersecting_curves}, 
   \ccRefPage{CGAL::insert_point})}
  \lcRawHtml{
    (<I><A HREF="Function_insert.html">CGAL::insert</A></I>,
    <I><A HREF="Function_insert_non_intersecting_curve.html">CGAL::insert_non_intersecting_curve</A></I>,
    <I><A HREF="Function_insert_non_intersecting_curves.html">CGAL::insert_non_intersecting_curves</A></I>,
    <I><A HREF="Function_insert_point.html">CGAL::insert_point</A></I>)
  }\\
Removal functions
  \lcTex{(\ccRefPage{CGAL::remove_edge}, \ccRefPage{CGAL::remove_vertex})}
  \lcRawHtml{
    (<I><A HREF="Function_remove_edge.html">CGAL::remove_edge</A></I>,
    <I><A HREF="Function_remove_vertex.html">CGAL::remove_vertex</A></I>)
  }\\
\ccc{CGAL::overlay}\lcTex{(\ccRefPage{CGAL::overlay})}\\
Input/output functions
  \lcTex{(\ccRefPage{CGAL::read},\ccRefPage{CGAL::write})}
  \lcRawHtml{
    (<I><A HREF="Function_read.html">CGAL::read</A></I>,
    <I><A HREF="Function_write.html">CGAL::write</A></I>)
  }\\

\end{ccRefClass}

\ccRefPageEnd
