\section{Third Party Software}

In this section we list the software that is used by the various
\cgal\ packages.


\subsection{Standard Template Library \label{thirdparty:stl}}

\cgal\ heavily uses the {\sc Stl}, and in particular adopted
many of its design ideas.   The {\sc Stl} comes with the compiler,
but it is possible to use the compiler together with an
alternative {\sc Stl} implementation. You can find online
documentation for the {\sc Stl} at various web sites, e.g., 
\path+http://www.sgi.com/tech/stl/+, \path+http://www.cplusplus.com/reference/stl/+,
or \path+http://msdn.microsoft.com/en-us/library/1fe2x6kt(VS.71).aspx+.


\subsection{Boost \label{thirdparty:Boost}}

Boost is a collection of libraries. \cgal\ needs some of them, that is
it is mandatory.  If Boost is not already on your system, e.g., on
Windows, you can download it from \path'http://www.boost.org'.


\subsection{Blas \label{thirdparty:Blas}}

The \blas\ (Basic Linear Algebra Subprograms) are routines that provide
standard building blocks for performing basic vector and matrix operations.
In \cgal, \blas\ is required by the packages
\ccRef[Estimation of Local Differential Properties]{Pkg:Jet_fitting_3}
and \ccRef[Approximation of Ridges and Umbilics]{Pkg:Ridges_3} only.

You can download the official release from \path'http://www.netlib.org/blas/'
or download optimized implementations from \path'http://www.netlib.org/blas/faq.html#5'.
Alternatively, installing \taucs\ provides \blas.


\subsection{Lapack \label{thirdparty:Lapack}}

\lapack\ provides routines for solving systems of simultaneous linear equations,
least-squares solutions of linear systems of equations, eigenvalue problems,
and singular value problems.
In \cgal, \lapack\ is required by the packages
\ccRef[Estimation of Local Differential Properties]{Pkg:Jet_fitting_3}
and \ccRef[Approximation of Ridges and Umbilics]{Pkg:Ridges_3} only.

You can download the official release from \path'http://www.netlib.org/lapack/'.
Alternatively, installing \taucs\ customized for \cgal\ provides \lapack.


\subsection{GMP \label{thirdparty:GMP}}

A library for multi precision integers and rational numbers.
\cgal\ offers adapters for these number types. The usage
of the {\sc Gmp} library is optional.  If it is not already on your system,
e.g., on Windows, you can download it from \path'http://gmplib.org/'
or from the download section of \path'http://www.cgal.org'.


\subsection{MPFR \label{thirdparty:MPFR}}

A library for multi precision floating point numbers.  The usage of
the {\sc Mpfr} library is optional, and you must install it when you
use {\sc Gmp}.  You can download {\sc Mpfr} from \path'http://www.mpfr.org'
or from the download section of \path'http://www.cgal.org'.

\subsection{RS \label{thirdparty:RS}}

\rs{} stands for Real Solutions and is devoted to the study of the real
roots of polynomial systems with a finite number of complex roots
(including univariate polynomials). \rs{} is used only by one model of the
\ccRef[Algebraic Kernel]{Pkg:AlgebraicKerneld}.

\rs{} is freely distributable for non-commercial use. You can download it
from \rspage{}.

\subsection{Leda \label{thirdparty:Leda}}

A library of efficient data structures and algorithms. \cgal\ offers
adapters to the {\sc Leda} number types. The usage is optional.
It is available commercially from \path'http://www.algorithmic-solutions.com',
and there exists a binary ``free edition''.


\subsection{Taucs \label{thirdparty:Taucs}}

\taucs\ is a library of sparse linear solvers.
In \cgal, it is used to improve the computations within the
\ccRef[Planar Parameterization of Triangulated Surface Meshes]{Pkg:SurfaceParameterization}
package only.

The \taucs\ web site is \path'http://www.tau.ac.il/~stoledo/taucs/'.\\
The latest official version is \taucs\ version 2.2, September 4, 2003.
Copyright (c) 2001, 2002, 2003 by Sivan Toledo, Tel-Aviv University,
stoledo@tau.ac.il. All Rights Reserved.\\
See \path'http://www.tau.ac.il/~stoledo/taucs/' for the license and the availability note.\\
Used by permission of Sivan Toledo.

The \cgal\ project provides a modified version of \taucs\ in the download
section of \path'http://www.cgal.org'. This version fixes some bugs,
supports 64-bit platforms and allows a simplified installation process.
It also contains a complete \lapack\ implementation.\\
{\em CAUTION:} Since version 3.3.1, \cgal\ is no longer compatible with the official
release of \taucs\ (currently 2.2). Make sure to use the modified
version provided in the download section.


\subsection{OpenNL \label{thirdparty:OpenNL}}

OpenNL (Open Numerical Library) is a library to easily construct and solve
sparse linear systems. It is the default solver of the
\ccRef[Surface Mesh Parameterization]{Pkg:SurfaceParameterization} package.

OpenNL's main page is \path'http://www.loria.fr/~levy/software/'.

\cgal\ includes a version of OpenNL in C++, made especially for \cgal\ by Bruno L\'evy.


\subsection{zlib \label{thirdparty:zlib}}

A data compression library.
It is used in the examples of the \ccRef[Surface Mesh Generation]{Pkg:SurfaceMesher3} package.
If it is not already on your system,
e.g., on Windows, you can download it from  \path'http://www.gzip.org/zlib'.

\subsection{Qt \label{thirdparty:Qt}}

Qt is a cross-platform application framework. The usage of Qt is optional, but note that
it is used for many \cgal\ 2D as well as 3D demos.

As Qt is the layer underneath {\sc Kde}, Qt is installed
on many Linux systems. Otherwise you can download it from
 \path'http://qt.nokia.com/'.

\subsection{libQGLViewer \label{thirdparty:libQGLViewer}}

A 3D widget based on \qt~4's \ccc{QGLWidget}. It can be downloaded from
\path'http://www.libqglviewer.com/'.

\subsection{Coin \label{thirdparty:Coin}}

An implementation of Open Inventor.  It is used in the demo
of the \ccRef[Kinetic Data Structures]{Pkg:Kds} package. You can download
it from \path'http://www.coin3d.org/'.

