\RCSdef{\IntervalskiplistRev}{$Id$}
\RCSdefDate{\IntervalskiplistDate}{$Date$}
% +------------------------------------------------------------------------+

\ccParDims

\ccUserChapter{Interval Skip List\label{chapter_Interval_skip_list}}
\input{Interval_skip_list/PkgDescription.tex}
\ccChapterRelease{\IntervalskiplistRev. \ \IntervalskiplistDate}
\ccChapterAuthor{Andreas Fabri}

\minitoc



% +========================================================================+
\section{Definition}
% +========================================================================+
  
An interval skip list is a data structure for finding all intervals 
that contain a point, and for stabbing queries, that is for answering 
the question whether a given point is contained in an interval or not. 
The implementation we provide is dynamic, that is the user can freely
mix calls  to the methods \ccc{insert(..)}, \ccc{remove(..)}, 
\ccc{find_intervals(..)}, and \ccc{is_contained(..)}

The interval skip list class is parameterized with an interval class.

The data structure was introduced by Hanson~\cite{h-islds-91}, and it is called
interval skip list, because it is an extension of the randomized list
structure known as skip list~\cite{p-slpab-90}.
 
% +========================================================================+
\section{Example Programs}
% +========================================================================+
\label{sectionIntervalskiplistExamples}

We give two examples. The first one uses a basic interval class.  In
the second example we create an interval skip list for the $z$-ranges
of the faces of a terrain, allowing to answer level queries.

% +-------------------------------------------------------------+
\subsection{First Example with Simple Interval}

The first example reads two numbers \ccc{n} and \ccc{d} from \ccc{std::cin}.
It creates \ccc{n} intervals of length \ccc{d} with the left endpoint at \ccc{n}.
It then reads out the intervals for the 1-dimensional points with
coordinates $0 ... n+d$. 

The interval skip list class has as template argument an interval
class. In this example we use the class \ccc{Interval_skip_list_interval}.

\newpage
\ccIncludeExampleCode{Interval_skip_list/intervals.cpp}

% +-------------------------------------------------------------+
\subsection{Example with Faces of a Triangulated Terrain}



The second example creates an interval skip list that allows to find all the faces
of a terrain intersected by an horizontal plane at a given height.
The data points for the terrain are  read from a file. 

As model for the interval concept, we use a class that is a wrapper
around a face handle of a triangulated terrain. Lower and upper bound
of the interval are smallest and largest $z$-coordinate of the face.

\ccIncludeExampleCode{Interval_skip_list/isl_terrain.cpp}


% +--------------------------------------------------------+

%\input{Interval_skip_list_ref/main}

% EOF


