\chapter{2D Meshes}

This package implements 2D unstructured triangular meshes. Given a
domain, with constraints, it constructs a triangulation conforming the
domain and satisfying shape and size constraints. Hence, this package 
use \cgal\ 2D triangulations\footnote{See \ccTexHtml{the \cgal\ Manual.}
{<a href="http://www.cgal.org/Manual/doc_html/basic_lib/Triangulation_2/Chapter_triangulation_user.html">the CGAL Manual</a>.}}.

Domains that can be meshed are \emph{planar straight line graphes}
(PSLG), which are sets of of vertices and segments such that all
endpoints of every segments are in the set and that segments intersect
only at end-points. Such a domain can represented by a \cgal\ 
constrained triangulation, whose constrained segment are the segments
of the domain.

The mesh class depends on one template parameter. It stands for a
\cgal\ constrained Delaunay triangulation (CDT) which represents the
PSLG and becomes the base class. Its geometric traits class should not
only provide geometric objects and predicates for the triangulation,
as usual, but also define the geometric constraints that the triangles
have to satisfy.

The algorithm used to compute the mesh is the \emph{Delaunay
  refinement}~\cite{s-mgdsa-00}. After having conformed the CDT,
triangles that do not satisfy geometric constraints will be destroyed
by inserting their circumcenters in the CDT. At all time, the algorithm
insures that segments of the CDT have Gabriel property: their diametral
circles do not contain any point.

The shape constraint on triangles should be that the circumradius is
lower than a bound $B$ times the shortest edge of the triangle. This is
equivalent to say that the minimum angle of the triangle is greater
than $\arcsin{\frac{1}{2B}}$. If not angles are smaller than $\theta$,
then no angles are greater than $\pi - \theta$. Unfortunalty, the
algorithm will terminate at all time only if $B \ge \sqrt{2}$. This
package cannot, for the moment, insure that angles of meshes are
greater than $20.7$~degres. The size constraint can be any constraint
that tends to prefere small triangles. Both types of constraints are
defined in a nested type \ccc{Is_bad} of the geometric traits class.

\subsection*{Concepts}
\ccRefConceptPage{MeshTraits_2}\\
\ccRefConceptPage{MeshFaceBase_2}

\subsection*{Classes}
\ccRefIdfierPage{CGAL::Mesh_2<Tr>}\\
\ccRefIdfierPage{CGAL::Mesh_face_base_2<Traits>}\\
\ccRefIdfierPage{CGAL::Mesh_default_traits_2<K>}\\
\ccRefIdfierPage{CGAL::Mesh_size_traits_2<K>}

\lcHtml{\subsection*{Links to the Reference Sections}}
