% +------------------------------------------------------------------------+
% | Cbp Reference Manual:  intro.tex
% +------------------------------------------------------------------------+
% | Polyhedron reference manual pages
% |
% | 14.05.1998   Lutz Kettner
\RCSdef{\polyhedronRefRev}{$Revision$}
\RCSdefDate{\polyhedronRefDate}{$Date$}
% +------------------------------------------------------------------------+

\clearpage
\chapter{3D Nef Polyhedron}
%% \section{Reference Pages for Polyhedral Surface}
\label{chapterPolyhedronRef}
%% \ccChapterRelease{\polyhedronRefRev. \ \polyhedronRefDate}\\
%% \ccChapterAuthor{Lutz Kettner}

% +------------------------------------------------------------------------+
\section*{Summary}

A Nef polyhedron in 3-dimensional space is
any point set generated from a finite number of open halfspaces by set
complement and set intersection operations. It is also closed under 
all other binary set operations and under topological (unary) set operations. 

A 3D Nef polyhedron can be represented by the local pyramids of the minimal
elments of its incidence structure. Without going into to much detail, a local
pyramid essentially reflects the topologic and geometric situation at a certain
location in a point set. For finite polyhedra the minimal elements 
of the incidence structure are vertices only. This means, that it suffices to 
model the topologic and geometric situation of the vertices. For 
3D Nef polyhedra, the local pyramid of a vertex is represented by 
a planar Nef polyhedra embedded on a sphere.

\subsection*{Classes}

\ccRefIdfierPage{CGAL::Nef_polyhedron_3<Traits>}\\ 
\ccRefIdfierPage{CGAL::Nef_polyhedron_3<Traits>::Vertex}\\ 
\ccRefIdfierPage{CGAL::Nef_polyhedron_3<Traits>::Halfedge}\\ 
\ccRefIdfierPage{CGAL::Nef_polyhedron_3<Traits>::Halffacet}\\ 
\ccRefIdfierPage{CGAL::Nef_polyhedron_3<Traits>::Volume}\\ 
\ccRefIdfierPage{CGAL::Nef_polyhedron_3<Traits>::SHalfedge}\\ 
\ccRefIdfierPage{CGAL::Nef_polyhedron_3<Traits>::SHalfloop}\\ 
\ccRefIdfierPage{CGAL::Nef_polyhedron_3<Traits>::SFace}\\ 
\ccRefIdfierPage{CGAL::Nef_polyhedron_3<Traits>::SFace_cycle_iterator}\\ 
\ccRefIdfierPage{CGAL::Nef_polyhedron_3<Traits>::Shell_entry_iterator} 

\subsection*{Functions}
\ccThree{ostream&}{}{page 999.}

\ccHtmlNoLinks\ccHtmlNoIndex
\ccFunction{template <class Traits>
            ostream& operator<<( ostream& out, 
                                 const CGAL::Nef_polyhedron_3<Traits>& N);}
    {\lcRawHtml{<A HREF="Function_operator.html">(go there)</A>}
     \lcTex{\hfill page~\pageref{refNef_polyhedron_operator_leftshift_3}}}

\ccHtmlNoLinks\ccHtmlNoIndex
\ccFunction{template <class Traits>
            istream& operator>>( istream& in, 
                                 CGAL::Nef_polyhedron_3<Traits>& N);}
    {\lcRawHtml{<A HREF="Function_operator--.html">(go there)</A>}
     \lcTex{\hfill page~\pageref{refNef_polyhedron_operator_rightshift_3}}}

\lcHtml{\subsection*{Links to the Reference Sections}}

%% EOF %%