% +------------------------------------------------------------------------+
% | Reference manual page: SHalfedge.tex
% +------------------------------------------------------------------------+
% | 14.05.2004   Peter Hachenberger
% | Package: Nef_3
% | 
\RCSdef{\RCSSHalfedgeRev}{$Revision$}
\RCSdefDate{\RCSSHalfedgeDate}{$Date$}
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefClass}[Nef_polyhedron_3<Traits>::]{SHalfedge}

\ccDefinition

\ccInclude{CGAL/Nef_polyhedron_3.h}

\ccTypes
\ccThree{Halfedge_const_handle}{h.halfedge() const;;}{}
\ccThreeToTwo

\ccNestedType{Mark}{type of mark.}

\ccNestedType{Sphere_circle}{sphere circle type stored in SHalfedge.}

\ccNestedType{Halffacet_const_handle}{const handle to Halffacet.}
\ccGlue
\ccNestedType{SVertex_const_handle}{const handle to SVertex.}
\ccGlue
\ccNestedType{SHalfedge_const_handle}{const handle to SHalfedge.}
\ccGlue
\ccNestedType{SFace_const_handle}{const handle to SFace.}

\ccCreation
\ccCreationVariable{se}

\ccConstructor{SHalfedge();}{default constructor.}

\ccOperations

\ccMethod{const Mark& mark() const;}{the mark of \ccVar\ .}

\ccMethod{const Sphere_circle& circle() const;}{the sphere circle of \ccVar\ .}

\ccMethod{SHalfedge_const_handle twin() const;}{the twin of \ccVar\ .}

\ccMethod{SVertex_const_handle source() const;}{the source svertex of \ccVar\ .}

\ccMethod{SHalfedge_const_handle prev() const;}
{the SHalfedge previous to \ccVar\ in a facet cycle.}

\ccMethod{SHalfedge_const_handle next() const;}
{the next SHalfedge of \ccVar\ in a facet cycle.}

\ccMethod{SHalfedge_const_handle sprev() const;}
{the SHalfedge previous to \ccVar\ in a sface cycle.}

\ccMethod{SHalfedge_const_handle snext() const;}
{the next SHalfedge of \ccVar\ in a sface cycle.}

\ccMethod{Halffacet_const_handle incident_facet() const;}{the incident facet of \ccVar\ .}

\ccMethod{Halffacet_const_handle incident_sface() const;}{the incident sface of \ccVar\ .}

\ccSeeAlso

\ccRefIdfierPage{CGAL::Nef_polyhedron_3<Traits>::Halfedge}\\
\ccRefIdfierPage{CGAL::Nef_polyhedron_3<Traits>::Halffacet}\\
\ccRefIdfierPage{CGAL::Nef_polyhedron_3<Traits>::SFace}

\ccTagDefaults
\end{ccRefClass}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+
