% +------------------------------------------------------------------------+
% | Reference manual page: Halffacet.tex
% +------------------------------------------------------------------------+
% | 14.05.2004   Peter Hachenberger
% | Package: Nef_3
% | 
\RCSdef{\RCSFacetRev}{$Revision$}
\RCSdefDate{\RCSFacetDate}{$Date$}
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefClass}[Nef_polyhedron_3<Traits>::]{Halffacet}

\ccDefinition


\ccInclude{CGAL/Nef_polyhedron_3.h}

\ccTypes
\ccThree{Halfedge_const_handle}{h.halfedge() const;;}{}
\ccThreeToTwo

\ccNestedType{Mark}{type of mark.}

\ccNestedType{Plane_3}{plane type stored in Halffacet.}

\ccNestedType{Object_list}{list of Object handles.}

\ccNestedType{Halffacet_const_handle}{const handle to Halffacet.}
\ccGlue
\ccNestedType{Volume_const_handle}{const handle to volume.}
\ccGlue
\ccNestedType{Halffacet_cycle_const_iterator}
{const iterator over the entries to all halffacet cycles of a halffacet.}

\ccCreation
\ccCreationVariable{f}

\ccConstructor{Halffacet();}{default constructor.}

\ccConstructor{Halffacet(const Plane_3& h, Mark m);}
{creates Halffacet with initial values for its mark and supporting plane.}

\ccOperations

\ccMethod{const Mark& mark() const;}{the mark of \ccVar\ .}

\ccMethod{const Plane_3& plane() const;}{the supporting plane of \ccVar\ .}

\ccMethod{Halffacet_const_handle  twin() const;}{the twin of \ccVar\ .}

\ccMethod{Volume_const_handle  volume() const;}{the incident volume of \ccVar\ .}

\ccMethod{Halffacet_cycle_const_iterator  facet_cycle_begin() const;}
{iterator over the entries to all halffacet cycles of \ccVar\ .}

\ccMethod{Halffacet_cycle_const_iterator  facet_cycle_end() const;}
{past-the-end iterator.}

\ccMethod{const Object_list&  boundary_entry_objects() const;}
{list of entries to all halffacet cycles of \ccVar\ .}

\ccSeeAlso

\ccRefIdfierPage{CGAL::Nef_polyhedron_3<Traits>::Volume}\\
\ccRefIdfierPage{CGAL::Nef_polyhedron_3<Traits>::Halfedge}\\
\ccRefIdfierPage{CGAL::Nef_polyhedron_3<Traits>::SHalfedge}


\ccTagDefaults
\end{ccRefClass}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+
