% +------------------------------------------------------------------------+
% | Reference manual page: Triangulation_simplex_3.tex
% +------------------------------------------------------------------------+
% | 27.09.2005   Nico Kruithof
% | Package: Triangulation_3
% | 
\RCSdef{\RCSTriangulationsimplexRev}{$Id$}
\RCSdefDate{\RCSTriangulationsimplexDate}{$Date$}
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefClass}{Triangulation_simplex_3<Triangulation_3>}
\label{refTriangulationSimplex}

\ccDefinition The class \ccRefName\ stores a simplex of any dimension
defined by the \ccc{Triangulation_3} class. It also defines the
operator less such that simplices can be stored in a \ccc{map} or a
\ccc{set} of simplices. The simplex is invalidated by any change in
the triangulation.

\ccInclude{CGAL/Triangulation_simplex_3.h}

\ccParameters 
%
It is parameterized by the triangulation it derives the simplices
from. 

\ccTypes
\ccThree{typedef Triangulation_simplex_3<Triangulation_3>}{Triangulated}{}
\ccThreeToTwo

\ccTypedef{typedef Triangulation_simplex_3<Triangulation_3> Simplex;}{
  The simplex class itself.}

\ccTypedef{typedef Triangulation_3::Vertex_handle Vertex_handle;}{}
\ccGlue
\ccTypedef{typedef Triangulation_3::Edge Edge;}{}
\ccGlue
\ccTypedef{typedef Triangulation_3::Facet Facet;}{}
\ccGlue
\ccTypedef{typedef Triangulation_3::Cell_handle Cell_handle;}{}

\ccTypedef{typedef Triangulation_3::Cell_circulator Cell_circulator;}{}
\ccGlue
\ccTypedef{typedef Triangulation_3::Facet_circulator Facet_circulator;}{}

\ccTypedef{typedef Triangulation_3::Edge_iterator Edge_iterator;}{}
\ccGlue
\ccTypedef{typedef Triangulation_3::Facet_iterator Facet_iterator;}{}

\ccTypedef{typedef Triangulation_3::Finite_vertices_iterator Finite_vertices_iterator;}{}
\ccGlue
\ccTypedef{typedef Triangulation_3::Finite_edges_iterator Finite_edges_iterator;}{}
\ccGlue
\ccTypedef{typedef Triangulation_3::Finite_facets_iterator Finite_facets_iterator;}{}
\ccGlue
\ccTypedef{typedef Triangulation_3::Finite_cells_iterator Finite_cells_iterator;}{}


\ccCreation
\ccCreationVariable{simplex}  %% choose variable name
\ccThree{Triangulation_simplex_3<Triangulation_3>}{simplex}{}
\ccThreeToTwo

\ccConstructor{Triangulation_simplex_3();}{Initializes the simplex to
  an invalid simplex.}

\ccConstructor{Triangulation_simplex_3(Vertex_handle vh);}{}
\ccGlue
\ccConstructor{Triangulation_simplex_3(Edge e);}{}
\ccGlue
\ccConstructor{Triangulation_simplex_3(Facet f);}{}
\ccGlue
\ccConstructor{Triangulation_simplex_3(Cell_handle ch);}{}

\ccConstructor{Triangulation_simplex_3(Cell_circulator ccir);}{}
\ccGlue
\ccConstructor{Triangulation_simplex_3(Facet_circulator fcir);}{}

\ccConstructor{Triangulation_simplex_3(Edge_iterator eit);}{}
\ccGlue
\ccConstructor{Triangulation_simplex_3(Facet_iterator fit);}{}

\ccOperations
\ccThree{Vertex_handle}{Vertex_handle(simplex)xx}{}
\ccThreeToTwo

\ccMethod{int dimension () const;}{returns the dimension of the
  simplex.}
%
\ccMethod{operator Vertex_handle () const;}{Returns the \ccc{Vertex_handle}
  stored in the simplex. \ccPrecond{dimension() == 0}}
\ccGlue
\ccMethod{operator Edge () const;}{Returns the \ccc{Edge}
  stored in the simplex. \ccPrecond{dimension() == 1}}
\ccGlue
\ccMethod{operator Facet () const;}{Returns the \ccc{Facet}
  stored in the simplex. \ccPrecond{dimension() == 2}}
\ccGlue
\ccMethod{operator Cell_handle () const;}{Returns the \ccc{Cell_handle}
  stored in the simplex. \ccPrecond{dimension() == 3}}

\ccMethod{Cell_handle incident_cell () const;}{Returns a cell incident
  to the simplex.}


\ccMethod{bool operator==(const
  Triangulation_simplex_3<Triangulation_3> &s1);}{Test whether two
  simplices are equal.}
%
\ccGlue
%
\ccMethod{bool operator< (const
  Triangulation_simplex_3<Triangulation_3> &s1);}{Defines a ordering
  on the simplices. This ordering depends on the memory layout and is
  independent of the geometry.  Therefore, the ordering is not intrinsic}

\ccSeeAlso
\ccRefIdfierPage{CGAL::Triangulation_3<TriangulationTraits_3,TriangulationDataStructure_3>}

\end{ccRefClass}
