% +------------------------------------------------------------------------+
% | Reference manual page: Triangulation_cell_base_with_info_3.tex
% +------------------------------------------------------------------------+
% | 29.3.2000   Monique Teillaud
% | Package: Triangulation3
% | 
\RCSdef{\RCSTriangulationcellbaseRev}{$Id$}
\RCSdefDate{\RCSTriangulationcellbaseDate}{$Date$}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefClass}{Triangulation_cell_base_with_info_3<Info, TriangulationTraits_3, TriangulationCellBase_3>}

\ccDefinition

The class \ccc{Triangulation_cell_base_with_info_3} is a model of the concept
\ccc{TriangulationCellBase_3}, the base cell of a 3D-triangulation.
It provides an easy way to add some user defined information in cells.
Note that input/output operators discard this additional information.

\ccInclude{CGAL/Triangulation_cell_base_with_info_3.h}

\ccParameters

The first template argument is the information the user would like to add
to a cell.  It has to be \ccc{DefaultConstructible} and \ccc{Assignable}.

The second template argument is the geometric traits class
\ccc{TriangulationTraits_3}.  It is actually not used by this class.

The third template argument is a cell base class from which
\ccc{Triangulation_cell_base_with_info_3} derives.  It has the default value
\ccc{Triangulation_cell_base_3<TriangulationTraits_3>}.

\ccIsModel \ccc{TriangulationCellBase_3}

\ccInheritsFrom \ccc{TriangulationCellBase_3}

\ccTypes
\ccTypedef{typedef Info Info;}{}

\ccCreationVariable{v}

\ccAccessFunctions
\ccThree{const Info&}{Facetxxxxxxxx}{}
\ccTagFullDeclarations

\ccMethod{const Info& info() const;}
{Returns a const reference to the object of type \ccc{Info} stored in the cell.}
\ccGlue
\ccMethod{Info & info();}
{Returns a reference to the object of type \ccc{Info} stored in the cell.}

\ccSeeAlso

\ccc{CGAL::Triangulation_cell_base_3}\\
\ccc{CGAL::Triangulation_cell_base_with_circumcenter_3}
\ccc{CGAL::Triangulation_vertex_base_with_info_3}

\end{ccRefClass}
