% +------------------------------------------------------------------------+
% | Reference manual page: Event.tex
% +------------------------------------------------------------------------+
% | 20.03.2005   Author
% | Package: Kinetic_data_structures
% | 
\RCSdef{\RCSDelaunayTriangulationVisitorRev}{$Id: RegularTriangulationVisitor_3.tex 29411 2006-03-12 07:28:13Z drussel $}
\RCSdefDate{\RCSDelaunayTriangulationVisitorDate}{$Date: 2006-03-12 08:28:13 +0100 (Sun, 12 Mar 2006) $}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+
\begin{ccRefConcept}{Kinetic::RegularTriangulationVisitor3}

\ccDefinition

This concept is for proxy objects which get notified when a kinetic regular triangulation changes.

\ccCreationVariable{v}

\ccOperations

\ccMethod{void remove_vertex(Vertex_handle);}{The vertex is about to be deleted.}

\ccMethod{void create_vertex(Vertex_handle);}{The vertex was just created.}

\ccMethod{void modify_vertex(Vertex_handle);}{The trajectory of the vertex just changed.}

\ccMethod{template <class It>  void create_cells(It begin, It end);}{New faces have just been made. The iterator \ccc{value_type} is a \ccc{TriangulationDataStructure_3::Cell_handle}.}
 
\ccMethod{template <class It> void remove_cells(It, It);}{The faces in the range are about to be deleted.  The \ccc{value_type} of the iterator is a \ccc{TriangulationDataStructure_3::Cell_handle}.}

\ccMethod{void before_edge_flip(Edge);}{The edge is about to be flipped.}

\ccMethod{void after_edge_flip(Facet);}{The facet was just created with a flip.}

\ccMethod{void before_facet_flip(Facet);}{The facet is about to be flipped.}

\ccMethod{void after_facet_flip(Edge);}{The edge was just created with a flip.}

\ccMethod{void pre_move(Key, Cell);}{The point defined by \ccc{Key} is about to move from the cell.}

\ccMethod{void post_move(Key, Cell);}{The point defined by \ccc{Key} just moved to the cell.}

\ccMethod{void pre_push(Key, Cell);}{The point defined by the key is about to be inserted into the cell.}

\ccMethod{void post_push(Vertex_handle);}{The point referred to by the vertex handle was just added to the triangulation, it previously was redundant.}

\ccMethod{void pre_pop(Vertex_handle);}{The vertex is about to be removed from the triangulation since its weight is too small.}

\ccMethod{void post_pop(Key, Cell);}{The point was just removed from the triangulation.}


\ccHasModels 

\ccc{Kinetic::Regular_triangulation_visitor_base_3}, 
\ccc{Kinetic::Regular_triangulation_event_log_visitor_3}

\end{ccRefConcept}


