
\ccRefPageBegin


\begin{ccRefClass}{HalfedgeDS_halfedge_max_base_with_id<Refs>}

\ccDefinition
  
The class \ccRefName\ is a model of the \ccc{HalfedgeDSHalfedge}
concept. \ccc{Refs} is an instantiation of a \ccc{HalfedgeDS}. 
It is equivalent to \ccc{CGAL::HalfedgeDS_halfedge_base< Refs, 
CGAL::Tag_true, CGAL::Tag_true, CGAL::Tag_true>} with an added integer
field which can be used to index halfedges in {\sc Bgl} algorithms.
The class contains support for the previous, next, opposite, vertex and 
face pointers and the required type definitions.
It can be used for deriving own halfedges.

Note that the user is in charge to set the index correctly before
running a graph algorithm.


\ccInclude{CGAL/HalfedgeDS_halfedge_max_base_with_id.h}

\ccIsModel

\ccRefConceptPage{HalfedgeDSHalfedge}

\ccCreation
\ccCreationVariable{h}

\ccConstructor{HalfedgeDS_halfedge_max_base_with_id();}{default constructor.}

\ccMethod{int id() const;}
{Returns the index.}
\ccGlue
\ccMethod{int& id();}
{Returns a reference to the index stored in the halfedge.}

\ccSeeAlso

\ccRefConceptPage{HalfedgeDS<Traits,Items,Alloc>}\\
\ccRefConceptPage{HalfedgeDSItems}\\
\ccRefConceptPage{PolyhedronItems_3}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_min_items}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_vertex_min_base<Refs>}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_face_min_base<Refs>}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_halfedge_base<Refs>}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_vertex_max_base_with_id<Refs>}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_face_max_base_with_id<Refs>}\\
\ccRefIdfierPage{CGAL::Polyhedron_items_with_id_3}\\

\end{ccRefClass}


\ccRefPageEnd


