

\begin{ccRefClass}{Polyhedron_items_with_id_3}

\ccDefinition
  
The class \ccRefName\ is a model of the \ccc{PolyhedronItems_3}
concept.  It provides definitions for vertices with points, halfedges,
and faces with plane equations, all of them with an additional integer
field which can be used to index the items in a {\sc Bgl} algorithm.
The polyhedron traits class must provide the respective types for 
the point and the plane equation.
Vertices and facets both contain a halfedge handle to an incident
halfedge.

\ccInclude{CGAL/Polyhedron_items_with_id_3.h}

\ccIsModel

\ccRefIdfierPage{PolyhedronItems_3}

\ccHeading{Types in 
   \ccc{Polyhedron_items_with_id_3::Vertex_wrapper<Refs,Traits>::Vertex}}
\ccThree{CGAL::Polyhedron_items_with_id_3}{items;;;;}{}
\ccThreeToTwo
%%\ccTwo{CGAL::Polyhedron_items_with_id_3 items;;;}{}

\ccTypedef{typedef Traits::Point_3 Point;}{}
\ccGlue
\ccTypedef{typedef CGAL::Tag_true Supports_vertex_point;}{}


\ccHeading{Types in \ccc{Polyhedron_items_with_id_3::Face_wrapper<Refs,Traits>::Face}}

\ccTypedef{typedef Traits::Plane_3 Plane;}{}
\ccGlue
\ccTypedef{typedef CGAL::Tag_true Supports_face_plane;}{}
% No longer required.
%\ccGlue
%\ccTypedef{typedef Traits::Normal Normal;}{}
%\ccGlue
%\ccTypedef{typedef CGAL::Tag_true Supports_face_normal;}{}

\ccHeading{Additional methods in all three items.}

\ccCreationVariable{item}

\ccMethod{int id() const;}
{Returns the index.}
\ccGlue
\ccMethod{int& id();}
{Returns a reference to the index stored in the item.}

\ccCreation
\ccCreationVariable{items}  %% choose variable name

\ccConstructor{Polyhedron_items_with_id_3();}{default constructor.}

\ccOperations

Supported as required by the \ccc{PolyhedronItems_3} concept.

\ccSeeAlso

\ccRefIdfierPage{CGAL::Polyhedron_3<Traits>}\\
\ccRefIdfierPage{CGAL::Polyhedron_min_items_3}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_min_items}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_items_2}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_vertex_max_base_with_id<Refs>}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_halfedge_max_base_with_id<Refs>}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_face_max_base_with_id<Refs>}\\



\end{ccRefClass}
