% +------------------------------------------------------------------------+
% | Reference manual page: ApolloniusGraphHierarchyVertexBase_2.tex
% +------------------------------------------------------------------------+
% | 12.04.2000   Author
% | Package: Package
% | 
%\RCSdef{\RCSRegulartriangulationtraitsRev}{$Id$}
%\RCSdefDate{\RCSRegulartriangulationtraitsDate}{$Date$}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+

\begin{ccRefConcept}{ApolloniusGraphHierarchyVertexBase_2}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries
\ccCreationVariable{hvb}


\ccDefinition 
The vertex of an Apollonius graph
included in an Apollonius graph hierarchy has to provide
some pointers to the corresponding vertices in the
graphs of the next and preceding levels.
Therefore, the concept \ccc{ApolloniusGraphHierarchyVertexBase_2}
refines the concept \ccc{ApolloniusGraphVertexBase_2}, by
adding two vertex handles to the corresponding vertices for the
next and previous level graphs.


\ccRefines
\ccc{ApolloniusGraphVertexBase_2}


\ccTypes
\ccc{ApolloniusGraphHierarchyVertexBase_2} does not introduce any
types in addition to those of \ccc{ApolloniusGraphVertexBase_2}.


\ccCreation
\ccCreationVariable{v}  %% choose variable name
\ccTwo{ApolloniusGraphHierarchyVertexBase_2 v(Site_2 s, Face_handle f);++}{}
%
\ccConstructor{ApolloniusGraphHierarchyVertexBase_2();}{Default
constructor.}
\ccGlue
\ccConstructor{ApolloniusGraphHierarchyVertexBase_2(Site_2 s).}
{Constructs a vertex associated with the site \ccc{s} and
  embedded at the center of \ccc{s}.}
\ccGlue
\ccConstructor
{ApolloniusGraphHierarchyVertexBase_2(Site_2 s, Face_handle f).}
{Constructs a vertex associated with
the site \ccc{s}, embedded at the center of \ccc{s},
and pointing to face \ccc{f}.}


\ccOperations
\ccThree{Vertex_handle}{v.set_down(Vertex_handle d)+}{}
%
\ccMethod{Vertex_handle up();}{Returns a handle to the corresponding
  vertex of the next level Apollonius graph. If such a vertex does not
  exist \ccc{Vertex_handle(NULL)} is returned.}
\ccGlue
\ccMethod{Vertex_handle down();}{Returns a handle to the corresponding
  vertex of the previous level Apollonius graph.}
\ccGlue
\ccMethod{void set_up(Vertex_handle u);}{Sets the handle for the
  vertex of the next level Apollonius graph.} 
\ccGlue 
\ccMethod{void set_down(Vertex_handle d);}{Sets the handle for the
  vertex of the previous level Apollonius graph;}




\ccHasModels

\ccc{CGAL::Apollonius_graph_hierarchy_vertex_base_2<CGAL::Apollonius_graph_vertex_base_2<Gt,StoreHidden> >}


\ccSeeAlso

\ccc{ApolloniusGraphDataStructure_2} \\
\ccc{ApolloniusGraphVertexBase_2}\\
\ccc{CGAL::Apollonius_graph_hierarchy_2<Gt,Agds>}\\
\ccc{CGAL::Triangulation_data_structure_2<Vb,Fb>}\\
\ccc{CGAL::Apollonius_graph_vertex_base_2<Gt,StoreHidden>}\\
\ccc{CGAL::Apollonius_graph_hierarchy_vertex_base_2<Agvb>}

\end{ccRefConcept}


% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+
