% +------------------------------------------------------------------------+
% | Reference manual page: ApolloniusGraphVertexBase_2.tex
% +------------------------------------------------------------------------+
% | 12.04.2000   Author
% | Package: Package
% | 
%\RCSdef{\RCSRegulartriangulationtraitsRev}{$Id$}
%\RCSdefDate{\RCSRegulartriangulationtraitsDate}{$Date$}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+

\begin{ccRefConcept}{ApolloniusGraphVertexBase_2}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries
\ccCreationVariable{vb}
\ccDefinition

The concept \ccc{ApolloniusGraphVertexBase_2} describes the
requirements for the vertex base class of the
\ccc{ApolloniusGraphDataStructure_2} concept. A vertex stores an
Apollonius site and provides access to one of its incident faces
through a \ccc{Face_handle}. In addition, it maintains a container of
sites. The container stores the hidden sites related to the vertex.

\ccTypes
\ccTwo{ApolloniusGraphVertexBase_2::Hidden_sites_iterator+}{}
\ccNestedType{Geom_traits}{A type for the geometric traits that defines
the site stored. \ccPrecond{The type \ccc{Geom_traits} must
define the type \ccc{Site_2}.}}
%
\ccGlue
\ccNestedType{Store_hidden}{A Boolean that indicates if
  hidden sites are actually stored or not. Its value is \ccc{true} if
  hidden sites are stored, \ccc{false} otherwise.}
%
\ccGlue
\ccNestedType{Site_2}{A type for the site stored.
\ccPrecond{This type must coincide with the type
\ccc{Geom_traits::Site_2}.}}
%
\ccGlue
\ccNestedType{Apollonius_graph_data_structure_2}{A type for the
  Apollonius graph data structure, to which the vertex belongs to.}
%
\ccGlue
\ccNestedType{Vertex_handle}{A type for the vertex handle of the
  Apollonius graph data structure.}
%
\ccGlue
\ccNestedType{Face_handle}{A type for the face handle of the
  Apollonius graph data structure.}
%
\ccGlue
\ccNestedType{Hidden_sites_iterator}{An iterator that
iterates over the hidden sites in the hidden sites
container of the vertex.
\ccPrecond Must be a model of \ccc{Iterator}.}


\ccCreation
\ccCreationVariable{v}  %% choose variable name

\ccTwo{ApolloniusGraphVertexBase_2 v(Site_2 s, Face_handle f);++}{}
%
\ccConstructor{ApolloniusGraphVertexBase_2();}{Default constructor.}
\ccGlue
\ccConstructor{ApolloniusGraphVertexBase_2(Site_2 s);}
{Constructs a vertex associated with the Apollonius site \ccc{s} and
embedded at the center of \ccc{s}.}
\ccGlue
\ccConstructor{ApolloniusGraphVertexBase_2(Site_2 s,
  Face_handle f);}{Constructs a vertex associated with
  the site \ccc{s}, embedded at the center of \ccc{s},
  and pointing to the face associated with the face handle \ccc{f}.}





\ccAccessFunctions
\ccThree{Hidden_sites_iterator}{v.number_of_hidden_sites()+}{}
%
\ccMethod{Site_2 site();}
{Returns  the Apollonius site.}
\ccGlue
\ccMethod{Face_handle face();}{Returns a handle to an incident face.}
\ccGlue
\ccMethod{unsigned int number_of_hidden_sites();}
{Returns the number of hidden sites in the hidden
sites container.}
\ccGlue
\ccMethod{Hidden_sites_iterator
hidden_sites_begin();}
{Starts at an arbitrary hidden site.}
\ccGlue
\ccMethod{Hidden_sites_iterator hidden_sites_end();}
	 {Past-the-end iterator.}




\ccHeading{Setting and unsetting}
\ccThree{void}{v.clear_hidden_sites_container()+}{}
\ccMethod{void set_site(Site_2 s);}
{Sets the Apollonius site.}
\ccGlue
\ccMethod{void set_face(Face_handle f);}{Sets the incident face.}
\ccGlue
\ccMethod{void add_hidden_site(Site_2 s);}
{Adds a hidden site to the container of hidden sites.}
\ccGlue
\ccMethod{void clear_hidden_sites_container();}
{Clears the container of hidden sites.}




\ccHeading{Checking}
\ccMethod{bool is_valid(bool verbose, int level) const;}
{Performs any required tests on a vertex.}


\ccHasModels

\ccc{CGAL::Apollonius_graph_vertex_base_2<Gt,StoreHidden>}.


\ccSeeAlso

\ccc{ApolloniusGraphDataStructure_2}\\
\ccc{ApolloniusGraphTraits_2}\\
\ccc{CGAL::Apollonius_graph_vertex_base_2<Gt,StoreHidden>}

\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+
