% +------------------------------------------------------------------------+
% | intro.tex
% +------------------------------------------------------------------------+
% | chapter title, some introduction and a kind of table-of-contents
% +------------------------------------------------------------------------+

\ccRefChapter{Examples of \CC\ Reference Pages}
\ccChapterRelease{\ccRevision. \ \ccDate}\\
\ccChapterAuthor{Lutz Kettner and Susan Hert}

\section*{Summary}

This example chapter belongs to the documentation of the \LaTeX\ style
file {\tt cc\_manual.sty} and the related tools, for example, the
\LaTeX\ to HTML converter. See the related documention for the details.

This example contains a reference page for an item of each category except
variable (which will look the same as a constant):
concept, constant, class, enum, function, function object class, function
object concept, and macro. It documents no
particular functionality. It serves only as an example for the various
layouts. The actual \LaTeX\ sources and the README file in the {\tt
  Tools/example/} directory should be studied in parallel to the
formatted output since these files contain further comments and 
descriptions of the tools used to create these pages. 
For example, the
table-of-contents below uses not only the \verb+\ccRefIdfierPage+
macro, but needs also a more hand-written layout for the
\verb+is_empty_range+ function with its parameter list.  All items,
except concepts and macros, are given including the global scope.


\subsection*{Concepts}

\ccRefIdfierPage{Circulator} 

\subsection*{Function Object Concepts}

\ccRefIdfierPage{Kernel::Less_xy_2}

\subsection*{Classes}

\ccRefIdfierPage{CGAL::Circulator_traits<C>} 

\subsection*{Function Object Classes}

\ccRefIdfierPage{CGAL::Less_xy_2}

\subsection*{Enums}

\ccRefIdfierPage{CGAL::Orientation}\\
\ccRefIdfierPage{CGAL::POSITIVE}\\
\ccRefIdfierPage{CGAL::NEGATIVE}

\subsection*{Functions}

\ccThree{Orientation}{}{page 100}
\lcTex{\ccAutoIndexingOff}
\ccFunction{bool CGAL::is_empty_range ( IC i, IC j);}
    {\hfill \ccRefPage{CGAL::is_empty_range}}
\lcTex{\ccAutoIndexingOn}

\subsection*{Constants}

\ccRefIdfierPage{CGAL::ORIGIN}

\subsection*{Macros}

\ccc{For_all(i,j)}\hfill \ccRefPage{For_all}

\lcHtml{\section*{Alphabetical Listing of Reference Pages}}

%% EOF %%
