% +------------------------------------------------------------------------+
% | Reference manual page: Polyhedron_items_3.tex
% +------------------------------------------------------------------------+
% | 17.03.1999   Lutz Kettner
% | Package: Polyhedron
% | 
\RCSdef{\RCSPolyhedronitemsRev}{$Revision$}
\RCSdefDate{\RCSPolyhedronitemsDate}{$Date$}
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefClass}{Polyhedron_items_3}

\ccDefinition
  
The class \ccRefName\ is a model of the \ccc{PolyhedronItems_3}
concept.  It provides definitions for vertices with points, halfedges,
and faces with plane equations. The polyhedron traits class must
provide the respective types for the point and the plane equation.

\ccInclude{CGAL/Polyhedron_items_3.h}

\ccIsModel

\ccRefIdfierPage{PolyhedronItems_3}

\ccHeading{Types in 
   \ccc{Polyhedron_items_3::Vertex_wrapper<Refs,Traits>::Vertex}}
\ccThree{CGAL::Polyhedron_items_3}{items;;;;}{}
\ccThreeToTwo
%%\ccTwo{CGAL::Polyhedron_items_3 items;;;}{}

\ccTypedef{typedef Traits::Point_3 Point;}{}
\ccGlue
\ccTypedef{typedef CGAL::Tag_true Supports_vertex_point;}{}


\ccHeading{Types in \ccc{Polyhedron_items_3::Face_wrapper<Refs,Traits>::Face}}

\ccTypedef{typedef Traits::Plane_3 Plane;}{}
\ccGlue
\ccTypedef{typedef CGAL::Tag_true Supports_face_plane;}{}
% No longer required.
%\ccGlue
%\ccTypedef{typedef Traits::Normal Normal;}{}
%\ccGlue
%\ccTypedef{typedef CGAL::Tag_true Supports_face_normal;}{}

\ccCreation
\ccCreationVariable{items}  %% choose variable name

\ccConstructor{Polyhedron_items_3();}{default constructor.}

\ccOperations

Supported as required by the \ccc{PolyhedronItems_3} concept.

\ccSeeAlso

\ccRefIdfierPage{CGAL::Polyhedron_3<Traits>}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_min_items}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_items_2}

\ccExample

The following example program defines a new face class based on the
\ccc{CGAL::HalfedgeDS_face_base} and adds a new color member variable.
The new face class is used to replace the face definition in the
\ccc{CGAL::Polyhedron_items_3} class. The main function illustrates the
access to the new member variable.
See also the \ccc{PolyhedronItems_3} concept for another illustrative
example.

\ccIncludeExampleCode{Polyhedron/polyhedron_prog_color.C}

\end{ccRefClass}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+

