\lcTex{\chapter*{Preface}}
\lcHtml{\chapter{Preface}}

\cgal\ is a {\em Computational Geometry Algorithms Library} written in \CC, 
developed by a consortium consisting of
\ccAnchor{http://www.inf.ethz.ch/}{ETH Z\"urich} (Switzerland), 
\ccAnchor{http://www.inf.fu-berlin.de/}{Freie Universit{\"a}t Berlin} (Germany), 
\ccAnchor{http://www.inria.fr/Equipes/PRISME-eng.html}{{\sc Inria} 
Sophia-Antipolis} (France),
\ccAnchor{http://www.informatik.uni-halle.de/}{Martin-Luther-Universit{\"a}t 
Halle-Wittenberg} (Germany),
\ccAnchor{http://www.mpi-sb.mpg.de/}{Max-Planck-Institut f{\"u}r Informatik},
Saarbr\"ucken (Germany),
\ccAnchor{http://info.risc.uni-linz.ac.at/}{{\sc Risc}} Linz (Austria)
\ccAnchor{http://www.math.tau.ac.il/}{Tel-Aviv University} (Israel), and
\ccAnchor{http://www.cs.uu.nl/}{Utrecht University} (the Netherlands). 
You can find more information about the project on the
\ccAnchor{http://www.cgal.org}{\cgal\ home page}
\ccTexHtml{at URL {\tt http://www.cgal.org}}{}.


Should you have any questions, comments, remarks or criticism concerning 
\cgal, please send a message to 
\ccTexHtml{{\tt contact@cgal.org}}{<A HREF="mailto:contact@cgal.org">&#60;contact@cgal.org&#62;</A>}.

\section*{Editorial Committee}

Andreas Fabri ({\sc Inria} Sophia-Antipolis) \\
%Bernd G\"artner (ETH Z\"urich) \\
Susan Hert (\ccHtmlNoLinksFrom{Max-Planck Institut f\"ur Informatik})\\
Shai Hirsch (Tel-Aviv University) \\
Michael Hoffmann (ETH Z\"urich) \\
Lutz Kettner (\ccHtmlNoLinksFrom{Max-Planck Institut f\"ur Informatik})\\
Sylvain Pion ({\sc Inria} Sophia-Antipolis)\\
Monique Teillaud ({\sc Inria} Sophia-Antipolis)\\
Remco Veltkamp (Utrecht University)\\
Mariette Yvinec ({\sc Inria} Sophia-Antipolis)\\



\section*{Authors}

Chapter~\ref{Numbertype}: 
Olivier Devillers, Sylvain Pion ({\sc Inria} Sophia-Antipolis),
Lutz Kettner (ETH Z\"urich),
Susan Hert, Stefan Schirra (\ccHtmlNoLinksFrom{Max-Planck-Institut f\"ur Informatik}).

Chapter~\ref{chapterStlExtensions}: 
Michael Hoffmann, Lutz Kettner (ETH Z\"urich).

Chapter~\ref{chap:Handles_and_Circs}:
Olivier Devillers, Mariette Yvinec ({\sc Inria} Sophia-Antipolis),
Michal Seel (\ccHtmlNoLinksFrom{Max-Planck-Institut f\"ur Informatik}),
Lutz Kettner (ETH Z\"urich).

Chapter~\ref{chapterGenerators}: 
Susan Hert (\ccHtmlNoLinksFrom{Max-Planck-Institut f\"ur Informatik}),
Michael Hoffmann, Lutz Kettner, Sven Sch\"onherr (ETH Z\"urich).

Chapter~\ref{chap:Miscellany}:
Michal Seel (\ccHtmlNoLinksFrom{Max-Planck-Institut f\"ur Informatik}).
Lutz Kettner (ETH Z\"urich).

Chapter~\ref{Chapter_operator_for_IO_streams}: 
Andreas Fabri ({\sc Inria} Sophia-Antipolis),
Geert-Jan Giezeman (Utrecht University),
Lutz Kettner (ETH Z\"urich).

Chapter~\ref{chapterWin}:
Matthias B\"asken (Martin-Luther-Universit{\"a}t Halle-Wittenberg),
Andreas Fabri ({\sc Inria} Sophia-Antipolis),
Lutz Kettner (ETH Z\"urich),
Stefan Schirra (\ccHtmlNoLinksFrom{Max-Planck-Institut f\"ur Informatik}).

Chapter~\ref{chapterGeoWin}:
Matthias B\"asken (Martin-Luther-Universit{\"a}t Halle-Wittenberg).

Chapter~\ref{ChapterGeomview}:
Andreas Fabri, Mariette Yvinec ({\sc Inria} Sophia-Antipolis).

Chapter~\ref{chapterQtwidget}:
Radu Ursu ({\sc Inria} Sophia-Antipolis).

\section*{Acknowledgement}

This work was supported
by the ESPRIT IV Long Term Research Projects No.~21957 (CGAL)
and No.~28155 (GALIA).


