
\begin{ccRefClass}{leda_rat_kernel_traits}

\ccDefinition

\ccInclude{CEP/Leda_rat_kernel/leda_rat_kernel_traits.h}

The class \ccRefName\  is a model for a CGAL kernel. This model uses the LEDA rational geometry
for the geometric predicates of the kernel.

\ccCreationVariable{LRK}


\ccHtmlLinksOff


\ccTypes

The class \ccRefName\ provides all type definitions required by the CGAL kernel concept
for Two-dimensional and Three-dimensional kernel. Please notice that
you have to define the macro \ccc{CGAL\_PROVIDE\_LEDA\_RAT\_KERNEL\_TRAITS\_3} before
including \ccc{leda\_rat\_kernel\_traits.h} when you want to use the Three-dimensional kernel.
We list only the geometric object types and some special types in this manual page; the type names
for the constructors and generalized predicate functors are documented for all CGAL
compatible kernels in the kernel manual (that's why they are not listed here, but of course
they are also in the class \ccRefName\ ).
Some of the type names in the documentation are prefixed by \ccc{LEDA\_NAMESPACE\_NAME};
that means that these types are in global scope for LEDA versions without a namespace
(LEDA 4.3) and that they are in namespace \ccc{leda} for LEDA versions with a namespace 
(LEDA 4.4 or higher).
The class \ccRefName\ obviously provides no type equality for its types with the CGAL types.

\ccThree{typedef leda_rat_point Point_2;}{the point type}{}
\ccThreeToTwo
\ccTypedef{typedef leda_rational FT;}{the field number type}
\ccTypedef{typedef leda_integer  RT;}{the ring number type}
\ccTypedef{typedef leda_rat_point Point_2;}{the 2d point type}
\ccTypedef{typedef leda_rat_vector Vector_2;}{the 2d vector type}
\ccTypedef{typedef LEDA_NAMESPACE_NAME::rat_direction Direction_2;}{the 2d direction type}
\ccTypedef{typedef leda_rat_line Line_2;}{the 2d line type}
\ccTypedef{typedef leda_rat_ray  Ray_2;}{the 2d ray type}
\ccTypedef{typedef leda_rat_segment Segment_2;}{the 2d segment type}
\ccTypedef{typedef leda_rat_triangle   Triangle_2;}{the 2d triangle type}
\ccTypedef{typedef leda_rat_rectangle  Iso_rectangle_2;}{the 2d isorectangle type}

If the macro \ccc{CGAL\_COMPATIBLE\_CIRCLES} is defined we provide a CGAL-compatible circle class
storing a center point and a squared radius.

\ccTypedef{typedef LEDA_NAMESPACE_NAME::cgal_rat_circle  Circle_2;}{the 2d circle type}

Otherwise our circle class is the default class from the LEDA kernel:

\ccTypedef{typedef leda_rat_circle Circle_2;}{the 2d circle type}
\ccTypedef{typedef CGAL::Object  Object_2;}{the 2d object type}

3d kernel types (use macro  \ccc{CGAL\_PROVIDE\_LEDA\_RAT\_KERNEL\_TRAITS\_3} ):

\ccTypedef{typedef leda_d3_rat_point Point_3;}{the 3d point type}
\ccTypedef{typedef leda_rat_vector   Vector_3;}{the 3d vector type}
\ccTypedef{typedef LEDA_NAMESPACE_NAME::rat_direction  Direction_3;}{the 3d direction type}
\ccTypedef{typedef LEDA_NAMESPACE_NAME::d3_rat_iso_cuboid  Iso_cuboid_3;}{the 3d isocuboid type}
\ccTypedef{typedef leda_d3_rat_line     Line_3;}{the 3d line type}
\ccTypedef{typedef leda_d3_rat_ray      Ray_3;}{the 3d ray type}
\ccTypedef{typedef leda_d3_rat_segment  Segment_3;}{the 3d segment type}

If the macro \ccc{CGAL\_COMPATIBLE\_SPHERES} is defined we provide a CGAL-compatible sphere class
storing a center point and a squared radius.

\ccTypedef{typedef LEDA_NAMESPACE_NAME::cgal_d3_rat_sphere  Sphere_3;}{the 3d sphere type}

Otherwise our sphere class is the default class from the LEDA 3d kernel:

\ccTypedef{typedef leda_d3_rat_sphere   Sphere_3;}{the 3d sphere type} 
 
\ccTypedef{typedef leda_d3_rat_plane         Plane_3;}{the 3d plane type}
\ccTypedef{typedef leda_d3_rat_triangle      Triangle_3;}{the 3d triangle type}
\ccTypedef{typedef LEDA_NAMESPACE_NAME::d3_rat_simplex       Tetrahedron_3;}{the 3d tetrahedron type}
\ccTypedef{typedef CGAL::Object              Object_3;}{the 3d object type}

Some packages of the CGAL basic library that are not fully kernel traits compatible
have an additional requirements for their traits classes - they need a polygon type definition.
An example is the Partition package. To meet this requirement we give the option to have a
polygon type definition in the LEDA rational kernel traits class; 
compile with the macro \ccc{CGAL\_PROVIDE\_LEDA\_PARTITION\_TRAITS} to
include the following polygon type definition in \ccRefName\ :

\ccTypedef{typedef CGAL::Polygon_2<CGAL::leda_rat_kernel_traits, std::list<leda_rat_point> > Polygon_2;}{the polygon type} 

All the type definitions for construction functors and for generalized predicate functors that
are required in a model for a 2-d/3-d CGAL kernel are provided. The type names
can be found in the CGAL kernel manual. I give one example:

\ccTypedef{typedef Construct_leda_rat_point  Construct_point_2;}{the construction functor for 2d points}


\ccHtmlLinksOn


\ccCreation

\ccConstructor{leda_rat_kernel_traits();}
{creates an object of type \ccRefName\ .}


\ccOperations

All access functions needed in a model for the CGAL 2-d/3-d kernel concept are provided.
The names of these access functions are the same in all kernels (see the CGAL kernel manual 
for details). I give one example for the point constructor:

\ccMethod{Construct_point_2  construct_point_2_object();}
{ returns a point construction object.}

\ccHtmlLinksOn

\end{ccRefClass} 
