\begin{ccRefConcept}{ConformingDelaunayTriangulationTraits_2}

\ccDefinition

In addition of the requirements of the concept
\ccc{DelaunayTriangulationTraits_2}, a model of the concept \ccRefName\ has
to provide a numeric field type \ccc{FT}, a type \ccc{Vector_2} and several
constructors on \ccc{Vector_2} and \ccc{Point_2}. These constructors are
used by the conforming algorithm to compute Steiner points on constrained
edges.

\ccRefines

\ccc{DelaunayTriangulationTraits_2}

\ccTypes

\ccNestedType{FT}{The field type.}
\ccNestedType{Vector_2}{The vector type.}
\ccNestedType{Construct_vector_2}{Constructor object. Must
  provide the operator \ccc{Vector_2 operator()(Point a, Point b)}
  that computes the vector $b-a$.}
\ccNestedType{Construct_scaled_vector_2}{Constructor object. Must
  provide the operator \ccc{Vector_2 operator()(Vector_2 v, FT scale)}
  that computes the vector $scale \cdot \mathbf{v}$.}
\ccNestedType{Construct_translated_point_2}{Construct object. Must
  provide the operator \ccc{Point_2 operator()(Point_2 p, Vector_2 v)}
  that computes the point $p + \mathbf{v}$.}
\ccNestedType{Construct_midpoint_2}{Constructor object. Must provide
  the operator \ccc{Point_2 operator()(Point_2 a, Point_2 b)} that
  computes the middle point of the segment $ab$.}
\ccNestedType{Compute_squared_distance_2}{Constructor object. Must
  provide the operator \ccc{FT operator()(Point_2 a, Point_2 b)} that
  computes the squared distance between $a$ and $b$.}

\ccCreationVariable{traits}

\ccHeading{Access to predicate and constructor objects}

\ccTwo{Construct_translated_point_2}{}
\ccMethod{Construct_vector_2 construct_vector_2_object();}{}
\ccGlue
\ccMethod{Construct_scaled_vector_2 construct_scaled_vector_2_object();}{}
\ccGlue
\ccMethod{Construct_translated_point_2
  construct_translated_point_2_object();}{}
\ccGlue
\ccMethod{Constructor_midpoint_2 construct_midpoint_2_object();}{}
\ccGlue
\ccMethod{Compute_squared_distance_2
  compute_squared_distance_2_object();}{}

\ccHasModels
Any model of the \ccc{Kernel} concept. In particular, all CGAL kernels.

\end{ccRefConcept}

%%% For emacs/AucTeX:
%%% Local Variables: ***
%%% mode:latex ***
%%% TeX-master: "ref_manual.tex"  ***
%%% End: ***
