%% Copyright (c) 2005  Foundation for Research and Technology-Hellas (Greece).
%% All rights reserved.
%%
%% This file is part of CGAL (www.cgal.org); you may redistribute it under
%% the terms of the Q Public License version 1.0.
%% See the file LICENSE.QPL distributed with CGAL.
%%
%% Licensees holding a valid commercial license may use this file in
%% accordance with the commercial license agreement provided with the software.
%%
%% This file is provided AS IS with NO WARRANTY OF ANY KIND, INCLUDING THE
%% WARRANTY OF DESIGN, MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE.
%%
%% $Source$
%% $Revision$ $Date$
%% $Name$
%%
%% Author(s)     : Menelaos Karavelas <mkaravel@tem.uoc.gr>



\begin{ccRefConcept}{DelaunayGraphNearestSiteQueryResult_2}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries
\ccDefinition

The concept \ccc{DelaunayGraphNearestSiteQueryResult_2} defines the
requirements of the \ccc{Query_result} type defined in the
\ccc{DelaunayGraphNearestSite_2} 
concept. Essentially it provides the requirements for a class
representing the result type of a nearest site query performed on a
Delaunay graph. Semantically, the query result is either a face, edge or
vertex of the Delaunay graph. It is a face if the query point is
equidistant to at least three vertices of the Delaunay graph, namely
the three vertices of the returned face. It is an edge if the query
point is equidistant to exactly two vertices of the Delaunay graph,
which are the source and target vertices of the edge. In all other
cases, the query result is a vertex, namely, the unique vertex of the
Delaunay graph closest to the query point. The
\ccc{DelaunayGraphNearestSiteQueryResult_2} concept encapsulates the semantics
described above.

\ccRefines
\ccc{DefaultConstructible}, \ccc{CopyConstructible}, \ccc{Assignable},
\ccc{EqualityComparable}

\ccTypes
\ccThree{typedef Delaunay_graph::Vertex_handle}{Vertex_handle+}{}
\ccTwo{DelaunayGraphNearestSiteQueryResult_2::Delaunay_graph+}{}
%\ccThreeToTwo
%
\ccNestedType{Delaunay_graph}{A type for the Delaunay graph. It must be a
  model of the \ccc{DelaunayGraph_2} concept.}
%\ccGlue
\ccTypedef{typedef Delaunay_graph::Vertex_handle Vertex_handle;}{Handle
  for the vertices of the Delaunay graph.}
\ccGlue
\ccTypedef{typedef Delaunay_graph::Face_handle Face_handle;}{Handle
  for the faces of the Delaunay graph.}
\ccGlue
\ccTypedef{typedef Delaunay_graph::Edge Edge;}{Type for the edges of the
  Delaunay graph.}

\ccCreationVariable{qr}  %% choose variable name


\ccHeading{Predicate Methods}
\ccThree{bool}{qr.is_vertex()+}{}
\ccThreeToTwo
%
\ccMethod{bool is_vertex();}{Returns \ccStyle{true} iff the result of
  the point location corresponds to a vertex of the Delaunay graph,
  i.e., iff the query point is closest to a single vertex of the
  Delaunay graph.}
\ccGlue
\ccMethod{bool is_edge();}{Returns \ccStyle{true} iff the result of
  the point location corresponds to an edge of the Delaunay graph,
  i.e., iff the query point is closest to exactly two vertices of the
  Delaunay graph, which are the source and target vertex of the
  afore-mentioned edge of the Delaunay graph.}
\ccGlue
\ccMethod{bool is_face();}{Returns \ccStyle{true} iff the result of
  the point location corresponds to a face of the Delaunay graph,
  i.e., iff the query point is closest to at least three vertices of
  the Delaunay graph, which are three vertices of the afore-mentioned
  face of the face of the Delaunay graph.}

\ccHeading{Conversion Operators}
\ccThree{Vertex_handle}{Vertex_handle(lr)+}{}
\ccThreeToTwo
%
\ccMethod{operator Vertex_handle();}{Converts to a vertex handle
  representing the vertex of the Delaunay graph which is the result of
  the point location query.
\ccPrecond{\ccc{is_vertex()} must be \ccStyle{true}.}}
%
\ccGlue
\ccMethod{operator Edge();}{Converts to the edge of the Delaunay graph
  which is the result of the point location query.
\ccPrecond{\ccc{is_edge()} must be \ccStyle{true}.}}
%
\ccGlue
\ccMethod{operator Face_handle();}{Converts to a handle to the face of the
  Delaunay graph which is the result of the point location query.
\ccPrecond{\ccc{is_face()} must be \ccStyle{true}.}}


\ccHasModels
\ccc{CGAL::Apollonius_graph_Voronoi_traits_2<AG2>::Nearest_site_2::Query_result}\\
\ccc{CGAL::Delaunay_triangulation_Voronoi_traits_2<DT2>::Nearest_site_2::Query_result}\\
\ccc{CGAL::Regular_triangulation_Voronoi_traits_2<RT2>::Nearest_site_2::Query_result}\\
\ccc{CGAL::Segment_Voronoi_diagram_Voronoi_traits_2<SVD2>::Nearest_site_2::Query_result}

\ccSeeAlso
\ccc{VoronoiTraits_2}\\
\ccc{DelaunayGraphPointLocator_2}\\
\ccc{CGAL::Apollonius_graph_Voronoi_traits_2<AG2>}\\
\ccc{CGAL::Delaunay_triangulation_Voronoi_traits_2<DT2>}\\
\ccc{CGAL::Regular_triangulation_Voronoi_traits_2<RT2>}\\
\ccc{CGAL::Segment_Voronoi_diagram_Voronoi_traits_2<SVD2>}
\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

