%% Copyright (c) 2005  Foundation for Research and Technology-Hellas (Greece).
%% All rights reserved.
%%
%% This file is part of CGAL (www.cgal.org); you may redistribute it under
%% the terms of the Q Public License version 1.0.
%% See the file LICENSE.QPL distributed with CGAL.
%%
%% Licensees holding a valid commercial license may use this file in
%% accordance with the commercial license agreement provided with the software.
%%
%% This file is provided AS IS with NO WARRANTY OF ANY KIND, INCLUDING THE
%% WARRANTY OF DESIGN, MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE.
%%
%% $Source$
%% $Revision$ $Date$
%% $Name$
%%
%% Author(s)     : Menelaos Karavelas <mkaravel@tem.uoc.gr>



\begin{ccRefConcept}{VoronoiDiagramFace_2}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries
\ccDefinition

The concept \ccc{VoronoiDiagramFace_2} defines the requirements of the
face provided by the class \ccc{Voronoi_diagram_2}.

\ccRefines
\ccc{DefaultConstructible}\\
\ccc{CopyConstructible}\\
\ccc{Assignable}\\
\ccc{EqualityComparable}\\
\ccc{LessThanComparable}

\ccTypes
%
\ccTwo{VoronoiDiagramFace_2::Ccb_halfedge_circulator+}{}
\ccNestedType{Vertex}{A type for the vertices of the Voronoi diagram.}
\ccGlue
\ccNestedType{Halfedge}{A type for the halfedges of the Voronoi diagram.}
\ccGlue
\ccNestedType{Vertex_handle}{Handle for the vertices of the Voronoi diagram.}
\ccGlue
\ccNestedType{Face_handle}{Handle for the faces of the Voronoi diagram.}
\ccGlue
\ccNestedType{Halfedge_handle}{Handle for the halfedges of the Voronoi
  diagram.}
\ccGlue
\ccNestedType{Ccb_halfedge_circulator}{A type for a bidirectional
  circulator over the halfedges of the connected components of the
  boundary of the face. The value type of the circulator is
  \ccc{Halfedge}.}
%% \ccGlue
%% \ccNestedType{Holes_iterator}{A type for a bidirectional iterator over
%%   the holes in the face. Since we have a Voronoi diagram that is a
%%   model of an abstract Voronoi diagram, such holes do not exist. The
%%   value type of the iterator is \ccc{Halfedge}.
%%   This iterator is simply added for similarity with arrangements.}
%
\ccThree{typedef typename Delaunay_graph::Vertex_handle}{Delaunay_vertex_handle;}{}
\ccThreeToTwo
%
\ccNestedType{Delaunay_graph}{A type for the Delaunay graph. It must be a
  model of the \ccc{DelaunayGraph_2} concept.}
\ccTypedef{typedef typename Delaunay_graph::Vertex_handle
  Delaunay_vertex_handle;}{A type for the handle to a dual vertex.}

\ccCreationVariable{f}  %% choose variable name


\ccHeading{Access Methods}
\ccThree{Ccb_halfedge_circulator}{f.outer_ccb()+}{}
%\ccThree{Dual_vertex_handle}{f.dual_vertex()+}{}
%
\ccMethod{Halfedge_handle halfedge();}{Returns an incident halfedge on
  the (outer connected component of the) boundary of \ccc{f}.}
%\ccGlue
%\ccMethod{Halfedge_handle halfedge_on_outer_ccb();}{Same as
%  \ccc{f.halfedge()}.}
\ccGlue
\ccMethod{Ccb_halfedge_circulator ccb();}{Returns a circulator for
  traversing the boundary of \ccc{f}.}
%% \ccGlue
%% \ccMethod{Holes_iterator holes_begin();}{Starts at an arbitrary halfedge
%%   on the boundary of a hole inside \ccc{f}. Since the faces in
%%   abstract Voronoi diagrams do not do not have holes, this method and
%%   the one below have been added for compliance with arrangements.}
%% \ccGlue
%% \ccMethod{Holes_iterator holes_end();}{Past-the-end iterator.}
%
\ccMethod{Delaunay_vertex_handle dual();}
{Returns a handle to the dual vertex, i.e., the
  corresponding dual vertex in the Delaunay graph.}

\ccHeading{Predicate Methods}
\ccThree{bool}{f.is_halfedge_on_outer_ccb(Halfedge e)+}{}
\ccMethod{bool is_unbounded();}{Returns \ccStyle{true} if the face in
  an unbounded face in the Voronoi diagram.}
%\ccGlue
%\ccMethod{bool is_halfedge_on_inner_ccb(Halfedge e);}{Returns
%  \ccStyle{true} if is \ccc{e} is a halfedge of an inner CCB of
%  \ccc{f}. Since in Voronoi diagrams, faces do not have holes, this
%  method is really not needed. It has been added for compliance with
%  arrangements.}
%\ccGlue
\ccMethod{bool is_halfedge_on_ccb(Halfedge e);}{Returns
  \ccStyle{true} if \ccc{e} is a halfedge of the boundary of
  \ccc{f}.}
\ccGlue
\ccMethod{bool is_valid();}{Returns \ccStyle{true} if the following
  conditions are met: the face does not have zero area; all its
  adjacent halfedges do not have zero length; all its adjacent
  halfedges return the face as their adjacent face.}

\ccHasModels
\ccc{CGAL::Voronoi_diagram_2<DG,VT>::Face}\\

\ccSeeAlso
\ccc{VoronoiDiagramVertex_2}\\
\ccc{VoronoiDiagramHalfedge_2}\\
\ccc{DelaunayGraph_2]\\
\ccc{CGAL::Voronoi_diagram_2<DG,VT>}
\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

