\ccUserChapter{Principal Component Analysis\label{chap:pca}}

\ccChapterAuthor{Pierre Alliez, Sylvain Pion and Ankit Gupta}

\minitoc

\input{Principal_component_analysis/intro}
\input{Principal_component_analysis/PkgDescription}

\section{Examples\label{subsec:pca_examples}}

\subsection{Bounding Box of a Point Set}

In the following example we use \stl\ containers of 2D and 3D points, and compute their axis-aligned bounding box. The kernel from which the input points originate is automatically deduced by the function.

\ccIncludeExampleCode{Principal_component_analysis/bounding_box.cpp}

\subsection{Centroid of a Point Set}

In the following example we use \stl\ containers of 2D and 3D points, and compute their centroid. The kernel from which the input points originate is automatically deduced by the function.

\ccIncludeExampleCode{Principal_component_analysis/centroid.cpp}

\subsection{Barycenter of a Set of Weighted Points}

In the following example we use \stl\ containers of 2D and 3D weighted points, and compute their barycenter. The kernel from which the input points originate is automatically deduced by the function.

\ccIncludeExampleCode{Principal_component_analysis/barycenter.cpp}

\subsection{Best Fitting Line of a 2D Point Set}

In the following example we use an \stl\ container of 2D points, and compute the best fitting line in the least squares sense. The kernel from which the input points originate is automatically deduced by the function.

\ccIncludeExampleCode{Principal_component_analysis/linear_least_squares_fitting_points_2.cpp}

