% +------------------------------------------------------------------------+
% | Reference manual page: SpatialPoint.tex
% +------------------------------------------------------------------------+
% | 1.07.2001   Johan W.H. Tangelder
% | Package: ASPAS
% | 
\RCSdef{\RCSSpatialPointRev}{$Id$}
\RCSdefDate{\RCSSpatialPointDate}{$Date$}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefConcept}{SearchTraits}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries

\ccDefinition
  
The concept \ccClassTemplateName\ defines the requirements for the template 
parameter of the search classes.  

\ccTypes

\ccNestedType{Point_d}{Point type. \ccc{CGAL::Kernel_traits} has to be
specialized for this type.}


\ccNestedType{Iso_box_d}{Iso box type. It is only needed for range search queries.}
\ccNestedType{Sphere_d}{Sphere type. It is only needed for range search queries.}

\ccNestedType{FT}{The number type of the \ccHtmlNoLinksFrom{Cartesian} coordinates of types \ccc{Point_d}}


\ccNestedType{Cartesian_const_iterator_d}{An random access iterator type to enumerate the 
\ccHtmlNoLinksFrom{Cartesian} coordinates of a point.}

\ccNestedType{Construct_cartesian_const_iterator_d}{Functor with operators to construct iterators on the
first and the past-the-end iterator for the \ccHtmlNoLinksFrom{Cartesian} coordinates of a point.}

%\ccNestedType{Construct_iso_box_d}{Functor with operator to construct the iso box from two points.}
%
\ccNestedType {Construct_center_d}{Functor with operator to construct 
the center of an object of type \ccc{Sphere_d}.}

\ccNestedType {Construct_squared_radius_d}{Functor with operator to compute 
the squared radius of a an object of type \ccc{Sphere_d}.}

\ccNestedType {Construct_min_vertex_d}{Functor with operator to construct 
the vertex with lexicographically smallest coordinates of an object of type \ccc{Iso_box_d}.}

\ccNestedType {Construct_max_vertex_d}{Functor with operator to construct 
the vertex with lexicographically largest coordinates of an object of type \ccc{Iso_box_d}.}




\ccHasModels
\ccc{CGAL::Cartesian_d<FT>}\\
\ccc{CGAL::Homogeneous_d<RT>}\\
\ccc{CGAL::Search_traits_2<Kernel>}\\
\ccc{CGAL::Search_traits_3<Kernel>}, \\
\ccc{CGAL::Search_traits<NT,Point,CartesianCoordinateIterator,ConstructCartesianCoordinateIterator,ConstructMinVertex,ConstructMaxVertex>}.


\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

