% +------------------------------------------------------------------------+
% | Reference manual page: Periodic_2Offset_2.tex
% +------------------------------------------------------------------------+
% | 16.03.2010   Nico Kruithof <Nico@nghk.nl>
% | Package: Package
% |
\RCSdef{\RCSPeriodicOffsetRev}{$Id$}
\RCSdefDate{\RCSPeriodicOffsetDate}{$Date$}
% |
\ccRefPageBegin
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+

\begin{ccRefConcept}{Periodic_2Offset_2}

\ccDefinition
The concept \ccc{Periodic_2Offset_2} describes a two-\/dimensional integer vector with some specialized access functions and operations.

\ccCreation
\ccCreationVariable{o}

\ccThree{Periodic_2Offset_2}{Offsetxxxxxxxxxxxxxxxxxxxxxxxxxxxxx}{}

\ccConstructor{Periodic_2Offset_2();}
{Default constructor.}
\ccGlue
\ccConstructor{Periodic_2Offset_2(int x, int y);}
{Constructs the offset (x,y).}

\ccOperations
\ccThree{Periodic_2Offset_2}{xxxxxxxxxxxxxxxxxxxxx}{}
\ccMethod{Periodic_2Offset_2 operator+(const Periodic_2Offset_2 & o')
  const;}
{Return the vector sum of \ccc{o} and \ccc{o'}.}
\ccGlue
\ccMethod{Periodic_2Offset_2 operator-(const Periodic_2Offset_2 & o')
  const;}
{Return the vector difference of \ccc{o} and \ccc{o'}.}
\ccGlue
\ccMethod{Periodic_2Offset_2 operator-() const;}
{Return the negative vector of \ccc{o}.}
\ccGlue
\ccMethod{void operator+=(const Periodic_2Offset_2 & o')
  const;}
{Add \ccc{o'} to \ccc{o} using vector addition.}
\ccGlue
\ccMethod{void operator-=(const Periodic_2Offset_2 & o')
  const;}
{Subtract \ccc{o'} from \ccc{o} using vector subtraction.}
\ccGlue
\ccMethod{bool operator==(const Periodic_2Offset_2 & o') const;}
{Return \ccc{true} if \ccc{o'} and \ccc{o} represent the same vector.}
\ccGlue
\ccMethod{bool operator!=(const Periodic_2Offset_2 & o') const;}
{Return \ccc{true} if \ccc{o'} and \ccc{o} do not represent the same
  vector.}
\ccGlue
\ccMethod{bool operator<(const Periodic_2Offset_2 & o') const;}
{Compare \ccc{o} and \ccc{o'} lexicographically.}

\ccAccessFunctions

\ccMethod{int operator[](int i);}
{Return the $i$-th entry of \ccc{o}. \ccPrecond{$i\in\{0,1\}$}}
\ccGlue
\ccMethod{int x() const;}
{Return the $x$-entry of \ccc{o}.}
\ccGlue
\ccMethod{int y() const;}
{Return the $y$-entry of \ccc{o}.}
\ccGlue
\ccMethod{bool is_null() const;}
{Returns \ccc{true} if \ccc{o} is equal to (0,0).}
\ccGlue
\ccMethod{bool is_zero() const;}
{Returns \ccc{true} if \ccc{o} is equal to (0,0).}

\ccHeading{I/O}
\ccFunction{istream& operator>>(istream & is, Periodic_2Offset_2
  & off);}
{Inputs an offset from \ccc{is}.}
\ccGlue
\ccFunction{ostream& operator<<(ostream & os, Periodic_2Offset_2
  & off) const;}
{Outputs an offset from \ccc{os}.}


\ccHasModels

\ccc{CGAL::Periodic_2_offset_2}

\ccSeeAlso

\ccc{Periodic_2TriangulationTraits_2}\\
\ccc{Periodic_2DelaunayTriangulationTraits_2}

\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+

