% +------------------------------------------------------------------------+
% | Reference manual page: Predicate_traits_d.tex
% +------------------------------------------------------------------------+

\begin{ccRefClass}[Box_intersection_d::]{Predicate_traits_d<BoxTraits,bool closed>}
\begin{ccAdvanced}

\ccDefinition

Default implementation of the \ccc{BoxIntersectionPredicateTraits_d}
concept. This very fine-grained predicate traits concept allows the
hand-crafted implementation of the individual interval comparison
tests. This is only for experts and might only be useful in the
context of special number types or exploitation of special assembler
instructions!  This generic default implementation is likely to
suffice for all practical purposes.

\begin{itemize}
  \item
    \ccc{BoxTraits}: requires the \ccc{BoxIntersectionTraits_d} concept.
  \item
    \ccc{bool closed}: specifies the topology, which can be half-open
    or closed. In the half-open case, two adjacent boxes do not
    intersect, whereas in the closed case they do.
\end{itemize}

\ccInclude{CGAL/Box_intersection_d/Box_traits_d.h}
and also automatically with\\
\ccInclude{CGAL/box_intersection_d.h}

\ccIsModel

\ccRefConceptPage{BoxIntersectionPredicateTraits_d}

\ccCreation
\ccCreationVariable{traits}

\ccConstructor{Predicate_traits_d();}{default constructor.}

\ccSeeAlso

\ccRefIdfierPage{CGAL::box_intersection_custom_predicates_d}\\
\ccRefIdfierPage{CGAL::box_intersection_all_pairs_custom_predicates_d}

\ccRefConceptPage{BoxIntersectionTraits_d}

\end{ccAdvanced}
\end{ccRefClass}

