% =============================================================================
% The CGAL Reference Manual
% Chapter: Geometric Optimisation
% -----------------------------------------------------------------------------
% file   : doc_tex/basic/Optimisation/Optimisation_ref/reference_part.tex
% package: Optimisation_doc
% author : Sven Schönherr <sven@inf.ethz.ch>
% -----------------------------------------------------------------------------
% $Revision$
% $Date$
% =============================================================================

\newcommand{\inputOpt}[1]{\input{Optimisation_ref/#1.tex}}

\newcommand{\linebreakByHand}{\ccTexHtml{\linebreak[4]}{}}
\newcommand{  \newlineByHand}{\ccTexHtml{\\}{}}

% cross references
\index{minimum enclosing|see{{smallest enclosing}}}
\index{minimum spanning|see{{smallest enclosing}}}
\index{concentric spheres|see{{annulus}}}

% -----------------------------------------------------------------------------
\section*{Introduction}

This chapter describes concepts, classes, and functions for solving
geometric optimisation problems. They are divided into four categories.

\paragraph{Bounding Areas and Volumes.}
Smallest enclosing circle and ellipse (2D), smallest enclosing rectangle,
parallelogram, and strip (2D), rectangular $p$-center (2D), smallest
enclosing sphere and annulus (dD).

\paragraph{Inscribed Areas.}
Maximum area and perimeter inscribed $k$-gon (2D), extremal inscribed
$k$-gon (2D).

\paragraph{Optimal Distances.}
All furthest neigbors (2D), width of point set (3D), polytope distance (dD).

\paragraph{Advanced Techniques.}
Monotone and sorted matrix search.

\section*{Assertions}
The optimisation code uses infix \ccc{OPTIMISATION} in the assertions,
e.g.\ defining the compiler flag
\ccc{CGAL_OPTIMISATION_NO_PRECONDITIONS} switches precondition
checking off, cf.~\cgalReferToAssertions


% -----------------------------------------------------------------------------
\subsection*{Bounding Areas and Volumes}

\ccRefIdfierPage{CGAL::Min_circle_2<Traits>}\\[1ex]
\ccRefIdfierPage{CGAL::Min_circle_2_traits_2<K>}\\[1ex]
\ccRefConceptPage{MinCircle2Traits}

\smallskip

\ccRefIdfierPage{CGAL::Min_ellipse_2<Traits>}\\[1ex]
\ccRefIdfierPage{CGAL::Min_ellipse_2_traits_2<K>}\\[1ex]
\ccRefConceptPage{MinEllipse2Traits}

\smallskip

\ccRefIdfierPage{CGAL::min_rectangle_2}\\
\ccRefIdfierPage{CGAL::min_parallelogram_2}\\
\ccRefIdfierPage{CGAL::min_strip_2}\\[1ex]
\ccRefIdfierPage{CGAL::Min_quadrilateral_default_traits_2<R>}\\[1ex]
\ccRefConceptPage{MinQuadrilateralTraits_2}

\smallskip

\ccRefIdfierPage{CGAL::rectangular_p_center_2}\\[1ex]
\ccRefIdfierPage{CGAL::Rectangular_p_center_default_traits_2<R>}\\[1ex]
\ccRefConceptPage{RectangularPCenterTraits_2}

\bigskip

\ccRefIdfierPage{CGAL::Min_sphere_d<Traits>}\\
\ccRefIdfierPage{CGAL::Min_annulus_d<Traits>}\\[1ex]
\ccRefIdfierPage{CGAL::Optimisation_d_traits_2<K,ET,NT>}\\
\ccRefIdfierPage{CGAL::Optimisation_d_traits_3<K,ET,NT>}\\
\ccRefIdfierPage{CGAL::Optimisation_d_traits_d<K,ET,NT>}\\[1ex]
\ccRefConceptPage{OptimisationDTraits}

% -----------------------------------------------------------------------------
\subsection*{Inscribed Areas}

\ccRefIdfierPage{CGAL::maximum_area_inscribed_k_gon_2}\\
\ccRefIdfierPage{CGAL::maximum_perimeter_inscribed_k_gon_2}\\
\ccRefIdfierPage{CGAL::extremal_polygon_2}\\[1ex]
\ccRefIdfierPage{CGAL::Extremal_polygon_area_traits_2<K>}\\
\ccRefIdfierPage{CGAL::Extremal_polygon_perimeter_traits_2<K>}\\[1ex]
\ccRefConceptPage{ExtremalPolygonTraits_2}

% -----------------------------------------------------------------------------
\subsection*{Optimal Distances}

%\ccRefIdfierPage{CGAL::width_2}%\\[1ex]
%\ccRefIdfierPage{CGAL::Min_quadrilateral_default_traits_2<K>}\\[1ex]
%\ccRefConceptPage{MinQuadrilateralTraits_2}

%\smallskip

\ccRefIdfierPage{CGAL::all_furthest_neighbors_2}\\[1ex]
%\ccRefIdfierPage{CGAL::All_furthest_neighbors_default_traits_2<R>}\\[1ex]
\ccRefConceptPage{AllFurthestNeighborsTraits_2}

\smallskip

\ccRefIdfierPage{CGAL::Width_3<Traits>}\\[1ex]
\ccRefIdfierPage{CGAL::Width_default_traits_3<K>}\\[1ex]
\ccRefConceptPage{WidthTraits_3}

\smallskip

\ccRefIdfierPage{CGAL::Polytope_distance_d<Traits>}\\[1ex]
\ccRefIdfierPage{CGAL::Optimisation_d_traits_2<K,ET,NT>}\\
\ccRefIdfierPage{CGAL::Optimisation_d_traits_3<K,ET,NT>}\\
\ccRefIdfierPage{CGAL::Optimisation_d_traits_d<K,ET,NT>}\\[1ex]
\ccRefConceptPage{OptimisationDTraits}

% -----------------------------------------------------------------------------
\subsection*{Advanced Techniques}

\ccRefIdfierPage{CGAL::monotone_matrix_search}\\[1ex]
\ccRefIdfierPage{CGAL::Dynamic_matrix<M>}\\[1ex]
\ccRefConceptPage{MonotoneMatrixSearchTraits}\\
\ccRefConceptPage{BasicMatrix}

\smallskip

\ccRefIdfierPage{CGAL::sorted_matrix_search}\\[1ex]
\ccRefIdfierPage{CGAL::Sorted_matrix_search_traits_adaptor<F,M>}\\[1ex]
\ccRefConceptPage{SortedMatrixSearchTraits}

\smallskip

% =============================================================================

% Bounding Areas and Volumes

\inputOpt{main_Min_circle_2}
\inputOpt{main_Min_ellipse_2}
\inputOpt{main_Min_quadrilateral_2}
\inputOpt{main_Rectangular_p_centers}

\inputOpt{main_Min_sphere_d}
\inputOpt{main_Min_annulus_d}
\inputOpt{main_Optimisation_d_traits}

% Inscribed Areas

\inputOpt{main_Extremal_polygons}

% Optimal Distances

\inputOpt{main_All_furthest_neighbors}

\inputOpt{main_Width_3}

\inputOpt{main_Polytope_distance_d}


% Advanced Techniques

\inputOpt{main_Matrix_search}


% ===== EOF ===================================================================
