% +------------------------------------------------------------------------+
% | Reference manual page: MeshWSEVertexBase_3.tex
% +------------------------------------------------------------------------+
% | 19.05.2008   Laurent Rineau
% | Package: Mesh_3
% |
\RCSdef{\RCSMeshWSEVertexBaseRev}{$Id: MeshWSEVertexBase_3.tex 43417 2008-06-03 13:33:01Z lrineau $}
\RCSdefDate{\RCSMeshWSEVertexBaseDate}{$Date: 2008-06-03 15:33:01 +0200 (Tue, 03 Jun 2008) $}
% |
\ccRefPageBegin
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefConcept}{MeshWSEVertexBase_3}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries

\ccDefinition
  
The concept \ccRefName\ refines the concept \ccc{SurfaceMeshVertexBase_3}
and additionally stores two integers. For each vertex of the mesh, the
meshing algorithm needs to know on which elements of the piecewise smooth
complex the vertex lie. For that purpose, those two integers are stored in
the vertex: the first one is the smallest dimension of all element of the
complex that contain the vertex. The second one is the index of the element
of smallest dimension that contains the vertex.

\ccRefines
\ccc{SurfaceMeshVertexBase_3}

\ccTypes

\ccCreationVariable{vertex}  %% choose variable name

\ccOperations

\ccMethod{int dimension() const;}{Gives the smallest dimension of all element
  of the complex that contain the vertex.}
\ccGlue
\ccMethod{void set_dimension(const int);}{Sets the smallest dimension of all element
  of the complex that contain the vertex.}

\ccMethod{int element_index() const;}{Gives the index of the element of
  smallest dimension that contains the vertex.}
\ccGlue
\ccMethod{void set_element_index(const int);}{Sets the index of the element of
  smallest dimension that contains the vertex.}

\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+

