\begin{ccRefFunctionObjectConcept}{AlgebraicKernel_d_2::Solve_2}

\ccDefinition
Computes the real  zero-dimensional solutions of a bivariate polynomial system. 
The multiplicity stored in the output iterator is the multiplicity in the system.

\ccRefines 
\ccc{Assignable}
\ccc{CopyConstructible}

\ccCreationVariable{fo}

\ccOperations \ccThree{+++++++++}{+++++++++}{}
A model of this type must provide:

%\ccThree{OutputIterator}{fo(argument_type,++}{}
\ccMethod{template < class OutputIterator >
    OutputIterator
    operator()( 
        AlgebraicKernel_d_2::Polynomial_2 f,
        AlgebraicKernel_d_2::Polynomial_2 g,
	OutputIterator res );}
{Computes all common solutions of $f$ and $g$ with multiplicity, and copies them as objects of type 
\ccc{std::pair<AlgebraicKernel_d_2::Algebraic_real_2, AlgebraicKernel_d_2::Multiplicity_type>} in \ccc{res}. 
\ccPrecond{ $f$ is square free.}
\ccPrecond{ $g$ is square free.}
\ccPrecond{ $f$ and $g$ are coprime.}
} 

%\ccThree{OutputIterator}{fo(AlgebraicKernel_d_2::Polynomial_2,++}{}
\ccMethod{
template < class OutputIterator > OutputIterator  operator()(
        AlgebraicKernel_d_2::Polynomial_2 f,
        AlgebraicKernel_d_2::Polynomial_2 g, 
        AlgebraicKernel_d_2::Bound xl,  
        AlgebraicKernel_d_2::Bound xu, 
        AlgebraicKernel_d_2::Bound yl,  
        AlgebraicKernel_d_2::Bound yu, 
        OutputIterator res);}
{Computes all common solutions of $f$ and $g$ in the closed box $[xl,xu]\times[yl,yu]$, and copies them as objects of 
type \ccc{std::pair<AlgebraicKernel_d_2::Algebraic_real_2, AlgebraicKernel_d_2::Multiplicity_type>} in \ccc{res}. 
\ccPrecond{ $f$ is square free.}
\ccPrecond{ $g$ is square free.}
\ccPrecond{ $f$ and $g$ are coprime.}
}

%\ccSeeAlso


\end{ccRefFunctionObjectConcept}
