
\ccHtmlNoClassLinks
\begin{ccClassTemplate} {list<T>}

\ccSection{list}

\ccDefinition
An object of the class \ccClassName\ is a sequence that supports
bidirectional iterators and allows constant time insert and erase
operations anywhere within the sequence.

\ccInclude{list}


\ccTypes
\ccNestedType{iterator}{A mutable bidirectional iterator.}
\ccNestedType{const_iterator}{A const bidirectional iterator.}

\ccCreation
\ccCreationVariable{L}


\ccConstructor{list();}
             {Introduces an empty list.}

\ccConstructor{list(const list<T> &q);}
 	    {Copy constructor.}

\ccConstructor{list(int n, const T& t = T() );}
            {Introduces a list with $n$ items, all initialized to $t$.}



\ccOperations

\ccMethod{list<T> & operator=(const list<T> &L1);}
        {Assignment.}

\ccMethod{bool operator==(const list<T> &L1) const;}
       {Test for equality: Two lists are equal, iff they have the same size
        and if their corresponding elements are equal.}

\ccMethod{bool operator!=(const list<T> &L1) const;}
       {Test for inequality.}

\ccMethod{iterator begin();}
       {Returns a mutable iterator referring to the first element in
        list~\ccVar.}

\renewcommand{\ccTagRmTrailingConst}{\ccFalse}
\ccMethod{const_iterator begin() const;}
       {Returns a constant iterator referring to the first element in
        list~\ccVar.}
\renewcommand{\ccTagRmTrailingConst}{\ccTrue}

\ccMethod{iterator end();}
       {Returns a mutable iterator which is the past-end-value of
        list~\ccVar.}

\renewcommand{\ccTagRmTrailingConst}{\ccFalse}
\ccMethod{const_iterator end() const;}
       {Returns a constant iterator which is the past-end-value of 
        list~\ccVar.}
\renewcommand{\ccTagRmTrailingConst}{\ccTrue}

\ccMethod{bool empty() const;}
	{Returns \ccStyle{true} if \ccVar\ is empty.}

\ccMethod{int size() const;}
	{Returns the number of items in list~\ccVar.}

\ccMethod{T& front();}
       {Returns a reference to the first item in list~\ccVar.}

\renewcommand{\ccTagRmTrailingConst}{\ccFalse}
\ccMethod{const T& front() const;}
       {Returns a const reference to the first item in list~\ccVar.}
\renewcommand{\ccTagRmTrailingConst}{\ccTrue}

\ccMethod{T& back();}
       {Returns a reference to the last item in list~\ccVar.}

\renewcommand{\ccTagRmTrailingConst}{\ccFalse}
\ccMethod{const T& back() const;}
       {Returns a const reference to the last item in list~\ccVar.}
\renewcommand{\ccTagRmTrailingConst}{\ccTrue}


\ccHeading{Insertion}

\ccMethod{void  push_front(const T&);}
       {Inserts an item in front of list~\ccVar.}

\ccMethod{void push_back(const T&);}
       {Inserts an item at the back of list~\ccVar.}

\ccMethod{iterator insert(iterator pos, const T& t);}
 {Inserts a copy of \ccStyle{t} in front of iterator \ccStyle{pos}.
  The return value points to the inserted item.}

\ccMethod{void insert(iterator pos,
	                           int n, const T& t = T());}
 {Inserts $n$ copies of \ccStyle{t} in front of iterator \ccStyle{pos}.}


\ccMethod{void insert(iterator pos,
	            const_iterator first,
	            const_iterator last);}
 {Inserts a copy of the range $\left[\right.$\ccStyle{first}, \ccStyle{last}$\left.\right)$
  in front of iterator \ccStyle{pos}.}

\ccHeading{Removal}

\ccMethod{void pop_front();}
 {Removes the first item from list~\ccVar.}

\ccMethod{void pop_back();}
 {Removes the last item from list~\ccVar.}

\ccMethod{void erase(iterator pos);}
 {Removes the item from list~\ccVar, where \ccStyle{pos} refers to.}

\ccMethod{void erase(iterator first,
	           iterator last);}
 {Removes the items in the range$\left[\right.$\ccStyle{first}, 
  \ccStyle{last}$\left.\right)$ from list~\ccVar.}




\end{ccClassTemplate} 
