%%
%%  *** CGAL Installation Guide ***
%%
%% file:     installation.tex
%%
%% authors:  Michael Hoffmann, Dima Pasechnik and Wieger Wesselink
%%
%% $Revision$ $Date$
%%

%% macro for GNU
\newcommand{\gnu}{\textsc{Gnu}}

%% macro for QT
\newcommand{\qt}{\textsc{Qt}}

%% macro for GMP
\newcommand{\gmp}{\textsc{Gmp}}

%% macro for Boost
\newcommand{\boost}{\textsc{Boost}}

%% macro for Core
\newcommand{\core}{\textsc{Core}}

%% macro for Windows-specific installation
\newcommand{\MSInst}{Windows-specific Installation}

%% macro for g++
\newcommand{\Gcc}[1]{\gnu~\texttt{g++}~{\rm #1}}
\newcommand{\gccurl}{\path'http://gcc.gnu.org/'}

%% macro for SUNPRO CC
\newcommand{\sunprocc}[1]{\textsc{Sunpro}~\texttt{CC}~{\rm #1}}
\newcommand{\sunproccurl}{\path'http://www.sun.com/software/Developer-products/cplusplus/'}

%% macro for SGI CC
\newcommand{\mipsprocc}{\textsc{SGI}~Mips(Pro)~\texttt{CC}}
\newcommand{\mipsprourl}{\path'http://www.sgi.com/software/irix/tools/c++.html'}

%% macro for Borland C++
\newcommand{\bcc}[1]{\textsc{Borland}~\texttt{C++}~{\rm #1}}
\newcommand{\bccurl}{\path'http://www.inprise.com/bcppbuilder/'}

%% macro for Microsoft Visual C++
\newcommand{\msvc}[1]{\textsc{MS}~Visual~\texttt{C++}~{\rm #1}}
\newcommand{\msvcurl}{\path'http://msdn.microsoft.com/visualc/'}

%% macro for Intel C++ Compiler
\newcommand{\icl}[1]{\textsc{Intel}~\texttt{C++}~{\rm #1}}
\newcommand{\iclurl}{\path'http://developer.intel.com/software/products/compilers/'}

%% macro for Microsoft Windows
\newcommand{\mswin}{\textsc{MS}~Windows}

%% macro for CGAL release number
\newcommand{\cgalrelease}{\cgalversion}

%% macro for CGAL directory
\newcommand{\cgaldir}{\texttt{CGAL-\cgalrelease}}

%% macro for YOUR CGAL directory :)
\newcommand{\yourcgaldir}{$<$\textit{insert your \cgaldir\ dir}$>$}

%% macro for CGAL install config directory
\newcommand{\cgalinstconfdir}{\cgaldir\texttt{/config/install}\index{directories!config/install@\texttt{config/install}}}

%% macros for WWW pages
\newcommand{\cgalhomepage}{\path'http://www.cgal.org'}
\newcommand{\gmppage}{\path'http://www.swox.com/gmp/'}
\newcommand{\boostpage}{\path'http://www.boost.org/'}
\newcommand{\corepage}{\path'http://www.cs.nyu.edu/exact/core/'}
\newcommand{\ledapage}{\path'http://www.mpi-sb.mpg.de/LEDA'}
\newcommand{\trolltechpage}{\path'http://www.trolltech.com'}
\newcommand{\qtpage}{\path'http://doc.trolltech.com/'}
\newcommand{\qtmocpage}{\path'http://doc.trolltech.com/moc.html'}

%% write index in typewriter type. (c) Susan :-)
\newcommand{\TTindex}[1]{\index{#1@{\tt #1}}}
\newcommand{\TTsubindex}[2]{\index{#1@{\tt #1}!{#2}}}
\newcommand{\TTsubindextwo}[2]{\index{#1!#2@{\tt #2} }}

\section{Introduction}

\cgal\ stands for \textit{Computational Geometry Algorithms Library}.
It is a software library written in \CC, whose development started in
an {\sc Esprit Ltr} project. The goal of \cgal\ is to make the large
body of geometric algorithms developed in the field of computational
geometry available for industrial application.

This document describes how to install \cgal\ on Unix-like systems.
Besides that, you will find some information about the makefile
structure of \cgal\ and the support for using \cgal\ together with
other software libraries, such as the \gnu\ Multiple Precision library
\gmp\footnote{\gmppage}, the \core\ library\footnote{\corepage} for
robust numerical and geometric computation, \leda, the Library of
Efficient Datatypes and Algorithms\footnote{\ledapage}, or
Trolltech's\footnote{\trolltechpage} \qt\ toolkit.

\section{Prerequisites}\label{sec:prerequisites}

In order to build the \cgal\ libraries you need a \CC\ compiler.  Most
recent compilers on Unix platforms and \mswin\ are supported, provided
that they reasonnably conform to the ISO 14882 standard for \CC.

\cgaldir\ supports the following compilers/operating systems:

\begin{center}\index{compilers!supported}\index{supported compilers}
  \renewcommand{\arraystretch}{1.3}
  \gdef\lcTabularBorder{2}
  \begin{tabular}{|l|l|} \hline
    \textbf{compiler}        & \textbf{operating system}\\\hline\hline
    \mipsprocc\ 7.4 (n32 and 64) \footnotemark[7] 
    & IRIX 6.5\\\hline
    \Gcc{3.2, 3.3, 3.4} \footnotemark[9]            
    & IRIX 6.5 / Solaris 2.6+ / Linux 2.x / MacOS X /
      \\ & \mswin\ 95/98/2000/XP/NT4\footnotemark[10]\\\hline
    \sunprocc{5.5} \footnotemark[11]                 
    & Solaris 2.6+\\\hline
    \msvc{7.1} (\textsc{.NET}) \footnotemark[12]           
    & \mswin\ 95/98/2000/XP/NT4\footnotemark[10]\\\hline
    \icl{8.0} \footnotemark[13]                          
    & \mswin\ 95/98/2000/XP/NT4\footnotemark[10]\\\hline
%%    \bcc{5.5.1} \footnotemark[13]                          
%%    & \mswin\ 95/98/2000/XP/NT4\footnotemark[10]\\\hline
  \end{tabular}
\end{center}
\footnotetext[7]{\mipsprourl}\addtocounter{footnote}{1}
\footnotetext[9]{\gccurl}\addtocounter{footnote}{1}
\footnotetext[10]{with Cygwin
  (\path~http://www.cygwin.com~)}\addtocounter{footnote}{1}
\footnotetext[11]{\sunproccurl}\addtocounter{footnote}{1}
\footnotetext[12]{\msvcurl}\addtocounter{footnote}{1}
\footnotetext[13]{\iclurl}\addtocounter{footnote}{1}
%%\footnotetext[13]{\bccurl}\addtocounter{footnote}{1}
\addtocounter{footnote}{1}

If you are going to install \cgal\ using
Cygwin\footnote{\path~http://www.cygwin.com~}, please read
Section~\ref{sec:cygwin} first.

Note that \Gcc{2.96/97} are not official \texttt{gcc} releases that
are neither supported by the \texttt{GCC}
team\footnote{\path'http://gcc.gnu.org/gcc-2.96.html'} nor by \cgal.
Please upgrade to a newer version, if you happen to have this compiler.

\section{Getting \cgal} \label{sec:gettingcgal}
\index{CGAL@\cgal!getting}\index{getting \cgal} 

The \cgal\ library can be downloaded from the \cgal\ 
homepage:\index{CGAL@\cgal!homepage}
\begin{quote}
      \cgalhomepage
\end{quote}
and go to the `Download' section. Just follow the instructions on this
page to obtain your copy of the library.

After you have downloaded the file containing the \cgal\ library, you
have to decompress it. Use the commands

\begin{verbatim}
      gunzip <filename>.tar.gz
      tar xvf <filename>.tar
\end{verbatim}

Alternatively, your browser might be able to invoke the right
decompression program by itself.

In both cases the directory \cgaldir\ will be created. This directory
contains the following subdirectories:\index{directories!structure}

\begin{center}
  \renewcommand{\arraystretch}{1.3}
  \gdef\lcTabularBorder{2}
  \begin{tabular}{|l|l|} \hline
    \textbf{directory} & \textbf{contents}\\\hline\hline
    \texttt{auxiliary} & packages that can optionally be used with \cgal\\\hline
    \texttt{config}    & configuration files for install script\\\hline
    \texttt{demo}      & demo programs (some of them need \leda, geomview
                         or other third-party products)\\\hline
    \texttt{doc\_html} & documentation (HTML)\\\hline
    \texttt{doc\_pdf}  & documentation (PDF)\\\hline
    \texttt{doc\_ps}   & documentation (Postscript)\\\hline
    \texttt{examples}  & example programs\\\hline
    \texttt{include}   & header files\\\hline
    \texttt{lib}       & (shared) object libraries\\\hline
    \texttt{make}      & files with platform dependent makefile settings\\\hline
    \texttt{scripts}   & some useful scripts (e.g. for creating makefiles)\\\hline
    \texttt{src}       & source files\\\hline
  \end{tabular}
\end{center}

The directory \texttt{auxiliary} contains a distribution of the \gnu\ 
Multiple Precision library \gmp\footnote{\gmppage}. The directory
\texttt{src/Core} contains a distribution of the \core\ 
library\footnote{\corepage} for robust numerical and geometric
computation.

The directory \texttt{include/boost} contains header files of the
\boost\ project\footnote{\boostpage}.

\gmp, \core\ and \boost\ are not part of \cgal\ and have their own
licenses.

\subsection{Visualization}\label{sec:vis}

The programs in the \texttt{demo} directory provide visual output.
Most of these use \ccc{CGAL::Qt_widget}, a widget and some helper
classes that allow to interact with two dimensional \cgal\ objects in
\qt\ based applications.\index{visualization!Qt}

If you have \leda\ installed, you might want to use
\ccc{CGAL::Window_stream} as an interface between two dimensional
\cgal\ objects and a \ccc{leda_window}. To be able to use the
\ccc{Window_stream}, you need do nothing more than compile \cgal\ with
\leda\ support.\index{visualization!LEDA}

Some demo programs for 3D structures require the geomview program for
visualization.\index{visualization!geomview} This is available from
\path'http://www.geomview.org' (note that it does not run on \mswin).

\section{Installing \cgal}

The directory \cgaldir\ contains a Bourne shell script called
\texttt{install\_cgal}\TTindex{install\_cgal}
\index{scripts!\texttt{install\_cgal}}. The script can be run in two
modes: a menu-driven interactive mode and a non-interactive mode.
Normally you should use the interactive mode, but in case you run into
problems with it or do not like it for some reason, you can still use
the non-interactive mode.

We first describe a sample installation in section
\ref{sec:sample-inst}. This provides you with an overview on how the
interactive installation works. If you want more detailed information
about specific menus and their options, take a look at section
\ref{sec:interactive-mode}. Finally, for the non-interactive mode
refer to section \ref{sec:non-interactive}.

If you want to use \leda\ together with \cgal, have a look at
section~\ref{sec:leda}.

\section{A Sample Installation}\label{sec:sample-inst}

In this section we sketch an example installation on a \textsc{Sun}
running Solaris~2.9 with the \Gcc{3.3} compiler. For a complete
description of the different menus and their options refer to section
\ref{sec:interactive-mode}.

\subsection{Starting the script}

Go to the \cgaldir\ directory and enter the command
\begin{verbatim}
      ./install_cgal -i
\end{verbatim}

You get a message indicating the \cgal\ version you are going to
install and that you are running the interactive mode. Then it takes
some time while the script locates a number of utility programs. You
will not get informed about this\footnote{If you are that curious what
  happens exactly, have a look at the file
  \texttt{\cgaldir/install.log}.\TTindex{install.log}}, but see some
dots written to the screen indicating progress.

{\ccTexHtml{\scriptsize}{}
\begin{alltt}
--------------------------------------------------------
  This is the install script for CGAL \cgalrelease
--------------------------------------------------------

starting interactive mode - one moment, please
.......

  Choosing compiler GNU 3.3.2.

\end{alltt}}
  
If there is any compiler installed on your system and accessible
through your \texttt{PATH} environment variable that is supported by
\cgal, one of these compilers is chosen. If there is more than one
compiler installed on your system (and supported by \cgal), you may
choose to use a different compiler from the compiler menu (cf.
Section~\ref{sec:compiler-menu}).

A menu similar to the following will appear on your screen.\index{main
  menu}\index{menus!main}

{\ccTexHtml{\scriptsize}{} \label{pic:main-menu}
\begin{alltt}
  ****************************************************************
  **              CGAL 3.1 Installation Main Menu               **
  **              -------------------------------               **
  **                                                            **
  **   OS:                  sparc_SunOS-5.9                     **
  **   Compiler:            GNU 3.3.2                           **
  **   Support for:         no other library.                   **
  **                                                            **
  **   Compiler is supported by CGAL.                           **
  **   The setup has not been tested.                           **
  **                                                            **
  **   There are no libs for this os/compiler.                  **
  **                                                            **
  **   <C>  Compiler Menu                                       **
  **   <S>  Support Menu                                        **
  **   <T>  Test (and save) setup                               **
  **   <A>  Run all setup tests (no cache)                      **
  **                                                            **
  **   <B>  Build CGAL Libraries                                **
  **                                                            **
  **   <Q>  Back to OS                                          **
  **                                                            **
  **   Your Choice:                                             **
  **                                                            **
  ****************************************************************
\end{alltt}}

The first lines below the headline contain some kind of status report:
current OS and compiler, and which third-party software libraries are
supported (such as \gmp, \core, \leda, or \qt). Moreover you can see
that the current setup has not yet been tested, and that there do not
exist \cgal\ libraries for this OS/compiler combination in the \cgal\ 
lib directory by now.

\subsection{Building the \cgal\ libraries}\label{sec:test-the-setup}

In a first step, you should test the current setup by typing ``{\tt
  t}''. Then a number of tests are done to check whether your compiler
supports certain language constructs or has specific bugs. There is
quite a number of these tests, so this step may take a while. For each
test you should get a message what particularly is tested at the
moment and what the result is.

{\ccTexHtml{\scriptsize}{}
\begin{verbatim}
  ****************************************************************
  **   The following lines show results of configuration tests. **
  **   Some of the tests might fail, since many compilers are   **
  **   still not completely ANSI/ISO compliant.                 **
  **   Since we worked around the arising problems,             **
  **             *** CGAL will work fine ***                    **
  **   regardless of the outcome of these tests.                **
  ****************************************************************
  Checking for standard header files
  algorithm ... ok.

  <many lines omitted>

  Testing for VC7_PRIVATE_TYPE_BUG ... ok.
  Saving current setup ... done.
\end{verbatim}
}

If all these tests have been completed successfully, the current
settings are saved into a file that resides in the directory
\cgalinstconfdir. Thus, if you run the install script a second time
for this OS/compiler, you will not have to go through the whole
config-/test cycle again, but the configuration will be retrieved from
the corresponding config file instead.

\subsection{Building the \cgal\ libraries}\label{sec:build-the-libs}

We are now ready to build the \cgal\ libraries.  Just type ``{\tt b}''
to start compilation. Building consists of three steps:
\begin{enumerate}
\item writing the include makefile,
\item compiling the static libraries \textit{and}
\item compiling the shared libraries.
\end{enumerate}
The include makefile\index{include makefile} encapsulates the OS-- and
compiler-specific settings and should be included (hence the name) in
all makefiles that compile \cgal\ applications. If everything went ok,
the output should look as follows. (Otherwise, you should have a look
at the error messages from compiler or linker.)

{\ccTexHtml{\scriptsize}{}
\begin{verbatim}
  ****************************************************************
  **                                                            **
  **                     Compiling CGAL 3.1                     **
  **                     ------------------                     **
  **                                                            **
  ****************************************************************

  OS:           sparc_SunOS-5.9
  COMPILER:     GNU 3.3.2
  GMP:          not supported
  GMPXX:        not supported
  CORE:         not supported
  LEDA:         not supported
  Qt:           not supported

  Generating Makefiles ... done.
  Building CGAL_lib ... done.
  Building CGAL_sharedlib ... done.

  ****************************************************************
  **             Please press <ENTER> to continue.              **
  ****************************************************************
\end{verbatim}}
{
}  

That's all, it's done. Press ``\texttt{<ENTER>}'' to return to the
main menu and proceed by installing for a different compiler (go to
the compiler menu and choose ``\texttt{c}'' to get a list of supported
compilers detected on your system), or with \gmp, \core, \leda, or
\qt\ support (go to the \gmp, \core, \leda, or \qt\ menu,
respectively). Another option is to simply quit the install script by
typing ``\texttt{q}''. When leaving the script, you get a list of
successful builds during the session.  Furthermore, the script prints
the setting of \texttt{CGAL\_MAKEFILE} for the last active
configuration. Remember to set this environment variable before
compiling \cgal\ applications.  On bourne shell derivatives, you would
type in our example
\begin{alltt}
      export CGAL_MAKEFILE=\cgaldir/make/makefile_sparc_SunOS-5.6_g++-3.4.3
\end{alltt}
while for \texttt{csh} descendants the syntax is
\begin{alltt}
      setenv CGAL_MAKEFILE \cgaldir/make/makefile_sparc_SunOS-5.6_g++-3.4.3
\end{alltt}
In Section~\ref{sec:makefiles} you can find more information on the
\cgal\ makefile structure, and how to set \texttt{CGAL\_MAKEFILE} when
using \cgal\ on several platforms.

%% TODO: some remark regarding visualization
%% If you want to use the visualization provided by
%% \ccc{CGAL::Window_stream} (Section~\ref{sec:vis}) and you do not have
%% the \leda\ libraries installed, or do not want to use them with \cgal,
%% you should now proceed to Section~\ref{sec:cgalwin} and install the
%% \texttt{CGALWin} library.

%% Now it would be a good idea to print and read the document ``Getting
%% Started with \cgal'' that can be found in various formats in the
%% \texttt{doc\_html}, \texttt{doc\_pdf} and \texttt{doc\_ps}
%% directories.

\section{The interactive mode}\label{sec:interactive-mode}
\index{interactive installation}\index{installation!interactive}
\TTsubindex{install\_cgal}{interactive mode}

To run the install script in the interactive mode, go to the \cgaldir\ 
directory and enter the command
\begin{verbatim}
      ./install_cgal -i
\end{verbatim}

After initialization during which certain utility programs are located
and your system is searched for compilers supported by \cgal, you get
into the \cgal\ installation \textit{main menu} (see page
\pageref{pic:main-menu} for a picture).

From the main menu you can reach a number of different sub-menus, of
which the most important maybe is the \textit{compiler menu}. This is
where you can choose the compiler you want to work with and set custom
compiler or linker options. The compiler menu is described in
Section~\ref{sec:compiler-menu}.

If you want to use \gmp, \core, \leda, or \qt\ with \cgal, you will
have to go to the \textit{gmp menu} (cf. Section~\ref{sec:gmp-menu}),
\textit{core menu} (cf. Section~\ref{sec:core-menu}), \textit{leda
  menu} (cf. Section~\ref{sec:leda-menu}), or \textit{qt menu} (cf.
Section~\ref{sec:qt-menu}), respectively.

There is no menu for \boost\ because it is available in the
\cgal\ installation by default.  If you want to specify an
alternate \boost\ installation, you can use the \texttt{CUSTOM\_CXXFLAGS}
facility.

Finally you can build the \cgal\ libraries by typing \texttt{b}.
However, it is recommended to run the \textit{setup test} -- which is
available in all menus as option \texttt{t} -- before. The setup test
includes an \stl\ test, a \gmp\ test, a \core\ test, a \leda\ test,
and a \qt\ test.  But not all tests are performed always; e.g., the
\gmp\ test is only done, if you enabled \gmp\ support. The install
script keeps track of the tests passed and only tests again, if you
change the setup in a way that might affect the test result. If you
want to redo \textit{all} tests, you have to choose option
``\texttt{a}'' from the main menu.  This also retests for
\gmp/\leda/\qt\ installations in system directories. Otherwise, this
is only done the first time you enable \gmp/\leda/\qt\ support for an
OS/compiler combination.

\subsection{Files created during installation}\label{sec:filescreated}

The install script stores all relevant settings for an OS/compiler
combination in the directory
\begin{center}
  \texttt{\cgalinstconfdir/$<$\textit{CGAL-OS-description}$>$}
\end{center}
where $<$\textit{CGAL-OS-description}$>$ identifies your OS/compiler
combination in a way specified in section \ref{sec:os-compiler-id}.
\footnote{Note that these files are only OS/compiler specific, i.e.
  there are no different files for with and without \leda\ support.}
This saves you typing everything again, if you upgrade
\index{upgrading \cgal}\index{CGAL@\cgal!upgrade} \cgal\ or another
package that makes recompiling the \cgal\ libraries necessary.

Besides the config files, \texttt{install\_cgal} uses several
temporary files during interactive installation. Most of them are
removed after use, but some are not, since it might be helpful to keep
some information about the last run.  You can keep or delete them as
you like, as they are not needed anymore once the script terminated.
A list of these files (all are plain ASCII and reside in \cgaldir)
follows.
\begin{center}\index{files!temporary}\index{logfiles}
  \renewcommand{\arraystretch}{1.3}
  \gdef\lcTabularBorder{2}
  \begin{tabular}{|l|l|} \hline
    \textbf{filename} & \textbf{content}\\\hline\hline
    \texttt{install.log}\TTindex{install.log} & 
    detailed overall protocol\\\hline
    \texttt{install.completed}\TTindex{install.completed} &
    list of systems for which \cgal\ libraries 
    have been built\\\hline
    \texttt{compile.log}\TTindex{compile.log} & 
    output of the last compiler call\\\hline
  \end{tabular}
\end{center}

\subsection{The Compiler Menu}\label{sec:compiler-menu}
\index{compiler menu}\index{menus!compiler}

Here is the place to set the compiler specific options, such as the
compiler to use (if more than one has been detected), custom
compiler or linker flags, or deciding whether to build shared libraries
or not.\bigskip

\fbox{
\begin{minipage}{.95\linewidth}
\vspace{2pt}
\centerline{{\large{\bf Compiler Menu}}}
\vspace{2pt}
\begin{description}
\item[$<$C$>$] Choose the compiler to be used from the list of
  detected compilers.  You can also register other compilers, if they
  have not been detected automatically.\index{compilers!choosing}
\item[$<$F$>$] Set custom compiler flags. These are the first flags
  given to the compiler in every call. Under normal circumstances
  there should be no need to set any such
  flag.\index{compilers!setting custom flags}
\item[$<$L$>$] Set custom linker flags. These are the first flags
  given to the linker in every call. Under normal circumstances
  there should be no need to set any such flag.
\item[$<$S$>$] Toggle shared libraries building.
  By default, shared libraries are built (e.g. \texttt{libCGAL.so}),
  but it is possible to only build static libraries using this option.
\end{description}
\vspace{2pt}
\end{minipage}
\hfill}

\subsection{The Support Menu}\label{sec:support-menu}
\index{support menu}\index{menus!support}

This menu provides the starting point to setup the support for
third-party software libraries such as \gmp, \core, \leda, or \qt.
\bigskip

\fbox{
\begin{minipage}{.95\linewidth}
\vspace{2pt}
\centerline{{\large{\bf Support Menu}}}
\vspace{2pt}
\begin{description}
\item[$<$G$>$] Setup support for the \gnu\ Multiple Precision library
  \gmp.\index{GMP@\gmp!enable support}
\item[$<$C$>$] Setup support for the \core\ library for robust
  numerical and geometric computation.\index{CORE@\core!enable
    support}
\item[$<$L$>$] Setup support for \leda, the Library of Efficient
  Datatypes and Algorithms.\index{LEDA@\leda!enable support}
\item[$<$K$>$] Setup support for Trolltech's \qt\ 
  toolkit.\index{Qt!enable support}
\end{description}
\vspace{2pt}
\end{minipage}
\hfill}

\subsection{The GMP Menu}\label{sec:gmp-menu}
\index{GMP@\gmp!menu}\index{menus!\gmp}

This menu is to set \gmp\ (\gnu\ Multiple Precision Library) specific
options, if you plan to use \gmp\ together with \cgal. In case you do
not already have \gmp\ installed on your system, a \gmp\ distribution
is shipped with \cgal. You can find it in the {\tt auxiliary}
directory. The menu provides an option to install \gmp\ in your \cgal\ 
directory tree\footnote{This option on \msvc\ just unpacks a
  pre-compiled library that comes with \cgal.}, but -- of course --
you can also install \gmp\ independently from \cgal.

If \gmp\ support is enabled for the first time, the script tests
whether \gmp\ is installed in standard system directories or in the
\cgal\ tree.  If this test does not succeed, you have to supply
directories containing the \gmp\ header files
(\texttt{GMP\_INCL\_DIR})\TTindex{GMP\_INCL\_DIR} and \gmp\ libraries
({\tt GMP\_LIB\_DIR})\TTindex{GMP\_LIB\_DIR}.  Even if the tests are
passed, you still have the option to set these directories
differently.

If you decide to install the \gmp\ distribution shipped with \cgal\ 
from the install script, \gmp\ will be configured by calling its
\textit{configure} script. \gmp\ being a C library, it requires a C
compiler. Its \textit{configure} script usually does a good job at
finding a C compiler on the system, but it also gives the possibility
to specify it by setting the environment variable \textit{CC} before
calling \textit{configure}.  If you want the \cgal\ install script to
build \gmp\ and specify the C compiler to be used, you can also to the
same, by setting the \textit{CC} environment variable (see the \gmp\ 
installation documentation for details).  If you need a more complex
configuration of \gmp, we recommend that you install \gmp\ yourself
separately.

If \gmp\ support is enabled, you may additionnally enable support for
GMPXX, \gmp's built-in C++ interface, from the \gmp\ menu. Note that
this is not supported by all C++ compilers, you should check the \gmp\ 
manual for more information.  Once you choose to have GMPXX support,
then if you install \gmp\ from the CGAL tree, \gmp\ will be configured
with C++ support.\bigskip

\index{GMP@\gmp!installing}\index{GMP@\gmp!enable support}
\fbox{
\begin{minipage}{.95\linewidth}
\vspace{2pt}
\centerline{{\large{\bf GMP Menu}}}
\vspace{2pt}
\begin{description}
\item[$<$C$>$] Install the \gmp\ distribution shipped with \cgal\ in
  the \cgal\ directory tree.
\item[$<$G$>$] Enable/Disable \gmp\ support in \cgal.
\item[$<$X$>$] Enable/Disable GMPXX support in \cgal.
\item[$<$I$>$] (\textit{present if \gmp\ support is enabled)} Set the
  include directory for \gmp.
\item[$<$L$>$] (\textit{present if \gmp\ support is enabled)} Set the
  directory containing the \gmp\ libraries.
\item[$<$M$>$] (\textit{present if \gmp\ support is enabled, there is a \gmp\
    installation in system directories or in the \cgal\ tree and {\tt
      GMP\_INCL\_DIR} or \texttt{GMP\_LIB\_DIR} have been set)} Use \gmp\
  installation from system directories / \cgal\ tree.
\end{description}
\vspace{2pt}
\end{minipage}
\hfill}

\subsection{The CORE Menu}\label{sec:core-menu}
\index{CORE@\core!menu}\index{menus!\core}

This menu is to set \core\ specific options, if you plan to use \core\ 
together with \cgal. Since \core\ requires \gmp, you have to enable
\gmp\ support together with \core\ support. Refer to
Section~\ref{sec:gmp-menu} for how to setup \gmp\ support for \cgal.

The current \core\ release is shipped together with \cgal. If \core\ 
support is enabled, the \core\ library is built and installed together
with the \cgal\ libraries. Hence, if you enable \core\ support, you
have to (re)build the \cgal\ libraries afterwards (cf.
Section~\ref{sec:build-the-libs}). Another option is to use a \core\ 
installation that is independent from \cgal. For this you have to
supply directories containing the \core\ header files
(\texttt{CORE\_INCL\_DIR})\TTindex{CORE\_INCL\_DIR} and the \core\ 
library ({\tt CORE\_LIB\_DIR})\TTindex{CORE\_LIB\_DIR}. \bigskip

\index{CORE@\core!installing}\index{CORE@\core!enable support}
\fbox{
\begin{minipage}{.95\linewidth}
\vspace{2pt}
\centerline{{\large{\bf CORE Menu}}}
\vspace{2pt}
\begin{description}
\item[$<$C$>$] Enable/Disable \core\ support in \cgal.
\item[$<$I$>$] (\textit{present if \core\ support is enabled)} Set the
  include directory for \core.
\item[$<$L$>$] (\textit{present if \core\ support is enabled)} Set the
  directory containing the \core\ library.
\item[$<$Z$>$] (\textit{present if \core\ support is enabled and {\tt
      CORE\_INCL\_DIR} or \texttt{CORE\_LIB\_DIR} have been set)} Use
  \core\ installation from \cgal\ directories.
\end{description}
\vspace{2pt}
\end{minipage}
\hfill}

\subsection{The \leda\ Menu}\label{sec:leda-menu}
\index{LEDA@\leda!menu}\index{menus!\leda}

This is the place to set \leda\ specific options, if you plan to use
\leda\ together with \cgal\ (see also Section~\ref{sec:leda}). In
order to enable \leda\ support in \cgal, \leda\ has to be installed on
your system.

If \leda\ support is enabled the first time, the script tests whether
\leda\ is installed in standard system directories. If this test does
not succeed, you have to supply directories containing the \leda\ 
header files (\texttt{LEDA\_INCL\_DIR})\TTindex{LEDA\_INCL\_DIR} and
\leda\ libraries ({\tt LEDA\_LIB\_DIR})\TTindex{LEDA\_LIB\_DIR}.  Even
if the tests are passed, you still have the option to set these
directories differently.\bigskip

\index{LEDA@\leda!enable support}
\fbox{
\begin{minipage}{.95\linewidth}
\vspace{2pt}
\centerline{{\large{\bf \leda\ Menu}}}
\vspace{2pt}
\begin{description}
\item[$<$E$>$] Enable/Disable \leda\ support in \cgal.
\item[$<$I$>$] (\textit{present if \leda\ support is enabled)} Set the
  include directory for \leda .
\item[$<$J$>$] (\textit{present if \leda\ support is enabled, \leda\ headers
    have been found in a system include directory and {\tt
      LEDA\_INCL\_DIR} has been set)} Use \leda\ header from system
  include directory.
\item[$<$L$>$] (\textit{present if \leda\ support is enabled)} Set the
  directory containing the \leda\ libraries.
\item[$<$M$>$] (\textit{present if \leda\ support is enabled, \leda\ 
    libs have been found in a system lib directory and
    \texttt{LEDA\_LIB\_DIR} has been set)} Use \leda\ libraries from
  system lib directory.
\end{description}
\vspace{2pt}
\end{minipage}
\hfill}

\subsection{The Qt Menu}\label{sec:qt-menu}
\index{Qt!menu}\index{menus!Qt}

This menu is to set \qt\ specific options, if you plan to use \qt\ 
together with \cgal . Note that for use with \cgal, \qt\ version 2.2
(or later) if required. In order to enable \qt\ support in \cgal, \qt\ 
has to be installed on your system first. Unlike for \gmp, there is no
option to install \qt\ from the \cgal\ installation script.  For
information on \qt, please refer to
\begin{quote}
  \qtpage
\end{quote}

\begin{ccAdvanced}
  The \qt\ menu has a basic mode and an advanced one. If your \qt\ 
  installation is standard, you shouldn't have to go into the advanced
  mode.
  
  The \qt\ menu starts in basic mode, unless \qt\ is installed in
  standard system directories (because in that case, the advanced mode
  is quicker).
\end{ccAdvanced}

\subsubsection{Basic mode (to use with a standard Qt installation)}

If \qt\ support is enabled the first time, the script tests whether
the \texttt{\$QTDIR} environment variable points to a valid \qt\ 
directory.  is installed in standard system directories. If that is
not the case, you have to supply the \qt\ directory containing your
\qt\ installation.  Even if the test passed, you still have the option
to set this directory differently.  If your \qt\ installation is not
standard, you would have to go into the advanced mode.\bigskip

\fbox{
\begin{minipage}{.95\linewidth}
\vspace{2pt}
\centerline{{\large{\bf Qt basic Menu}}}
\vspace{2pt}
\begin{description}
\item[$<$K$>$] Enable/Disable Qt support in \cgal.\index{Qt!enable
    support}
\item[$<$A$>$] (\textit{present if Qt support is enabled)} Go to the
  advanced mode
\item[$<$D$>$] (\textit{present if Qt support is enabled}) Set the
  Qt directory.
\item[$<$E$>$] (\textit{present if Qt support is enabled,
    \texttt{\$QTDIR} points to a valid Qt directory and {\tt QT\_DIR}
    has been set}) Use \texttt{\$QTDIR} as Qt directory.
\end{description}
\vspace{2pt}
\end{minipage}
\hfill}


\begin{ccAdvanced}
\subsubsection{Advanced mode (to use with a non-standard Qt
  installation) }

In that mode, you have to specify separately directories containing
the \qt\ header files (\texttt{QT\_INCL\_DIR})\TTindex{QT\_INCL\_DIR}
and the \qt\ library (\texttt{QT\_LIB\_DIR})\TTindex{QT\_LIB\_DIR},
and the path to the MOC\footnote{\qtmocpage} executable
(\texttt{QT\_MOC})\TTindex{QT\_MOC} unless they are in system
directories. Even in that case, you still have the option to set them
differently.

\fbox{
\begin{minipage}{.95\linewidth}
\vspace{2pt}
\centerline{{\large{\bf Qt advanced Menu}}}
\vspace{2pt}
\begin{description}
\item[$<$K$>$] Enable/Disable Qt support in \cgal.\index{Qt!enable
    support}
\item[$<$B$>$] (\textit{present if Qt support is enabled)} Go to the
  basic mode
\item[$<$I$>$] (\textit{present if Qt support is enabled}) Set the
  directory containing Qt headers.
\item[$<$J$>$] (\textit{present if Qt support is enabled, Qt headers
    are in system directories and {\tt QT\_INCL\_DIR} has been set})
  Use Qt headers from system include directories.
\item[$<$L$>$] (\textit{present if Qt support is enabled}) Set the
  directory containing Qt library.
\item[$<$M$>$] (\textit{present if Qt support is enabled, Qt library
    is in system directories and {\tt QT\_LIB\_DIR} has been set})
  Use Qt library from system library directories.
\item[$<$O$>$] (\textit{present if Qt support is enabled}) Set the
  path to MOC executable.
\item[$<$P$>$] (\textit{present if Qt support is enabled, MOC is in path and {\tt QT\_MOC} has been set})
  Use Qt MOC executable in path.
\end{description}
\vspace{2pt}
\end{minipage}
\hfill}

\end{ccAdvanced}

\section{The non-interactive mode}\label{sec:non-interactive}
\index{non-interactive
  installation}\index{installation!non-interactive}
\TTsubindex{install\_cgal}{non-interactive mode}

To run the install script in the non-interactive mode, go to the
\cgaldir\ directory and enter the command
\begin{verbatim}
      ./install_cgal -ni <compiler>
\end{verbatim}
where \texttt{<compiler>} is the C++ compiler
executable.\index{compilers!choosing}\\ You can either specify a full
path, e.g. \texttt{/usr/local/bin/g++}, or just the basename, e.g.
\texttt{g++}, which means the script searches your \texttt{PATH} for
the compiler location. If your compiler call contains whitespaces it
has to be quoted, e.g.  \texttt{./install\_cgal -ni "CC -n32"}.  The
options given this way become part of your \cgal-OS
description\index{OS description} (see section
\ref{sec:os-compiler-id}) which is useful e.g. to distinguish between
different compilers using the same frontend (\mipsprocc\ on
\texttt{IRIX6}).

There are a number of additional command line options to customize
your \cgal\ setup which are discussed below. You should read the
corresponding paragraphs before you continue, especially if one or
more of the following conditions apply to you:
\begin{itemize}
\item you want to use \gmp\ together with \cgal\ 
  (Section~\ref{sec:gmp-setup}),
\item you want to use \gmp's built-in C++ interface together with
  \cgal\ (Section~\ref{sec:gmpxx-setup}),
\item you want to use \core\ together with \cgal\ 
  (Section~\ref{sec:core-setup}),
\item you want to use \leda\ together with \cgal\ 
  (Section~\ref{sec:leda-setup}),
\item you want to use \qt\ together with \cgal\ 
  (Section~\ref{sec:qt-setup}).
\end{itemize}

Once you started the script, it should give you a message indicating
the \cgal\ version you are going to install and that you are running
the non-interactive mode. Then it proceeds by locating some utility
programs, determining your OS and compiler version and displaying the
settings you gave via command line. Your compiler is also checked for
a number of bugs resp. support of certain language features; a message
\texttt{ok} always indicates that your compiler works as it should,
that is, a feature is supported or a bug is \textit{not} present. On
the other hand, \texttt{no} or \texttt{unfortunately} indicate a lack
of support or the presence of a bug.

Finally the current setup is summarized, system specific directories
for makefiles and libraries are created (if they did not exist before)
and a new include makefile is written into the makefile directory. If
there already exists a makefile for the current OS/compiler
combination, it is backed up and you should get a corresponding
message.

To compile the \cgal\ libraries go now to the \texttt{src} directory.
Then type \texttt{make -f makefile\_lib} to compile the \cgal\ object
library and \texttt{make -f makefile\_sharedlib} to compile the \cgal\ 
shared object library. If you want to make changes to the makefiles
first, see section \ref{sec:makefiles} for an explanation of the
makefile structure of \cgal.

If you enabled \core\ support and want to use the \core\ distribution
shipped with \cgal, go to the \texttt{src/Core} directory and type
\texttt{make} to compile the \core\ library.

If you enabled \qt\ support, go to the \texttt{src/CGALQt} directory
and type \texttt{make} to compile the \cgal\ \qt\ support library.

%%When this is finished it would be a good idea to print and read the
%%`Getting Started with \cgal'\index{CGAL@\cgal!getting started} document
%%\texttt{getting\_started.ps} that can be found in the \texttt{doc\_ps}
%%directory.

\subsection{Setting up support for GMP}\label{sec:gmp-setup}
\index{GMP@\gmp!enable support}

By default there is no support for \gmp, but you can change this
easily by use of the command line option ``\texttt{-gmp}''. If \gmp\ is
installed in system directories on your system, you are already done
now. If this is not the case, you have to supply the directories
containing the \gmp\ header files (``\texttt{--GMP\_INCL\_DIR}
\textit{$<$dir$>$}'')\TTindex{GMP\_INCL\_DIR} and the \gmp\ library
(``\texttt{--GMP\_LIB\_DIR}
\textit{$<$dir$>$}'')\TTindex{GMP\_LIB\_DIR}.

\subsection{Setting up support for GMPXX}\label{sec:gmpxx-setup}
\index{GMPXX@\texttt{GMPXX}!enable support}

By default there is no support for GMPXX, \gmp's built-in C++
interface, but you can change this easily by use of the command line
option ``\texttt{-gmpxx}''.  The only requirement for this to work is
that \gmp\ support is enabled correctly.

\subsection{Setting up support for CORE}\label{sec:core-setup}
\index{CORE@\core!enable support}

By default there is no support for \core, but you can change this
easily by use of the command line option ``\texttt{-core}''. If you
want to use the \core\ distribution shipped with \cgal, this is all
you have to do. Otherwise, you also have to supply the directories
containing the \core\ header files (``\texttt{--CORE\_INCL\_DIR}
\textit{$<$dir$>$}'')\TTindex{CORE\_INCL\_DIR} and the \core\ library
(``\texttt{--CORE\_LIB\_DIR}
\textit{$<$dir$>$}'')\TTindex{CORE\_LIB\_DIR}.

\subsection{Setting up \leda\ support}\label{sec:leda-setup}
\index{LEDA@\leda!enable support}

See also section \ref{sec:leda}. By default there is no support for
\leda, but you can change this easily by use of the command line
option ``\texttt{-leda}''.  Unless \leda\ is installed in system
directories, you have to supply the directories containing
the \leda\ header files (``\texttt{--LEDA\_INCL\_DIR}
\textit{$<$dir$>$}'')\TTindex{LEDA\_INCL\_DIR} resp. the \leda\ 
libraries for your compiler (``\texttt{--LEDA\_LIB\_DIR} {\it
  $<$dir$>$}''\TTindex{LEDA\_LIB\_DIR}).

\subsection{Setting up support for Qt}\label{sec:qt-setup}
\index{Qt!enable support}

By default there is no support for \qt, but you can change this easily
by use of the command line option ``\texttt{-qt}''. If \qt\ is
installed in system directories on your system or the \texttt{\$QTDIR}
environment variable points to the \qt\ directory, you are already
done now. If this is not the case, you have to supply either the \qt\ 
directory (``\texttt{--QT\_DIR}~\textit{$<$dir$>$}'')\TTindex{QT\_DIR}
if your \qt\ installation is standard, either directories containing
the \qt\ header files
(``\texttt{--QT\_INCL\_DIR}~\textit{$<$dir$>$}'')\TTindex{QT\_INCL\_DIR}
and the \qt\ library
(``\texttt{--QT\_LIB\_DIR}~\textit{$<$dir$>$}'')\TTindex{QT\_LIB\_DIR},
and the path to the MOC\footnote{\qtmocpage} executable
(``\texttt{--QT\_MOC} \textit{$<$exe$>$}'')\TTindex{QT\_MOC} if your
\qt\ installation is not standard.

\subsection{Setting custom compiler/linker flags}\label{sec:custom-setup}
\index{compilers!setting custom flags}

You can supply custom compiler and linker flags using the options
\mbox{(``\texttt{--CUSTOM\_CXXFLAGS}
  \textit{$<$flags$>$}'')\TTindex{CUSTOM\_CXXFLAGS}} and
\mbox{(``\texttt{--CUSTOM\_LDFLAGS}
  \textit{$<$flags$>$}'')\TTindex{CUSTOM\_LDFLAGS}}.  These are the
first flags given to the compiler/linker in every call.

\textit{Note:} Do not forget to quote your options in case they
contain spaces. Example:
\begin{verbatim}
  ./install_cgal -ni g++ --CUSTOM_CXXFLAGS "-I/my/include -O2"
\end{verbatim}


\subsection{Disabling shared libraries building}\label{sec:disable-shared-setup}
\index{compilers!disabling shared libraries building}

You can disable the building of shared libraries (e.g. \texttt{libCGAL.so})
using the option \mbox{``\texttt{--disable-shared}''\TTindex{disable-shared}}.
This way, only static libraries (object file archives) are built.

Example:
\begin{verbatim}
  ./install_cgal --disable-shared -ni g++
\end{verbatim}


\subsection{Other Options}\label{sec:other-options}

There are some less important features of the install script we will
summarize here.

First of all, you can get the version number of \texttt{install\_cgal}
with option ``\texttt{--version}''. Note that all other options are
ignored in this case.\TTsubindex{install\_cgal}{version number}

Second there is an option ``\texttt{-os \textit{$<$compiler$>$}}''
where \textit{$<$compiler$>$} is your \CC\ compiler. This allows you
to determine your \cgal-OS description\index{OS description} (see section
\ref{sec:os-compiler-id}). The compiler can either be given by an
absolute path like
\begin{verbatim}
  ./install_cgal -os /usr/local/gcc-3.4.3/sun/bin/g++
\end{verbatim}
or just by denoting its basename, as long as it is on your path:
\begin{verbatim}
  ./install_cgal -os CC
\end{verbatim}
The option is intended for testing purposes and automatic detection of
the correct include makefile (see also section \ref{sec:makefiles}).

Finally, there exists an option
``\texttt{--verbose}''\TTsubindex{install\_cgal}{verbose mode} that
can be set in interactive mode as well as in non-interactive mode.
When set you get a detailed summary of error messages occurring during
\textit{any} compiler test (determining \stl\ version etc.). Normally
you only get these messages, if a required test (such as the general
\stl\ test) fails, otherwise you are just informed, \textit{if} it
succeeded or not.  This option is not recommended for general use, but
it can be useful to check why a certain test fails that was expected
to be passed.

\section{Upgrading a previous \cgal\ installation}
\label{sec:upgrade}\index{upgrading \cgal}\index{CGAL@\cgal!upgrade}

In case you already have a previous release of \cgal\ installed on
your system, you might like to reuse your configuration files and
\gmp\ installations. Simply use the following command to copy them
into the right place:\TTsubindex{install\_cgal}{upgrade option}
\begin{verbatim}
./install_cgal --upgrade <OLD_CGAL_DIR>
\end{verbatim}
where \texttt{<OLD\_CGAL\_DIR>} is the root directory of your existing
\cgal\ installation\\ (e.g. \texttt{/pub/local/CGAL-3.0}).  You can
then build all libraries for the actual operating system that existed
in your previous \cgal\ installation with
\TTsubindex{install\_cgal}{rebuild-all option}
\begin{verbatim}
./install_cgal --rebuild-all
\end{verbatim}

If you want to install \cgal\ for more than one operating system in
the same directory structure, you have to run the latter command
(\texttt{rebuild-all}) once on each operating system.

Using \texttt{--build-all} instead of \texttt{--rebuild-all} will save
you the time of the configuration tests, and will only rebuild the libraries.

If you want to install only one configuration on a given operating system,
you can specify its name (the base name of a file in \cgalinstconfdir) with
the option \texttt{--rebuild <config>} or \texttt{--build <config>}.

\textbf{Note} that some compilers that have been supported in previous
\cgal\ releases might not be supported in \cgal-\cgalrelease\ anymore,
see section \ref{sec:prerequisites}. Trying to build
\cgal-\cgalrelease\ with these compilers will most probably fail. You
can solve this problem by deleting the obsolete config files (see
section \ref{sec:filescreated}) from \cgalinstconfdir\ before issuing
the \texttt{rebuild-all} command.

Similarly, you might want to use compilers with \cgal-\cgalrelease\ 
that have not been supported in previous releases. For these compilers
please follow the usual procedure as described in section
\ref{sec:interactive-mode} or \ref{sec:non-interactive}.

\section{Identifying OS and Compiler}\label{sec:os-compiler-id}
\index{OS description}\index{identifying OS and compiler}

Since \cgal\ supports several different operating systems and
compilers, this is also reflected in the structure of the \cgal\ 
directory tree. Each OS/compiler combination has its own lib directory
under \texttt{\cgaldir/lib}) (and analogously its own include
makefile\index{include makefile} in \texttt{\cgaldir/make}) named as
determined by the following scheme.
\begin{center}
  \textit{$<$arch$>$\texttt{\_}$<$os$>$\texttt{-}$<$os-version$>$\texttt{\_}$<$comp$>${\tt
    -}$<$comp-version$>$}[\texttt{\_}LEDA]
\end{center}

\begin{description}
\item[$<$arch$>$] is the system architecture as defined by ``{\tt
    uname -p}'' or ``\texttt{uname -m}'',
\item[$<$os$>$] is the operating system as defined by ``\texttt{uname
    -s}'',
\item[$<$os-version$>$] is the operating system version as defined by
  ``\texttt{uname -r}'',
\item[$<$comp$>$] is the basename of the compiler executable (if it
  contains spaces, these are replaced by "-") \textit{and}
\item[$<$comp-version$>$] is the compiler's version number (which
  unfortunately can not be derived in a uniform manner, since it is
  quite compiler specific).
\end{description}

The suffix \texttt{\_}LEDA is appended to indicate \leda\ support. 

We call the resulting string \cgal-OS description.\\ Examples are
\texttt{mips\_IRIX-6.2\_CC-7.2} or {\tt
  sparc\_SunOS-5.5\_g++-3.4.3\_LEDA}.\\ You can use the install script
to get your \cgal-OS description, see section \ref{sec:other-options}.

\section{The \cgal\ makefile structure}\label{sec:makefiles}
\index{makefile structure}

The \cgal\ distribution contains the following makefiles:
\begin{itemize}
\item \texttt{\cgaldir/src/makefile\_lib} for compiling the \cgal\ 
  object library \texttt{libCGAL.a},
  
\item \texttt{\cgaldir/src/makefile\_sharedlib} for compiling the
  \cgal\ shared object library \texttt{libCGAL.so}
  \textit{and}
  
\item \texttt{\cgaldir/examples/*/makefile} for compiling the \cgal\ 
  example programs.
\end{itemize}

All these makefiles are generic: they can be used for more than one
compiler.  To achieve this, the first section of each makefile
contains an include statement that looks as follows:

\begin{verbatim}
      CGAL_MAKEFILE = /users/jannes/CGAL-3.1/make/makefile_<CGAL-OS description>
      include $(CGAL_MAKEFILE)
\end{verbatim}
%$

The file \texttt{CGAL\_MAKEFILE}\TTindex{CGAL\_MAKEFILE} is an include
file\index{include makefile} with platform dependent makefile
settings. The abbreviation \texttt{<CGAL-OS description>} (see section
\ref{sec:os-compiler-id} for details) is used to identify the
operating system and compiler for which the settings hold. For
example, the file \texttt{makefile\_mips\_IRIX64-6.5\_CC-n32-7.30}
contains makefile settings for the IRIX 6.5 operating system and the
\mipsprocc\ 7.3 compiler.  These include files are automatically
generated by the \texttt{install\_cgal} script and they are all
located in the \texttt{\cgaldir/make} directory.  For convenience, the
\texttt{install\_cgal} script will substitute the include makefile
that was generated most recently.

If you want to compile an application or an object library with a
different compiler, the only thing you need to do is to substitute
another include makefile for the \texttt{CGAL\_MAKEFILE} variable. An
alternative way to do this is to create an environment variable
\texttt{CGAL\_MAKEFILE}. To pass the value of the environment variable
to the makefile you can either comment out the \texttt{CGAL\_MAKEFILE}
line in the makefile or use an appropriate command line option for the
make utility.  A comfortable way to set \texttt{CGAL\_MAKEFILE} is by
using \texttt{install\_cgal~-os} (see section
\ref{sec:other-options}).  E.g. if your compiler is \texttt{g++}, you
would type
\begin{alltt}
CGAL_MAKEFILE=`\yourcgaldir/install_cgal -os g++`
\end{alltt}
in bourne shell resp.
\begin{alltt}
setenv CGAL_MAKEFILE `\yourcgaldir/install_cgal -os g++`
\end{alltt}
in csh derivatives. 

\textit{Tip:} Include the setting of \texttt{CGAL\_MAKEFILE} into your
shell startup script (e.g. \texttt{.}(\texttt{t})\texttt{cshrc} for
(\texttt{t})\texttt{csh} or \texttt{.bashrc} for \texttt{bash}).

All makefiles contain sections with compiler and linker flags.  You
can add your own flags here. For example, you might want to add the
flag \texttt{-DCGAL\_NO\_PRECONDITIONS} to turn off precondition
checking. The flags \texttt{\$(CGAL\_CXXFLAGS)} and
\texttt{\$(CGAL\_LDFLAGS)} should never be removed.

The default extension for \cgal\ source files is \texttt{.C}.  The
last section of the makefiles contains a suffix rule that tells the
compiler how to create a \texttt{.o}-file from a \texttt{.C}-file.  If
you want to use the default rule that is defined by the make utility,
you may want to remove this suffix rule.  However, note that this may
have consequences for the makefile variables \texttt{CGAL\_CXX} and
\texttt{CXXFLAGS}.

\section{Compiling a \cgal\ application}
\index{building applications} 
\index{compiling applications}

There is a script for conveniently creating makefiles for \cgal\ applications,
see section~\ref{sec:create_cgal_makefile}.

The directories \texttt{\cgaldir/examples} and \texttt{\cgaldir/demo}
contain many subdirectories with non-graphical and graphical example
programs.  In all these directories you will find a makefile that is
ready for use.

You either need to substitute the \texttt{CGAL\_MAKEFILE} variable in
these makefiles (see section \ref{sec:makefiles}), or set the
environment variable, to point to the makefile in the \texttt{\cgaldir/make}
directory.  Then just type \texttt{make}.

\section{Installation on Cygwin}\label{sec:cygwin}
\index{Cygwin!installation on}\index{installation!on Cygwin}

Cygwin is a free Unix-like environment for MS-Windows, distributed by
Cygnus Solutions. For our tests we have used version 1.3.2 and
$B$-20.1.

It consists of a port of a large number of GNU tools, such as bash,
make, gcc, gas, file utilities, etc, as well as tools ensuring an
ability to emulate Unix-like access to resources, for instance mount.
For a comprehensive introduction and details, see
\path~http://www.cygwin.com/~ .

Make sure that the link \texttt{/bin/sh.exe} exists. If not, create
it:
\begin{verbatim}
cd /bin
ln -s bash.exe sh.exe
\end{verbatim}

\subsection{Pathnames}
\index{Cygwin!pathnames}

Cygwin has a UNIX-like way of navigating hard drives, NFS shares, etc.
This is also the way in which directories and pathnames have to given
to the installation script. They are automatically converted to
Win32-style pathnames when given to the compiler or linker.

The main difference is that directories are seperated by slash (``/'')
rather than by backslash (``$\backslash$'').  The other difference is
concerned with specifying drives. One way is to use POSIX-style
pathnames that map Win32-style drives (\texttt{A:}, \texttt{B:}) to
\texttt{//a/\ldots}, \texttt{//b/\ldots} respectively. For instance,
the path
\texttt{D:$\backslash$Mystuff$\backslash$Mydir$\backslash$LEDA}
translates to \texttt{//d/Mystuff/Mydir/LEDA}.

Alternatively, it can be done using the mount utility, that can be
used to establish a map between Win32-style drives and the Unix-like
style. More precisely, it maps the forest of the directories/files on
Win32-drives to a tree with the root that is usually located at the top
level of the boot drive, say \texttt{C:}.  The root location can be
seen by typing \texttt{mount} command without parameters.  For
instance, if \texttt{D:} is mounted on
\texttt{C:$\backslash$ddrive}\footnote{by typing \texttt{mount D:
    /ddrive}} then the path
\texttt{D:$\backslash$Mystuff$\backslash$Mydir$\backslash$LEDA}
translates to \texttt{/ddrive/Mystuff/Mydir/LEDA}.

\paragraph{Upper/lower case and spaces in file names}
Behavior of Cygwin in this regard might be different from the \mswin\ 
behavior. In particular, using spaces in filenames should better be
avoided.

\paragraph{Links, shortcuts, etc} should be avoided as well.

\subsection{\msvc{}-setup}
\index{Cygwin!setup for \msvc{}}
\index{msvc@\msvc{}!setup on cygwin}

A number of environment variables has to be set (or updated)
in order to use the installation.

\texttt{PATH} should contain \msvc{} command line tools locations.
The environment variables \texttt{INCLUDE} and \texttt{LIB} should
point to the location of \msvc{} header files and to the location of
the \msvc{} libraries, respectively.  The interface for doing this is
different for NT and for Win9*.

\paragraph{\mswin-NT4.0.}
\index{Cygwin!setup on NT4}

One can set the corresponding environment variables using the
usual NT interface\footnote{open MyComputer, press right mouse button,
  select Properties, select Environment, set the relevant variables}.
Alternatively, they can be set in the \texttt{.bashrc} file for the
particular user, or in the system-wide \texttt{bash} customization
file (usually \texttt{/etc/bashrc}).

The result should look roughly as follows, assuming that
\texttt{C:$\backslash$PROGRA$\sim$1$\backslash$MICROS$\sim$2$\backslash$}
is the location of the \msvc{} installation.
\begin{verbatim}
LIB=C:\PROGRA~1\MICROS~2\VC98\LIB
INCLUDE=C:\PROGRA~1\MICROS~2\VC98\INCLUDE
\end{verbatim}
and \texttt{PATH} should contain
\begin{verbatim}
/PROGRA~1/MICROS~2/Common/msdev98/BIN:
/PROGRA~1/MICROS~2/VC98/BIN:/PROGRA~1/MICROS~2/Common/TOOLS:
/PROGRA~1/MICROS~2/Common/TOOLS/WINNT
\end{verbatim}

\paragraph{\mswin-9*.} 
\index{Cygwin!setup on \mswin-9*}

First, the memory for environment variables has to be increased.
Select the Cygwin icon from the Start-menu, press the right mouse
button and choose \textit{Properties}. Go to \textit{Memory}, select
\textit{Initial Environment}, set it to at least 2048 and
\textit{apply} the changes.

Second, edit the file \texttt{cygwin.bat} (or \texttt{cygnus.bat} in
Cygwin~0.9), located in the cygwin main directory and add the line
\begin{verbatim}
call C:\PROGRA~1\MICROS~2\VC98\Bin\MSCVARS32.BAT
\end{verbatim}
%\nonlinkedpath'C:\PROGRA~1\MICROS~2\'
%\texttt{C:$\backslash$PROGRA$\sim$1$\backslash$MICROS$\sim$2$\backslash$}
customized according to where \msvc{} is installed on your
system. Depending on the version of \msvc{} you might have to replace
\texttt{MSCVARS32.BAT} by \texttt{VCVARS32.BAT}.


%%
%% EOF
%%


