%% ==============================================================
%% Specification: Sorted Matrix Search
%% --------------------------------------------------------------
%% file  : spec_sorted_matrix_search.awi
%% author: Michael Hoffmann
%% $Id$
%% ==============================================================

\cgalColumnLayout
  
\begin{ccRefFunction}{sorted_matrix_search}
  \ccIndexMainItem[t]{sorted matrix search}
  \ccIndexSubitem[t]{searching}{in sorted matrices}
  \ccIndexSubitem[t]{matrix}{sorted}
  \ccIndexSubitem[t]{matrix}{searching}
  \ccIndexMainItem[t]{Frederickson/Johnson matrix search}
  
  \begin{ccAdvanced}
    \ccDefinition The function \ccRefName\ selects the smallest entry
    in a set of sorted matrices that fulfills a certain feasibility
    criterion.
    
    More exactly, a matrix $M = (m_{i j}) \in S^{r \times l}$
    (over a totally ordered set $S$) is sorted, iff
      \begin{eqnarray*}
        \forall \, 1 \le i \le r,\; 1 \le j < l\; :\; m_{i j} \le m_{i (j+1)} 
        \;\; {\it and}\\ 
        \forall \, 1 \le i < r,\; 1 \le j \le l\; :\; m_{i j} \le m_{(i+1) j} 
        \;\;.
      \end{eqnarray*}
      
      Now let $\mathcal{M}$ be a set of $n$ sorted matrices over $S$
      and $f$ be a monotone predicate on $S$, i.e.
      $$
      f\: :\: S \longrightarrow\, \textit{bool} \quad{\rm with}\quad f(r)
      \;\Longrightarrow\; \forall\, t \in S\,,\: t > r \; :\; f(t)\;.
      $$

    If we assume there is any feasible element in one of the matrices
    in $\mathcal{M}$, there certainly is a smallest such element. This is the one
    we are searching for.
    
    The feasibility test as well as some other parameters can (and
    have to) be customized through a traits class. 
    
    \ccInclude{CGAL/sorted_matrix_search.h}

    \def\ccLongParamLayout{\ccTrue} 
    
    \ccGlobalFunction{template < class RandomAccessIterator, class
      Traits > Traits::Value sorted_matrix_search(
      RandomAccessIterator f, RandomAccessIterator l, const Traits&
      t);}

    returns the element \ccc{x} in one of the sorted matrices from the
    range $\left[ f,\, l \right)$, for which \ccc{t.is_feasible( x)}
    is true and \ccc{t.compare( x, y)} is true for all other
    \ccc{y} values from any matrix for which \ccc{t.is_feasible(
      y)} is true.
    
    \ccPrecond
    \begin{enumerate}
    \item All matrices in $\left[f,\, l\right)$ are sorted according
      to \ccc{Traits::compare_non_strictly}.
    \item There is at least one entry $x$ in a matrix $M \in
      \left[f,\, l\right)$ for which \ccc{Traits::is_feasible(x)} is
      true.
    \end{enumerate}
    
    \ccRequire
    \begin{enumerate}
    \item \ccc{Traits} is a model for
      \ccc{SortedMatrixSearchTraits}.
    \item Value type of \ccc{RandomAccessIterator} is
      \ccc{Traits::Matrix}.
    \end{enumerate}
    
    \ccSeeAlso
    \ccRefConceptPage{SortedMatrixSearchTraits}
    
    \ccImplementation The implementation uses an algorithm by
    Frederickson and Johnson\cite{fj-fkppc-83,fj-gsrsm-84} and runs in
    $\mathcal{O}(n \cdot k + f \cdot \log (n \cdot k))$, where $n$ is
    the number of input matrices, $k$ denotes the maximal dimension of
    any input matrix and $f$ the time needed for one feasibility test.
    
    \ccExample In the following program we build a random vector $a =
    (a_i)_{i = 1,\,\ldots,\,5}$ (elements drawn uniformly from $\{
    0,\,\ldots,\,99 \}$) and construct a Cartesian matrix $M$
    containing as elements all sums $a_i + a_j,\: i,\,j \in
    \{1,\,\ldots,\,5\}$. If $a$ is sorted, $M$ is sorted as well. So
    we can apply \ccc{sorted_matrix_search} to compute the upper bound
    for the maximal entry of $a$ in $M$.
    
    \ccIncludeExampleCode{Matrix_search/sorted_matrix_search.cpp}

  \end{ccAdvanced}
\end{ccRefFunction}

\begin{ccRefClass}{Sorted_matrix_search_traits_adaptor<F,M>}
  \begin{ccAdvanced}
    \ccCreationVariable{t}\ccTagFullDeclarations
    
    \ccInclude{CGAL/Sorted_matrix_search_traits_adaptor.h}
    
    \ccDefinition The class \ccClassTemplateName\ can be used as an
    adaptor to create sorted matrix search traits classes for
    arbitrary feasibility test and matrix classes \ccc{F} resp.
    \ccc{M}.

    \ccIsModel
    \ccRefConceptPage{SortedMatrixSearchTraits}
    
    \ccRequirements

    \begin{enumerate}
    \item \ccc{M} is a model for \ccc{BasicMatrix} \textit{and}
    \item \ccc{F} defines a copy constructor and a monotone \ccc{bool
        operator()( const Value&)}.
    \end{enumerate}

    \ccCreation
    
    \ccConstructor{Sorted_matrix_search_traits_adaptor<F,M>( const F&
      m);}{initializes \ccVar\ to use \ccc{m} for feasibility
      testing.}
    
    \ccTypes 
    
    \ccNestedType{Matrix}{typedef to \ccc{M}.}
    
    \ccNestedType{Value}{typedef to \ccc{Matrix::Value}.}
    
    \ccNestedType{Compare_strictly}{typedef to
      \ccc{std::less<Value>}.}
    
    \ccNestedType{Compare_non_strictly}{typedef to
      \ccc{std::less_equal<Value>}.}

    \ccOperations
    
    \ccMemberFunction{Compare_strictly compare_strictly()
      const;}{returns the \ccc{Compare_strictly} object to be used for
      the search.}
    
    \ccMemberFunction{Compare_non_strictly compare_non_strictly()
      const;}{returns the \ccc{Compare_non_strictly} object to be used
      for the search.}
    
    \ccMemberFunction{bool is_feasible(const Value& a);}{uses the
      feasibility test given during creation.}

    \ccTagDefaults
  \end{ccAdvanced}
\end{ccRefClass}

\begin{ccRefConcept}{SortedMatrixSearchTraits}
  \begin{ccAdvanced}
    \ccCreationVariable{t}\ccTagFullDeclarations
    
    \ccDefinition The concept \ccRefName\ defines types and operations
    needed to compute the smallest entry in a set of sorted matrices
    that fulfills a certain feasibility criterion using the function
    \ccc{sorted_matrix_search}.
    
    \ccTypes 
    
    \ccNestedType{Matrix}{The class used for representing matrices.
      It has to be a model for \ccc{BasicMatrix}.}

    \ccTypedef{typedef Matrix::Value Value;}{The class used for
      representing the matrix elements.}
    
    \ccNestedType{Compare_strictly}{An adaptable binary function
      class: \ccc{Value} $\times$ \ccc{Value} $\rightarrow$ \ccc{bool}
      defining a non-reflexive total order on \ccc{Value}. This
      determines the direction of the search.}
    
    \ccNestedType{Compare_non_strictly}{An adaptable binary function
      class: \ccc{Value} $\times$ \ccc{Value} $\rightarrow$ \ccc{bool}
      defining the reflexive total order on \ccc{Value} corresponding
      to \ccc{Compare_strictly}.}

    \ccOperations
    
    \ccMemberFunction{Compare_strictly compare_strictly()
      const;}{returns the \ccc{Compare_strictly} object to be used for
      the search.}
    
    \ccMemberFunction{Compare_non_strictly compare_non_strictly()
      const;}{returns the \ccc{Compare_non_strictly} object to be used
      for the search.}
    
    \ccMemberFunction{bool is_feasible( const Value& a);}{The
      predicate to determine whether an element \ccc{a} is feasible.
      It has to be monotone in the sense that \ccc{compare( a, b)} and
      \ccc{is_feasible( a)} imply \ccc{is_feasible( b)}.}

    \ccHasModels
    \ccRefIdfierPage{CGAL::Sorted_matrix_search_traits_adaptor<F,M>}
    
    \ccSeeAlso
    \ccRefIdfierPage{CGAL::sorted_matrix_search}\\
    \ccRefConceptPage{BasicMatrix}
    
    \ccTagDefaults
  \end{ccAdvanced}
\end{ccRefConcept}
  
%% --------------------------------------------------------------
%% EOF spec_sorted_matrix_search.awi
%% --------------------------------------------------------------
