\ccRefPageBegin
 
\def\ccLongParamLayout{\ccFalse}
\begin{ccRefConcept}{Gps::GeneralPolygonWithHoles_2}

\ccTypes
% ======
\ccThree{GeneralPolygonWithHoles}{Hole_const_iterator~}{}
\ccThreeToTwo

% \ccNestedType{Size}{number of holes size type.}

\ccNestedType{General_polygon_2}{the general-polygon type used to
represent the outer boundary and each hole. Must model the Gps::GeneralPolygon_2 concept.}

\ccNestedType{Hole_const_iterator}{a bidirectional iterator
  over the polygonal holes. Its value type is
  \ccc{General_polygon_2}.}

\ccDefinition
% ===========
A model of this concept represents a general polygon with holes. This is the 
base concept for polygon with holes, and therefore does not require the ability
to access its boundary or holes, but only to be default constructable, copy 
constructable, and assignable.

% \lcTex{\ccwParamIndent=0mm}
\ccThree{GeneralPolygonWithHoles_2}{polygon.outer_boundary()~~~}{}
\ccThreeToTwo

\ccCreation
\ccCreationVariable{polygon}

\ccConstructor{GeneralPolygonWithHoles_2();}{default constructor.}
\ccGlue
\ccConstructor{GeneralPolygonWithHoles_2(GeneralPolygonWithHoles_2 other);}
{copy constructor.}
\ccGlue
\ccMethod{GeneralPolygonWithHoles_2 operator=(other);}{assignment operator.}

\ccConstructor{template <class InputIterator>
GeneralPolygonWithHoles_2(General_polygon_2 & outer,
                          InputIterator begin, InputIterator end);}
{constructs a general polygon with holes using a given general polygon \ccc{outer}
as the outer boundary and a given range of holes. If \ccc{outer} is an empty
general polygon, then an unbounded polygon with holes will be created. The holes must be
contained inside the outer boundary, and the polygons representing the holes 
must be strictly simple and pairwise disjoint, except perhaps at the vertices.}

\ccPredicates
% ===========
\ccMethod{bool is_unbounded();}
{returns \ccc{true} if the outer boundary is empty, and \ccc{false}
otherwise.}

\ccAccessFunctions
% ================

\ccHasModels
%===========
\ccc{CGAL::General_polygon_with_holes_2<General_polygon>}\\
\ccc{CGAL::Polygon_with_holes_2<Kernel,Container>}\\
\ccc{CGAL::Gps_circle_segment_traits_2<Kernel>::Polygon_with_holes_2}\\
\ccc{CGAL::Gps_traits_2<ArrTraits,GeneralPolygon>::Polygon_with_holes_2}

\end{ccRefConcept}

\ccRefPageEnd
