% +------------------------------------------------------------------------+
% | Reference manual page: VisibilityComplexFace.tex
% +------------------------------------------------------------------------+
% | Package: Visibility_complex
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+

\begin{ccRefConcept}{VC2Face}

\ccDefinition

The concept \ccRefName\ defines the requirements for the \ccc{Face} type in
the \ccc{Visibility_complex_2<VC2GeomTraits,VC2Items>} class. It is also
required in the \ccc{Face_wrapper<Vc>} member class template of an items
class, see the \ccc{VC2Items} concept.

A (front or rear) view is either an edge of the viewed object, or a
cusp-edge of the viewed constraint.

\ccTypes
\ccThree{typedef Face::Vertex_handle}{Vertex_handle;}{}
\ccThreeToTwo

\ccNestedType{Gt}{Geometric traits class.}
\ccGlue
\ccNestedType{Vertex}{Model of \ccc{VC2Vertex}.}
\ccGlue
\ccNestedType{Edge}{Model of \ccc{VC2Edge}.}
\ccGlue
\ccNestedType{Face}{Model of \ccc{VC2Face}, can actually be a subclass of
the containing class.}
\ccGlue
\ccNestedType{Vertex_handle}{Handle to vertices.}
\ccGlue
\ccNestedType{Face_handle}{Handle to faces.}
\ccGlue
\ccNestedType{Edge_handle}{Handle to edges.}
\ccGlue
\ccNestedType{Vertex_const_handle}{Const handle to vertices.}
\ccGlue
\ccNestedType{Face_const_handle}{Const handle to faces.}
\ccGlue
\ccNestedType{Edge_const_handle}{Const handle to edges.}
\ccGlue
\ccNestedType{Border_iterator}{Iterator over the edges of the upper or
lower border of a face. Starts from the source, and ends at the sink. Can
be initialized from an \ccc{Edge_handle} and a \ccc{Face_handle}, or with
the *_(begin|end) methods.}
\ccGlue
\ccNestedType{Border_const_iterator}{Const counterpart.}


\ccThree{Border_iterator}{v.set_bottom_edge( Edge_handle e);}{}
\ccThreeToTwo

\ccCreation
\ccCreationVariable{f}

\ccConstructor{Face();}{Default constructor.}

\ccAccessFunctions

\ccTagFullDeclarations
\ccMethod{Vertex_handle sup();}{Returns the sink of face \ccVar.}
\ccGlue
\ccMethod{Vertex_handle inf();}{Returns the source of face \ccVar.}
\ccGlue
\ccMethod{Edge_handle front_view();}{Returns the front view.}
\ccGlue
\ccMethod{Edge_handle back_view();}{Returns the rear view.}
\ccGlue
\ccMethod{Border_iterator top_begin();}{}
\ccMethod{Border_iterator top_end();}{}
\ccMethod{Border_iterator bottom_begin();}{}
\ccMethod{Border_iterator bottom_end();}{Iterators over the
edges of the lower and upper borders of the face.}

All the latter methods have const counterparts returning const handles and
iterators.

\ccOperations
\ccMethod{void set_sup(Vertex_handle v);}
    {Sets the sink of face \ccVar\ to $v$ and sets the source face of $v$ to
    \ccVar.}
\ccGlue
\ccMethod{void set_inf(Vertex_handle v);}
    {Sets the source of face \ccVar\ to $v$ and sets the sink face of $v$ to
    \ccVar.}
\ccGlue
\ccMethod{void set_back_view(Edge_handle); const}
    {Sets the rear view.}
\ccGlue
\ccMethod{void set_front_view(Edge_handle); const}
    {Sets the front view.}


\ccTagDefaults

\ccSeeAlso

\ccRefIdfierPage{CGAL::Visibility_complex_2<VC2GeomTraits,VC2Items>} \\
\ccRefConceptPage{VC2Items}\\
\ccRefConceptPage{VC2Vertex}\\
\ccRefConceptPage{VC2Edge}


\end{ccRefConcept}
\ccRefPageEnd
% +----------------------------------------------------------------------------+
