% =============================================================================
% The CGAL Reference Manual
% Chapter: Optimisation
% -----------------------------------------------------------------------------
% file  : doc_tex/basic/Optimisation/main.tex
% author: Bernd Gärtner, Sven Schönherr (sven@inf.fu-berlin.de)
% -----------------------------------------------------------------------------
% $Revision$
% $Date$
% =============================================================================

\newcommand{\linebreakByHand}{\ccTexHtml{\\}{}}
\newcommand{\SaveSpaceByHand}{}  %%%% [2]{\ccTexHtml{#1}{#2}}

\chapter{Geometric Optimisation} \label{Optimisation}
\RCSdefDate{\OptRCSDate}{$Date$}

\ccChapterRelease{Release: 2.0 \ccTexHtml{\quad}{ , } \OptRCSDate}

\ccChapterAuthor{Bernd G{\"a}rtner}\ccTexHtml{\\}{<br>}
\ccChapterAuthor{Michael Hoffmann}\ccTexHtml{\\}{<br>}
\ccChapterAuthor{Sven Sch{\"o}nherr}

\ccTexHtml{\thispagestyle{empty}}{}

\begin{ccTexOnly}\section*{Introduction}\end{ccTexOnly}
\begin{ccHtmlOnly}<H2>Introduction</H2><P>\end{ccHtmlOnly}

This chapter describes routines for solving geometric optimisation
problems. The first two sections contain algorithms for computing and
updating the smallest enclosing circle resp.\ ellipse of a finite
point set. Formally, the `smallest enclosing circle' is the boundary
of the closed disk of minimum area covering the point set. It is known
that this disk is unique. We usually identify the disk with its
bounding circle, allowing us to talk about points being on the
boundary of the circle, etc. The same holds for the smallest enclosing
ellipse. These algorithms work in an incremental manner. They are
implemented as semi-dynamic data structures, thus allowing to insert
points while maintaining the smallest enclosing circle resp.\ ellipse.

The remaining sections describe algorithms for searching in matrices with
specific properties and some applications. In particular, there are
general implementations of
\begin{itemize}
  \item monotone matrix search (see Section~\ref{secMonotoneMatrixSearch}),
    which can be applied to compute
    \begin{itemize}
      \item extremal polygons of a convex polygon
        (see Section~\ref{secComputingExtremalPolygons}) \textit{or}
      \item all furthest neighbors for the vertices of a convex polygon
        (see Section~\ref{secAllFurthestNeighbors}),
    \end{itemize}
  \item and sorted matrix search (see Section~\ref{secSortedMatrixSearch}),
    which can be used to compute the $p$-centers of a planar point set
    (see Section~\ref{sec_RectangularPCenters}).
\end{itemize}

\subsubsection*{Traits Class}
The class and function templates are parameterized with a traits class
which defines the abstract interface between the optimisation
algorithm and the primitives it uses. We provide traits class
implementations that interface the optimisation algorithms with the
\cgal\ kernel. For some algorithms, in addition, we provide traits
class adapters to user supplied point classes. Finally, we describe
the requirements that must be fulfilled by traits classes for
optimisation algorithms.  This is at the same time a specification for
using the provided traits class implementations as for users who want
to supply their own traits class.

\subsubsection*{Assertions}
The optimisation code uses infix \ccc{OPTIMISATION} in the assertions,
e.g.\ defining the compiler flag
\ccc{CGAL_OPTIMISATION_NO_PRECONDITIONS} switches precondition
checking off, cf.~Section~\ref{assertions}.

\newcommand{\cgalSetOptTraitsAdaptLayout}{\ccTexHtml{%
    \ccSetThreeColumns{CGAL_Oriented_side}{}{returns constants
      \ccc{CGAL_LEFTTURN}, \ccc{CGAL_COLLINEAR}}
    \ccPropagateThreeToTwoColumns}{}}
\newcommand{\cgalSetOptTraitsAdaptReqLayout}{\ccTexHtml{%
    \ccSetThreeColumns{CGAL_Oriented_side}{da.get_hw( Point p).}{}
    \ccPropagateThreeToTwoColumns}{}}

\newcommand{\cgalSetOptTraitsReqLayout}{\ccTexHtml{%
    \ccSetThreeColumns{CGAL_Oriented_side}{}{returns
      \ccc{CGAL_ON_BOUNDED_SIDE}, \ccc{CGAL_ON_BOUNDARY}}
    \ccPropagateThreeToTwoColumns}{}}

\ccHtmlNoClassToc

\input{smallest_enclosing_circles}

\input{smallest_enclosing_ellipses}

\input{spec_extremal_polygons}
 
\input{spec_all_furthest_neighbors}
 
\input{spec_rectangular_p_centers}
 
\input{spec_monotone_matrix_search}
 
\input{spec_sorted_matrix_search}

% ===== EOF ===================================================================
