% +------------------------------------------------------------------------+
% | Reference manual page: Polyhedron_incremental_builder_3.tex
% +------------------------------------------------------------------------+
% | 17.03.1999   Lutz Kettner
% | Package: Polyhedron
% | 
\RCSdef{\RCSPolyhedronincrementalbuilderRev}{$Revision$}
\RCSdefDate{\RCSPolyhedronincrementalbuilderDate}{$Date$}
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefClass}{Polyhedron_incremental_builder_3<HDS>}
\label{pagePolyIncrBuilder}

\ccDefinition
\ccCreationVariable{B}
  
The auxiliary class \ccClassTemplateName\ supports the incremental
construction of polyhedral surfaces, which is for example convenient
when constructing polyhedral surfaces from file formats, such as the
Object File Format (OFF)~\cite{p-gmgv15-94},
OpenInventor~\cite{w-impoo-94} or VRML~\cite{bpp-vrml-95,vrmls-96}.
\ccClassTemplateName\ needs access to the internal halfedge data
structure of type \ccc{HDS} of the polyhedral surface. It is intended
to be used within a modifier, see \ccc{CGAL::Modifier_base} in the 
Support Library Reference Manual.

The incremental builder might be of broader interest for other uses of
the halfedge data structures, but it is specifically bound to the
definition of polyhedral surfaces given here. During construction all
conditions of polyhedral surfaces are checked and in case of violation
an error status is set. A diagnostic message will be issued to
\ccc{cerr} if the \ccc{verbose} flag has been set at construction
time.

The incremental construction starts with a list of all point
coordinates and concludes with a list of all facet polygons. Edges are
not explicitly specified. They are derived from the vertex incidence
information provided from the facet polygons. The polygons are given as a
sequence of vertex indices.  The halfedge data structure \ccc{HDS} must
support vertices (i.e., \ccc{Supports_halfedge_vertex} $\equiv$
\ccc{CGAL::Tag_true}). The correct order of allowed method calls to build a
polyhedral surface is given as a regular expression below. Vertices and
facets can be added in arbitrary order as long as
\ccc{add_vertex_to_facet()} refers only to vertex indices that are
already known.

{\it
    \hspace*{6mm} begin\_surface $($add\_vertex $|$ 
                  $($begin\_facet add\_vertex\_to\_facet$\:*$
                            end\_facet\/$))\:*$ end\_surface
}


\ccInclude{CGAL/Polyhedron_incremental_builder_3.h}

\ccTypes

\ccTwo{CGAL::Polyhedron_incremental_builder_3<HDS>:: HalfedgeDS}{}

\ccNestedType{HalfedgeDS}{halfedge data structure \ccc{HDS}.}
\ccGlue
\ccNestedType{Point_3}{point type of the vertex.}
\ccGlue
\ccNestedType{size_type}{size type.}

\ccCreation
\ccThree{void}{B.remove_unconnected_vertices();;;}{}
\ccThreeToTwo

\ccConstructor{Polyhedron_incremental_builder_3(HDS& hds, 
               bool verbose = false);}
 {stores a reference to the halfedge data structure \ccc{hds} of a
   polyhedral surface in its internal state. An existing polyhedral
   surface in \ccc{hds} remains unchanged. The incremental builder
   appends the new polyhedral surface. If \ccc{verbose} is \ccc{true},
   diagnostic messages will be printed to \ccc{cerr} in case of
   malformed input data.}

\newpage
\ccOperations

\ccMethod{void begin_surface( size_type v, size_type f, size_type h = 0);}
{starts the construction. $v$ is the number of vertices
    to expect, $f$ the number of facets, and $h$ the number of
    halfedges. If $h$ is unspecified (\ccc{== 0}) it is estimated using
    Euler's equation (plus 5\% for the so far unknown holes and genus of
    the object). These values are used to reserve space in the
    halfedge data structure \ccc{hds}. If the representation supports
    insertion these values do not restrict the class of constructible
    polyhedra. If the representation does not support insertion the
    object must fit into the reserved sizes.}  

\ccMethod{void add_vertex( const Point_3& p);}{
    adds $p$ to the vertex list.}  
\ccGlue
\ccMethod{void begin_facet();}{starts a facet.}
\ccGlue
\ccMethod{void add_vertex_to_facet( size_type i);}{adds a vertex with
  index $i$ to the current facet. The first point added with
  \ccc{add_vertex()} has the index 0.}
\ccGlue
\ccMethod{void end_facet();}{ends a facet.}
\ccGlue
\ccMethod{void end_surface();}{ends the construction.}

\ccMethod{bool error() const;}{returns error status of the builder.}
\ccGlue
\ccMethod{void rollback();}{undoes all changes made to the halfedge
  data structure since the last \ccc{begin_surface()}.}

\ccMethod{bool check_unconnected_vertices();}{returns
  \ccc{true} if unconnected vertices are detected. If \ccc{verbose} was set to
  \ccc{true} (see the constructor above) debug information about the
  unconnected vertices is printed.}

\ccMethod{bool remove_unconnected_vertices();}{returns
  \ccc{true} if all unconnected vertices could be removed successfully.
  This happens either if no unconnected vertices had appeared or if the
  halfedge data structure supports the removal of individual elements.}


\ccSeeAlso

\ccRefIdfierPage{CGAL::Polyhedron_3<Traits>}\\
\ccRefIdfierPage{HalfedgeDS}\\
\ccc{CGAL::Modifier_base} in the Support Library Reference Manual.

\ccExample

A modifier class creates a new triangle in the halfedge data structure
using the incremental builder.

\ccIncludeExampleCode{Polyhedron/polyhedron_prog_incr_builder.C}

\end{ccRefClass}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+

