% begin cgal manual page

\begin{ccRefClass}{Nef_polyhedron_2<T>}\ccCreationVariable{N}

\ccDefinition

An instance of data type \ccc{Nef_polyhedron_2<T>} is a subset of the
plane that is the result of forming complements and intersections
starting from a finite set \ccc{H} of
halfspaces. \ccc{Nef_polyhedron_2} is closed under all binary set
operations \ccc{intersection}, \ccc{union}, \ccc{difference},
\ccc{complement} and under the topological operations \ccc{boundary},
\ccc{closure}, and \ccc{interior}.

The template parameter \ccc{T} is specified via an extended kernel
concept. \ccc{T} must be a model of the concept
\ccc{ExtendedKernelTraits_2}.

\ccInclude{CGAL/Nef_polyhedron_2.h}

\ccSetOneOfTwoColumns{7cm}

\ccTypes

\ccNestedType{Line}{the oriented lines modeling halfplanes}

\ccNestedType{Point}{the affine points of the plane.}

\ccNestedType{Direction}{directions in our plane.}

%\ccNestedType{Aff_transformation}{affine transformations of the plane.}

\ccEnum{enum Boundary { EXCLUDED,  INCLUDED }}{construction selection.}

\ccEnum{enum Content { EMPTY,  COMPLETE }}{construction selection}

\ccSetOneOfTwoColumns{3cm}

\ccCreation

\ccConstructor{Nef_polyhedron_2<T>(Content plane = EMPTY)}{
creates an instance \ccc{N} of type \ccc{Nef_polyhedron_2<T>}
and initializes it to the empty set if \ccc{plane == EMPTY}
and to the whole plane if \ccc{plane == COMPLETE}. 
}

\ccConstructor{Nef_polyhedron_2<T>(Line l, Boundary line = INCLUDED)}{
creates a Nef polyhedron \ccc{N} containing the halfplane left of
\ccc{l} including \ccc{l} if \ccc{line==INCLUDED}, excluding \ccc{l}
if \ccc{line==EXCLUDED}.}

\ccConstructor{template <class Forward_iterator>
Nef_polyhedron_2<T>(Forward_iterator it, Forward_iterator end, 
Boundary b = INCLUDED)}{
creates a Nef polyhedron \ccc{N} from the simple polygon \ccc{P}
spanned by the list of points in the iterator range \ccc{[it,end)} and
including its boundary if \ccc{b = INCLUDED} excluding the boundary
otherwise. \ccc{Forward_iterator} has to be an iterator with
value type \ccc{Point}. This construction expects that \ccc{P} is
simple. The degenerate cases where \ccc{P} contains no point, one
point or spans just one segment (two points) are correctly handled. In
all degenerate cases there's only one unbounded face adjacent to the
degenerate polygon. If \ccc{b == INCLUDED} then \ccc{N} is just the
boundary. If \ccc{b == EXCLUDED} then \ccc{N} is the whole plane
without the boundary.  }

\ccSetTwoOfThreeColumns{4cm}{3cm}

\ccOperations

\ccMethod{void clear(Content plane = EMPTY) ;}{
makes \ccc{N} the empty set if \ccc{plane == EMPTY} and the
full plane if \ccc{plane == COMPLETE}. 
}

\ccMethod{bool is_empty() ;}{
returns true if \ccc{N} is empty, false otherwise.}

\ccMethod{bool is_plane() ;}{
returns true if \ccc{N} is the whole plane, false otherwise.}

\ccHeading{Constructive Operations} 

\ccMethod{Nef_polyhedron_2<T> complement() ;}{
returns the complement of \ccc{N} in the plane.}

\ccMethod{Nef_polyhedron_2<T> interior() ;}{
returns the interior of \ccc{N}.}

\ccMethod{Nef_polyhedron_2<T> closure() ;}{
returns the closure of \ccc{N}.}

\ccMethod{Nef_polyhedron_2<T> boundary() ;}{
returns the boundary of \ccc{N}.}

\ccMethod{Nef_polyhedron_2<T> regularization() ;}{
returns the regularized polyhedron (closure of interior).}

\ccMethod{Nef_polyhedron_2<T> intersection(const Nef_polyhedron_2<T>& N1) ;}{
returns \ccc{N} $\cap$ \ccc{N1}. }

\ccMethod{Nef_polyhedron_2<T> join(const Nef_polyhedron_2<T>& N1) ;}{
returns \ccc{N} $\cup$ \ccc{N1}. Note that ``union'' is a keyword of C++
and cannot be used for this operation.}

\ccMethod{Nef_polyhedron_2<T> difference(const Nef_polyhedron_2<T>& N1) ;}{
returns \ccc{N} $-$ \ccc{N1}.}

\ccMethod{Nef_polyhedron_2<T> symmetric_difference(const 
Nef_polyhedron_2<T>& N1) ;}{
returns the symmectric difference \ccc{N - T} $\cup$ \ccc{T - N}.}

%\ccMethod{ Nef_polyhedron_2<T> transform(const Aff_transformation& t) ;}{returns $t(\ccc{N})$.}

Additionally there are operators \ccc{*,+,-,^,!} which implement the
binary operations \emph{intersection}, \emph{join}, \emph{difference},
\emph{symmetric difference}, and the unary operation
\emph{complement}, respectively. There are also the corresponding
modification operations \ccc{*=,+=,-=,^=}.

There are also comparison operations like \ccc{<,<=,>,>=,==,!=} which
implement the relations subset, subset or equal, superset, superset or
equal, equality, inequality, respectively.

\ccHeading{Exploration - Point location - Ray shooting}
As Nef polyhedra are the result of forming complements 
and intersections starting from a set \ccc{H} of halfspaces that are
defined by oriented lines in the plane, they can be represented by
an attributed plane map $M = (V,E,F)$. For topological queries
within \ccc{M} the following types and operations allow exploration
access to this structure. 

\ccSetOneOfTwoColumns{3cm}

\ccTypes

\ccNestedType{Explorer}{a decorator to examine the underlying plane map. 
See the manual page of \ccc{Explorer}. 
}

\ccNestedType{Object_handle}{a generic handle to an object of the underlying
plane map. The kind of object \ccc{(vertex, halfedge, face)} can 
be determined and the object can be assigned to a corresponding
handle by the three functions:\\
\ccc{bool assign(Vertex_const_handle& h, Object_handle)}\\
\ccc{bool assign(Halfedge_const_handle& h, Object_handle)}\\
\ccc{bool assign(Face_const_handle& h, Object_handle)}\\
where each function returns \ccc{true} iff the assignment to
\ccc{h} was done. 
}

\ccEnum{enum Location_mode { DEFAULT, NAIVE, LMWT}}{ selection
flag\footnote {LMWT = Locally Minimum Weight Triangulation, a locally
optimized constrained triangulation where the weight corresponds to
the lenght of the edges of the triangulation.} for the point location
mode.}

\ccSetTwoOfThreeColumns{3cm}{1cm}

\ccOperations

\ccMethod{bool contains(Object_handle h) ;}{
returns true iff the object \ccc{h} is contained in the set
represented by \ccc{N}. }

\ccMethod{bool contained_in_boundary(Object_handle h) ;}{
returns true iff the object \ccc{h} is contained in the $1$-skeleton
of \ccc{N}. }

\ccMethod{Object_handle locate(const Point& p, Location_mode m =
DEFAULT) ;}{ returns a generic handle \ccc{h} to an object (face,
halfedge, vertex) of the underlying plane map that contains the point
\ccc{p} in its relative interior. The point \ccc{p} is contained in
the set represented by \ccc{N} if \ccc{N.contains(h)} is true. The
location mode flag \ccc{m} allows one to choose between different
point location strategies.  }

\ccMethod{Object_handle ray_shoot(const Point& p, const Direction& d,
Location_mode m = DEFAULT) ;}{ returns a handle \ccc{h} with
\ccc{N.contains(h)}, that can be converted to a
\ccc{Vertex_/Halfedge_/Face_const_handle} as described above. The
object returned is intersected by the ray starting in \ccc{p} with
direction \ccc{d} and has minimal distance to \ccc{p}.  The operation
returns the null handle \ccc{NULL} if the ray shoot along \ccc{d} does
not hit any object \ccc{h} of \ccc{N} with \ccc{N.contains(h)}. The
location mode flag \ccc{m} allows one to choose between different
point location strategies.  }

\ccMethod{Object_handle ray_shoot_to_boundary(const Point& p, const
Direction& d, Location_mode m = DEFAULT) ;}{ returns a handle \ccc{h},
that can be converted to a \ccc{Vertex_/Halfedge_const_handle} as
described above. The object returned is part of the $1$-skeleton of
\ccc{N}, intersected by the ray starting in \ccc{p} with direction
\ccc{d} and has minimal distance to \ccc{p}.  The operation returns
the null handle \ccc{NULL} if the ray shoot along \ccc{d} does not hit
any $1$-skeleton object \ccc{h} of \ccc{N}. The location mode flag
\ccc{m} allows one to choose between different point location
strategies.  }

\ccMethod{Explorer explorer() ;}{
returns a decorator object that allows read-only access of
the underlying plane map. See the manual page \ccc{Explorer} for its 
usage.}

\ccHeading{Input and Output}
A Nef polyhedron \ccc{N} can be visualized in a \ccc{Window_stream W}. 
The output operator is defined in the file 
\ccc{CGAL/IO/Nef_\-poly\-hedron_2_\-Win\-dow_\-stream.h}.
 
\ccImplementation

Nef polyhedra are implemented on top of a halfedge data structure and
use linear space in the number of vertices, edges and facets.
Operations like \ccc{empty} take constant time. The operations
\ccc{clear}, \ccc{complement}, \ccc{interior}, \ccc{closure},
\ccc{boundary}, \ccc{regularization}, input and output take linear
time. All binary set operations and comparison operations take time
$O(n \log n)$ where $n$ is the size of the output plus the size of the
input.

The point location and ray shooting operations are implemented in two
flavors. The \ccc{NAIVE} operations run in linear query time without
any preprocessing, the \ccc{DEFAULT} operations (equals \ccc{LMWT})
run in sub-linear query time, but preprocessing is triggered with the
first operation. Preprocessing takes time $O(N^2)$, the sub-linear
point location time is either logarithmic when LEDA's persistent
dictionaries are present or if not then the point location time is
worst-case linear, but experiments show often sublinear runtimes.  Ray
shooting equals point location plus a walk in the constrained
triangulation overlayed on the plane map representation. The cost of
the walk is proportional to the number of triangles passed in
direction \ccc{d} until an obstacle is met. In a minimum weight
triangulation of the obstacles (the plane map representing the
polyhedron) the theory provides a $O(\sqrt{n})$ bound for the number
of steps. Our locally minimum weight triangulation approximates the
minimum weight triangulation only heuristically (the calculation of
the minimum weight triangulation is conjectured to be NP hard). Thus
we have no runtime guarantee but a strong experimental motivation for
its approximation.

\ccExample

Nef polyhedra are parameterized by a so-called extended geometric
kernel. There are three kernels, one based on a homogeneous
representation of extended points called
\ccc{Extended_homogeneous<RT>} where \ccc{RT} is a ring type providing
additionally a \ccc{gcd} operation, one based on a Cartesian
representation of extended points called \ccc{Extended_cartesian<NT>}
where \ccc{NT} is a field type, and finally
\ccc{Filtered_extended_homogeneous<RT>} (an optimized version of the
first). The following example uses the filtered homogeneous kernel to
construct the intersection of two halfspaces.

\ccIncludeExampleCode{Nef_2/simple_intersection.C}

After line (*) \ccc{N3} is the intersection of \ccc{N1} and \ccc{N2}. 
The member types of \ccc{Nef_polyhedron_2< Extended_homogeneous<NT> >}
map to corresponding types of the standard CGAL geometry kernel
(type equality in pseudo-code notation):
\begin{ccExampleCode}
CGAL::Nef_polyhedron_2< CGAL::Extended_cartesian<FT> >::Point
  == CGAL::Cartesian<FT>::Point_2

CGAL::Nef_polyhedron_2< CGAL::Extended_homogeneous<RT> >::Point
   == CGAL::Homogeneous<RT>::Point_2

CGAL::Nef_polyhedron_2< CGAL::Filtered_extended_homogeneous<RT> >::Point
   == CGAL::Homogeneous<RT>::Point_2
\end{ccExampleCode}
The same holds for the types \ccc{Line} and \ccc{Direction} in the
local scope of \ccc{Nef_polyhedron_2<...>}.

\end{ccRefClass}


