%% Copyright (c) 2003,2004,2005  INRIA Sophia-Antipolis (France).
%% All rights reserved.
%%
%% This file is part of CGAL (www.cgal.org).
%% You can redistribute it and/or modify it under the terms of the GNU
%% General Public License as published by the Free Software Foundation,
%% either version 3 of the License, or (at your option) any later version.
%%
%% Licensees holding a valid commercial license may use this file in
%% accordance with the commercial license agreement provided with the software.
%%
%% This file is provided AS IS with NO WARRANTY OF ANY KIND, INCLUDING THE
%% WARRANTY OF DESIGN, MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE.
%%
%% $URL$
%% $Id$
%% 
%%
%% Author(s)     : Menelaos Karavelas <mkaravel@iacm.forth.gr>


\begin{ccRefConcept}{SegmentDelaunayGraphHierarchyVertexBase_2}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries
\ccCreationVariable{hvb}


\ccDefinition 
The vertex of a segment Delaunay graph
included in a segment Delaunay graph hierarchy has to provide
some pointers to the corresponding vertices in the
graphs of the next and preceeding levels.
Therefore, the concept \ccc{SegmentDelaunayGraphHierarchyVertexBase_2}
refines the concept \ccc{SegmentDelaunayGraphVertexBase_2}, by
adding two vertex handles to the correponding vertices for the
next and previous level graphs.


\ccRefines
\ccc{SegmentDelaunayGraphVertexBase_2}


\ccTypes
\ccc{SegmentDelaunayGraphHierarchyVertexBase_2} does not introduce
any types in addition to those of
\ccc{SegmentDelaunayGraphVertexBase_2}.


\ccCreation
\ccCreationVariable{v}  %% choose variable name
\ccTwo{SegmentDelaunayGraphHierarchyVertexBase_2 v;+++}{}
%

The \ccc{SegmentDelaunayGraphHierarchyVertexBase_2} concept does not
introduce any constructors in addition to those of the
\ccc{SegmentDelaunayGraphVertexBase_2} concept.

%% In addition to the default and copy constructors the following
%% constructors must be defined.

%% \ccConstructor{SegmentDelaunayGraphHierarchyVertexBase_2(Storage_site_2 ss);}
%% {Constructs a vertex associated with the site represented by the
%%   storage site \ccc{ss}.}
%% %
%% \ccGlue
%% \ccConstructor
%% {SegmentDelaunayGraphHierarchyVertexBase_2(Storage_site_2 s,
%%   Face_handle f);}
%% {Constructs a vertex associated with
%% the site represented by the storage site \ccc{ss} and pointing to the
%% face associated with the face handle \ccc{f}.}


\ccOperations
\ccThree{Vertex_handle}{v.set_down(Vertex_handle d)+}{}
%
\ccMethod{Vertex_handle up();}{Returns a handle to the corresponding
  vertex of the next level segment Delaunay graph. If such a vertex
  does not exist \ccc{Vertex_handle()} is returned.}
%
\ccGlue
\ccMethod{Vertex_handle down();}{Returns a handle to the corresponding
  vertex of the previous level segment Delaunay graph. If such a
  vertex does not exist \ccc{Vertex_handle()} is returned.}
%
\ccGlue
\ccMethod{void set_up(Vertex_handle u);}{Sets the handle for the
  vertex of the next level segment Delaunay graph.}
%
\ccGlue 
\ccMethod{void set_down(Vertex_handle d);}{Sets the handle for the
  vertex of the previous level segment Delaunay graph.}




\ccHasModels

\ccc{CGAL::Segment_Delaunay_graph_hierarchy_vertex_base_2<CGAL::Segment_Delaunay_graph_vertex_base_2<Gt,SSTag> >}


\ccSeeAlso

\ccc{SegmentDelaunayGraphDataStructure_2} \\
\ccc{SegmentDelaunayGraphVertexBase_2}\\
\ccc{CGAL::Segment_Delaunay_graph_hierarchy_2<Gt,DS>}\\
\ccc{CGAL::Triangulation_data_structure_2<Vb,Fb>}\\
\ccc{CGAL::Segment_Delaunay_graph_vertex_base_2<Gt,SSTag>}\\
\ccc{CGAL::Segment_Delaunay_graph_hierarchy_vertex_base_2<Vbb>}

\end{ccRefConcept}


% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+
