\ccDefGlobalScope{CGAL::}
\begin{ccRefClass}[Qt::]{PainterOstream<K>}

\ccDefinition
An object of type \ccRefName\ provides output operators for \cgal\ kernel objects.
As \cgal\ has unbounded objects the \ccRefName\ must be constructed with a clipping rectangle.
This is typically the visible area of the widget where the unbounded object is displayed.

\ccInclude{CGAL/Qt/PainterOstream.h}

\ccCreationVariable{os}

\ccCreation
\ccConstructor{PainterOstream<K>(QPainter* qp, QRectF clippingRect);}{The clipping rect is used for unbounded \cgal\ objects.}

\ccOperations

\ccMethod{PainterOstream<K> operator<<(K::Point_2);}{Draws a point.}

\ccMethod{PainterOstream<K> operator<<(K::Segment_2);}{Draws a segment.}

\ccMethod{PainterOstream<K> operator<<(K::Ray_2);}{Draws a clipped ray.}

\ccMethod{PainterOstream<K> operator<<(K::Line_2);}{Draws a clipped line.}

\ccMethod{PainterOstream<K> operator<<(K::Triangle_2);}{Draws a triangle.}

\ccMethod{PainterOstream<K> operator<<(K::Iso_rectangle_2);}{Draws an iso rectangle.}

\ccMethod{PainterOstream<K> operator<<(K::Circle_2);}{Draws a circle.}

\ccMethod{PainterOstream<K> operator<<(K::Circular_arc_2);}{Draws a circular arc.}

\ccMethod{PainterOstream<K> operator<<(std::list<K::Point_2>);}{Draws a polyline. In order to close it the first and last point must be equal. }

\ccMethod{PainterOstream<K> operator<<(Bbox_2);}{Draws an iso rectangle.}

\ccMethod{PainterOstream<K> operator<<(QPen);}{Sets the pen used in the next paint operations.}

\ccMethod{PainterOstream<K> operator<<(QBrush);}{Sets the brush used in the next paint operations.}

\end{ccRefClass}







