% +------------------------------------------------------------------------+
% | Reference manual page: Pm_bounding_box_traits.tex (Planar_map)
% +------------------------------------------------------------------------+
% | 
% | Package: pm (Planar_map_2)
% | 
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+

\renewcommand{\ccRefPageBegin}{\begin{ccAdvanced}}
\renewcommand{\ccRefPageEnd}{\end{ccAdvanced}}

%File_header
\begin{ccRefClass}{File_header}

\ccCreationVariable{file_header}

\ccDefinition
Generally, the \ccRefName \/ class defines and sets parameters that
should be defined while using the I/O functions.  This configuration
includes the verbose flag, a flag that controls writing a file with or
without comments, etc.  The class is the base class of the classes
\ccc{Pm_file_scanner} and \ccc{Pm_file_writer}.  The list of
parameters for \ccRefName\/ is as follows:

\begin{itemize}
\item {\bf verbose } define a verbose format for printing the \ccc{Planar map}. This flag is set by default to false.
\item {\bf ascii} ascii format. This flag is set by default to true.
\item {\bf no\_comments} - no comments in output. This flag is set by default to false.
\item {\bf index\_offset} - offset for the indices. This flag is set by default to 0.
\item {\bf has\_colors} - The format specifies the colors of the \ccc{Planer map} components. This flag is set by default to false.
\item {\bf dimension} - specifies the dimension of \ccc{Planer map}. This flag is set by default to 2.
\end{itemize}

In addition the \ccRefName \/ class includes the information regarding the 
number of vertices, halfedges and faces the \ccc{Planar map} has.

%The following requirement catalog lists the primitives, i.e., types, member functions
%etc., that must be defined for any \ccc{Planar map} file writer class that can be used to parameterize the reading function of \ccc{Planar map}. 


\ccCreation
When creating a \ccRefName \/ object, the user sets the parameters as needed.
 
%the default configurations are provided as above and hence the user has to define only those configurations which are different from the default.

\ccConstructor{File_header ();} 
{constructs a default \ccRefName\ which contains the default configuration.}

\ccConstructor{File_header (int v, int h, int f, bool verbose = false, bool no_comments = false, 
   bool ascii = true, int offset = 0, bool colors = false, int dim = 2);} 
{constructs \ccRefName\ with \ccc{v} vertices \ccc{h} halfedges and \ccc{f} faces, the other parameters can also be set by the user, otherwise they are set to their default values.}

\ccConstructor{File_header(const File_header& file_header);}
{copy construction.}

\ccModifiers

\ccThree{size_t}{file_header.set_number_of_verticesaaa(size_t n);}{}

\ccMethod{void set_verbose(bool b);}{sets the verbose flag to b.}
\ccGlue
\ccMethod{void set_ascii(bool b);} {sets the ascii flag to b.}
\ccGlue
\ccMethod{void set_no_comments(bool b);}{sets the no\_comments flag to b.}
\ccGlue
\ccMethod{void set_index_offset(int i);}{sets index\_offset to i.}
\ccGlue
\ccMethod{void set_colors(bool b);}{sets the colors flag to b.}
\ccGlue
\ccMethod{void set_dimension(int i);}{sets the dimension to i.}
\ccGlue
\ccMethod{void set_number_of_vertices(size_t n);}{sets the number of vertices to n.}
\ccGlue
\ccMethod{void set_number_of_halfedges(size_t n);}{sets the number of halfedges to n.}
\ccGlue
\ccMethod{void set_number_of_faces(size_t n);}{sets the number of faces to n.}

\ccAccessFunctions
%\ccGlueBegin
\ccMethod{bool verbose();}{returns true if the format is verbose.}
\ccGlue
\ccMethod{bool ascii();}{returns true if the format is given by ascii.}
\ccGlue
\ccMethod{bool no_comments();}{returns true if the format is defined without comments.}
\ccGlue
\ccMethod{bool comments();}{returns true if the format is defined with comments.}
\ccGlue
\ccMethod{int index_offset();}{returns the offset defined for the indices in the format.}
\ccGlue
\ccMethod{bool has_colors();}{returns true if the format presents the \ccc{Planar map} by colors.}
\ccGlue
\ccMethod{int dimension();}{returns the dimension defined by the format.}
\ccGlue
\ccMethod{size_t number_of_vertices();}{returns the number of vertices defined by the format.}
\ccGlue
\ccMethod{size_t number_of_halfedges();}{returns the number of halfedges defined by the format.}
\ccGlue
\ccMethod{size_t number_of_faces();}{returns the number of faces defined by the format.}
%\ccGlueEnd

\end{ccRefClass} % File_header

\renewcommand{\ccRefPageBegin}{}
\renewcommand{\ccRefPageEnd}{}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+












