% +------------------------------------------------------------------------+
% | Reference manual page: Pm_bounding_box_traits.tex (Planar_map)
% +------------------------------------------------------------------------+
% | 
% | Package: pm (Planar_map_2)
% | 
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+

\renewcommand{\ccRefPageBegin}{\begin{ccAdvanced}}
\renewcommand{\ccRefPageEnd}{\end{ccAdvanced}}

%Pm_file_writer
\begin{ccRefClass}{Pm_drawer<Planar_map, Window>}

\ccCreationVariable{pm_drawer}

\ccDefinition
The \ccRefName\ class is inherited from the \ccc{File_header} class. 
This class contains functions for sending \ccc{Planar map} components to a given graphic stream.
Users have to make sure that methods for writing \ccStyle{Point} and \ccStyle{X\_curve} defined in  
the \ccc{Planar map traits} class are provided when using the graphic stream they choose to work with.
This class is templated with \ccc{Planar map} and the graphic stream type, and hence the user can work with \ccRefName\ with its own \ccc{Planar map} and graphic stream. 
 
%The following requirement catalog lists the primitives, i.e., types, member functions
%etc., that must be defined for any \ccc{Planar map} file writer class that can be used to parameterize the reading function of \ccc{Planar map}. 

\ccTypes

The following handles and iterators have appropriate constant counterparts. The mutable types are assignable to their
constant counterparts. The iterators are assignable to the respective handle types. 
Wherever the handles appear in function parameter lists, the appropriate iterator can be used as well. 

\ccNestedType{Vertex_handle}{handle to the \ccc{Planar map} vertex.}
\ccNestedType{Halfedge_handle}{handle to the \ccc{Planar map} halfedge.}
\ccNestedType{Face_handle}{handle to the \ccc{Planar map} face}.
\ccNestedType{Vertex_iterator}{a bidirectional iterator over the vertices of the \ccc{Planar map}.}
\ccNestedType{Halfedge_iterator}{a bidirectional iterator over the halfedges of the \ccc{Planar map}.}
\ccNestedType{Face_iterator}{a bidirectional iterator over the faces of the \ccc{Planar map}.}

\ccCreation

\ccConstructor{Pm_drawer (Window& w);} {constructs \ccRefName\ for a given graphic stream.}

\ccOperations

\ccMethod{Window&  window();}
{return the graphic stream the \ccc{Planar map} is written to.} 

\ccMethod{void draw_vertex (Vertex_handle v);}
{writes a vertex of the \ccc{Planar map} to the graphic stream.}

\ccMethod{void draw_halfedge (Halfedge_handle h);}
{writes an halfedge of the \ccc{Planar map} to the graphic stream.}

\ccMethod{void draw_face (Face_handle f);}
{writes a face of the \ccc{Planar map} to the graphic stream.}

\ccMethod{void draw_vertices (Vertex_iterator Vertices_begin, Vertex_iterator Vertices_end);}
{writes all the vertices in the range [Vertices\_begin, Vertices\_end) to the graphic stream.}

\ccMethod{void draw_halfedges (Halfedge_const_iterator Halfedges_begin, Halfedge_const_iterator Halfedges_end);}{writes all the halfedges in the range [Halfedges\_begin, Halfedges\_end) to the graphic stream.}

\ccMethod{void draw_write_faces (Face_iterator Faces_begin, Face_iterator Faces_end);}
{writes all the faces in the range [Faces\_begin, Faces\_end) to the graphic stream.}

\end{ccRefClass} % Pm_file_writer

\renewcommand{\ccRefPageBegin}{}
\renewcommand{\ccRefPageEnd}{}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+











%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "Pm_file_scanner"
%%% End: 
