% +------------------------------------------------------------------------+
% | Reference manual page: Pm_bounding_box_traits.tex (Planar_map)
% +------------------------------------------------------------------------+
% | 
% | Package: pm (Planar_map_2)
% | 
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+

%Pm_file_writer
\begin{ccRefConcept}{Pm_drawer}

\ccCreationVariable{pm_drawer}

\ccDefinition
The class \ccRefName\ contains functions for writing (or drawing) the \ccc{Planar map} componenets to a given graphic stream. 
The user has to make sure that methods for writing Point and X_curve types of \ccc{Planar_map} are defined in the graphic stream he chooses to work with.
This class is templated with \ccc{Planar map}, and hence the user can work with \ccRefName\ with its own \ccc{Planar map}. 
 
%The following requirement catalog lists the primitives, i.e., types, member functions
%etc., that must be defined for any \ccc{Planar map} file writer class that can be used to parameterize the reading function of \ccc{Planar map}. 

\ccTypes

The following handles and iterators have appropriate constant counterparts. The mutable types are assignable to their
constant counterparts. The iterators are assignable to the respective handle types. 
Wherever the handles appear in function parameter lists, the appropriate iterator can be used as well. 

\ccNestedType{Vertex_handle}{handle to the \ccc{Planar map} vertex.}
\ccNestedType{Halfedgee_handle}{handle to the \ccc{Planar map} halfedge.}
\ccNestedType{Face_handle}{handle to the \ccc{Planar map} face.}
\ccNestedType{Vertex_iterator}{a bidirectional iterator over the vertices of the \ccc{Planar map.}
\ccNestedType{Halfedge_iterator}{a bidirectional iterator over the halfedges of the \ccc{Planar map} .}
\ccNestedType{Face_iterator}{a bidirectional iterator over the faces of the \ccc{Planar map} .}

\ccCreation

\ccConstructor{Pm_drawer(Window& w);} 
{constructs \ccRefName\ for a given graphic stream.}

\ccOperations

\ccMethod{Window&  window();}
{returns the graphic stream the \ccc{Planar map} is written to.} 

\ccMethod{void draw_vertex(Vertex_handle v);}
{writes a vertex of the \ccc{Planar map} to the graphic stream.}

\ccMethod{void draw_halfedge(Halfedge_handle h);}
{writes an halfedge of the \ccc{Planar map} to the graphic stream.}

\ccMethod{void draw_face(Face_handle f);}
{writes a face of the \ccc{Planar map} to the graphic stream.}

\ccMethod{void draw_vertices(Vertex_iterator Vertices_begin, Vertex_iterator Vertices_end);}
{writes all the vertices in the range [Vertices_begin, Vertices_end) to the graphic stream.}

\ccMethod{draw_halfedges(Halfedge_const_iterator Halfedges_begin, Halfedge_const_iterator Halfedges_end);}
{writes all the halfedges in the range [Halfedges_begin, Halfedges_end) to the graphic stream.}

\ccMethod{draw_faces(Face_iterator Faces_begin, Face_iterator Faces_end);}
{writes all the faces in the range [Faces_begin, Faces_end) to the graphic stream.}

\end{ccRefConcept} % Pm_file_writer

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+










