% +------------------------------------------------------------------------+
% | Reference manual page: Bitangent.tex
% +------------------------------------------------------------------------+
% | Package: Visibility_complex
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+

\begin{ccRefConcept}{VC2Bitangent}

\ccDefinition

The \ccRefName{} concept defines the minimal requirement for the local
\ccc{Bitangent_2} type of the \ccc{VC2GeomTraits} concept.  The
\ccc{Bitangent_2} type is used as a base class for the concept
\ccc{VC2Vertex}.

A bitangent is a directed line segment tangent to two disks.

\ccTypes

\ccNestedType{Disk}{Type of disks defining the bitangent.}
\ccGlue
\ccNestedType{Disk_handle}{Const handle to disks.}
\ccGlue
\ccEnum{enum Type {LL,LR,RL,RR};}{Enum type to specify the type of the
bitangent. The possible values are \ccc{LL}, \ccc{RR}, \ccc{RL} and
\ccc{LR} respectively for left-left,right-right,right-left and left-right
bitangents.}
\ccGlue
\ccNestedType{Arc_2}{A model of concept \ccc{VC2Arc}.}
\ccNestedType{Point_2}{The type of the endpoints of the segment.}

\ccCreation

\ccCreationVariable{b}

\ccConstructor{VC2Bitangent();}{Default constructor.}
\ccGlue
\ccConstructor{VC2Bitangent(Type t, Disk_handle source, Disk_handle target);}
{Creates the bitangent with type t directed from source to target.}
\ccGlue
\ccConstructor{VC2Bitangent(const VC2Bitangent& sibling, bool reverse, Type t);}
{Creates the bitangent from \ccc{sibling.source_object()} to
\ccc{sibling.target\_object()} with type \ccc{t} if reverse is false, and
the same bitangent with opposite orientation otherwise.}
\ccGlue
\ccConstructor{VC2Bitangent(Type t, const Arc& source, const Arc&
               target);}{Creates the
bitangent with type t directed from the arc source to the arc target. If
the two arcs do not have a common bitangent, behaviour is undefined.}


\ccAccessFunctions
\ccTagFullDeclarations
\ccMethod{Type type(); const}{Returns the type of \ccVar.}
\ccGlue
\ccMethod{Disk_handle source_object(); const}{Returns a handle to the 
source disk.}
\ccGlue
\ccMethod{Disk_handle target_object(); const}{Returns a handle to the
target disk.}
\ccGlue
\ccMethod{Point_2 source(); const}{Returns the source tangency point of
\ccVar. It is possibly approximated (but the visibility complex is computed
exactly anyway).}
\ccGlue
\ccMethod{Point_2 target(); const}{Returns the target tangency point of
\ccVar.}

\ccHasModels
\ccc{CGAL::Visibility_complex_2_point_traits<Kernel,DistanceNT,RToDistanceNT>::Bitangent_2}\\
\ccc{CGAL::Visibility_complex_2_segment_traits<Kernel,DistanceNT,RToDistanceNT>::Bitangent_2}\\
\ccc{CGAL::Visibility_complex_2_polygon_traits<Kernel,DistanceNT,RToDistanceNT>::Bitangent_2}\\
\ccc{CGAL::Visibility_complex_2_circle_traits<Kernel>::Bitangent_2}

\ccSeeAlso
\ccRefConceptPage{VC2Vertex}\\
\ccRefConceptPage{VC2GeomTraits}


\ccTagDefaults
\end{ccRefConcept}
\ccRefPageEnd
