% +------------------------------------------------------------------------+
% | Reference manual page: VisibilityComplexVertex.tex
% +------------------------------------------------------------------------+
% | Package: Visibility_complex
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+

\begin{ccRefConcept}{VC2Vertex}

  
% ------------------------------------------------------------------------------
\ccDefinition

The concept \ccRefName{} represents the vertex class in the visibility
complex.  It defines the requirements for the \ccc{Vertex} type in the
\ccc{Visibility_complex_2<VC2GeomTraits,VC2Items>} class. It is also
required in the \ccc{Vertex_wrapper<Vc>} member class template of an items
class, see the \ccc{VC2Items} concept. In addition to the requirement
below, the concept \ccRefName{} must inherit from the \ccc{VC2Bitangent}
concept.

\ccInheritsFrom
\ccRefConceptPage{VC2Bitangent}

\ccTypes
\ccNestedType{Gt} {Geometric traits class.}
\ccGlue
\ccNestedType{Bitangent_2} {Model of \ccc{VC2Bitangent}. Same as 
\ccc{Gt::Bitangent\_2}.}
\ccGlue
\ccNestedType{Vertex}{Model of \ccc{VC2Vertex}, can actually be a subclass of
the containing class.}
\ccGlue
\ccNestedType{Edge}{Model of \ccc{VC2Edge}.}
\ccGlue
\ccNestedType{Face}{Model of \ccc{VC2Face}.}
\ccGlue
\ccNestedType{Vertex_handle}{Handle to vertices.}
\ccGlue
\ccNestedType{Face_handle}{Handle to faces.}
\ccGlue
\ccNestedType{Edge_handle}{Handle to edges.}
\ccGlue
\ccNestedType{Vertex_const_handle}{Const handle to vertices.}
\ccGlue
\ccNestedType{Face_const_handle}{Const handle to faces.}
\ccGlue
\ccNestedType{Edge_const_handle}{Const handle to edges.}


\ccCreation
\ccCreationVariable{v}

\ccConstructor{Vertex();}{Default constructor.}

Theses constructors pass their arguments to the underlying bitangent.

\ccConstructor{Vertex(Type t, Disk_handle source, Disk_handle target);}{}
\ccGlue
\ccConstructor{Vertex(const Vertex& sibling, bool reverse, Type t);}{}
\ccGlue
\ccConstructor{Vertex(Type t, Edge_handle source, Edge_handle target);}{}


\ccAccessFunctions

\ccTagFullDeclarations
\ccMethod{Edge_handle ccw_target_edge();}{next edge on the target object}
\ccGlue
\ccMethod{Edge_handle ccw_source_edge();}{next edge on the source object}
\ccGlue
\ccMethod{Edge_handle cw_source_edge();}{previous edge on the target object}
\ccGlue
\ccMethod{Edge_handle cw_target_edge();}{previous edge on the source object}
\ccGlue
\ccMethod{Edge_handle cw_target_edge(Disk_handle);}{previous edge on the
specified object}
\ccGlue
\ccMethod{Edge_handle ccw_target_edge(Disk_handle);}{next edge on the
specified object}
\ccGlue
\ccMethod{Edge_handle target_cusp_edge();}{If the vertex is a constraint,
     returns the cusp-edge on the source tangency point with sink
     \ccVar{}. If the vertex is regular, an invalid handle is returned.}
\ccGlue
\ccMethod{Edge_handle source_cusp_edge();}{Same thing, on the target.}
\ccGlue
\ccMethod{Face_handle sup();}{returns the face of which \ccVar{} is the
source.}
\ccGlue
\ccMethod{Face_handle inf();}{returns the face of which \ccVar{} is the
sink.}
\ccGlue
\ccMethod{Vertex_handle pi();}{returns the vertex with opposite
orientation, allocating it with new if necessary.}


All the latter methods have const counterparts returning const handles.


\ccMethod{bool is_constraint(); const}{returns true if the vertex is a
constraint.}

\ccOperations

The following methods set the pointers which the latter accessors return.

\ccMethod{void set_ccw_edge(Edge_handle);}{the choice between target and source
                                     is made by looking at the edge's object.}
\ccGlue
\ccMethod{void set_cw_edge(Edge_handle);}{}
\ccGlue
\ccMethod{void set_cw_edge(Edge_handle);}{}
\ccGlue
\ccMethod{void set_cw_edge(Edge_handle);}{}
\ccGlue
\ccMethod{void set_inf(Face_handle);}{}
\ccGlue
\ccMethod{void set_sup(Face_handle);}{}
\ccGlue
\ccMethod{void set_pi(Vertex_handle);}{}
\ccGlue
\ccMethod{void set_target_cusp_edge(Edge_handle e);}
\ccGlue
\ccMethod{void set_source_cusp_edge(Edge_handle e);}


\ccTagDefaults

\ccSeeAlso

\ccRefConceptPage{VC2Bitangent}\\
\ccRefIdfierPage{CGAL::Visibility_complex_2<VC2GeomTraits,VC2Items>}\\
\ccRefConceptPage{VC2Items}\\
\ccRefConceptPage{VC2Edge}\\
\ccRefConceptPage{VC2Face}
% ------------------------------------------------------------------------------

% +----------------------------------------------------------------------------+
\ccTagDefaults
\end{ccRefConcept}
\ccRefPageEnd
% +----------------------------------------------------------------------------+

