
\ccThree{boolx}{a.link5( LinkB a, B b)}{}
\ccThreeToTwo

\ccHtmlNoClassIndex\ccHtmlNoLinks
\begin{ccClass}{LinkA}
\ccCreationVariable{a}

A class \ccClassName\ with \verb+\ccHtmlNoClassIndex+ and
\verb+\ccHtmlNoLinks+ to suppress cross linking:

  \ccFunction{
     bool link1(const LinkA& a, const B& b);}{%
             a function is still indexed.
         }
  \ccGlue
  \ccMethod{
     bool link2(const LinkA& a, const B& b);}{%
             a method is never indexed.
         }
  \ccGlue
  \ccStruct{struct LocalX {};}{a nested struct is not indexed.}
\end{ccClass}


\begin{ccClass}{LinkB}
\ccCreationVariable{b}

A class \ccClassName\ without \verb+\ccHtmlNoClassIndex+ but the individual
declarations are prefixed with \verb+\ccHtmlNoIndex+ and 
\verb+\ccHtmlNoLinks+:

  \ccHtmlNoIndex\ccHtmlNoLinks
  \ccFunction{
     bool link3(const LinkB& a, const B& b);}{%
             explicitly not indexed.
         }
  \ccGlue
  \ccMethod{
     bool link4(const LinkB& a, const B& b);}{%
             a method is never indexed.
         }
  \ccGlue
  \ccHtmlNoIndex
  \ccStruct{struct LocalY {};}{a nested struct explicitly not indexed.}
\end{ccClass}

The same for a global function and struct.

  \ccHtmlNoIndex\ccHtmlNoLinks
  \ccFunction{
     bool link5(const LinkB& a, const B& b);}{%
             explicitly not indexed.
         }
  \ccGlue
  \ccHtmlNoIndex\ccHtmlNoLinks
  \ccStruct{struct GlobalX {};}{a global struct explicitly not indexed and 
                                not linked.}
  \ccGlue
  \ccStruct{struct GlobalY {};}{a global struct indexed and linked.}

Try it for a reference environment.

\ccFunction{
     bool link6(const UnlinkedRefClassA& a, const B& b);}{%
             UnlinkedRefClass is not linked.
}

\ccHtmlNoRefIndex\ccHtmlNoRefLinks
\begin{ccRefClass}{UnlinkedRefClassA}
\ccCreationVariable{a}

A class \ccRefName\ with \verb+\ccHtmlNoRefIndex+ and
\verb+\ccHtmlNoRefLinks+ to suppress cross linking:

  \ccMethod{
     bool link7(const UnlinkedRefClassA& a, const B& b);}{%
             a method is never indexed.
         }
  \ccGlue
  \ccStruct{struct LocalX {};}{a nested struct is not indexed.}
\end{ccRefClass}

And now try removing links from certain sections of the text.

\begin{ccClass}{turn_off}

\ccDefinition

Class that creates unwanted links so we turn them off
using \verb+\ccHtmlLinksOff+, \verb+\ccHtmlLinksOn+, and
\verb+\ccHtmlNoLinksFrom+.

A link to this \ccc{turn_off} should be here, but \ccHtmlLinksOff not
to this \ccc{turn_off} nor this other \ccc{turn_off}\ccHtmlLinksOn as they
are between \verb+\ccHtmlLinksOff+ and \verb+\ccHtmlLinksOn+ commands.
However this \ccc{turn_off} link should be there.  This
\ccHtmlNoLinksFrom{\ccc{turn_off} and this other \ccc{turn_off}}, which
are inside the argument of a \verb+\ccHtmlNoLinksFrom+ command, should
not be linked.

\end{ccClass}

\ccFunction{
     bool turn_off(const A& a, const B& b);}{%
             a function name that is linked.
         }

\ccHtmlLinksOff
\ccFunction{
   bool test_me(const turn_off& T);}{%
      The \ccc{turn_offs} here should not be linked
   }
\ccHtmlLinksOn




% ----------------------------------------------------------------------
