% +------------------------------------------------------------------------+
% | Reference manual page: HalfedgeDS_vertex_base.tex
% +------------------------------------------------------------------------+
% | 22.03.1999   Lutz Kettner
% | Package: HalfedgeDS
% | 
\RCSdef{\RCSHalfedgeDSvertexbaseRev}{$Revision$}
\RCSdefDate{\RCSHalfedgeDSvertexbaseDate}{$Date$}
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefClass}{HalfedgeDS_vertex_base<Refs>}

\ccDefinition
  
The class \ccRefName\ is a model of the \ccc{HalfedgeDS_Vertex}
concept. \ccc{Refs} is an instantiation of a \ccc{HalfedgeDS}. 
The full declaration states three parameters:

~~~~~~\ccc{template <class Refs, class T = CGAL::Tag_true, class Point = void>}\\
\mbox{}~~~~~~\ccc{class HalfedgeDS_vertex_base;}

\ccRefName\ defines a vertex including a reference to an incident halfedge.

\ccc{CGAL::HalfedgeDS_vertex_base<Refs,CGAL::Tag_false>} is a vertex
without a reference to an incident halfedge. It is empty besides the
required type definitions. It can be used for deriving own vertex
implementations.

\ccc{CGAL::HalfedgeDS_vertex_base<Refs,CGAL::Tag_true,Point>} is a vertex
with a reference to an incident halfedge and it stores a point of type
\ccc{Point}.  It can be used as a vertex for a model of the
\ccc{Polyhedron_items} concept.

\ccc{CGAL::HalfedgeDS_vertex_base<Refs,CGAL::Tag_false,Point>} is a vertex
without a reference to an incident halfedge and it stores a point of
type \ccc{Point}.  It can be used as a vertex for a model of the
\ccc{Polyhedron_items} concept.

\ccInclude{CGAL/HalfedgeDS_vertex_base.h}

\ccIsModel

\ccc{HalfedgeDS_Vertex}

\ccTypes
\ccThree{const Point&;;}{point() const;MMMMMMMMMMMM}{}
\ccThreeToTwo

\ccNestedType{Point}{point type for three argument version.}

\ccCreation
\ccCreationVariable{v}

\ccConstructor{HalfedgeDS_vertex_base();}{default constructor.}
\ccGlue
\ccConstructor{HalfedgeDS_vertex_base( const Point& p);}
    {initialized with point $p$.}

\ccOperations

\ccTagFullDeclarations
\ccMethod{Point&                point();}{}
\ccGlue
\ccMethod{const Point&          point() const;}{}
\ccTagDefaults

\ccSeeAlso

\ccc{HalfedgeDS},
\ccc{HalfedgeDS_Items},
\ccc{Polyhedron_items},
\ccc{CGAL::HalfedgeDS_halfedge_base<Refs>},\\
\ccc{CGAL::HalfedgeDS_face_base<Refs>},
\ccc{CGAL::HalfedgeDS_vetex_min_base<Refs>}.

\end{ccRefClass}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+

