% +------------------------------------------------------------------------+
% | Reference manual page: HalfedgeDS_face_base.tex
% +------------------------------------------------------------------------+
% | 22.03.1999   Lutz Kettner
% | Package: HalfedgeDS
% | 
\RCSdef{\RCSHalfedgeDSfacebaseRev}{$Revision$}
\RCSdefDate{\RCSHalfedgeDSfacebaseDate}{$Date$}
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefClass}{HalfedgeDS_face_base<Refs>}
  
\ccDefinition
  
The class \ccRefName\ is a model of the \ccc{HalfedgeDS_Face}
concept. \ccc{Refs} is an instantiation of a \ccc{HalfedgeDS}. 
The full declaration states three parameters:

~~~~~~\ccc{template <class Refs, class T = CGAL::Tag_true, class Traits = void>}\\
\mbox{}~~~~~~\ccc{class HalfedgeDS_face_base;}

\ccRefName\ defines a face including a reference to an incident halfedge.

\ccc{CGAL::HalfedgeDS_face_base<Refs,CGAL::Tag_false>} is a face
without a reference to an incident halfedge. It is empty besides the
required type definitions. It can be used for deriving own faces.

\ccc{CGAL::HalfedgeDS_face_base<Refs,CGAL::Tag_true,Traits>} is a face with
a reference to an incident halfedge and it stores a plane equation of
type \ccc{Traits::Plane}.  It can be used as a face for a model of the
\ccc{Polyhedron_items} concept.

\ccc{CGAL::HalfedgeDS_face_base<Refs,CGAL::Tag_false,Traits>} is a face
without a reference to an incident halfedge and it stores a plane
equation of type \ccc{Traits::Plane}.  It can be used as a face for a
model of the \ccc{Polyhedron_items} concept.

\ccInclude{CGAL/HalfedgeDS_face_base.h}

\ccIsModel

\ccc{HalfedgeDS_Face}

\ccTypes
\ccThree{typedef Traits::Normal;;}{f.normal() const;}{}
\ccThreeToTwo

\ccTypedef{typedef Traits::Plane Plane;}
    {plane equation type for three argument version.}
\ccGlue
\ccTypedef{typedef Traits::Normal Normal;}
    {normal vector of plane equation.}

\ccCreation
\ccCreationVariable{f}

\ccConstructor{HalfedgeDS_face_base();}{default constructor.}

\ccOperations

\ccTagFullDeclarations
\ccMethod{Plane&                plane();}{}
\ccGlue
\ccMethod{const Plane&          plane() const;}{}
\ccGlue
\ccMethod{Normal                normal() const;}{}
\ccTagDefaults

\ccSeeAlso

\ccc{HalfedgeDS},
\ccc{HalfedgeDS_Items},
\ccc{Polyhedron_items},
\ccc{CGAL::HalfedgeDS_vertex_base<Refs>},\\
\ccc{CGAL::HalfedgeDS_halfedge_base<Refs>},
\ccc{CGAL::HalfedgeDS_face_min_base<Refs>}.

\end{ccRefClass}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+

