\begin{ccRefClass}{Filtered_predicate<EP, FP, C2E, C2F>}

\KernelRefLayout\gdef\ccTagOperatorLayout{\ccFalse}

\ccDefinition

\ccClassTemplateName is an adaptor for predicate function objects that allows
one to produce efficient and exact predicates.  It is used to build
\ccc{CGAL::Filtered_kernel<CK>} and can be used for other
predicates too.

\ccc{EP} is the exact but supposedly slow predicate that is able to evaluate
the predicate correctly.  It will be called only when the filtering predicate,
\ccc{FP}, cannot compute the correct result.  This failure of \ccc{FP} must be
done by throwing an exception.

To convert the geometric objects that are the arguments of the predicate,
we use the function objects \ccc{C2E} and \ccc{C2F}, which must be of the form
\ccc{Cartesian_converter} or \ccc{Homogeneous_converter}.

\ccInclude{CGAL/Filtered_predicate.h}

\ccTypes
\ccTypedef{typedef FP::result_type result_type;}
{ The return type of the function operators.
  It must also be the same type as \ccc{EP::result_type}.}

\ccCreation
\ccCreationVariable{fo}

\ccConstructor{Filtered_predicate<EP, FP, C2E, C2F>();}{Default constructor.}

\ccOperations

\ccMemberFunction{template <class A1> result_type operator()(A1 a1);}
{ The unary function operator for unary predicates. }

\ccMemberFunction{template <class A1, class A2>
                  result_type operator()(A1 a1, A2 a2);}
{ The binary function operator for binary predicates. }

Similar function operators are defined for up to 7 arguments.

\ccExample

The following example defines an efficient and exact version of the
orientation predicate over three points using the Cartesian representation
with double coordinates and without reference counting
(\ccc{Simple_cartesian<double>::Point_2}).
Of course, the orientation predicate can already be found in the kernel, but
you can follow this example to filter your own predicates.
It uses the fast but inexact predicate based on interval arithmetic for
filtering and the slow but exact predicate based on multi-precision floats
when the filtering predicate fails.

\ccIncludeExampleCode{Filtered_kernel/Filtered_predicate.cpp}

\end{ccRefClass}
