\begin{ccRefClass} {Weighted_point_2<Kernel>}

\ccDefinition
An object of the class \ccRefName\ is a point in the two-dimensional
Euclidean plane $\E^2$ with an associated weight (and thus can also
be viewed as a circle with the point as center point and the weight
as squared radius).  The type of the weight is \ccc{Kernel::RT},
the ring type of the defining kernel.

\ccInheritsFrom
\ccc{Kernel::Point_2}

\ccTypes

\ccNestedType{Kernel}{the kernel in which the point lies}

\ccCreation
\ccCreationVariable{p}

\ccConstructor{Weighted_point_2(const Origin &ORIGIN, const Kernel::RT& w = 0);}
            {introduces a variable \ccVar\ with \ccHtmlNoLinksFrom{Cartesian} 
             coordinates $(0,0)$ and weight \ccc{w}.}

\ccConstructor{Weighted_point_2(const Kernel::RT &hx, const Kernel::RT &hy, 
                                const Kernel::RT &hw = Kernel::RT(1), 
                                const Kernel::RT w = 0);}
            {introduces a point \ccVar\ initialized to $(hx/hw,hy/hw)$ with 
             weight \ccc{w}.
	     \ccPrecond{\ccc{hw} $\neq$ \ccc{Kernel::RT(0)}.} }

\ccConstructor{Weighted_point_2(const Point_2<Kernel> &p,
                                const Kernel::RT& w = 0);}
            {introduces a variable \ccVar\ with \ccHtmlNoLinksFrom{Cartesian} 
             coordinates \ccc{(p.x(),p.y())} and weight \ccc{w}.}


\ccOperations
%\ccSetTwoOfThreeColumns{5cm}{4cm}

\ccMethod{bool operator==(const Weighted_point_2<Kernel> &q) const;}
       {Test for equality. Two points are equal, iff their $x$ and $y$ 
        coordinates are equal and their weights are equal.}

\ccMethod{bool operator!=(const Weighted_point_2<Kernel> &q) const;}
       {Test for inequality.}

Here are the access functions for the components of the weighted point.

\ccMethod{Kernel::RT weight() const;}
       {returns the weight associated with the point.}
\ccGlue
\ccMethod{Point_2<Kernel> point() const;}
       {returns the unweighted point.}

\ccExample

The following declaration creates two points with \ccHtmlNoLinksFrom{Cartesian} double coordinates.

\begin{cprog}

  CGAL::Weighted_point_2< CGAL::Cartesian<double> > p(1.0, 2.0), q(1.0, 2.0, 2.0), r;
\end{cprog} 

The variable \texttt{p} is a point with \ccHtmlNoLinksFrom{Cartesian}
coordinates 1.0 and 2.0 and weight 0.0 while \texttt{q} has the same 
coordinates but weight 2.5.
The variable {\tt r} is uninitialized and should first be used on 
the left hand side of an assignment. 

\ccSeeAlso
\ccRefIdfierPage{CGAL::Point_2<Kernel>} \\
\ccRefIdfierPage{CGAL::Weighted_point_3<Kernel>}

\end{ccRefClass} 
