\ccDefGlobalScope{}
\begin{ccRefClass}{cgal_d3_rat_sphere}

\ccDefinition

\ccInclude{CEP/Leda_rat_kernel/LEDA_RATKERNEL/cgal_d3_rat_sphere.h}

The class \ccRefName\  is a 3d sphere class using the LEDA rational kernel. It stores a center point
and a squared radius (like CGAL). The class is in namespace \ccc{leda} for LEDA versions with a namespace
(4.4 or higher) and else in global scope.


\ccCreationVariable{S}

\ccCreation

\ccConstructor{cgal_d3_rat_sphere();}
{introduces a variable of type \ccRefName\ .} 
  
\ccConstructor{cgal_d3_rat_sphere(const leda_d3_rat_point& p1, const leda_d3_rat_point& p2, 
               CGAL::Orientation ori = CGAL::COUNTERCLOCKWISE);}
{introduces a variable of type \ccRefName\ with center $p1$, a point
$p2$ on the sphere and orientation $ori$. }		  
  
\ccConstructor{cgal_d3_rat_sphere(const leda_d3_rat_point& p1, 
               CGAL::Orientation ori = CGAL::COUNTERCLOCKWISE);}
{introduces a variable of type \ccRefName\ with center $p1$, orientation $ori$
and radius $0$.}	
  
\ccConstructor{cgal_d3_rat_sphere(const leda_d3_rat_point& p1, const leda_rational& sqrad, 
               CGAL::Orientation ori = CGAL::COUNTERCLOCKWISE);}
{introduces a variable of type \ccRefName\ with center $p1$, orientation $ori$
and squared radius $sqrad$.}	 


\ccOperations

\ccMethod{leda_d3_rat_point  center();}
{returns the center of the sphere.}  
  
\ccMethod{leda_rational squared_radius();}
{returns the square of the radius.} 

\ccMethod{leda_rational sqr_radius();} 
{returns the square of the radius.} 
  
\ccMethod{CGAL::Orientation orientation();}
{returns the orientation of the sphere.}  
  
\ccMethod{bool is_degenerate();}
{returns $true$ if the radius is 0, $false$ otherwise.} 

\end{ccRefClass} 
