% +------------------------------------------------------------------------+
% | STL User Manual:  Circulator_stl.tex
% +------------------------------------------------------------------------+
% | Requirements for circulators in analogy to STL iterators.
% | Adaptors between circulators and iterators.
% | Proposal for CGAL.
% |
% | 27.01.1997   Lutz Kettner
% |              Adapted from the iterator chapter and the circulator
% |              chapter of the CGAL Reference Manual circulator.tex R1.3.
% | 
% | $Revision$
% | $Date$
% +------------------------------------------------------------------------+

\cleardoublepage
\chapter{Circulators}
\label{sectionCirculatorWarning}

Circulators are quite similar to iterators that are described in
Chapter~\ref{chapterIterators}. Circulators are a generalization of
pointers that allow a programmer to work with different circular data
structures like a ring list in a uniform manner. Please note that
circulators are not part of the \stl, but of \cgal. A summary of the
requirements for circulators is presented here. Thereafter, a couple
of adaptors are described that convert between iterators and
circulators. For the complete description of the requirements, support
to develop own circulators, and the adaptors please refer to the \cgal\ 
Reference Manual: Part 3: Support Library.

The specialization on circular data structures gives the reason for
the slightly different requirements for circulators than for
iterators. A circular data structure has no natural past-the-end
value. In consequence, a container supporting circulators will not
have an {\tt end()}-member function, only a {\tt begin()}-member
function.  The semantic of a range is different for a circulator $c$:
The range $\left[c, c\right)$ denotes the sequence of all elements in
the data structure. For iterators, this range would be empty. A
separate test for an empty sequence has been added to the
requirements. A comparison $c ==$ {\tt NULL} for a circulator $c$
tests whether the data structure is empty or not. As for
\CC, we recommend the use of 0 instead of {\tt NULL}. An example
function demonstrates a typical use of circulators. It counts the
number of elements in the range $\left[c, d\right)$:

\begin{verbatim}
template <class Circulator, class Size>
void count( Circulator c, Circulator d, Size& n) {
    n = 0;
    if ( c != 0) {
        do {
            ++n;
        } while (++c != d);
    }
}
\end{verbatim}

Given a circular data structure $S$, the expression {\tt
  count(}$S${\tt.begin(),} $S${\tt.begin(), counter)} returns the
number of elements of $S$ in the {\tt counter} parameter.

As for iterators, circulators come in different flavors. There are
{\em forward, bidirectional\/} and {\em random access circulators}.
They are either {\em mutable} or {\em constant}. The past-the-end
value is not applicable for circulators.

{\bf Reachability:} 
A circulator $d$ is called {\em reachable} from a circulator $c$ if
and only if there is a finite sequence of applications of
\ccStyle{operator++} to $c$ that makes $c == d$. If $c$ and $d$ refer
to the same non-empty data structure, then $d$ is reachable from $c$,
and $c$ is reachable from $d$. In particular, any circulator $c$
referring to a non-empty data structure will return to itself after a
finite sequence of applications of \ccStyle{operator++} to $c$.

{\bf Range:} 
Most of the library's algorithmic templates that operate on data
structures have interfaces that use {\em ranges}. A range is a pair of
circulators that designate the beginning and end of the computation. A
range $\left[c, c\right)$ is a {\em full range}; in general, a range
$\left[c, d\right)$ refers to the elements in the data structure
starting with the one pointed to by $c$ and up to but not including
the one pointed to by $d$. Range $\left[c, d\right)$ is valid if and
only if both refer to the same data structure.  The result of the
application of the algorithms in the library to invalid ranges is
undefined.

{\bf Warning:} Please note that the definition of a range is different
to that of iterators. An interface of a data structure must declare
whether it works with iterators, circulators, or both. \stl\ algorithms
always specify only iterators in their interfaces. A range $\left[c,
  d\right)$ of circulators used in an interface for iterators will
work as expected as long as $c\; !\!= d$. A range $\left[c, c\right)$ will
be interpreted as the empty range like for iterators, which is
different than the full range that it should denote for circulators.

Algorithms could be written to support both, iterators and
circulators, in a single interface. Here, the range $\left[c,
  c\right)$ would be interpreted correctly. For more information how
to program functions with this behavior, please refer to the \cgal\ 
Reference Manual.

\medskip

As we said in the introduction, we are a little bit sloppy in the
presentation, in order to make it easier to understand.  A class is
said to be a circulator if it fulfills a set of requirements.  In the
following sections we do not present the requirements, but we state
properties that are true, if the requirements are fulfilled.  The
difference is best seen by an example: We write that the return value
of the test for equality returns a \ccStyle{bool}. The requirement is
only that the return value is convertible to \ccStyle{bool}.


\begin{ccHtmlClassFile}{Circulator.html}{Requirements for Circulators}
\begin{ccClass}{Circulator}

\ccSection{Forward Circulator}

\ccDefinition

A class \ccClassName\ that satisfies the requirements of a forward circulator
for the value type \ccStyle{T}, supports the following operations.

\ccCreation
\ccCreationVariable{c}
%\ccSetThreeColumns{Circulator&}{int n + Circulator d}{}
%\ccSetThreeColumns{difference_type}{difference_type n += d}{}
\ccPropagateThreeToTwoColumns

\ccConstructor{Circulator();}
{}

\ccConstructor{Circulator(const Circulator& d);}
{}

\ccOperations

\ccMethod{bool operator=(const Circulator &d);}
{Assignment.}

\ccMethod{bool operator==(NULL) const;}
{Test for emptiness.}

\ccMethod{bool operator!=(NULL) const;}
{Test for non-emptiness. The result is the same as \ccStyle{!(c == NULL)}.}

\ccMethod{bool operator==(const Circulator &d) const;}
{Test for equality: Two circulators are equal if they refer to the same item.}

\ccMethod{bool operator!=(const Circulator &d) const;}
{Test for inequality. The result is the same as \ccStyle{!(c == d)}.}

\ccMethod{T& operator*();}
{Returns the value of the circulator.
 If \ccClassName\ is mutable \ccStyle{*c = t} is valid.
 \ccPrecond \ccVar\ is dereferenceable.}

\ccMethod{Circulator& operator++();}
{Prefix increment operation.
\ccPrecond \ccVar\ is dereferenceable. \ccPostcond \ccVar\ is dereferenceable.}

\ccMethod{const Circulator& operator++(int);}
{Postfix increment operation. The result is the same as that of 
 \ccStyle{Circulator tmp = c; ++c; return tmp;}~.}

\end{ccClass} 


\ccHtmlNoClassLinks
\ccHtmlNoClassIndex
\begin{ccClass}{Circulator}

\ccSection{Bidirectional Circulator}

\ccDefinition

A class \ccClassName\ that satisfies the requirements of a bidirectional
circulator for the value type \ccStyle{T}, supports the following operations
in addition to the operations supported by a forward circulator.

\ccCreationVariable{c}
\ccOperations

\ccMethod{Circulator& operator--();}
{Prefix decrement operation.
 \ccPrecond \ccVar\ is dereferenceable. \ccPostcond \ccVar\ 
  is dereferenceable.}

\ccMethod{const Circulator& operator--(int);}
{Postfix decrement operation. The result is the same as that of 
 \ccStyle{Circulator tmp = c; --c; return tmp;}~.}

\end{ccClass} 


\ccHtmlNoClassLinks
\ccHtmlNoClassIndex
\begin{ccClass}{Circulator}

\ccSection{Random Access Circulator}
\label{sectionRandomAccessCirculatorRequ}

\ccDefinition

A class \ccClassName\ that satisfies the requirements of a random access
Circulator for the value type \ccStyle{T}, supports  the following operations
in addition to the operations supported by a bidirectional Circulator.

\ccCreationVariable{c}

\ccOperations

\ccMethod{Circulator& operator+=(int n);}
{The result is the same as if the prefix increment operation 
 was applied $n$ times, but it is computed in constant time.}

\ccMethod{Circulator operator+(int n);}
{Same as above, but returns a new circulator.}

\renewcommand{\ccTagRmEigenClassName}{\ccTrue}
\ccFunction{Circulator operator+(int n, Circulator c);}
{Same as above.}
\renewcommand{\ccTagRmEigenClassName}{\ccFalse}

\ccMethod{Circulator& operator-=(int n);}
{The result is the same as if the prefix decrement operation 
 was applied $n$ times, but it is computed in constant time.}

\ccMethod{Circulator operator-(int n);}
{Same as above, but returns a new circulator.}


\ccMethod{T& operator[](int n);}
{Returns \ccStyle{*(c + n)}.}

\ccMethod{int operator-(const Circulator& d) const;}
{returns the difference between the two circulators within the
  interval $\left[ 1-s , s-1 \right]$ for a sequence size $s$. The
  difference for a fixed circulator \ccVar\ (or $d$) with all other
  circulators $d$ (or \ccVar) is a consistent ordering of the elements
  in the data structure. There has to be a minimal circulator
  $d_{\mbox{\footnotesize min}}$ for which the difference \ccVar $-
  d_{\mbox{\footnotesize min}}$ to all other circulators \ccVar\ is
  non negative.}

\ccMethod{Circulator min_circulator() const;}
{Returns the minimal circulator $c_{\mbox{\footnotesize min}}$ in
  constant time.} 

There are no comparison operators required.
\end{ccClass} 
\end{ccHtmlClassFile} 

% +-----------------------------------------------------+
\newpage
\section{Adaptor: Container with Iterators from Circulator}
\label{sectionContainerFromCirc}

Algorithms working on iterators cannot be applied to circulators in
full generality, only to subranges (see the warning in
Section~\ref{sectionCirculatorWarning}). The following adaptors
convert circulators to iterators (with the unavoidable space and time
drawback) to reestablish this generality.

\begin{ccClassTemplate}{Container_from_circulator<C>}

\ccDefinition

The adaptor \ccClassTemplateName\ is a class that converts any
circulator type \ccStyle{C} to a kind of container class, i.e.~a class
that provides an \ccStyle{iterator} and a \ccStyle{const_iterator}
type and two member functions -- \ccStyle{begin()} and \ccStyle{end()}
-- that return the appropriate iterators. In analogy to \stl\ 
container classes these member functions return a \ccc{const_iterator}
in the case that the container itself is constant and a mutable
\ccc{iterator} otherwise.

\ccInclude{CGAL/circulator.h}

\ccTypes

\ccNestedType{Circulator}{the template argument \ccc{C}.}

\ccNestedType{iterator}{}
\ccGlue
\ccNestedType{const_iterator}{}

\ccCreation

\ccCreationVariable{container}
%\ccSetTwoColumns{Circulator}{}

\ccConstructor{Container_from_circulator();}{%
    the resulting iterators will have a singular value. }

\ccConstructor{Container_from_circulator(const C& c);}{%
    the resulting iterators will have a singular value if the circulator
    \ccStyle{c} correspond to an empty sequence.
   }

\ccOperations
%\ccSetThreeColumns{const_iterator}{container.begin() const;}{}

\def\ccTagRmTrailingConst{\ccFalse}

\ccMethod{iterator begin();}{the start iterator.}
\ccGlue
\ccMethod{const_iterator begin() const;}{the start const iterator.}
\ccGlue
\ccMethod{iterator end();}{the past-the-end iterator.}
\ccGlue
\ccMethod{const_iterator end() const;}{the past-the-end const iterator.}
\def\ccTagRmTrailingConst{\ccTrue}

The \ccc{iterator} and \ccc{const_iterator} types are of the
appropriate iterator category. In addition to the operations required
for their category, they have a member function
\ccc{current_circulator()} that returns a circulator pointing to the
same position as the iterator does.

\ccExample

The generic {\tt reverse()} algorithm from the \stl\ can be used with an
adaptor if at least a bidirectional circulator {\tt c} is given.

\begin{ccExampleCode}
Circulator c;  // c is assumed to be a bidirectional circulator.
CGAL::Container_from_circulator<Circulator> container(c);
reverse( container.begin(), container.end());
\end{ccExampleCode}

\ccImplementation

The forward and bidirectional iterator adaptors keep track of the
number of rounds a circulator has done around the ring-like data
structure. This is a kind of winding number. It is used to distinguish
between the start position and the end position which will be denoted
by the same circulator. This winding number is zero for the
\ccStyle{begin()}-iterator and one for the \ccStyle{end()}-iterator.
It is incremented whenever a circulator passes the \ccStyle{begin()}
position. Two iterators are equal if their internally used circulators
and winding numbers are equal. This is more general than necessary
since the \ccStyle{end()}-iterator is not supposed to move any more.

The random access iterator has to be able to compute the size of the
data structure. It is needed for the difference of a past-the-end
iterator and the begin iterator.  Therefore, the constructor for the
random access iterator choose the minimal circulator for the internal
anchor position. The minimal circulator is part of the random access
circulator requirements, see
Section~\ref{sectionRandomAccessCirculatorRequ}.

\end{ccClassTemplate}


% +-----------------------------------------------------+
\newpage

\section{Adaptor: Circulator from Iterator}
\label{sectionCircFromIter}
 
To obtain circulators, one could use a container class like those in
the Standard Template Library (\stl) or a pair of \ccStyle{begin()}-,
\ccStyle{end()}-iterators and one of the following adaptors. The adaptor
for iterator pairs is described here, the adaptor for container classes
is described in the next section.

%\begin{ccClassTemplate}{Circulator_from_iterator<I>}
\begin{ccRefClass}{Circulator_from_iterator<I>}
\ccDefinition
  
The adaptor \ccClassTemplateName\ converts two iterators of type
\ccc{I}, a begin and a past-the-end value, to a circulator of equal
category. The iterator must be at least of the forward iterator
category. The circulator will be mutable or non-mutable according to
the iterator. Iterators provide no \ccc{size_type}. This adapter
assumes \ccc{std::size_t} instead.

\ccInclude{CGAL/circulator.h}

\ccTypes
%\ccSetThreeColumns{typedef const T&}{const_reference;}{}

\ccUnchecked\ccTypedef{typedef I         iterator;}{}

In addition all types required for circulators are provided. 

\ccCreation
\ccCreationVariable{c}

\ccConstructor{Circulator_from_iterator();}{%
  a circulator \ccVar\ on an empty sequence.}

\ccConstructor{Circulator_from_iterator(const I& begin, const I& end);}{%
  a circulator \ccVar\ initialized to refer to the element
  \ccStyle{*begin} in  a range {\tt [}\ccStyle{begin}{\tt
    ,}\ccStyle{end}{\tt )}.
  %The circulator \ccVar\ contains a singular value if \ccStyle{begin==end}.
   Returns a circulator on an empty sequence if \ccStyle{begin==end}.
}

\ccOperations

The adaptors conform to the requirements of the different circulator
categories. An additional member function \ccc{current_iterator()} is
provided that returns the current iterator that points to the same
position as the circulator does.

\ccExample

This program uses two adaptors, iterators to circulators and back to
iterators. It applies an \stl\ sort algorithm on a \stl\ vector with three
elements. The resulting vector will be {\tt [2 5 9]} as it will be
checked by the assertions. The program is part of the \cgal\ 
distribution.

%\ccIncludeVerbatim{circulator_prog1.C}
\ccIncludeExampleCode{Circulator/circulator_prog1.C}

Another example usage for this adaptor are random access circulators
over the built-in C arrays. Given an array of type {\tt T*}  with a
begin pointer {\tt b} and a past-the-end pointer {\tt e} the adaptor
\ccStyle{Circulator_from_iterator< T*> c( b,e)} is a random circulator
\ccStyle{c} over this array.

%\end{ccClassTemplate} 
\end{ccRefClass}

% +-----------------------------------------------------+
\newpage
\section{Adaptor: Circulator from Container}
\label{sectionCircFromContainer}

To obtain circulators, one could use a container class like those in the
Standard Template Library (\stl) or a pair of \ccStyle{begin()}-,
\ccStyle{end()}-iterators and one of the provided adaptors here.
The adaptor for iterator pairs is described in the previous section,
the adaptor for container classes is described here.

\begin{ccClassTemplate}{Circulator_from_container<C>}

\ccHtmlCrossLink{Const_circulator_from_container}
\ccHtmlCrossLink{Const_circulator_from_container<C>}
\ccHtmlIndexC[class]{Const_circulator_from_container<C>}

\ccDefinition
  
The adaptor \ccClassTemplateName\ provides a circulator for an \stl\
container $C$ of equal category as the iterator provided by the container. 
The iterator must be at least of the forward iterator
category. The corresponding non-mutable circulator is called
\ccc{Const_circulator_from_container<C>}.

The container type \ccc{C} is supposed to conform to the \stl\ 
requirements for container (i.e.~to have a \ccStyle{begin()} and an
\ccStyle{end()} iterator as well as the local types
\ccStyle{reference}, \ccStyle{const_reference}, \ccStyle{value_type},
\ccStyle{size_type}, and \ccStyle{difference_type}).

\ccInclude{CGAL/circulator.h}

\ccTypes
%\ccSetThreeColumns{typedef container::const_reference}{const_reference;}{}

All types required for circulators are provided. 

\ccCreation
\ccCreationVariable{c}

\ccConstructor{Circulator_from_container();}{%
  a circulator \ccVar\ on an empty sequence.}

\ccConstructor{Circulator_from_container(C* container);}{%
  a circulator \ccVar\ initialized to refer to the first element in
  \ccStyle{container}, i.e. \ccStyle{container.begin()}.
  The circulator \ccVar\ corresponds to an empty sequence if
  \ccStyle{container} is empty.
}

\ccConstructor{Circulator_from_container(C* container, C::iterator i);}{%
  a circulator \ccVar\ initialized to refer to the element \ccStyle{*i} in
  \ccStyle{container}. \ccPrecond \ccStyle{*i} is dereferenceable and refers
  to \ccStyle{container}.
}

\ccOperations

The adaptors conform to the requirements of the different circulator
categories. An additional member function \ccc{current_iterator()} is
provided that returns the current iterator that points to the same
position as the circulator does.

\ccExample

This program uses two adaptors, container to circulators and back to
iterators. It applies an \stl\ sort algorithm on a \stl\ vector with three
elements. The resulting vector will be {\tt [2 5 9]} as it will be
checked by the assertions. The program is part of the \cgal\ 
distribution.

%\ccIncludeVerbatim{circulator_prog2.C}
\ccIncludeExampleCode{Circulator/circulator_prog2.C}

\end{ccClassTemplate} 

% EOF





