% +------------------------------------------------------------------------+
% | Reference manual page: Periodic_3Offset_3.tex
% +------------------------------------------------------------------------+
% | 19.2.2009   Manuel Caroli
% | Package: Periodic_3_triangulation_3
% | 
\RCSdef{\RCSPeriodicOffsetRev}{$Id$}
\RCSdefDate{\RCSPeriodicOffsetDate}{$Date$}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+

\begin{ccRefConcept}{Periodic_3Offset_3}

\ccDefinition
The concept \ccRefName\ describes a three-dimensional integer vector
with some specialized access functions and operations.

\ccCreation
\ccCreationVariable{o}

\ccThree{Periodic_3Offset_3}{Offsetxxxxxxxxxxxxxxxxxxxxxxxxxxxxx}{}

\ccConstructor{Periodic_3Offset_3();}
{Default constructor.}
\ccGlue
\ccConstructor{Periodic_3Offset_3(int x, int y, int z);}
{Constructs the offset (x,y,z).}

\ccOperations
\ccMethod{Periodic_3Offset_3 operator+(const Periodic_3Offset_3 & o')
  const;}
{Return the vector sum of \ccc{o} and \ccc{o'}.}
\ccGlue
\ccMethod{Periodic_3Offset_3 operator-(const Periodic_3Offset_3 & o')
  const;}
{Return the vector difference of \ccc{o} and \ccc{o'}.}
\ccGlue
\ccMethod{Periodic_3Offset_3 operator-() const;}
{Return the negative vector of \ccc{o}.}
\ccGlue
\ccMethod{void operator+=(const Periodic_3Offset_3 & o')
  const;}
{Add \ccc{o'} to \ccc{o} using vector addition.}
\ccGlue
\ccMethod{void operator-=(const Periodic_3Offset_3 & o')
  const;}
{Subtract \ccc{o'} from \ccc{o} using vector subtraction.}
\ccGlue
\ccMethod{bool operator==(const Periodic_3Offset_3 & o') const;}
{Return \ccc{true} if \ccc{o'} and \ccc{o} represent the same vector.}
\ccGlue
\ccMethod{bool operator!=(const Periodic_3Offset_3 & o') const;}
{Return \ccc{true} if \ccc{o'} and \ccc{o} do not represent the same
  vector.}
\ccGlue
\ccMethod{bool operator<(const Periodic_3Offset_3 & o') const;}
{Compare \ccc{o} and \ccc{o'} lexicographically.}

\ccAccessFunctions

\ccMethod{int operator[](int i);}
{Return the $i$-th entry of \ccc{o}.}
\ccGlue
\ccMethod{int x() const;}
{Return the $x$-entry of \ccc{o}.}
\ccGlue
\ccMethod{int y() const;}
{Return the $y$-entry of \ccc{o}.}
\ccGlue
\ccMethod{int z();}
{Return the $z$-entry of \ccc{o}.}
\ccGlue
\ccMethod{bool is_null() const;}
{Returns \ccc{true} if \ccc{o} is equal to (0,0,0).}

\ccHeading{I/O}
\ccFunction{istream& operator>>(istream & is, Periodic_3_offset_3
  & off);}
{Inputs an offset from \ccc{is}.}
\ccGlue
\ccFunction{ostream& operator<<(ostream & os, Periodic_3_offset_3
  & off) const;}
{Outputs an offset from \ccc{os}.}


\ccHasModels

\ccc{CGAL::Periodic_3_offset_3}

\ccSeeAlso

\ccc{Periodic_3DelaunayTriangulationTraits_3}

\end{ccRefConcept}