% +------------------------------------------------------------------------+
% | Reference manual page: Sweep_line_2.tex
% +------------------------------------------------------------------------+
% | 
% | Package: Arrangement_2
% | 
% +------------------------------------------------------------------------+

\ccRefPageBegin

\begin{ccRefClass}{Sweep_line_2<Traits, Visitor>}
%\label{arr_ref:arr_obs}

\ccDefinition
%============

\ccClassTemplateName\ 

\ccInclude{CGAL/Sweep_line_2.h}

\ccInheritsFrom\ccc{Basic_sweep_line_2<Traits, Visitor>}

\ccTypes
%=======


\ccTypedef{typedef typename Sweep_line_2<Traits, Visitor>::Traits_2 Traits_2;}
    {the traits type.}
\ccGlue

\ccTypedef{typedef typename Sweep_line_2<Traits, Visitor>::X_monotone_curve_2 X_monotone_curve_2;}
    {the $x$-monotone curve type.}
\ccGlue
\ccTypedef{typedef typename Sweep_line_2<Traits, Visitor>::Point_2 Point_2;}
    {the point type.}
\ccGlue

\ccTypedef{typedef typename Sweep_line_2<Traits, Visitor>::Event Event;}
    {the event type.}
\ccGlue

\ccTypedef{typedef typename Sweep_line_2<Traits, Visitor>::Subcurve Subcurve;}
    {the subcurve type.}
\ccGlue

\ccTypedef{typedef typename Sweep_line_2<Traits, Visitor>::Status_line_iterator Status_line_iterator;}
{the iterator type of the status line, its value type is  \ccc{Subcurve*}.}
\ccGlue
\ccTypedef{typedef typename Sweep_line_2<Traits, Visitor>::Event_queue_iterator Event_queue_iterator;}
{the iterator type of the event queue, its value type is  \ccc{Event*}.}
\ccGlue

\ccTypedef{typedef typename Sweep_line_2<Traits, Visitor>::Visitor Visitor;}
    {the visitor type.}
\ccGlue

\ccCreation
\ccCreationVariable{obs}
%=======================

\ccConstructor{Sweep_line_2 (Visitor *visitor);} 
    {constructs a sweep line object with a pointer to a sweep line visitor.}
 
\ccConstructor{Sweep_line_2 (Traits_2 *traits, Visitor *visitor);} 
    {constructs a sweep line object with pointer to a triats object and a pointer to a sweep-line visitor.}



\end{ccRefClass}

\ccRefPageEnd
