\begin{ccRefConcept}{PureComplexDSVertex}

\ccDefinition

The concept \ccRefName\ describes what a vertex is in a model of the concept
\ccc{PureComplexDataStructure}. It sets requirements of combinatorial nature
only, as geometry is not concerned here. In particular, we only require that
the vertex hold a handle to a simplex adjacent to it in the complex.

This concept is a \emph{sub-concept} of the \ccc{PureComplexDataStructure}
concept.

\ccHasModels

\ccc{Pure_complex_ds_vertex<PCDS>}

\ccTypes

\ccNestedType{Simplex_handle}{A handle to a Simplex.}

\ccNestedType{template<typename PC2> Rebind_PCDS}{This nested template
class must define a nested type \ccc{Other} which is the rebound vertex
class template, that is: \ccc{Other == PureComplexDSVertex<PC2>}.}

\ccCreation	
\ccCreationVariable{v}

\ccConstructor{PureComplexDSVertex();}{The default constructor (no adjacent
simplex is set).}
\ccGlue
\ccConstructor{PureComplexDSVertex(Simplex_handle s);}{Sets the incident
simplex to \ccc{s}. \ccPrecond \ccc{s} must not be the default-constructed
\ccc{Simplex_handle}.}

\ccOperations

\ccMethod{void set_simplex(Simplex_handle s);}{Set \ccc{s} as the vertex's
adjacent simplex. \ccPrecond \ccc{s} must not be the default-constructed
\ccc{Simplex_handle}.}

\ccMethod{Simplex_handle simplex() const;}{Returns a handle to a simplex
adjacent to the vertex.}

\ccHeading{Validity check}

\ccMethod{bool is_valid(bool verbose=false, int level=0) const;}{Performs any
desired test on a vertex. Al least, checks that the pointer to an incident
simplex is not the default constructed handle (\emph{i.e.}, is not
\ccc{NULL}). The parameter \ccc{level} is not used, but can be used in derived
classes.}

\ccHeading{Memory management}

\ccMethod{void*   for_compact_container() const;}{}
\ccGlue\ccMethod{void* & for_compact_container();}{}

These member functions are required by the classes
\ccc{Pure_complex_data_structure<Dimensionality, PCDSVertex, PCDSSimplex>} and
\ccc{Pure_complex<PCTraits, PCDS>} (and its derived classes) because they use
the \cgal\ container class \ccc{Compact_container} to store their vertices and
simplices. See the documentation of \ccc{Compact_container} for the exact
requirements.

\ccHeading{Input/Output}

\ccFunction{template<class PCDS> istream& operator>>(istream & is,
        Pure_complex_ds_vertex<PCDS> & v);}
{Reads (possible) non-combinatorial information about a vertex from the stream \ccc{is}
into \ccc{v}.}

\ccFunction{template<class PCDS> ostream& operator<<(ostream & os, const
        Pure_complex_ds_vertex<PCDS> & v);}
{Writes (possible) non-combinatorial information about vertex \ccc{v} to the stream
    \ccc{os}.}

\ccSeeAlso

\ccc{PureComplexDSSimplex}\\
\ccc{PureComplexDataStructure}

\end{ccRefConcept}
