\section{Third Party Software}

In this section we list the software that is used by the various
\cgal\ packages.


\subsection{Standard Template Library \label{thirdparty:stl}}

\cgal\ heavily uses the {\sc Stl}, and in particular adopted
many of its design ideas.   The {\sc Stl} comes with the compiler,
but it is possible to use the compiler together with an
alternative {\sc Stl} implementation.


\subsection{Boost \label{thirdparty:Boost}}

Boost is a collection of libraries. \cgal\ needs some of them, that is
it is mandatory.  If Boost is not already on your system, e.g., on
Windows, you can download it from \path'http://www.boost.org'.

\subsection{Blas \label{thirdparty:Blas}}

A library for Basic Linear Algebra Subroutines.
It is used in the \ccc{Jet_fitting_3} and \ccc{Ridges_3} package.

For {\sc Amd} processors \blas\ is freely provided by  the {\sc Amd} Core Math Library ({\sc Acml}) and can be downloaded
from \path'http://developer.amd.com/acml.jsp'.

\subsection{Lapack \label{thirdparty:Lapack}}

A library providing a full suite of Linear Algebra.
It is used in the \ccc{Jet_fitting_3} and \ccc{Ridges_3} package.

For {\sc Amd} processors \lapack\ is freely provided by  the {\sc Amd} Core Math Library ({\sc Acml}) and can be downloaded
from \path'http://developer.amd.com/acml.jsp'.

\subsection{GMP \label{thirdparty:GMP}}

A library for multi precision integers and rational numbers.
\cgal\ offers adapters for these number types. The usage
of the {\sc Gmp} library is optional.  If it is not already on your system,
e.g., on Windows, you can download it from \path'www.swox.com/gmp'
or from the Download section of \path'http://www.cgal.org'.


\subsection{MPFR \label{thirdparty:MPFR}}

A library for multi precision floating point numbers.  The usage of
the {\sc Mpfr} library is optional, and you must install it when you
use {\sc Gmp}.  You can download {\sc Mpfr} from \path'http://www.mpfr.org'
or from the Download section of \path'http://www.cgal.org'.


\subsection{Leda \label{thirdparty:Leda}}

A library of efficient data structures and algorithms. \cgal\ offers
adapters to the {\sc Leda} number types. The usage is optional.
It is only available commercially from \path'http://www.algorithmic-solutions.com'.


\subsection{Taucs \label{thirdparty:Taucs}}

A library of sparse linear solvers.
It can be used by the \ccc{Surface_mesh_parameterization} package
in order to speed up the algorithm.
You can download the official release from
\path'http://www.tau.ac.il/~stoledo/taucs/' or download a version customized
by \cgal\ team from the Download section of \path'http://www.cgal.org'.


\subsection{OpenNL \label{thirdparty:OpenNL}}

OpenNL (Open Numerical Library) is a library to easily construct and solve
sparse linear systems. It is the default solver of the
\ccc{Surface_mesh_parameterization} package.

The author is Bruno L\'evy.
OpenNL main page is \path'http://www.loria.fr/~levy/software/'.

\cgal\ includes a version of OpenNL in C++, made especially for \cgal\ by Bruno L\'evy.


\subsection{zlib \label{thirdparty:zlib}}

A data compression library.
It is used in the examples of the \ccc{Surface_mesher} package.
If it is not already on your system,
e.g., on Windows, you can download it from  \path'http://www.gzip.org/zlib'.

\subsection{Qt \label{thirdparty:Qt}}

A {\sc Gui} library. The usage of Qt is optional, but note that
it is used for all 2D demos.

As Qt is the layer underneath {\sc Kde}, Qt is installed
on many Linux systems. Otherwise you can download it from
 \path'http://www.trolltech.com'.


\subsection{Coin \label{thirdparty:Coin}}

An implementation of Open Inventor.  It is used in the demo
of the \ccc{Kinetic_data_structures} package. You can download
it from \path'http://www.sim.no'.

