% +------------------------------------------------------------------------+
% | CGAL Reference Manual: Reference manual for Qt_widget.tex
% +------------------------------------------------------------------------+
% |
% | 02.04.2003  Radu Ursu
% | 
% | \RCSdef{\qtwidgetRev}{$Id$}
% | \RCSdefDate{\qtwidgetDate}{$Date$}
% +------------------------------------------------------------------------+

% +-----------------------------------------------------+
\begin{ccRefClass}{Qt_widget_standard_toolbar}

\ccDefinition

The standard toolbar includes the basic tools used for zooming and
translating in a \ccc{Qt_widget}.

\ccInclude{CGAL/IO/Qt_widget_standard_toolbar.h}
\ccGlue

\ccInheritsFrom
\ccc{QToolBar}

\ccCreation
\ccCreationVariable{stoolbar}
\ccSetTwoColumns{Qt_widget_standard_toolbar}{}

\ccConstructor{Qt_widget_standard_toolbar(Qt_widget *w, QMainWindow
*mw , QWidget* parent, bool newline = true, const char* name =
0);}
{ This constructor creates a new toolbar, called \ccc{name}, in your
  application, containing all the standard tools. The first parameter
  \ccc{w} is a non-null pointer to the Qt\_widget object on which the
  toolbar functionalities act. The second parameter \ccc{mw} is a
  pointer to the \ccc{QMainWindow} that manages the toolbar. The later
  is added to the top area of the \ccc{QMainWindow}, unless
  \ccc{mw=0}. \ccc{mw}, \ccc{parent}, \ccc{newline}, \ccc{name} are
  passed to the \ccc{QMainWindow} constructor (with first parameter
  \ccc{label=''Qt_widget standard toolbar''}). }

\ccConstructor{Qt_widget_standard_toolbar(Qt_widget *w, QMainWindow
*parent = 0, const char* name = 0);}
{ Simplified version of the previous one. The \ccc{parent} is the
  \ccc{QMainWindow} that manages the toolbar. }

\ccMethod{const QToolBar* toolbar();}{Deprecated: (in CGAL-2.4 the
standard toolbar was not derived from \ccc{QToolBar}) Returns a pointer to
the \ccc{QToolBar this} itself. }

\ccHeading{public slots:}
\ccMethod{void back();}{Goes back in the history list of the standard toolbar.}
\ccMethod{void forward();}{Goes forward in the history list of the
standard toolbar.}
\ccMethod{void clear_history();}{Clears the history list of the
standard toolbar.}

\ccExample
\begin{ccExampleCode}
#include <CGAL/Cartesian.h>
#include <CGAL/Point_2.h>
#include <CGAL/Delaunay_triangulation_2.h>
#include <CGAL/IO/Qt_widget_Delaunay_triangulation_2.h>

#include <qapplication.h>
#include <qmainwindow.h>

#include <CGAL/IO/Qt_widget.h>
#include <CGAL/IO/Qt_widget_layer.h>
#include <CGAL/IO/Qt_widget_standard_toolbar.h>

typedef CGAL::Cartesian<double>             Rep;
typedef CGAL::Point_2<Rep>                  Point;
typedef CGAL::Delaunay_triangulation_2<Rep> Delaunay;

Delaunay dt;

class My_layer : public CGAL::Qt_widget_layer{
  void draw(){
    *widget << CGAL::BLACK;
    *widget << dt;
  }
};

class My_widget : public CGAL::Qt_widget {
public:
  My_widget(QMainWindow* c) : CGAL::Qt_widget(c) {};
private:
  //this event is called only when the user presses the mouse
  void mousePressEvent(QMouseEvent *e)
  {
    Qt_widget::mousePressEvent(e);
    dt.insert(Point(x_real(e->x()), y_real(e->y())));
    redraw();
  }
};

class My_window : public QMainWindow{
public:
  My_window(int x, int y)
  {
    widget = new My_widget(this);
    setCentralWidget(widget);
    resize(x,y);
    widget->set_window(0, x, 0, y);
    
    //How to attach the standard toolbar
    stoolbar = new CGAL::Qt_widget_standard_toolbar(widget, this,
                                                    "Standard toolbar");
    widget->attach(&v);
  }
private:
  My_widget *widget;
  My_layer  v;
  CGAL::Qt_widget_standard_toolbar *stoolbar;
};

int main( int argc, char **argv )
{
    QApplication app( argc, argv );
    My_window W(400,400);
    app.setMainWidget( &W );
    W.show();
    W.setCaption("Using the Standard Toolbar");
    return app.exec();
}
\end{ccExampleCode}

This example is implemented in the fifth tutorial. You can 
look over the code to see how the code works.

\end{ccRefClass}

% +-----------------------------------------------------+
% EOF







