%% Copyright (c) 2004  SciSoft.  All rights reserved.
%%
%% This file is part of CGAL (www.cgal.org); you may redistribute it under
%% the terms of the Q Public License version 1.0.
%% See the file LICENSE.QPL distributed with CGAL.
%%
%% Licensees holding a valid commercial license may use this file in
%% accordance with the commercial license agreement provided with the software.
%%
%% This file is provided AS IS with NO WARRANTY OF ANY KIND, INCLUDING THE
%% WARRANTY OF DESIGN, MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE.
%%
%% 
%%
%% Author(s)     : Fernando Cacciola <fernando_cacciola@hotmail.com>


\begin{ccRefClass}{boost::graph_traits< CGAL::Polyhedron_3<Traits> >}

%% add template arg's if necessary

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[class]{} %% add further index entries
\ccDefinition

The class \ccRefName\ and corresponding free-function overloads provides the specializations for \ccc{Polyhedron_3} required to make it a {\em mutable} model of the Boost Graph types: \ccc{BidirectionalGraph}, \ccc{AdjacencyGraph} and \ccc{EdgeAndVertexListGraph}.

\ccInclude{CGAL/boost/graph/Polyhedron_graph_traits.h}

\ccTypes
  \ccTypedef{typename Polyhedron_3::Vertex_handle   vertex_descriptor;}
    {The vertex descriptor.}
  
  \ccTypedef{typename Polyhedron_3::Halfedge_handle edge_descriptor;}
    {The edges descriptor.}
  
  \ccTypedef{-implementation-defined- vertex_iterator;}{A \ccc{Polyhedron_3::Vertex_iterator}
    wrapped to return a \ccc{Polyhedron_3::Vertex_handle} when dereferenced.}
  
  \ccTypedef{-implementation-defined- edge_iterator;}{A \ccc{Polyhedron_3::Halfedge_iterator}
    wrapped to return a \ccc{Polyhedron_3::Halfedge_handle} when dereferenced.}
  
  \ccTypedef{-implementation-defined- in_edge_iterator;}{An edge iterator which only iterates over 
  the incoming \ccc{halfedges} around a vertex. It correspons to a
  \ccc{Polyhedron_3::Halfedge_around_vertex_circulator}
  wrapped to return an \ccc{Polyhedron_3::Halfege_handle} when dereferenced}
  
  \ccTypedef{-implementation-defined- out_edge_iterator;}{An edge iterator which only iterates over 
  the outgoing halfedges around a vertex. It correspons to a \ccc{Polyhedron_3::Halfedge_around_vertex_circulator}
  wrapped to return an \ccc{Polyhedron_3::Halfege_handle} referring to the {\em opposite halfege} when
  dereferenced.}
  
  \ccTypedef{boost::directed_tag directed_category;}{Indicates this is a directed graph.}
  
  \ccTypedef{boost::disallow_parallel_edge_tag edge_parallel_category;}
  {Indicates this graph does not support multiedges.}
  
  \ccTypedef{boost::bidirectional_graph_tag  traversal_category;}
    {Indicates this graph is bidirectional.}
    
  \ccTypedef{typename Polyhedron_3::size_type vertices_size_type;}
    {The size tye of the vertex list.}
    
  \ccTypedef{typename Polyhedron_3::size_type edges_size_type;}
    {The size tye of the edge list.}
    
  \ccTypedef{typename Polyhedron_3::size_type degree_size_type;}
    {The size tye of the adjacency list.}
  
\ccIsModel
\ccc{BidirectionalGraph}
\ccc{AdjacencyGraph}
\ccc{EdgeAndVertexListGraph}

\ccSeeAlso

\end{ccRefClass}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

