% +------------------------------------------------------------------------+
% | Reference manual page: Triangulation_vertex_base_with_info_2.tex
% +------------------------------------------------------------------------+
% | 19.08.2003   Author
% | Package: Package
% | 
\RCSdef{\RCSTriangulationvertexbasewithinfoRev}{$Id$}
\RCSdefDate{\RCSTriangulationvertexbasewithinfoDate}{$Date$}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefClass}{Triangulation_vertex_base_with_info_2<Info,Traits,Vb>}  %% add template arg's if necessary

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[class]{} %% add further index entries

\ccDefinition
  
The class \ccRefName\ is designed to be used as a base vertex class
of a triangulation. It provides an easy way to add some user defined information in vertices.

\ccInclude{CGAL/Triangulation_vertex_base_with_info_2.h}

\ccParameters

The first template parameter is the information the user would like to add
to a vertex.  It has to be \ccc{DefaultConstructible} and \ccc{Assignable}.

The second template parameter is the geometric traits class
which provides the \ccc{Point_2}. It is strongly 
recommended to instantiate this parameter
with the traits class used for   the triangulation.
This ensures that the point type defined by \ccRefName\
matches  the point type defined by 
the triangulation.

The third template parameter is a vertex base class from which
\ccc{Triangulation_vertex_base_with_info_3} derives.  By default
this parameter is instantiated by
\ccc{CGAL::Triangulation_vertex_base_2<Traits>}.

\ccIsModel
The parameter \ccc{Vb} is a model of some vertex base concept.
\ccRefName\ derives from \ccc{Vb} and will be a model of the
same vertex base concept :
\ccc{TriangulationVertexBase_2}, or \\
\ccc{RegularTriangulationVertexBase_2}.

\ccTypes
\ccTypedef{typedef Info Info;}{}


\ccCreationVariable{v}  %% choose variable name

\ccAccessFunctions
\ccThree{const Info&}{Facetxxxxxxxxxx}{}

\ccTagFullDeclarations

\ccMethod{const Info& info() const;}
{Returns a const reference to the object of type \ccc{Info} stored in the
vertex.}
\ccGlue
\ccMethod{Info& info();}
{Returns a reference to the object of type \ccc{Info} stored in the vertex.}


\ccSeeAlso

\ccc{CGAL::Triangulation_face_base_with_info_2<Info,Traits,Fb>}\\
\ccc{CGAL::Triangulation_vertex_base_2<Traits,Vb>} \\
\ccc{CGAL::Regular_triangulation_vertex_base_2<Traits,Vb>} \\


\end{ccRefClass}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

