% +------------------------------------------------------------------------+
% | Reference manual page: Triangulation_traits_2.tex
% +------------------------------------------------------------------------+
% | 06.04.2000   Author
% | Package: Package
% | 
\RCSdef{\RCSTriangulationtraitsRev}{$Id$}
\RCSdefDate{\RCSTriangulationtraitsDate}{$Date$}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefConcept}{TriangulationTraits_2}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries

\ccDefinition
  
The concept \ccRefName\ describes 
 the set of requirements to be
fulfilled
by any class used to instantiate the first template parameter of the class 
\ccc{Triangulation_2<Traits,Tds>}.
This concept provides the types of the geometric primitives used in the
triangulation and some function object types
for the required predicates on those primitives.

\ccTypes
\ccNestedType{Point_2}{The  point type.}
\ccGlue
\ccNestedType{Segment_2}{The segment  type.}
\ccGlue
\ccNestedType{Triangle_2}{The triangle type.}

\ccNestedType{Construct_segment_2} {A constructor object for
\ccc{Segment_2}. Provides~: \\
\ccc{Segment_2 operator()(Point_2 p,Point_2 q)}, \\ 
which constructs a  segment from two points.}
\ccGlue
\ccNestedType{Construct_triangle_2} {A constructor object for
\ccc{Triangle_2}. Provides~: \\
\ccc{Triangle_2 operator()(Point_2 p,Point_2 q,Point_2 r )}, \\
which constructs a triangle from three points.}

\ccNestedType{Less_x_2}{Predicate object. Provides
the operator~: \\
\ccc{bool operator()(Point p, Point q)} \\
which returns \ccc{true} if \ccc{p} is before \ccc{q}
according to the $x$-ordering of points.}
\ccGlue
\ccNestedType{Less_y_2}{Predicate object. Provides
the operator~: \\
\ccc{bool operator()(Point p, Point q)} \\
which returns \ccc{true} if \ccc{p} is before \ccc{q}
according to the $y$-ordering of points.}
\ccGlue
\ccNestedType{Compare_x_2}{Predicate object. Provides
the operator~: \\
\ccc{Comparison_result operator()(Point p, Point q)} \\
which returns 
\ccc{SMALLER, EQUAL} or \ccc{ LARGER}
 according to the
$x$-ordering of points \ccc{p} and \ccc{q}.}
\ccGlue
\ccNestedType{Compare_y_2}{Predicate object. Provides
the operator~: \\ 
\ccc{Comparison_result operator()(Point p, Point q)}\\
which returns 
(\ccc{SMALLER, EQUAL} or \ccc{ LARGER})
according to the
$y$-ordering of points \ccc{p} and \ccc{q}.}
\ccGlue
\ccNestedType{Orientation_2}{Predicate object. Provides
the  operator~: \\
\ccc{Orientation operator()(Point p, Point q, Point r)}\\
which returns \ccc{LEFT_TURN}, \ccc{RIGHT_TURN} or \ccc{COLLINEAR}
depending on $r$ being, with respect to
the oriented line \ccc{pq}, 
on the left side , on the right side or on the line.}
\ccGlue
\ccNestedType{Side_of_oriented_circle_2}{Predicate object. Must
provide the operator
\ccc{Oriented_side operator()(Point p, Point q, Point r, Point s)}
which takes four points $p, q, r, s$ as arguments and returns
\ccc{ON_POSITIVE_SIDE}, \ccc{ON_NEGATIVE_SIDE} or, 
\ccc{ON_ORIENTED_BOUNDARY} according to the position of points \ccc{s}
with respect to the oriented circle through  through $p,q$
and $r$.
 This type is required only if the function 
\ccc{side_of_oriented_circle(Face_handle f, Point p)} is
called.}
\ccGlue
\ccNestedType{Construct_circumcenter_2}{Constructor object. Provides
the operator~: \\ 
\ccc{ Point operator()(Point p, Point q, Point r)} \\
which returns
the  circumcenter of the three points  \ccc{p, q} and \ccc{r}.
This type is required only if  the function 
\ccc{Point circumcenter(Face_handle  f)}is called.}

\ccCreation
\ccCreationVariable{traits}  %% choose variable name
Only a default constructor, copy constructor
 and an assignment operator are required. 
Note that further constructors
can be provided. 
\ccThree{TriangulationTraits_2}{traits=gtrxx  }{}
\ccConstructor{TriangulationTraits_2();}{default constructor.}
\ccGlue
\ccConstructor{TriangulationTraits_2(TriangulationTraits_2 gtr);}
{Copy constructor}
\ccMethod{TriangulationTraits_2 operator=(TriangulationTraits_2 gtr);}
{Assignment operator.}

\ccHeading{Predicate functions}
\ccThree{Construct_circumcenter_2}{traits.construct_circumcenter_2_object();}
{}
The following functions give access to the  predicate 
and constructor objects.
\ccThree{Construct_segment_2}{gt.compare_x(Point p0, Point p1)x}{}
\ccMethod{Construct_segment_2 construct_segment_2_object();}{}
\ccGlue
\ccMethod{Construct_triangle_2 construct_triangle_2_object();}{}
\ccGlue
\ccMethod{Comparison_x_2 compare_x_2_object();}{}                               \ccGlue
\ccMethod{Comparison_y_2 compare_y_2_object();}{}
\ccGlue
\ccMethod{Orientation_2  orientation_2_object();}{}
\ccGlue
\ccMethod{Side_of_oriented_circle_2
side_of_oriented_circle_2_object();}
{Required only
if \ccc{side_of_oriented_circle} is called
called.}
\ccGlue
\ccMethod{Construct_circumcenter_2 construct_circumcenter_2_object();}
{Required only if \ccc{circumcenter} is called.}



\ccHasModels
All the CGAL Kernels \\
\ccRefIdfierPage{CGAL::Triangulation_euclidean_traits_2<K>} \\
\ccRefIdfierPage{CGAL::Projection_traits_xy_3<K>}\\
\ccc{CGAL::Projection_traits_yz_3<K>}\\
\ccc{CGAL::Projection_traits_zx_3<K>}
\begin{ccDeprecated}
\ccRefIdfierPage{CGAL::Triangulation_euclidean_traits_xy_3<K>}, \\
\ccc{CGAL::Triangulation_euclidean_traits_yz_3<K>}, \\
\ccc{CGAL::Triangulation_euclidean_traits_zx_3<K>}.
\end{ccDeprecated}

\ccSeeAlso
\ccc{CGAL::Triangulation_2<Traits,Tds>}



\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

