% +------------------------------------------------------------------------+
% | Reference manual page: Arr_polyline_traits.tex (Arrangement)
% +------------------------------------------------------------------------+
% | 
% | Package: arr (Arrangement_2)
% | 
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+
% +========================================================================+
%  Arr_polyline_traits_2<Segment_traits>
% +========================================================================+
\begin{ccRefClass}{Arr_polyline_traits_2<Segment_traits>}

\ccDefinition
    The class \ccRefName\ is a traits class for polyline curves, which are
    piecewise linear curves --- chains of segments, where each two neighboring
    segments in the chain share a common endpoint. The traits class uses
    functionality of the \ccc{Segment_traits} to handle the segments that 
    comprise the polyline curve.

    The template parameter \ccc{Segment_traits} corresponds to a traits class
    for line segment that is a model of the \ccc{ArrangementTraits_2} concept 
    (such as \ccc{Arr_segment_traits_2<Kernel>} or 
    \ccc{Arr_segment_cached_traits_2<Kernel>}).

    The \ccc{Kernel} must use a number type that supports exact computations
    with rational numbers, such as \ccc{Quotient<Gmpz>} or 
    \ccc{leda_rational}. Other inexact representations can be used at the 
    user's own risk.

\ccInclude{CGAL/Arr_polyline_traits_2.h}

\ccIsModel
    \ccc{ArrangementTraits_2} \lcTex{(\ccRefPage{ArrangementTraits_2}).}

% The Conic_arc_2 class:
%
\subsection*{Class \ccc{Arr_polyline_traits_2<Segment_traits>::Curve_2}}

The \ccc{Curve_2} class nested within the polylines' traits is used to
represent piecewise linear curves and support their construction from
arbitrary containers of points. The copy and default constructor as well as 
the assignment operator are provided for polyline curves. In addition, 
an \ccc{operator<<} for the curves is defined for standard output streams.

\begin{ccClass}{Arr_polyline_traits_2<Segment_traits>::Curve_2}

\ccTypes

    \ccNestedType{const_iterator}{A reversible iterator for traversing the
     points that comprise the polyline curves. Supports the increment 
     (\ccc{operator++}), decrement (\ccc{operator--}), dereference 
     (\ccc{operator*}) and equality (\ccc{operator==} and \ccc{operator!=}) 
     operators.}

    \ccCreation
    \ccCreationVariable{cv}

    \ccStyle{template <class Container>} \\
    \ccConstructor{Curve_2 (const Container& points);}
  {constructs a polyline defined by the sequence of points in the container.
   The \ccc{Container} class must provide a \ccc{const_iterator} whose type
   is \ccc{Segment_traits::Point_2}.
   If the container contains $n$ points labeled $p_{0},p_{1},\ldots,p_{n-1}$,
   the generate polyline consists of $n-1$ segments, where the $k$th segment 
   is defined by the endpoints $[p_{k-1},p_{k}]$. The first point in the 
   container is considered as the source point of the polyline while the last 
   point is considered as its target.
   \ccPrecond{There are at least two points in the container}.}

\ccOperations

\ccMethod{const_iterator begin() const;}
  {returns a \ccc{const_iterator} pointing at the source point of the 
   polyline.}

\ccMethod{const_iterator end() const;}
  {returns a \ccc{const_iterator} pointing after the end of the polyline.}

\ccMethod{const_iterator rbegin() const;}
  {returns a \ccc{const_iterator} pointing at the target point of the 
   polyline.}

\ccMethod{const_iterator rend() const;}
  {returns a \ccc{const_iterator} pointing before the beginning of the 
   polyline.}

\ccMethod{int points() const;}
  {returns the number of points that comprise the polyline. Note that if there
   are $n$ points in the polyline, it is comprised of $n-1$ segments.}

\end{ccClass}

\end{ccRefClass}

% EOF -----------------------------------------------------------------------80

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+
