
\begin{ccRefClass}{Combination_enumerator<CombinationElement>}

\ccDefinition

The class \ccRefName\ represents one combination (subset), and enumerates all
fixed-size combinations (subsets) of a range of consecutive elements. For
example, it can enumerate all the subsets of size 2 of the range $[3,7)$ ($7$
excluded) which gives the enumeration \{3,4\}, \{3,5\}, \{3,6\}, \{4,5\},
\{4,6\}, \{5,6\}.  The range consists of elements of type
\ccc{CombinationElement} and is specified by its first element and the element
just beyond its last one.

The template parameter should be a model of the concept \ccc{CombinationElement}.

Each combination is uniquely represented as an increasing sequence of elements.
Thus, the combinations can be lexicographically ordered. They are enumerated in
that order, so that we can talk about the first or last subset.

%\ccIsModel
%\ccRefConceptPage{ConceptName}

\ccInclude{CGAL/Combination_enumerator.h}

\ccCreation

\ccCreationVariable{c}
\ccConstructor{Combination_enumerator(int k, const CombinationElement & first,
const CombinationElement & beyond);}{This constructors initializes \ccVar\ to
enumerate the subsets of size \ccc{k} of the range of elements \ccc{[first,
beyond)}. The current subset is set to the first subset of the enumeration.
\ccPrecond{\ccc{1 <= k <= beyond - first}}}

\ccConstructor{Combination_enumerator(const Combination_enumerator & combi);}%
{The copy constructor.}

\ccHeading{Access to the current combination}

\ccMethod{const CombinationElement & operator[](int i);}{Returns the \ccc{i}-th
element of the current combination. \ccPrecond{\ccc{0 <= i < }
\ccVar.\ccc{number_of_elements()}}}

\ccHeading{Access to the enumeration}

\ccMethod{int number_of_elements();}{Returns the size of the enumerated
combinations (the parameter \ccc{k} from the class' constructor).}

\ccMethod{const CombinationElement & min_element();}{Returns the smallest
possible value in all enumerated combinations (the parameter \ccc{first} of the
class' constructor).}

\ccMethod{const CombinationElement & beyond_element();}{Returns the successor
to the largest possible value in all enumerated combinations (the parameter
\ccc{beyond} of the class' constructor).}

\ccMethod{bool finished();}{Returns \ccc{true} if and only if all combinations
have been enumerated.}

\ccOperations

\ccMethod{void reset();}{Resets the enumerator. The current combination is set
to the first one of the enumeration.}

\ccMethod{void operator++();}{Moves \ccVar\ to the next combination.}

\ccMethod{Combination_enumerator operator++(int);}{Post-incrementation. Same as
the pre-incrementation above, but returns the original value of \ccVar.}

%\ccSeeAlso

\end{ccRefClass}
