% +------------------------------------------------------------------------+
% | Reference manual page: Bitangent_base.tex
% +------------------------------------------------------------------------+
% | 06.06.2000 Pierre Angelier
% | Package: Visibility_complex_2
% | 
\RCSdef{\RCSBitangentBaseRev}{$Revision$}
\RCSdefDate{\RCSBitangentBaseDate}{$Date$}
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+

\begin{ccRefConcept}{Bitangent_base}
\label{pageVC_Bitangent_baseRef}
  
The \ccRefName\ concept defines the minimal requirement for a
\emph{combinatorial} bitangent, i.e. a bitangent with no underlying geometric
segment. The only information stored by the \ccRefName\ concept is the type and
the two disks defining a bitangent. The \ccc{Bitangent_2} concept will inherit
from \ccRefName\ . The only additional functionality the \ccc{Bitangent_2} will
provide are the constructors giving the coordinates of the bitangent's
endpoints. In other words the \ccc{Bitangent_2} concept will add geometric
information.

% ------------------------------------------------------------------------------
\ccTypes
\ccThree{Bitangent_base_2}{Disk_handle}{}
\ccThreeToTwo

\ccNestedType{Disk}{type of disks defining the bitangent. }
\ccGlue
\ccNestedType{Disk_handle}{handle to \ccc{Disk}.}
\ccGlue
\ccNestedType{Type}{enumerated type to specify the type of the bitangent. The
		    possible values are \ccc{LL,RR,RL} or \ccc{LR} respectively 
		    for left-left,right-right,right-left and left-right 
		    bitangents.}{}
% ------------------------------------------------------------------------------

% ------------------------------------------------------------------------------
\ccThree{Disk_handle}{ b.source_object(); }{}
\ccThreeToTwo
\ccCreation
\ccCreationVariable{b}

\ccConstructor{Bitangent_base();}{default constructor.}
\ccGlue
\ccConstructor{Bitangent_base(Type t, Disk_handle source, Disk_handle target);}
{ Creates the combinatorial bitangent with type t directed from source to target. }
\ccGlue
% ------------------------------------------------------------------------------

% ------------------------------------------------------------------------------
\ccOperations

\ccTagFullDeclarations
\ccMethod{Disk_handle source_object(); const}
{returns a pointer to the disk that \ccVar\ leaves.}
\ccGlue
\ccMethod{Disk_handle target_object(); const}
{returns a pointer to the disk that \ccVar\ enters.}
\ccGlue
\ccMethod{Type type(); const}
{returns the type of the bitangent. }

\ccTagDefaults
% ------------------------------------------------------------------------------

\ccTagDefaults
\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+

