% +------------------------------------------------------------------------+
% | Reference manual page: VisibilityComplexFace.tex
% +------------------------------------------------------------------------+
% | Last revision: 09.07.2002   
% | Author : Pierre Angelier <Pierre.Angelier@ens.fr>
% | Maintainer: Laurent Rineau <Laurent.Rineau@ens.fr>
% | Package: Visibility_complex
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+

\begin{ccRefConcept}{VisibilityComplexFace}
\label{pageVCFaceRef}
  
% +----------------------------------------------------------------------------+
\ccDefinition

The concept \ccRefName\ defines the requirements for the \ccc{Face} type in the
\ccc{VisibilityComplex} concept. It is also required in the
\ccc{Face_wrapper<_Vc,_Tr>} member class template of an items class, see the
\ccc{VisibilityComplex_items} concept.
% +----------------------------------------------------------------------------+

% ------------------------------------------------------------------------------
\ccTypes
\ccThree{typedef Face::Vertex_handle}{Vertex_handle;}{}
\ccThreeToTwo

\ccNestedType{Gt} {geometric traits class. }
\ccGlue
\ccNestedType{Vertex}{model of \ccc{Vertex}.}
\ccGlue
\ccNestedType{Edge}{model of \ccc{Edge}.}
\ccGlue
\ccNestedType{Face}{model of \ccc{Face}.}

\ccNestedType{Vertex_handle}{handle to vertex.}
\ccGlue
\ccNestedType{Edge_handle}{handle to halfedge.}
\ccGlue
\ccNestedType{Face_handle}{handle to face.}
% ------------------------------------------------------------------------------

% ------------------------------------------------------------------------------
\ccThree{Edge_handle}{v.set_bottom_edge( Edge_handle e);}{}
\ccThreeToTwo

\ccCreation
\ccCreationVariable{f}

\ccConstructor{Face();}{default constructor.}
% ------------------------------------------------------------------------------

% ------------------------------------------------------------------------------
\ccOperations

\ccTagFullDeclarations
\ccMethod{Edge_handle sup(); const}
    {returns the sink of face \ccVar.}
\ccGlue
\ccMethod{Edge_handle inf(); const}
    {returns the source of face \ccVar.}
\ccGlue
\ccMethod{void set_sup(Vertex_handle v);}
    {sets the sink of face \ccVar\ to $v$ and sets the source face of $v$ to
    \ccVar.}
\ccGlue
\ccMethod{void set_inf(Vertex_handle v);}
    {sets the source of face \ccVar\ to $v$ and sets the sink face of $v$ to
    \ccVar.}
\ccGlue
\ccMethod{Edge_handle top_edge(); const}
    {returns the last edge on the left boundary of \ccVar\ that has been swept.
    If \ccVar\ belongs to the current antichain then this is the target node of the
    underlying upward directed graph of the antichain. }
\ccGlue
\ccMethod{Edge_handle bottom_edge(); const}
    {returns the last edge on the right boundary of \ccVar\ that has been swept. 
    If \ccVar\ belongs to the current antichain then this is the source node of the
    underlying upward directed graph of the antichain. }
\ccGlue
\ccMethod{void set_top_edge(Edge_handle e);}
    {sets $e$ as the last edge on the left boundary of \ccVar\ that has been
    swept.}
\ccGlue
\ccMethod{void set_bottom_edge(Edge_handle e);}
    {sets $e$ as the last edge on the right boundary of \ccVar\ that has been
    swept.}

\ccThree{Disk_handle}{ v.set_backward_edge( Disk_handle d) ;}{}
\ccMethod{Disk_handle backward_object(); const}
{returns a pointer to the disk in the backward view of the face \ccVar.}
\ccGlue
\ccMethod{Disk_handle forward_object(); const}
{returns a pointer to the disk in the forward view of the face \ccVar.}
\ccMethod{void set_backward_object(Disk_handle d);}
    {sets $d$ as the backward view of \ccVar.}
\ccGlue
\ccMethod{void set_forward_object(Disk_handle d);}
    {sets $d$ as the forward view of \ccVar.}
\ccTagDefaults
% ------------------------------------------------------------------------------

% ------------------------------------------------------------------------------
\ccHasModels

\ccRefIdfierPage{CGAL::Visibility_complex_face_base<Vc>}
% ------------------------------------------------------------------------------

% ------------------------------------------------------------------------------
\ccSeeAlso

\ccRefConceptPage{VisibilityComplex} \\
\ccRefConceptPage{VisibilityComplexItems}\\
\ccRefConceptPage{VisibilityComplexVertex}\\
\ccRefConceptPage{VisibilityComplexEdge}
% ------------------------------------------------------------------------------

% +----------------------------------------------------------------------------+
\ccTagDefaults
\end{ccRefConcept}
\ccRefPageEnd
% +----------------------------------------------------------------------------+
