% +------------------------------------------------------------------------+
% | Reference manual page: ConvexHullTraits_2.tex
% +------------------------------------------------------------------------+
% | 14.05.2001   Susan Hert and Stefan Schirra
% | Package: Convex_hull_2
% | 
% +------------------------------------------------------------------------+


\begin{ccRefConcept}{ConvexHullTraits_2}
\ccIndexTraitsClassRequirements[p]{convex hull, 2D}
\ccIndexTraitsClassRequirements[p]{extreme points, 2D}

\ccDefinition
  
All convex hull and extreme point algorithms provided in \cgal\ are
parameterized with a traits class \ccStyle{Traits}, which defines the
primitives (objects and predicates) that the convex hull algorithms use.
\ccRefName\ defines the complete set of primitives required in these
functions.  The specific subset of these primitives required by each function
is specified with each function.

\ccTypes
\ccAutoIndexingOff
\ccSetTwoColumns{ConvexHullTraits_2::Less_rotate_ccw_2}{}

\ccNestedType{Point_2}%
       {The point type on which the convex hull functions operate.}

\ccNestedType{Equal_2}%
       {Binary predicate object type comparing \ccc{Point_2}s.  Must provide 
        \ccc{bool operator()(Point_2 p, Point_2 q)} where \ccc{true}
        is returned iff $p ==_{xy} q$, false otherwise.
       }

\ccNestedType{Less_xy_2}%
       {Binary predicate object type comparing \ccc{Point_2}s
        lexicographically.  Must provide 
        \ccc{bool operator()(Point_2 p, Point_2 q)} where \ccc{true}
        is returned iff $p <_{xy} q$.
        We have $p<_{xy}q$, iff $p_x < q_x$ or $p_x = q_x$ and $p_y < q_y$,
        where $p_x$ and $p_y$ denote $x$ and $y$ coordinate of point $p$,
        respectively.
       }

\ccNestedType{Less_yx_2}%
       {Same as \ccc{Less_xy_2} with the roles of $x$ and $y$ interchanged.}

\ccNestedType{Left_turn_2}%
       {Predicate object type that must provide
        \ccc{bool operator()(Point_2 p,Point_2 q,Point_2 r)}, which
        returns \ccc{true} iff \ccc{r} lies to the left of the
        oriented line through \ccc{p} and \ccc{q}.}

\ccNestedType{Less_signed_distance_to_line_2}%
       {Predicate object type that must provide 
        \ccc{bool operator()(Point_2 p, Point_2 q, 
                             Point_2 r,Point_2 s)}, which returns \ccc{true} iff
        the signed distance from $r$ to the line $l_{pq}$ through $p$ and $q$
        is smaller than the distance from $s$ to $l_{pq}$. It is used to
        compute the point right of a line with maximum unsigned distance to
        the line. The predicate must provide a total order compatible
        with convexity, {\it i.e.}, for any line segment $s$ one of the 
        endpoints 
        of $s$ is the smallest point among the points on $s$, with respect to
        the order given by \ccc{Less_signed_distance_to_line_2}.}

\ccNestedType{Less_rotate_ccw_2}%
       {Predicate object type that must provide 
        \ccc{bool operator()(Point_2 e, Point_2 p,Point_2 q)},
        where \ccc{true} is returned iff a tangent at $e$ to the point set
        $\{e,p,q\}$ hits $p$ before $q$ when rotated counterclockwise around 
        $e$.
        Ties are broken such that the point with larger distance to $e$
        is smaller!}


\ccCreation
\ccCreationVariable{traits}  %% choose variable name

Only a copy constructor is required.

\ccConstructor{ConvexHullTraits_2(ConvexHullTraits_2& t);}{}

\ccOperations

The following member functions to create instances of the above predicate
object types must exist. 

\setlength\parskip{0mm}
\ccMemberFunction{Equal_2 equal_2_object(); }{}
\ccGlue
\ccMemberFunction{Less_xy_2 less_xy_2_object(); }{}
\ccGlue
\ccMemberFunction{Less_yx_2 less_yx_2_object(); }{}
\ccGlue
\ccMemberFunction{Less_signed_distance_to_line_2 less_signed_distance_to_line_2_object(); }{}
\ccGlue
\ccMemberFunction{Less_rotate_ccw_2 less_rotate_ccw_2_object( ); }{}
\ccGlue
\ccMemberFunction{Left_turn_2 left_turn_2_object(); }{}


\ccParDims
\ccHasModels

\ccRefIdfierPage{CGAL::Convex_hull_constructive_traits_2<R>} \\
\ccRefIdfierPage{CGAL::Convex_hull_traits_2<R>} \\
\ccRefIdfierPage{CGAL::Projection_traits_xy_3<K>}\\
\ccc{CGAL::Projection_traits_yz_3<K>}\\
\ccc{CGAL::Projection_traits_zx_3<K>}
\begin{ccDeprecated}
\ccRefIdfierPage{CGAL::Convex_hull_projective_xy_traits_2<Point_3>} \\
\ccRefIdfierPage{CGAL::Convex_hull_projective_xz_traits_2<Point_3>} \\
\ccRefIdfierPage{CGAL::Convex_hull_projective_yz_traits_2<Point_3>} \\
\end{ccDeprecated}
\ccAutoIndexingOn

\ccSeeAlso

\ccRefConceptPage{IsStronglyConvexTraits_3}

\ccParDims
\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

