% +------------------------------------------------------------------------+
% | Reference manual page: Regular_triangulation_traits_2.tex
% +------------------------------------------------------------------------+
% | 12.04.2000   Author
% | Package: Package
% | 
\RCSdef{\RCSRegulartriangulationtraitsRev}{$Revision$}
\RCSdefDate{\RCSRegulartriangulationtraitsDate}{$Date$}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefConcept}{Regular_triangulation_traits_2}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries

\ccDefinition
  
The concept \ccRefName\ fulfill the requirements of
concept \ccc{Triangulation_traits_2} 
described \ccRefPage{Triangulation_traits_2}
and additionally provides  a type
\ccc{Weitghed_point}  (which derives from the type \ccc{Point} 
and add a weight data member )
and the power tests for weighted points.
The traits must also provide the types 
\ccc{Ray} and \ccc{Line} to output the dual power diagram,
and also eventually a \ccc{Distance} type 
(analogue to the distance type defined in concept
\ccc{Delaunay_triangulation_traits_2}
to answer to lowest power query (localisation in the power diagram).


\ccTypes
\ccNestedType{Bare_point}
\ccGlue    
\ccNestedType{Weighted_point}
\ccGlue
\ccNestedType{Line}{}
\ccGlue
\ccNestedType{Ray}{}
\ccGlue
\ccNestedType{Direction}{}
\ccGlue
\ccNestedType{Distance} {NOT YET required.}
 

\ccCreation
\ccCreationVariable{traits}  %% choose variable name

\ccConstructor{Regular_triangulation_traits_2();}{default constructor.}

\ccPredicates
\ccMethod
{Oriented_side  power_test(const Weighted_point &p,
                           const Weighted_point &q,
                           const Weighted_point &r,
                           const Weighted_point &s);} 
{The two dimensional  power test.}
\ccMethod
{Oriented_side  power_test(const Weighted_point &p,
                           const Weighted_point &q,
                           const Weighted_point &r);}
{The degenerate one dimensional power test  for collinear
Weighted points.
\ccPrecond The points included in \ccc{p}, \ccc{q} 
and \ccc{r} are collinear.}

\ccOperations
\ccMethod{Rt power(Weighted_point wp, Weighted_point wq) const;}{Returns the power product
of \ccc{wp} \ and \ccc{wq}. This function is NOT YET required nor used.}


\ccHasModels

\ccc{CGAL::Regular_triangulation_traits_2<Rep>}


\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

