% +------------------------------------------------------------------------+
% | Reference manual page: ImplicitSurfaceTraits_3.tex
% +------------------------------------------------------------------------+
% | 18.01.2006   Laurent Rineau
% | Package: Surface_mesher
% | 
\RCSdef{\RCSImplicitSurfaceTraitsRev}{$Id$}
\RCSdefDate{\RCSImplicitSurfaceTraitsDate}{$Date$}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefConcept}{ImplicitSurfaceTraits_3}

\ccDefinition
  
The concept \ccRefName\  describes the requirements of the traits class to
be plugged  as \ccc{Traits} in \ccc{Implicit_surface_3<Traits, Function>}.
The concept provides the types, predicates and constructors objects
that are  used in the 
the partial specialisation  of 
the  surface mesher traits generator:
\ccc{Surface_mesh_traits_generator_3<Implicit_surface_3<Traits, Function> >}.




\ccTypes

\ccNestedType{FT}{The numerical type.}
\ccGlue
\ccNestedType{Point_3}{The point type. This point type must have a
  constructor \ccc{Point_3(FT, FT, FT)}.}
\ccGlue
\ccNestedType{Line_3}{The line type.}
\ccGlue
\ccNestedType{Ray_3}{The ray type.}
\ccGlue
\ccNestedType{Segment_3}{The segment type.}
\ccGlue
\ccNestedType{Vector_3}{The vector type.}
\ccGlue
\ccNestedType{Sphere_3}{The sphere type.}

\ccTwo{Construct_translated_point_3}{}

\ccNestedType{Compute_squared_distance_3}
{A predicate object that must provide the function operator\\
\ccc{FT operator()(Point_3, Point_3)} which return the squared distance
between two points.}

\ccNestedType{Compute_squared_radius_3}
{A predicate object that must provide the function operator\\
\ccc{FT operator()(const Sphere_3& s)} which returns the squared radius
of~\ccc{s}.}


\ccNestedType{Construct_center_3}
{A predicate object that must provide the function operator\\
\ccc{Point_3 operator()(const Sphere_3& s)} which computes the center of
the sphere~\ccc{s}.}

\ccNestedType{Construct_line_3}
{A predicate object that must provide the function operator\\
\ccc{Line_3 operator()(const Point_3 &p, const Point_3 &q)} which
returns a line  passing through the points \ccc{p} and~\ccc{q}.}

\ccNestedType{Construct_midpoint_3}
{A predicate object that must provide the function operator\\
\ccc{Point_3 operator()(const Point_3& p, const Point_3& q)} which computes
the midpoint of the segment \ccc{pq}.}

\ccNestedType{Construct_scaled_vector_3}
{A predicate object that must provide the function operator\\
\ccc{Vector_3 operator()(const Vector_3 &v, const FT& scale)} which returns
the vector \ccc{v} scaled by a factor \ccc{scale}.}

\ccNestedType{Construct_translated_point_3}
{A predicate object that must provide the function operator\\
\ccc{Point_3 operator()(const Point_3& p, const Vector_3& v)} which returns
the point obtained by translating \ccc{p} by the vector~\ccc{v}.}

\ccNestedType{Construct_vector_3}
{A predicate object that must provide the function operator\\
\ccc{Vector_3 operator()(const Point_3 &a, const Point_3 &b)} which returns
the vector \ccc{b-a}.}

\ccOperations

The following functions give access to the predicate and construction
objects:

\ccThree{onstruct_translated_point_3xxx}{construct_translated_point_3_object()x}{}
\ccCreationVariable{traits}

\ccMethod{Compute_squared_distance_3 compute_squared_distance_3_object();}{}
\ccMethod{Compute_squared_radius_3 compute_squared_radius_3_object();}{}
\ccMethod{Construct_center_3 construct_center_3_object();}{}
\ccMethod{Construct_line_3 construct_line_3_object();}{}
\ccMethod{Construct_midpoint_3 construct_midpoint_3_object();}{}
\ccMethod{Construct_scaled_vector_3 construct_scaled_vector_3_object();}{}
\ccMethod{Construct_translated_point_3 construct_translated_point_3_object();}{}
\ccMethod{Construct_vector_3 construct_vector_3_object();}{}


\ccHasModels

Any CGAL Kernel.

\ccSeeAlso

\ccc{Implicit_surface_3<Traits, Function>},\\
\ccc{make_surface_mesh}

\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

