\RCSdef{\RCSCandSSurfaceMeshCTRev}{$Id$}
\RCSdefDate{\RCSCandSSurfaceMeshCTDate}{$Date$}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefConcept}{PiecewiseSmoothSurfaceMeshComplex_2InTriangulation_3}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries

\ccDefinition
  
The concept \ccRefName\ describes a data structure
designed  to represent a  two dimensional pure complex 
embedded in a three dimensional triangulation. It refines the concept
\ccc{SurfaceMeshComplex_2InTriangulation_3} and adds a few requirements
needed to mesh piecewise smooth surfaces. In addition to the types and methods
of \ccc{SurfaceMeshComplex_2InTriangulation_3}, \ccRefName\ adds methods to mark
certain edges of the complex, and attach some information to marked edges.

\ccRefines
\ccc{SurfaceMeshComplex_2InTriangulation_3}

\ccTypes
\ccNestedType{Edge_info}{The type of info that can be attached to marked
  edges. That type must to have at least two members \ccc{is_cached} of
  type \ccc{bool} and \ccc{lineic_center} of type
  \ccc{Triangulation::Point_3} (\ccc{Triangulation} is defined in
  \ccc{SurfaceMeshComplex_2InTriangulation_3}).}

\ccCreationVariable{c2t3}  %% choose variable name

\ccHeading{Queries}

\ccMethod{bool is_marked(Edge e);}{Returns \ccc{true} iff the edge \ccc{e}
  is marked.}
\ccGlue
\ccMethod{bool is_marked(Cell_handle c, int i, int j);}{Returns \ccc{true}
  iff the edge \ccc{(c,i,j)} is marked.}

\ccMethod{size_type number_of_marked_edges() const;}
{Returns the number of marked edges of the 2D complex.}

\ccMethod{Edge_info get_info(Edge e);}
{Get info attached
to edge \ccc{e} in the 2D complex.
\ccPrecond Edge \ccc{e} has to be a marked edge.}
\ccGlue
\ccMethod{Edge_info get_info(Cell_handle c, int i, int j);}
{Get info attached
to edge \ccc{(c,i,j)} in the 2D complex.
\ccPrecond Edge \ccc{(c,i,j)} has a marked edge.}



\ccHeading{Modification}

\ccMethod{void remove_from_complex(Edge e);}{Removes edge \ccc{e} from the 2D
complex, if the edge is ISOLATED. It the edge \ccc{e} is a BOUNDARY,  
REGULAR or SINGULAR edge, does nothing.}
\ccGlue
\ccMethod{void remove_from_complex(Cell_handle c, int i, int j);}
{Removes edge
\ccc{(c,i,j)} from the 2D complex, if the edge is ISOLATED. It the edge
\ccc{(c,i,j)} is a BOUNDARY, REGULAR or SINGULAR edge, does nothing.}

\ccMethod{void mark(Edge e);}{Marks edge \ccc{e} of the 2D
complex. If \ccc{e} is not in the complex, inserts it.}
\ccGlue
\ccMethod{void mark(Cell_handle c, int i, int j);}
{Marks edge \ccc{(c,i,j)} of  the 2D complex. If \ccc{e} is not in the
  complex, inserts it.}
\ccGlue
\ccMethod{bool unmark(Edge e);}{Unmarks edge \ccc{e} of the 2D
complex (but do not remove it from the complex).
 Returns \ccc{true} iff \ccc{e} was marked.}
\ccGlue
\ccMethod{bool unmark(Cell_handle c, int i, int j);}
{Unmarks edge \ccc{(c,i,j)} of  the 2D complex (but do not remove it from
  the complex).
Returns \ccc{true} iff \ccc{e} was marked.}

\ccMethod{void set_info(Edge e, Edge_info ei);}
{Sets info attached to edge \ccc{e} in the 2D complex.
\ccPrecond Edge \ccc{e} has to be a marked edge.}
\ccGlue
\ccMethod{void set_info(Cell_handle c, int i, int j, Edge_info ei);}
{Sets info attached to edge \ccc{(c,i,j)} in the 2D complex.
\ccPrecond Edge \ccc{(c,i,j)} has to be a marked edge.}

\ccMethod{void mark(Edge e, Edge_info ei);}{Marks edge \ccc{e} of the 2D
complex. If \ccc{e} is not in the complex, inserts it. Then sets the info
attached to the edge \ccc{e}.}
\ccGlue
\ccMethod{void mark(Cell_handle c, int i, int j, Edge_info ei);}
{Marks edge \ccc{(c,i,j)} of  the 2D complex. If \ccc{e} is not in the
  complex, inserts it. Then sets the info attached to the edge \ccc{(c,i,j)}.}

\ccHasModels

\ccc{Surface_mesh_complex_2_in_triangulation_3<Tr, Edge_info>}, when
\ccc{Edge_info} has two data members \ccc{is_cached} of type \ccc{bool}
and \ccc{lineic_center} of type \ccc{Triangulation::Point_3}.


\ccSeeAlso

%\ccc{Complex_2InTriangulation\_3}, \\
%\ccc{PureComplex_2InTriangulation_3}\\
\ccc{make_curves_and_surface_mesh}.


\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

