% +------------------------------------------------------------------------+
% | Reference manual page: SurfaceMeshFacetsCriteria.tex
% +------------------------------------------------------------------------+
% | 02.12.2005   Mariette Yvinec, Laurent Rineau
% | Package: Surface_mesher
% | 
\RCSdef{\RCSSurfaceMeshFacetsCriteriaRev}{$Id$}
\RCSdefDate{\RCSSurfaceMeshFacetsCriteriaDate}{$Date$}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefConcept}{SurfaceMeshFacetsCriteria_3}

\ccDefinition
  
The Delaunay refinement process involved in  the 
function template \ccc{make_surface_mesh} 
is guided by a set of refinement criteria.
The concept \ccRefName\ describes the type  which
handles those criteria. 
It corresponds to the requirements for the template parameter
\ccc{FacetsCriteria} of the surface mesher function
\ccc{make_surface_mesh<SurfaceMeshC2T3,Surface,FacetsCriteria,Tag>}
%and the piecewise smooth mesher
%function \ccc{make_piecewise_smooth_surface_mesh<SurfaceMeshC2T3,Surface,
%  FacetsCriteria,EdgesCriteria,Tag>}
.

Typically the meshing criteria are a set
of elementary criteria, each of which
has to be met by  the facets of the final mesh.
The meshing algorithm eliminates in turn  {\em bad} facets, i.e.,
facets that do not meet all the criteria.

The size and quality of the final mesh 
depends on the order according to which bad facets
are handled. Therefore, the meshing algorithm 
needs to be able to quantify the facet qualities and to compare
the qualities of different faces.
The concept \ccRefName\ 
defines a type \ccc{Quality} designed to measure
the quality of a mesh facet. 
Typically this quality
is a multicomponent variable.  Each component corresponds to
one criterion and measures how much the facet deviates from
meeting this criterion. Then, the  comparison operator on qualities
is just a lexicographical comparison. The meshing algorithm handles facets
with lowest quality first. The qualities are computed by a function
\ccc{is_bad(Facet f, Quality& q)}.

\ccTypes

\ccNestedType{Facet}{The type of facets. This type has to match
the \ccc{Facet} type in  the triangulation type used  by 
the mesher function. (This triangulation type
is the type \ccc{SurfaceMeshC2T3::Triangulation} 
provided by the model of
\ccc{SurfaceMeshComplex_2InTriangulation_3} plugged 
 as first template parameter of
 \ccc{make_surface_mesh}).}

\ccNestedType{Quality}{Default constructible, copy constructible,
  assignable, and less-than comparable type.}

\ccOperations
\ccCreationVariable{criteria}

\ccMethod{bool is_bad (const Facet& f, Quality& q);}{Assigns the quality
  of the facet \ccc{f} to~\ccc{q}, and returns \ccc{true} is \ccc{f} does
  not meet the criteria.}

\ccHasModels

\ccc{Surface_mesh_default_criteria_3<Tr>}

\ccSeeAlso
\ccc{make_surface_mesh<SurfaceMeshC2T3,Surface,FacetsCriteria,Tag>}


\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

