\begin{ccRefConcept}{ConformingDelaunayTriangulationTraits_2}

\ccDefinition

The concept \ccRefName\ refines the concept
\ccc{ConstrainedDelaunayTriangulationTraits_2} by providing a numeric
field type \ccc{FT}, a type \ccc{Vector_2} and several constructors on
\ccc{Vector_2}, \ccc{Point_2}, and a predicate on angles.
The field type has to be a model of
the concept \ccc{SqrtFieldNumberType}. This field type and the
constructors are used by the conforming algorithm to compute Steiner
points on constrained edges.

\ccRefines

\ccc{DelaunayTriangulationTraits_2}

\ccTypes

\ccNestedType{FT}{The field type. It must be a model of
  \ccc{SqrtFieldNumberType}, that is must be a number type
  supporting the operations $+$, $-$, $*$, $/$, and $\sqrt{\cdot}$.}
\ccNestedType{Vector_2}{The vector type.}
\ccNestedType{Construct_vector_2}{Constructor object. Must
  provide the operator \ccc{Vector_2 operator()(Point a, Point b)}
  that computes the vector $b-a$.}
\ccNestedType{Construct_scaled_vector_2}{Constructor object. Must
  provide the operator \ccc{Vector_2 operator()(Vector_2 v, FT scale)}
  that computes the vector $scale \cdot \mathbf{v}$.}
\ccNestedType{Construct_translated_point_2}{Constructor object. Must
  provide the operator \ccc{Point_2 operator()(Point_2 p, Vector_2 v)}
  that computes the point $p + \mathbf{v}$.}
\ccNestedType{Construct_midpoint_2}{Constructor object. Must provide
  the operator \ccc{Point_2 operator()(Point_2 a, Point_2 b)} that
  computes the midpoint of the segment $ab$.}
\ccNestedType{Compute_squared_distance_2}{Constructor object. Must
  provide the operator \ccc{FT operator()(Point_2 a, Point_2 b)} that
  computes the squared distance between $a$ and $b$.}
\ccNestedType{Angle_2}{Predicate object. Must provide the operator
  \ccc{CGAL::Angle operator()(Point_2 p, Point_2 q, Point_2 r)} that
  returns OBTUSE, RIGHT or ACUTE depending on the angle formed by the three
  points p, q, r (q being the vertex of the angle).}

\ccCreationVariable{traits}

\ccHeading{Access to predicate and constructor objects}

\ccThree{Construct_translated_point_2xx}{construct_translated_point_2_object()}{}
\ccMethod{Construct_vector_2 construct_vector_2_object();}{}
\ccGlue
\ccMethod{Construct_scaled_vector_2 construct_scaled_vector_2_object();}{}
\ccGlue
\ccMethod{Construct_translated_point_2
  construct_translated_point_2_object();}{}
\ccGlue
\ccMethod{Constructor_midpoint_2 construct_midpoint_2_object();}{}
\ccGlue
\ccMethod{Compute_squared_distance_2
  compute_squared_distance_2_object();}{}
\ccGlue
\ccMethod{Angle_2 angle_2_object();}{}

\ccHasModels
Any model of \ccc{Kernel} concept. In particular, all \cgal\ kernels.

\end{ccRefConcept}

%%% For emacs/AucTeX:
%%% Local Variables: ***
%%% mode:latex ***
%%% TeX-master: "../Mesh_2.tex"  ***
%%% End: ***
