% +------------------------------------------------------------------------+
% | Reference manual page: HalfedgeDSItems.tex
% +------------------------------------------------------------------------+
% | 22.03.1999   Lutz Kettner
% | Package: HalfedgeDS
% | 
\RCSdef{\RCSHalfedgeDSItemsRev}{$Id$}
\RCSdefDate{\RCSHalfedgeDSItemsDate}{$Date$}
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefConcept}{HalfedgeDSItems}

\ccDefinition
  
The concept \ccRefName\ wraps the four item types -- vertex,
halfedge, face {\bf\ttfamily and ccb}-- for a halfedge data structure.
A \ccRefName\ contains four member class templates named \ccc{Vertex_wrapper},
\ccc{Halfedge_wrapper}, \ccc{Face_wrapper}, {\bf\ttfamily and \ccc{Ccb_wrapper}}
, each with two template parameters, \ccc{Refs} and \ccc{Traits}.
\ccc{Refs} requires an
instantiated halfedge data structure \ccc{HalfedgeDS} as argument,
\ccc{Traits} is a geometric traits class supplied by the class that
uses the halfedge data structure as internal representation. \ccc{Traits}
is not used by the halfedge data structure itself. These four member 
class templates provide a local type named \ccc{Vertex}, \ccc{Halfedge},
, \ccc{Face} {\bf\ttfamily and \ccc{Ccb}} respectively.
The requirements on these
types are described on page~\pageref{pageHalfedgeDSItemsVertexRef},
page~\pageref{pageHalfedgeDSItemsHalfedgeRef}, 
page~\pageref{pageHalfedgeDSItemsFaceRef},
and page~\pageref{pageHalfedgeDSItemsCcbRef} respectively.

\ccTypes
\ccTwo{HalfedgeDSItems:: Halfedge_wrapper<Refs,Traits>::HalfedgeM}{}

\ccNestedType{Vertex_wrapper<Refs,Traits>::Vertex}
    {model of \ccc{HalfedgeDSVertex}.}
\ccGlue
\ccNestedType{Halfedge_wrapper<Refs,Traits>::Halfedge}
    {model of \ccc{HalfedgeDSHalfedge}.}
\ccGlue
\ccNestedType{Face_wrapper<Refs,Traits>::Face}
    {model of \ccc{HalfedgeDSFace}.}
\ccGlue
\ccNestedType{\bf\ttfamily Ccb_wrapper<Refs,Traits>::Ccb}
    {\bf\ttfamily model of \ccc{HalfedgeDSCcb}.}

\ccHasModels

\ccRefIdfierPage{CGAL::HalfedgeDS_min_items}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_items_2}\\
\ccRefIdfierPage{CGAL::Polyhedron_items_3}

\ccSeeAlso

\ccRefConceptPage{HalfedgeDS<Traits,Items,Alloc>}\\
\ccRefConceptPage{HalfedgeDSVertex}\\
\ccRefConceptPage{HalfedgeDSHalfedge}\\
\ccRefConceptPage{HalfedgeDSFace}\\
\ccRefConceptPage{HalfedgeDSCcb}\\
\ccRefConceptPage{PolyhedronItems_3}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_vertex_base<Refs>}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_halfedge_base<Refs>}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_face_base<Refs>}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_ccb_base<Refs>}

\ccExample

The following example shows the canonical implementation of the
\ccc{CGAL::HalfedgeDS_min_items} class. It uses the base classes for the
item types that are provided in the library.

\begin{ccExampleCode}
struct HalfedgeDS_min_items {
    template < class Refs, class Traits>
    struct Vertex_wrapper {
        typedef CGAL::HalfedgeDS_vertex_min_base< Refs>   Vertex;
    };
    template < class Refs, class Traits>
    struct Halfedge_wrapper {
        typedef CGAL::HalfedgeDS_halfedge_min_base< Refs> Halfedge;
    };
    template < class Refs, class Traits>
    struct Face_wrapper {
        typedef CGAL::HalfedgeDS_face_min_base< Refs>     Face;
    };
    template < class Refs, class Traits>
    struct Ccb_wrapper {
        typedef CGAL::HalfedgeDS_ccb_min_base< Refs>     Ccb;
    };
};
\end{ccExampleCode}

See page~\pageref{pageHalfedgeDSitemsRef} for an example implementation 
of the \ccc{CGAL::HalfedgeDS_items_2} class.

\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+

