% +------------------------------------------------------------------------+
% | Reference manual page: HalfedgeDS_face_base.tex
% +------------------------------------------------------------------------+
% | 22.03.1999   Lutz Kettner
% | Package: HalfedgeDS
% | 
\RCSdef{\RCSHalfedgeDSfacebaseRev}{$Id$}
\RCSdefDate{\RCSHalfedgeDSfacebaseDate}{$Date$}
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefClass}{HalfedgeDS_face_base<Refs>}
  
\ccDefinition
  
The class \ccRefName\ is a model of the \ccc{HalfedgeDSFace}
concept. \ccc{Refs} is an instantiation of a \ccc{HalfedgeDS}.  The
template declaration of \ccRefName\ has {\XHDS four} parameters with some
defaults that allow to select various flavors of faces. 

{\XHDS

\begin{tabbing}
\mbox{}~~~~~~ \= \ccc{template <} \=\ccc{class Refs,}\\
              \> \>\ccc{class Tag_halfedge      } \mbox{}~~~ \=\ccc{= CGAL::Tag_true,}\\
              \> \>\ccc{class Tag_plane         } \>\ccc{= CGAL::Tag_false,}\\
              \> \>\ccc{class Tag_halfedge_cycle} \>\ccc{= CGAL::Tag_true}\\
     \> \ccc{class HalfedgeDS_face_base;}
\end{tabbing}

If \ccc{Tag_halfedge} $\equiv$ \ccc{CGAL::Tag_true} a reference to the incident halfedge is supported.

If \ccc{Tag_plane} $\neq$ \ccc{CGAL::Tag_false} a plane object is supported (and the type \ccc{Tag_plane} corresponds to the type of the plane object).

If \ccc{Tag_halfedge_cycle} $\equiv$ \ccc{CGAL::Tag_true} halfedge cycles are supported.


Faces may be bounded by one or multiple halfedge cycles and a face object can optionally store the bounding cycle in one of two mutually exclusive ways: 

Directly storing the incident halfedge (when faces support only one outer halfedge cycle), configuration selected
with \ccc{Tag_halfedge} $\equiv$ \ccc{CGAL::Tag_true}

or

Storing iterator pairs defining the sequences of outer and inner halfedge cycles that bound the face.
With \ccc{Tag_halfedge_cycle} $\equiv$ \ccc{CGAL::Tag_true}



The choice between storing just one halfedge or \ccc{halfedge_cycle} sequences is made by the combination 
of the two type tags \ccc{Tag_halfedge} and \ccc{Tag_halfedge_cycle}. These are mutually
exclusive and only one can be \ccc{CGAL::Tag_true}.

}

\ccInclude{CGAL/HalfedgeDS_face_base.h}

\ccIsModel

\ccRefConceptPage{HalfedgeDSFace}

\ccTypes
\ccThree{const Plane&;;}{plane() const;MMMMMMMMMMMM}{}
\ccThreeToTwo

\ccNestedType{Plane}{plane type for three argument version.}


% No longer required.
%\ccTypedef{typedef Traits::Plane_3 Plane_3;}
%    {plane equation type for three argument version.}
%\ccGlue
%\ccTypedef{typedef Traits::Vector_3 Vector_3;}
%    {normal vector of plane equation.}

\ccCreation
\ccCreationVariable{f}

\ccConstructor{HalfedgeDS_face_base();}{default constructor.}
\ccGlue
\ccConstructor{HalfedgeDS_face_base( const Plane& pln);}
    {initialized with plane \ccc{pln}.}

\ccOperations

\ccTagFullDeclarations
\ccMethod{Plane&                plane();}{}
\ccGlue
\ccMethod{const Plane&          plane() const;}{}
\ccTagDefaults

% No longer required.
%\ccTagFullDeclarations
%\ccMethod{Plane&                plane();}{}
%\ccGlue
%\ccMethod{const Plane&          plane() const;}{}
%\ccGlue
%\ccMethod{Normal                normal() const;}{}
%\ccTagDefaults

\ccSeeAlso

\ccRefConceptPage{HalfedgeDS<Traits,Items,Alloc>}\\
\ccRefConceptPage{HalfedgeDSItems}\\
\ccRefConceptPage{PolyhedronItems_3}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_items_2}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_vertex_base<Refs>}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_halfedge_base<Refs>}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_halfedge_cycle_base<Refs>}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_face_min_base<Refs>}

\end{ccRefClass}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+

