% +------------------------------------------------------------------------+
% | Reference manual page: HalfedgeDS_halfedge_base.tex
% +------------------------------------------------------------------------+
% | 22.03.1999   Lutz Kettner
% | Package: HalfedgeDS
% | 
\RCSdef{\RCSHalfedgeDShalfedgebaseRev}{$Id$}
\RCSdefDate{\RCSHalfedgeDShalfedgebaseDate}{$Date$}
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefClass}{HalfedgeDS_halfedge_base<Refs>}

\ccDefinition
  
The class \ccRefName\ is a model of the \ccc{HalfedgeDSHalfedge}
concept. \ccc{Refs} is an instantiation of a \ccc{HalfedgeDS}. 
The full declaration states four template parameters:

\begin{tabbing}
\mbox{}~~~~~~ \= \ccc{template <} \=\ccc{class Refs,}\\
              \> \>\ccc{class Tag_prev   } \=\ccc{= CGAL::Tag_true,}\\
              \> \>\ccc{class Tag_vertex } \>\ccc{= CGAL::Tag_true,}\\
              \> \>\ccc{class Tag_face   } \>\ccc{= CGAL::Tag_true,}\\
              \> \>\ccc{class Tag_ccb} \>\ccc{= CGAL::Tag_false}\\
     \> \ccc{class HalfedgeDS_halfedge_base;}
\end{tabbing}

If \ccc{Tag_prev} $\equiv$ \ccc{CGAL::Tag_true} a reference to the previous
halfedge is supported.

If \ccc{Tag_vertex} $\equiv$ \ccc{CGAL::Tag_true} an incident vertex is
supported.

If \ccc{Tag_face} $\equiv$ \ccc{CGAL::Tag_true} an incident face is
supported.

{\bf\ttfamily If \ccc{Tag_ccb} $\equiv$ \ccc{CGAL::Tag_true} a host ccb is
supported.}

{\bf\ttfamily
The incidence relation between a halfedge and a face can be stored in a halfedge in 
one of two mutually exclusive ways: directly storing the incident face or
storing the ccb common to the halfedge and the face.

Since multiple ccbs were introduced in \cgal\ version 3.4, to keep backward compatibility,
the choice between those methods is selected by the combination 
of the two type tags \ccc{Tag_face} and \ccc{Tag_ccb}.
These are mutually exclusive and only one can be \ccc{CGAL::Tag_true}.
}

In all cases, a reference to the next halfedge and to the opposite
halfedge is supported.

\ccInclude{CGAL/HalfedgeDS_halfedge_base.h}

\ccIsModel

\ccRefConceptPage{HalfedgeDSHalfedge}

\ccCreation
\ccCreationVariable{h}

\ccConstructor{HalfedgeDS_halfedge_base();}{default constructor.}

\ccSeeAlso

\ccRefConceptPage{HalfedgeDS<Traits,Items,Alloc>}\\
\ccRefConceptPage{HalfedgeDSItems}\\
\ccRefConceptPage{PolyhedronItems_3}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_items_2}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_vertex_base<Refs>}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_face_base<Refs>}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_ccb_base<Refs>}\\
\ccRefIdfierPage{CGAL::HalfedgeDS_halfedge_min_base<Refs>}

\end{ccRefClass}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+

