%% Copyright (c) 2004  SciSoft.  All rights reserved.
%%
%% This file is part of CGAL (www.cgal.org); you may redistribute it under
%% the terms of the Q Public License version 1.0.
%% See the file LICENSE.QPL distributed with CGAL.
%%
%% Licensees holding a valid commercial license may use this file in
%% accordance with the commercial license agreement provided with the software.
%%
%% This file is provided AS IS with NO WARRANTY OF ANY KIND, INCLUDING THE
%% WARRANTY OF DESIGN, MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE.
%%
%% 
%%
%% Author(s)     : Fernando Cacciola <fernando_cacciola@hotmail.com>

\begin{ccRefConcept}{GetCost}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries

\ccCreationVariable{gc}  %% choose variable name
\ccDefinition

The concept \ccRefName\ describes the requirements for the {\em policy function object} which gets the {\em collapse cost} of an edge.

The cost returned is a \ccc{boost::optional} value (i.e. it can be absent). An {\em absent} cost could be the result of a computational limitation (such as overflow), or can be intentionally returned to prevent the edge from being collapsed.

A model of this concept can simply return the cost stored in the
passed cache object, if any, or perform the actual computation.

\ccRefines
\ccc{DefaultConstructible}\\
\ccc{CopyConstructible}

\ccTypes
  \ccNestedType{ECM}{The type of the surface to simplify.
   Must be a model of the \ccc{EdgeCollapsableMesh} concept.}{}
\ccGlue    
  \ccNestedType{Params}{The type of the model-specific parameters needed. Can be \ccc{void}.}{}
\ccGlue    
  \ccNestedType{FT}{A field type representing the collapse cost}{}
\ccGlue    
  \ccTypedef{typename boost::graph_traits<ECM>::edge_descriptor edge_descriptor;}
  {A {\sc Bgl} edge descriptor representing an edge of the surface.}
\ccGlue    
  \ccTypedef{boost::optional<FT> result_type;}{The type of the result (an optional cost value).}

\ccCreation
\ccCreationVariable{gc}  %% choose variable name

\ccConstructor{GetCost();}{Default constructor} 

\ccOperations

  \ccMethod{template<class Cache>
            result_type operator()( edge_descriptor const& edge
                                  , ECM&                   surface 
                                  , Cache const&           cache
                                  , Params const*          params
                                  ) const;
           }
  {Computes and returns the cost of collapsing \ccc{edge} using the model-specific \ccc{params}.\\
   \ccc{edge} is required to be in the \ccc{surface}.\\
   If \ccc{Cache} is a model of \ccc{CostCache} or \ccc{CostAndPlacementCache},
   which means that \ccc{cache} stores the cost, a model of this \ccc{GetCost} concept
   can simply return the cached cost (but is not required to do so).\\
   \ccc{params} can be a \ccStyle{NULL} pointer.
  }
  
\ccHasModels
\ccRefIdfierPage{CGAL::Surface_mesh_simplification::Cached_cost<ECM>}.
\ccRefIdfierPage{CGAL::Surface_mesh_simplification::Edge_length_cost<ECM>}.
\ccRefIdfierPage{CGAL::Surface_mesh_simplification::LindstromTurk_cost<ECM>}.

\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+
