%% Copyright (c) 2004  SciSoft.  All rights reserved.
%%
%% This file is part of CGAL (www.cgal.org); you may redistribute it under
%% the terms of the Q Public License version 1.0.
%% See the file LICENSE.QPL distributed with CGAL.
%%
%% Licensees holding a valid commercial license may use this file in
%% accordance with the commercial license agreement provided with the software.
%%
%% This file is provided AS IS with NO WARRANTY OF ANY KIND, INCLUDING THE
%% WARRANTY OF DESIGN, MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE.
%%
%% 
%%
%% Author(s)     : Fernando Cacciola <fernando_cacciola@hotmail.com>

\begin{ccRefConcept}{GetPlacement}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries

\ccDefinition

The concept \ccRefName\ describes the requirements for the {\em policy function object} which gets the {\em collapse placement} of an edge; that is, the position of the vertex that replaces the edge after the collapse.

The placement returned is an \ccc{boost::optional} value (i.e. it can be absent). An {\em absent} placement could be the result of a computational limitation (such as overflow), or can be intentionally returned to prevent the edge from being collapsed.

A model of this concept can simply return the placement stored in the passed collapse data, if any, or perform the actual computation.

\ccRefines
\ccc{DefaultConstructible}
\ccc{CopyConstructible}

\ccTypes
  \ccNestedType{TSM}{The type of the surface to simplify. Must be a model of the \ccc{TSM} concept.}{}
\ccGlue    
  \ccNestedType{Params}{The type of the model-specific parameters needed. Can be \ccc{void}.}{}
\ccGlue    
  \ccTypedef{typename Surface_geometric_traits<TSM>::Point Point;}{The Point type for the surface vertex.}
\ccGlue    
  \ccTypedef{typename boost::graph_traits<TSM>::edge_descriptor edge_descriptor;}{A BGL \ccc{EdgeDescriptor} representing an {\em undirected edge} of the surface.}
\ccGlue    
  \ccTypedef{boost::optional<Point> result_type;}{The type of the result (an optional point)}

\ccCreation
\ccCreationVariable{gp}  %% choose variable name

\ccConstructor{GetCost();}{Default constructor}

\ccOperations

  \ccMethod{template<class Collapse_data>
            result_type operator()( edge_descriptor const& edge
                                  , TSM&                   surface 
                                  , Collapse_data const&   data
                                  , Params const*          params
                                  ) const;
           }
  {Computes and returns the placement, that is, the position of the vertex which replaces the collapsing \ccc{edge},
   using the model-specific \ccc{params}.\\
   \ccc{edge} is required to be in the \ccc{surface}.\\
   The generic type \ccc{Collapse_data} must be a model of the \ccc{CollapseData} meta concept.\\
   If \ccc{Collapse_data} is a model of \ccc{FullCollapseData}, which means that
   \ccc{data} stores a cache of the placement, a model can simply return the placement cached
   in \ccc{data} (but is not required to do so).\\
   \ccc{params} can be a \ccc{NULL} pointer.
  }
  
\ccHasModels
\ccRefIdfierPage{CGAL::Triangulated_surface_mesh::Simplification::Edge_collapse::Cached_cost<TSM>}.
\ccRefIdfierPage{CGAL::Triangulated_surface_mesh::Simplification::Edge_collapse::Edge_length_cost<TSM>}.
\ccRefIdfierPage{CGAL::Triangulated_surface_mesh::Simplification::Edge_collapse::LindstromTurk_cost<TSM>}.

\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+
