%% Copyright (c) 2004  SciSoft.  All rights reserved.
%%
%% This file is part of CGAL (www.cgal.org); you may redistribute it under
%% the terms of the Q Public License version 1.0.
%% See the file LICENSE.QPL distributed with CGAL.
%%
%% Licensees holding a valid commercial license may use this file in
%% accordance with the commercial license agreement provided with the software.
%%
%% This file is provided AS IS with NO WARRANTY OF ANY KIND, INCLUDING THE
%% WARRANTY OF DESIGN, MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE.
%%
%% 
%%
%% Author(s)     : Fernando Cacciola <fernando_cacciola@hotmail.com>


\begin{ccRefClass}{Surface_mesh_simplification::Set_partial_collapse_data<TSM,GetCost>}

%% add template arg's if necessary

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[class]{} %% add further index entries
\ccDefinition

The class \ccRefName\ provides a model for the \ccc{SetCollpaseData}
where the \ccc{CollapseData} it assigns is
\ccc{Partial_collapse_data<TSM>}.\\ The class \ccRefName\ has two
template arguments: The first is the type of surface being simplified
and must be a model of the \ccc{TriangulatedSurfaceMesh} concept. The
second is the policy which actually computes the cached cost and must
be a model of the \ccc{GetCost} concept.

\ccIsModel
\ccc{SetCollapseData}

\ccInclude{CGAL/Surface_mesh_simplification/Policies/Edge_collapse/Set_partial_collapse_data.h}

\ccTypes
  \ccTypedef{TSM TSM;}{The type of the surface to simplify.}
  \ccGlue
  \ccTypedef{boost::graph_traits<TSM>::edge_descriptor edge_descriptor;}{A {\sc Bgl} edge descriptor representing an {\em undirected edge} of the surface.}
  \ccGlue
  \ccTypedef{Partial_collapse_data<TSM> Collapse_data;}{A type of collapse data which caches only the cost.}
  \ccGlue
  \ccTypedef{typename GetCost::Params Cost_params;}{The type of the parameters to the \ccc{GetCost} policy. It must be \ccc{DefaultConstructible} so it cannot be \ccc{void}.}
  \ccGlue
  \ccTypedef{void Placement_params;}{The type of the unused parameters to the non-existing placement subfunction.}

\ccCreation
\ccCreationVariable{sd}  %% choose variable name

\ccConstructor{Set_partial_collapse_data<TSM,GetCost>( GetCost const& get_cost); }
{Initializes an instance storing a const reference to the \ccc{get_cost} policy which is used to actually compute the cost.}

\ccOperations

\ccMethod
  {void operator()( Collapse_data& data
                  , edge_descriptor const& edge
                  , TSM& surface
                  , CostParams const* cparams
                  , PlacementParam const* pparams
                  );
  }
{Calls \ccc{GetCost(edge,surface,data,cparams)} to obtain the actual collapse cost \ccc{c}. Then constructs a \ccc{Partial_collapse_data<TSM>(c)} and assigns it to \ccc{data}.
}  


\ccSeeAlso
\ccc{CGAL::Surface_mesh_simplification::Set_empty_collapse_data<TSM,GetCost>}\\
\ccc{CGAL::Surface_mesh_simplification::Set_full_collapse_data<TSM,GetCost,GetPlacement>}\\
\ccc{CGAL::Surface_mesh_simplification::Set_partial_collapse_data_LindstromTurk<TSM>}\\
\ccc{CGAL::Surface_mesh_simplification::Set_full_collapse_data_LindstromTurk<TSM>}

\end{ccRefClass}


% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

