%% Copyright (c) 2004  SciSoft.  All rights reserved.
%%
%% This file is part of CGAL (www.cgal.org); you may redistribute it under
%% the terms of the Q Public License version 1.0.
%% See the file LICENSE.QPL distributed with CGAL.
%%
%% Licensees holding a valid commercial license may use this file in
%% accordance with the commercial license agreement provided with the software.
%%
%% This file is provided AS IS with NO WARRANTY OF ANY KIND, INCLUDING THE
%% WARRANTY OF DESIGN, MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE.
%%
%% 
%%
%% Author(s)     : Fernando Cacciola <fernando_cacciola@hotmail.com>


\begin{ccRefClass}{Surface_mesh_simplification::Set_full_collapse_data<TSM,GetCost,GetPlacement>}

%% add template arg's if necessary

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[class]{} %% add further index entries
\ccDefinition

The class \ccRefName\ provides a model for the
\ccc{SetCollpaseData} where the \ccc{CollapseData} it assigns is \ccc{Full\_collapse\_data<TSM>}.\\
The class \ccRefName\ has three template arguments: The first is the type of surface being simplified 
and must be a model of the \ccc{TriangulatedSurfaceMesh} concept. The second is the policy which actually computes the cached
cost and must be a model of the \ccc{GetCost} concept. The third is the policy computing the placement
and must be a model of \ccc{GetPlacement}.

\ccIsModel
\ccc{SetCollapseData}

\ccInclude{CGAL/Surface_mesh_simplification/Policies/Edge_collapse/Set_partial_collapse_data.h}

\ccTypes
  \ccTypedef{TSM TSM;}{The type of the surface to simplify.}
  \ccGlue
  \ccTypedef{boost::graph_traits<TSM>::edge_descriptor edge_descriptor;}{A {\sc Bgl} edge descriptor
            representing an {\em undirected edge} of the surface.
            }
  \ccGlue
  \ccTypedef{Full_collapse_data<TSM> Collapse_data;}
  {A type of collapse data which caches both the cost and placement.}
  \ccGlue
  \ccTypedef{typename GetCost::Params Cost_params;}
  {The type of the parameters to the \ccc{GetCost} policy.
  It must be \ccc{DefaultConstructible} so it cannot be \ccc{void}.
  }
  \ccGlue
  \ccTypedef{typename GetPlacement::Params Placement_params;}{The type of the parameters to the 
             \ccc{GetPlacement} policy. It must be \ccc{DefaultConstructible} so it cannot be \ccc{void}.
            } 
            
\ccCreation
\ccCreationVariable{sd}  %% choose variable name

\ccConstructor{Set_full_collapse_data<TSM,GetCost,GetPlacement>( GetCost const& get_cost, GetPlacement const& get_placemet); }
{Initializes an instance storing a const reference to the \ccc{get_cost} and \ccc{get_placement} policies which are used to actually compute the cost and placement.}

\ccOperations

\ccMethod
  {void operator()( Collapse_data& data
                  , edge_descriptor const& edge
                  , TSM& surface
                  , CostParams const* cparams
                  , PlacementParam const* pparams
                  );
  }
{Calls \ccc{GetCost(edge,surface,data,cparams)} to obtain the actual cost \ccc{c}, and \ccc{GetPlacement(edge,surface,data,pparams)} to obtain the actual placement \ccc{p}. Then constructs a \ccc{Full_collapse_data<TSM>(c,p)} and assigns it to \ccc{data}.
}  


\ccSeeAlso
\ccc{CGAL::Surface_mesh_simplification::Set_empty_collapse_data<TSM,GetCost>}\\
\ccc{CGAL::Surface_mesh_simplification::Set_partial_collapse_data<TSM,GetCost,GetPlacement>}\\
\ccc{CGAL::Surface_mesh_simplification::Set_partial_collapse_data_LindstromTurk<TSM>}\\
\ccc{CGAL::Surface_mesh_simplification::Set_full_collapse_data_LindstromTurk<TSM>}

\end{ccRefClass}


% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

