%% Copyright (c) 2006  SciSoft.  All rights reserved.
%%
%% This file is part of CGAL (www.cgal.org); you may redistribute it under
%% the terms of the Q Public License version 1.0.
%% See the file LICENSE.QPL distributed with CGAL.
%%
%% Licensees holding a valid commercial license may use this file in
%% accordance with the commercial license agreement provided with the software.
%%
%% This file is provided AS IS with NO WARRANTY OF ANY KIND, INCLUDING THE
%% WARRANTY OF DESIGN, MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE.
%%
%% 
%%
%% Author(s)     : Fernando Cacciola <fernando_cacciola@hotmail.com>

\begin{ccRefConcept}{SetCollapseData}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries


\ccDefinition

The concept \ccRefName\ describes the requirements for the {\em policy function object} which assigns the {\em collapse data} of an edge.


\ccTypes
  \ccNestedType{TSM}{The type of the surface to simplify. Must be a model of the \ccc{TriangulatedSurfaceMesh} concept.}{}
  \ccGlue
  \ccTypedef{boost::graph_traits<TSM>::edge_descriptor edge_descriptor;}{A {\sc Bgl} edge descriptor representing an undirected edge of the surface.}{}
  \ccGlue
  \ccNestedType{Collapse_data}{The concrete type of collapse data being assigned by this policy.}{}
  \ccGlue
  \ccNestedType{Cost_params}{The type of the parameters to the cost subfunction. Can be \ccc{void}.}{}
  \ccGlue
  \ccNestedType{Placement_params}{The type of the parameters to the placement subfunction. Can be \ccc{void}.}{}

\ccOperations

\ccMethod
  {void operator()( Collapse_data& data
                  , edge_descriptor const& edge
                  , TSM& surface
                  , CostParams const* cparams
                  , PlacementParam const* pparams
                  );
  }
{Assigns a \ccc{Collapse_data} object to \ccc{data}.\\
If \ccc{Collapse_data} is a model of \ccc{FullCollapseData}, the object assigned holds {\em cost} and {\em placement} values computed
for the given \ccc{edge} using the model-specific parameters \ccc{cparams} and \ccc{pparams}.\\
If \ccc{Collapse_data} is a model of \ccc{PartialCollapseData}, the object assigned holds only the {\em cost}, computed 
 using \ccc{cparams}. \ccc{pparams} is ignored and can be a null pointer.\\
If \ccc{Collapse_data} is a model of \ccc{EmptyCollapseData}, the objects assigned is a default constructed empty objects holding no values. In this case, only the \ccc{data} argument is used and the cost/placement 
\ccc{params} can be null pointers.\\
\ccc{edge} is required to belong to the \ccc{surface}.\\
The concrete model specifies whether \ccc{cparams} or \ccc{pparams}, when not ignored, can be null pointers.
}  

\ccHasModels
\ccRefIdfierPage{CGAL::Triangulated_surface_mesh::Simplification::Edge_collapse::Set_empty_collapse_data<TSM>}\\
\ccRefIdfierPage{CGAL::Triangulated_surface_mesh::Simplification::Edge_collapse::Set_partial_collapse_data<TSM,GetCost>}\\
\ccRefIdfierPage{CGAL::Triangulated_surface_mesh::Simplification::Edge_collapse::Set_full_collapse_data<TSM,GetCost,GetPlacement>}\\

\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+
