%% Copyright (c) 2006  SciSoft.  All rights reserved.
%%
%% This file is part of CGAL (www.cgal.org); you may redistribute it under
%% the terms of the Q Public License version 1.0.
%% See the file LICENSE.QPL distributed with CGAL.
%%
%% Licensees holding a valid commercial license may use this file in
%% accordance with the commercial license agreement provided with the software.
%%
%% This file is provided AS IS with NO WARRANTY OF ANY KIND, INCLUDING THE
%% WARRANTY OF DESIGN, MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE.
%%
%% 
%%
%% Author(s)     : Fernando Cacciola <fernando_cacciola@hotmail.com>

\begin{ccRefConcept}{SetCache}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries


\ccDefinition

The concept \ccRefName\ describes the requirements for the {\em policy function object} which assigns the the cache object associated to each edge.


\ccTypes
  \ccNestedType{ECM}{The type of the surface to simplify.
  Must be a model of the \ccc{EdgeCollapsableMesh} concept.}{}
  \ccGlue
  \ccTypedef{boost::graph_traits<ECM>::edge_descriptor edge_descriptor;}
  {A {\sc Bgl} edge descriptor representing an edge of the surface.}{}
  \ccGlue
  \ccNestedType{Cache}{The concrete type of cache record being assigned by this policy.}{}
  \ccGlue
  \ccNestedType{Cost_params}{The type of the parameters to the cost subfunction.
  Can be \ccc{void}.}{}
  \ccGlue
  \ccNestedType{Placement_params}{The type of the parameters to the placement subfunction.
   Can be \ccc{void}.}{}

\ccOperations

\ccMethod
  {void operator()( Cache&                 cache
                  , edge_descriptor const& edge
                  , ECM&                   surface
                  , CostParams const*      cparams
                  , PlacementParam const*  pparams
                  );
  }
{Assigns a \ccc{Cache} object to \ccc{cache}.\\
If \ccc{Cache} is a model of \ccc{CostAndPlacementCache}, \ccc{cache}
holds {\em cost} and {\em placement} values precomputed for the given 
\ccc{edge} using the model-specific parameters \ccc{cparams} and \ccc{pparams}.\\
If \ccc{Cache} is a model of \ccc{CostCache}, \ccc{cache} holds only 
the {\em cost} precomputed using \ccc{cparams}. \ccc{pparams} is ignored
and can be a null pointer.\\
If \ccc{Cache} is a model of \ccc{NoCache}, \ccc{cache} is an
default-constructed empty struct holding no values. In this case, 
only the \ccc{cache} argument is used and the cost/placement 
\ccc{params} can be null pointers.\\
\ccc{edge} is required to belong to the \ccc{surface}.
}  

\ccHasModels
\ccRefIdfierPage{CGAL::Surface_mesh_simplification::Set_no_cache<ECM>}\\
\ccRefIdfierPage{CGAL::Surface_mesh_simplification::Set_cost_cache<ECM,GetCost>}\\
\ccRefIdfierPage{CGAL::Surface_mesh_simplification::Set_cost_and_placement<ECM,GetCost,GetPlacement>}\\

\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+
