\begin{ccRefFunction}{convex_hull_3}
\ccIndexMainItemBegin{convex hull, 3D}
\ccIndexMainItemBegin{quickhull, 3D}
\ccIndexSubitemBegin{convex hull, 3D}{quickhull}

\ccDefinition

The function \ccRefName\ computes the convex hull of a given set of 
three-dimensional points 
Two versions of this function 
are available.  The first can be used when it is known that the result
will be a polyhedron and the second when a degenerate hull
may also be possible.

\ccInclude{CGAL/convex_hull_3.h}

\ccFunction{
template <class InputIterator, class Polyhedron_3, class Traits>
void convex_hull_3(InputIterator first, InputIterator last,
                    Polyhedron_3& P,
                    const Traits& ch_traits = Default_traits);
}
{
computes the convex hull of the set of points in the range
[\ccc{first}, \ccc{last}).  The polyhedron \ccc{P} is cleared, then
the convex hull is stored in \ccc{P} 
and the plane equations of each face are computed.
\ccPrecond: There are at least four points in the range 
[\ccc{first}, \ccc{last}) not all of which are collinear.
}

\ccFunction{
template <class InputIterator, class Traits>
void convex_hull_3(InputIterator first, InputIterator last,
                    Object& ch_object,
                    const Traits& ch_traits = Default_traits);
}
{
computes the convex hull of the set of points in the range
[\ccc{first}, \ccc{last}).  The result, which may be a point, a segment,
a triangle, or a polyhedron, is stored in \ccc{ch_object}.  When
the result is a polyhedron, the plane equations of each face are computed.
}

\ccHeading{Requirements}
Both functions require the following:
\begin{enumerate}
   \item \ccc{InputIterator::value_type} is equivalent to \ccc{Traits::Point_3}.
   \item \ccc{Traits} is a model of the concept \ccc{ConvexHullTraits_3}
         \ccIndexMainItem[c]{ConvexHullTraits_3}.  When it is known that
         the input points are not all coplanar, the types \ccc{Traits_xy}, 
         \ccc{Traits_yx}, and \ccc{Traits_yz} need not be provided.
         For the purposes of checking the postcondition that the convex hull
         is valid, \ccc{Traits} should also be a model of the concept
         \ccc{IsStronglyConvexTraits_3}.
        %\ccIndexMainItem[c]{IsStronglyConvexTraits_3}
\end{enumerate}

Both functions have an additional requirement for the polyhedron that is
to be constructed. For the first version this is that:
\begin{itemize}
  \item \ccc{Polyhedron_3} is a model of \ccc{ConvexHullPolyhedron_3},
\end{itemize}
and for the second, it is required that
\begin{itemize}
 \item \ccc{Traits} defines a type \ccc{Polyhedron_3} that is a model of 
       \ccc{ConvexHullPolyhedron_3}.
\end{itemize}

The default traits class for both versions of \ccc{convex_hull_3} is 
\ccc{Convex_hull_traits_3<R>},%
with the representation \ccc{R} determined by \ccc{InputIterator::value_type}.

\ccSeeAlso

\ccRefIdfierPage{CGAL::convex_hull_incremental_3} \\
\ccRefIdfierPage{CGAL::ch_eddy}  \\
\ccRefIdfierPage{CGAL::convex_hull_2} 

\ccImplementation
The algorithm implemented by these functions is the quickhull algorithm of 
Barnard \textit{et al.} \cite{bdh-qach-96}.  

\ccExample

The following program computes the convex hull of a set of 250 random
points chosen from a sphere of radius 100.  It then determines if the resulting
hull is a segment or a polyhedron.  Notice that the traits class is not
necessary in the call to \ccc{convex_hull_3} but is used in the definition
of \ccc{Polyhedron_3}.

\ccIncludeExampleCode{Convex_hull_3/quickhull_3.cpp}

\ccIndexSubitemEnd{convex hull, 3D}{quickhull}
\ccIndexMainItemEnd{quickhull, 3D}
\ccIndexMainItemEnd{convex hull, 3D}
\end{ccRefFunction}
