% +------------------------------------------------------------------------+
% | Reference manual page: Env_sphere_traits.tex
% +------------------------------------------------------------------------+
% | 
% | Package: Envelope_3
% | 
% +------------------------------------------------------------------------+

\ccRefPageBegin

\begin{ccRefClass}{Env_sphere_traits_3<ConicTraits>}
    
\ccDefinition 
%============

The traits class \ccRefName\ models the \ccc{EnvelopeTraits_3}
concept, and is used for the construction of lower and upper envelopes 
of spheres. Note that when projecting the intersection curve of two 
spheres (a circle in 3D) onto the $xy$-plane, the resulting curve is an 
ellipse. The traits class is therefore parameterized by an 
arrangement-traits class that is capable of handling conic 
curves --- namely an instantiation of the \ccc{Arr_conic_traits_2} 
class-template --- and inherits from it.

The conic-traits class defines a nested type named \ccc{Rat_kernel},
which is a geometric kernel parameterized by an exact rational type.
\ccRefName\ defines its \ccc{Surface_3} type to be constructible from
\ccc{Rat_kernel::Sphere_3}. Namely, it can handle spheres whose center
points have rational coordinates (i.e., of the type \ccc{Rat_kernel::FT}),
and whose squared radius is also rational. The \ccc{Surface_3} type is
also convertible to a \ccc{Rat_kernel::Sphere_3} object.

The \ccc{Xy_monotone_surface_3} type is the same as the nested
\ccc{Surface_3} type. The traits-class simply ignores the upper
hemisphere when it computes lower envelopes, and ignores the lower
hemisphere when it computes upper envelopes.

\ccInclude{CGAL/Env_sphere_traits_3.h}
 
\ccIsModel
    \ccc{EnvelopeTraits_3}

\ccInheritsFrom
    \ccc{ConicTraits}

\end{ccRefClass}

\ccRefPageEnd
