\begin{ccRefConcept}{PureComplexSimplex}

\ccDefinition

The concept \ccRefName\ describes the requirements on the type used by the
class \ccc{Pure_complex<PCTraits, PCDS>}, and its derived classes, to
represent a simplex.

\ccRefines

\ccc{PureComplexDSSimplex}

We only list below the additional specific requirements of \ccRefName.

Compared to \ccc{PureComplexDSSimplex}, the main difference is the addition of
methods to access and iterate over the position of the simplex's vertices as
well as a method for constructing the center of the simplex's circumsphere.

\ccHasModels

\ccc{Pure_complex_simplex<PCTraits, PCDSSimplex>}

\ccTypes

\ccNestedType{Point}%
{The type of the point stored in the simplex's vertices. It must be the same
as the point type \ccc{PureComplexTraits::Point} (or its refined concepts)
defined by the geometric traits of the \ccc{Pure_complex<PCTraits, PCDS>}
class.}

\ccNestedType{Point_const_iterator}{An iterator over the points of the
simplex.}

\ccCreationVariable{s}

\ccOperations

\ccMethod{Point_const_iterator points_begin() const;}
{Returns an iterator pointing to the first point of the simplex.}
\ccGlue
\ccMethod{Point_const_iterator points_end() const;}
{Returns an iterator pointing beyond the last point of the simplex.}

\ccMethod{Point circumcenter() const;}{Returns the center of the sphere
circumscribing the simplex.}

\ccSeeAlso

\ccc{Pure_complex_simplex<PCTraits, PCDSSimplex>}\\
\ccc{PureComplexVertex}\\
\ccc{Pure_complex<PCTraits, PCDS>}

\end{ccRefConcept}
