\begin{ccRefClass}{Pure_complex_ds_simplex<PCDS, PCDSSimplexStoragePolicy>}

\ccDefinition

The class \ccRefName\ serves as the default simplex template parameter in the
class \ccc{Pure_complex_data_structure<Dimensionality, PCDSVertex,
PCDSSimplex>}.

This class does not provide any geometric capabilities but only combinatorial
(adjacency) information. Thus, if the \ccc{Pure_complex_data_structure} is
used as a parameter of a geometric complex, then its simplex template
parameter has to fulfill additional geometric requirements, i.e. it has to be
a model of the refined concept \ccc{PureComplexSimplex}.

This class can be used directly or can serve as a base to derive other classes
with some additional attributes tuned for a specific application.

\ccInclude{CGAL/Pure_complex_ds_simplex.h}

\ccParameters

The first template parameter, \ccc{PCDS}, must be a model of the
\ccc{PureComplexDataStructure} concept. It defaults to \ccc{void}, which is
used to break some dependency cycles.

The second parameter, \ccc{PCDSSimplexStoragePolicy}, indicates whether or not
the simplex should additionally store the mirror indices (the indices, in each
neighbor, of the mirror vertices). This improves speed a little, but takes
more space. It can take two ``values'':\begin{itemize}

\item \ccc{PCDS_simplex_default_storage_policy}, which is the \textbf{default}
value. In that case, the mirror indices are \textbf{not stored}.

\item \ccc{PCDS_simplex_mirror_storage_policy}. In that case, the mirror
indices are stored.
\end{itemize}
 See the user manual (TODO) for how to choose the second option.

\ccIsModel

\ccc{PureComplexDSSimplex}

\ccSeeAlso

\ccc{Pure_complex_ds_vertex<PCDS>}

\end{ccRefClass}
