\begin{ccRefConcept}{TriangulationFace}

\ccDefinition

A \ccRefName\ simply describes a \ccc{k}-face \ccc{f} in a triangulation.
It gives access to a handle to a full cell \ccc{c} containing the face
\ccc{f} in its boundary, as well as the indices of the vertices of \ccc{f} in
\ccc{c}. It must hold that \ccc{f} is a \textbf{proper} face of cell
\ccc{c}, \emph{i.e.}, the dimension of \ccc{f} is strictly less than
the dimension of \ccc{c}.

\ccTypes

\ccNestedType{Full_cell_handle}{Must be the same as the nested type
\ccc{TDS::Full_cell_handle} of the \ccc{TDS} in which the \ccc{Face} is
defined/used.}

\ccNestedType{Vertex_handle}{Must be the same as the nested type
\ccc{TDS::Vertex_handle} of the \ccc{TDS} in which the \ccc{Face} is
defined/used.}

\ccHasModels

\ccc{Triangulation_face<TDS>}.

\ccCreation
\ccCreationVariable{f}

\ccConstructor{Triangulation_face(Triangulation_face g);}{Copy constructor.}

\ccConstructor{Triangulation_face(Full_cell_handle c);}{Sets the \ccc{Face}'s
cell to \ccc{c}. \ccPrecond \ccc{s} must be a handle to an existing
cell (not the default-constructed \ccc{Full_cell_handle()}).}

\ccConstructor{Triangulation_face(const int ad);}{Setup the \ccc{Face} knowing
the ambient dimension \ccc{ad}. Sets the \ccc{Face}'s cell to the
default-constructed one.}

\ccHeading{Access functions}

\ccMethod{Full_cell_handle full_cell() const;}{Returns a handle to a cell that
has the face in its boundary.}

\ccMethod{int feature_dimension() const;}{Returns the dimension of the face
(one less than the number of vertices).}

\ccMethod{int index(int i) const;}{Returns the index of the \ccc{i}-th vertex
of the face in the cell \ccVar.\ccc{full_cell()}. \ccPrecond $0\leq i\leq$\ccVar.\ccc{feature_dimension()}.}

\ccMethod{Vertex_handle vertex(int i) const;}{Returns a handle to the
\ccc{i}-th \ccc{Vertex} of the face in the cell \ccVar.\ccc{full_cell()}.
\ccPrecond $0\leq i\leq$\ccVar.\ccc{feature_dimension()}.}

\ccHeading{Update functions}

\ccMethod{void clear();}{Sets the facet to the empty set.}

\ccMethod{void set_full_cell(Full_cell_handle c);}{Sets the cell of the face to
\ccc{c}. \ccPrecond \ccc{c} must not be the default-constructed
\ccc{Full_cell_handle}.}

\ccMethod{void set_index(int i, int j);}{Sets the index of the \ccc{i}-th
vertex of the face. \ccPrecond $0\leq j\leq$\ccVar.\ccc{full_cell()->ambient_dimension()}.}

\ccSeeAlso

\ccc{TriangulationDataStructure}, \\
\ccc{Triangulation_face<TDS>}.

\end{ccRefConcept}
