% +------------------------------------------------------------------------+
% | Reference manual page: Triangulation_hierarchy_2.tex
% +------------------------------------------------------------------------+
% | 16.08.2000   Mariette Yvinec
% | Package: Triangulation
% | 
\RCSdef{\RCSTriangulationhierarchyRev}{$Revision$}
\RCSdefDate{\RCSTriangulationhierarchyDate}{$Date$}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefClass}{Triangulation_hierarchy_2<Tr>}
%% add template arg's if necessary

\ccDefinition
The class \ccRefName\ implements a triangulation augmented with
a data structure which allows fast point location queries.
The data structure is a hierarchy 
of triangulations. The triangulation at the lowest level is
the original triangulation where operations and point location are to 
be performed.
Then at each succedding level, the data structure
stores a triangulation of a small random sample of the vertices
of the triangulation at the preceeding level. Point location
is done through a top-down nearest neighbor query.
The nearest neighbor query is first
performed naively in the top level triangulation.
Then, at each following level, the nearest neighbor at that level
is found through a linear walk performed from
the nearest neighbor found at the preceeding level.
Because the number of vertices in each triangulation is only a small
fraction of the number of vertices of the preceeding triangulation 
the data structure remains small and achieves fast point location 
queries on real
data. As proved in~\cite{d-iirdt-98}, this structure has an optimal behaviour
when it is built for Delaunay triangulations.
However it can be used as well for other triangulations
and the \ccRefName\ class is templated by a parameter
which is to be instantiated by one of the \cgal\ triangulation
classes.

\ccInclude{CGAL/Triangulation_hierarchy_2.h}

\ccInheritsFrom

\ccc{Tr}

\ccTypes
The class \ccRefName\ inherits the types from its base triangulation
class \ccc{Tr}. 

\ccCreation
\ccCreationVariable{trh}  %% choose variable name

\ccConstructor{Triangulation_hierarchy_2(const Traits& gt =
Traits());}{default constructor.}
\ccGlue
\ccConstructor{Triangulation_hierarchy_2(const
Triangulation_hierarchy_2& trh1);}{Each triangulation in the hierarchy 
is duplicated.}
\ccGlue
\ccMethod{Triangulation_hierarchy_2<Tr> operator=(const Triangulation_hierarchy_2<Tr>& tr);}
{Assignment. Each triangulation in the hierarchy is duplicated.}

\ccHeading{Helper functions}
\ccMethod{void swap(Triangulation_hierarchy_2<Tr>& trh1);}
{The triangulations \ccc{trh1} and \ccVar\ are swapped.
\ccVar. \ccc{swap(tr)} should be preferred to \ccc{trh} = \ccc{trh1} or to
\ccc{trh(trh1)} if \ccc{trh} is deleted after that.}
\ccGlue
\ccMethod{void clear();}{Delete all triangulations in the hierarchy.}

\ccHeading{Insertion and Removal}
The class \ccRefName\ overwrites the following insertion and removal
member functions to update the whole data structure at each operation.

\ccMethod{Vertex_handle insert(const Point& p);}{Inserts  point \ccc{p}.
If point \ccc{p} coincides with an already existing vertex, this 
vertex is returned and the triangulation hierarchy is not updated.}
\ccGlue
\ccMethod{Vertex_handle push_back(const Point& p);}
{Equivalent to \ccc{insert(p)}.}
\ccGlue
\ccMethod{template < class InputIterator >
          int
          insert(InputIterator first, InputIterator last);}
{inserts the points in the range
 $\left[\right.$\ccc{first}, \ccc{last}$\left.\right)$.
 Returns the number of inserted points.
 \ccPrecond The \ccc{value_type} of \ccc{first} and \ccc{last}
 is \ccc{Point}.}

\ccMethod{void    remove(Vertex_handle v);}
{removes the vertex from the triangulation hierarchy.}
\ccGlue
\ccMethod{void remove_degree_3(Vertex_handle v);}
{Removes a vertex of degree three.
\ccPrecond{Vertex \ccc{v} is a finite vertex with degree three.}}
\ccMethod{void remove_second(Vertex_handle v);}{Removes the before
last finite vertex.}
\ccGlue
\ccMethod{void remove_first(Vertex_handle v);}{Removes the last finite vertex.}

\ccHeading{Point location}
The following point location member functions are overwritten.
They take advantage of the hierarchy to achieve an efficient
point location.


\ccMethod{ Face_handle  locate(const Point& p) const;}
{Locates the point \ccc{p} in the triangulation. See the description of the
\ccc{locate} member functions in the class \ccc{Triangulation_2<Traits,Tds>}. }

\ccMethod{ Face_handle  locate(const Point& p, Locate_type& lt, int& li) const;}
{Same as above. Additionally, the locate type \ccc{lt}
 and the index \ccc{li} describing precisely the location are set.}

\begin{ccAdvanced}
\ccHeading{Checking}
\ccMethod{bool is_valid() const;}{The \ccc{is_valid()} member function is
overwritten
to check the validity of the hierarchy, as well as the validity of the
bottom triangulation.}
\end{ccAdvanced}

\ccSeeAlso
\ccc{CGAL::Triangulation_2<Traits,Tds>} \\
\ccc{TriangulationHierarchyVertexBase_2}, \\
\ccc{CGAL::Triangulation_hierarchy_vertex_base_2<Vb>}


%\ccExample

%A short example program.
%Instead of a short program fragment, a full running program can be
%included using the 
%\verb|\ccIncludeExampleCode{examples/Package/Triangulation_hierarchy_2_prog.C}| 
%macro. The program example would be part of the source code distribution and
%also part of the automatic test suite.

%\begin{ccExampleCode}
%void your_example_code() {
%}
%\end{ccExampleCode}

%%% \ccIncludeExampleCode{examples/Package/Triangulation_hierarchy_2_prog.C}

\end{ccRefClass}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

