
\ccHtmlNoClassLinks
\begin{ccClassTemplate} {map<Key, T, Compare>}

\ccSection{map}

\ccDefinition
An object of the class \ccClassTemplateName\ supports unique keys of 
type \ccStyle{Key}, and provides retrieval of values of type \ccStyle{T}
based on the keys. The keys into the map are ordered by the ordering
relation \ccStyle{Compare}.

Elements are stored in maps as \ccStyle{pairs} of \ccStyle{Key} and 
\ccStyle{T}.

\ccInclude{map}

\ccTypes
\ccNestedType{iterator}{A const bidirectional iterator.}


\ccCreation
\ccCreationVariable{M}


\ccConstructor{map(const Compare& comp = Compare());}
             {Introduces an empty map.}

\ccConstructor{map(const map<Key, T, Compare> &M1);}
 	    {Copy constructor.}

\ccOperations


\ccMethod{map<Key, T, Compare> & operator=(const map<Key, T, Compare> &M1);}
        {Assignment.}

\ccMethod{bool operator==(const map<Key, T, Compare> &M1);}
{Equality test: Two maps are equal, if the sequences \ccVar\ and \ccStyle{M1}
 are elementwise equal.}


\ccMethod{bool operator<(const map<Key, T, Compare> &M1);}
{Returns \ccStyle{true} if \ccVar\ is lexicographically less than \ccStyle{M1},
 \ccStyle{false} otherwise.}

\ccMethod{iterator begin() const;}
       {Returns a constant iterator referring to the first element in
        map~\ccVar.}

\ccMethod{iterator end() const;}
       {Returns a constant past-the-end iterator of map~\ccVar.}

\ccMethod{bool empty() const;}
	{Returns \ccStyle{true} if \ccVar\ is empty.}

\ccMethod{int size() const;}
	{Returns the number of items in map~\ccVar.}

\ccMethod{T& operator[](const Key& k);}
{Returns a reference to the type \ccStyle{T} value associated with
key \ccStyle{k}. If the map is constant then a const reference is 
returned. In contrast to vector or deque, the \ccStyle{pair(k,T())}
is inserted into the map, if no element is associated with the key.}

\ccHeading{Insert and Erase}

\ccMethod{iterator insert(iterator pos, pair<const Key&,T> val);}
{Inserts \ccStyle{val} into the map if \ccStyle{val} is not already
 present in \ccVar. The iterator \ccStyle{pos} is the starting point of
 the search.  The return value points to the inserted item.}

\ccMethod{pair<iterator, bool> insert(pair<const Key&,T> val);}
{Inserts \ccStyle{val} into the map if \ccStyle{val} is not already
 present in \ccVar. Returns a pair, where \ccStyle{first}
 is the iterator that points to the inserted item or to the
 item that is already present in \ccVar, and where \ccStyle{second}
 is \ccStyle{true} if the insertion took place.}

\ccMethod{void erase(iterator pos);}
{Erases the element where pos points to.}

\ccMethod{int erase(Key k);}
{Erases all elements that equal \ccStyle{k}. Returns the number
 of erased elements.}

\ccHeading{Miscellaneous}

\ccMethod{iterator find(Key k);}
{Returns an iterator that either points to the element \ccStyle{k},
 or \ccStyle{end()} if \ccStyle{k} is not present in map \ccVar.}

\ccMethod{int count(Key k);}
{Returns the number of occurrences of \ccStyle{k} in map \ccVar.}


\ccMethod{iterator lower_bound(Key k);}
{Returns an iterator that points to the first element of \ccVar\ 
that is not less than \ccStyle{k}. If all elements are less than
\ccStyle{k} then \ccStyle{end()} is returned. If \ccStyle{k}
is present in the map the returned iterator points to \ccStyle{k}.}

\ccMethod{iterator upper_bound(Key k);}
{Returns an iterator that points to the first element of the map
that is greater than \ccStyle{k}. If no element is greater than
\ccStyle{k} then \ccStyle{end()} is returned. If \ccStyle{k}
is present in the map the returned iterator points to \ccStyle{k}.}

\end{ccClassTemplate} 
