\begin{ccRefClass} {Gmpq}
\label{Gmpq}

\ccDefinition

An object of the class \ccStyle{Gmpq} is an arbitrary precision rational
number based on the {\sc Gnu} Multiple Precision Arithmetic Library. 

\ccInclude{CGAL/Gmpq.h}

\ccIsModel
\ccc{Field}\\
\ccc{RealEmbeddable}\\
\ccc{Fraction}

\ccCreation
\ccCreationVariable{q}

\ccConstructor{Gmpq();}
             {creates an uninitialized \ccc{Gmpq} \ccVar.}

\ccHidden \ccConstructor{Gmpq(const Gmpq& q);}
            {copy constructor.}\ccGlue


\ccConstructor{Gmpq(int i)}
            {creates a \ccc{Gmpq} initialized with
             \ccStyle{i}.}\ccGlue


\ccConstructor{Gmpq(Gmpz n)}
            {creates a \ccc{Gmpq} initialized with
             \ccStyle{n}.}\ccGlue


\ccConstructor{Gmpq(Gmpfr f)}
            {creates a \ccc{Gmpq} initialized with
             \ccStyle{f}.}\ccGlue


\ccConstructor{Gmpq(int n, int d)}
            {creates a \ccc{Gmpq} initialized with
             \ccStyle{n/d}.}\ccGlue


\ccConstructor{Gmpq(signed long n, unsigned long d)}
            {creates a \ccc{Gmpq} initialized with
             \ccStyle{n/d}.}\ccGlue


\ccConstructor{Gmpq(unsigned long n, unsigned long d)}
            {creates a \ccc{Gmpq} initialized with
             \ccStyle{n/d}.}\ccGlue


\ccConstructor{Gmpq(Gmpz n, Gmpz d)}
            {creates a \ccc{Gmpq} initialized with
             \ccStyle{n/d}.}\ccGlue


\ccConstructor{Gmpq(double d)}
            {creates a \ccc{Gmpq} initialized with
             \ccStyle{d}.}


\ccConstructor{Gmpq(const std::string& str)}
            {creates a \ccc{Gmpq} initialized with \ccStyle{str}, which can
	    be an integer like "41" or a fraction like "41/152". White
	    space is allowed in the string, and ignored.}\ccGlue


\ccConstructor{Gmpq(const std::string& str, int base)}
            {creates a \ccc{Gmpq} initialized with \ccStyle{str} in base
	    \ccc{base}, which is an integer between 2 and 62. White space
	    in the string is ignored.}

%\ccSetTwoOfThreeColumns{5cm}{4cm}
%SetThreeColumns{std::ostream& }{}{\hspace*{8cm}}

\ccThree{xxxxxxxxxxxxxx}{xxxxxxxxxxxxxxxxxxxxxxx}{}
\ccOperations
\ccFunction{std::ostream& operator<<(std::ostream& out, const Gmpq& q);}
	{writes \ccc{q} to the ostream \ccc{out}, in the form $n/d$.}

\ccFunction{std::istream& operator>>(std::istream& in, Gmpq& q);}
	{reads a number from \ccc{in}, then converts it to a
	\ccc{Gmpq}. The number may be an integer, a rational number in
	the form $n/d$, or a floating-point number.}

There are two access functions, namely to the
numerator and the denominator of a rational.
Note that these values are not uniquely defined. 
It is guaranteed that \ccStyle{q.numerator()} and 
\ccStyle{q.denominator()} return values \ccStyle{nt_num} and
\ccStyle{nt_den} such that \ccStyle{q = nt_num/nt_den}, only
if  \ccStyle{q.numerator()} and \ccStyle{q.denominator()} are called
consecutively wrt. \ccStyle{q}, i.e.~\ccStyle{q} is not involved in 
any other operation between these calls.

\ccMethod{Gmpz numerator() const;}
       {returns the numerator of \ccStyle{q}.}
\ccGlue
\ccMethod{Gmpz denominator() const;}
       {returns the denominator of \ccStyle{q}.}

\ccImplementation
\ccc{Gmpq}s are reference counted.

\end{ccRefClass} 
\ccDefGlobalScope{CGAL::}
