\section{Overview - TODO - OPEN Questions for Release 3.3}

{\em this section is for the reviewer and to be removed for the release. }


OPEN:
\begin{itemize}
\item there is a problem with io stream operators for CORE types in case 
      gmpxx.h is included too. 
\end{itemize}


DONE:
\begin{itemize}
\item rm inexact version of \ccc{MP_float}. 
\item \ccc{utils.h} and \ccc{utils_classes.h} left in NTS\\
      contains: \\
      \ccc{min}, \ccc{max}, \ccc{is_valid}\\
      \ccc{Min}, \ccc{Max}, \ccc{Is_valid}\\
      TODO: mv to STL-extension\\
      TODO: wrap up STL-extension ! 
\end{itemize}

Remarks:
\begin{itemize}
\item io support: keep \ccc{Output_rep} 
\end{itemize}

Keep in mind: 
\begin{itemize}
\item \ccc{mpf_class} is not supported yet. why not? is it possible?  
\item can we do better for \ccc{mpz_class}, \ccc{mpq_class }
\item what about namespace of leda types ? 
     \ccc{leda_integer} vs. \ccc{leda::integer}
\end{itemize}

\subsection{some remarks on current status of number type}
\begin{itemize}
\item  \ccc{Interval_nt}\\
       consider \ccc{Interval_nt} as not exact
\item \ccc{Lazy_exact_nt}:\\
      Now supports all algebraic structures that are real embeddable.\\
      Supports \ccc{Coercion_traits< Lazy_exact_nt<A> , Lazy_exact_nt<B> >}\\ 
      From Rons email: The output behavior is not the same, as the internal NT. 

\item \ccc{Counted_number}:\\
        The type has been left undocumented.\\
        Implementation supports all algebraic structures, all functions are counted.\\
        Functors of \ccc{RealEmbeddable} are not counted. \\
        It's current implementation does not use the \ccc{result_type} of the used 
        functors. i.e. does not fully support \ccc{Interval_nt} as internal type.

\item \ccc{mpz_class}:\\
       Implementation supports expression templates, 
       up to the same level as the old \cgal\ implementation.       
       i.e. it is possible to call CGAL::square(x+x) but the result is 
       \ccc{mpz_class } and not the according expression template.  

\item \ccc{mpq_class}:\\
        same as \ccc{mpz_class}.

\item \ccc{Quotient<NT>}\\
        For an exact NT it is always a model of \ccc{Field}. (implemented)\\
        For inexact types it is a FieldWithSqrt in case the internal type has a sqrt.
        This is not implemented yet, since it is unclear what this sqrt is good for. 
        Since all inexact types with sqrt are Fields, and thus it make no sense to use 
        them as the internal type.  \\
        Supports \ccc{Coercion_traits}. 
\end{itemize}
