\ccRefPageBegin

\begin{ccRefClass}{AABB_HalfedgeGraph_segment_primitive<HalfedgeGraph,OneHalfedgeGraphPerTree,cache_datum>}

\ccDefinition
  
If \ccc{OneHalfedgeGraphPerTree} is \ccc{CGAL::Tag_false}, the class is a model of the concept \ccc{AABBPrimitive}.
If \ccc{OneHalfedgeGraphPerTree} is \ccc{CGAL::Tag_true}, the class is a model of the concept \ccc{AABBPrimitiveWithSharedData}.
It wraps an \ccc{edge_descriptor} of a class model of \ccc{HalfedgeGraph} to a 3D segment.
The class model of \ccc{HalfedgeGraph} from which the primitive is built should not be deleted
while the AABB tree holding the primitive is in use.



\ccParameters
\ccc{HalfedgeGraph} is a model of the halfedge graph concept.\\
\ccc{OneHalfedgeGraphPerTree} is either \ccc{CGAL::Tag_true} or \ccc{CGAL::Tag_false}. In the former case, we guarantee that all the primitives will be from a common \ccc{HalfedgeGraph} and some data 
will be factorized so that the size of the primitive is reduced. In the latter case, the primitives can be from different graphs and extra storage is required in the primitives. The default is \ccc{CGAL::Tag_true}.\\
\ccc{cache_datum} is either \ccc{CGAL::Tag_true} or \ccc{CGAL::Tag_false}. In the former case, the datum is stored in the primitive, while in the latter it is constructed on the fly to reduce
the memory footprint. The default is \ccc{CGAL::Tag_false} (datum is not stored).

\ccInclude{CGAL/AABB_HalfedgeGraph_segment_primitive.h}

\ccTypes
\ccTypedef{typedef boost::property_traits< boost::property_map< HalfedgeGraph, vertex_point_t>::type >::value_type Point;}{The point type.}
\ccGlue
\ccTypedef{typedef Kernel_traits<Point>::Kernel::Segment_3 Datum;}{Geometric data type.}
\ccGlue
\ccTypedef{typedef boost::graph_traits<HalfedgeGraph>::edge_descriptor Id;}{Id type.}

\ccCreation
\ccCreationVariable{p}

\ccConstructor{
template <class Iterator>
AABB_HalfedgeGraph_segment_primitive(Iterator it,const HalfedgeGraph& graph)}
{Constructs a primitive. \ccc{Iterator} is an input iterator with \ccc{Id} as \ccc{value_type}.
The example below gives a way to call this constructor the insert-by-range method of the class \ccc{CGAL::AABB_tree<Traits>}.}


\ccSeeAlso

\ccc{AABBPrimitive},\\
\ccc{AABB_primitive<Id,ObjectPropertyMap,PointPropertyMapPolyhedron,ExternalPropertyMaps,cache_datum>},\\
\ccc{AABB_FaceGraph_triangle_primitive<FaceGraph,OneFaceGraphPerTree,cache_datum>}.\\

\ccIncludeExampleCode{AABB_tree/AABB_HalfedgeGraph_edge_example.cpp}

\end{ccRefClass}

\ccRefPageEnd
