% +------------------------------------------------------------------------+
% | Reference manual page: PartitionIsValidTraits_2.tex
% +------------------------------------------------------------------------+
% | 10.05.2000   Susan Hert
% | Package: Partition_2
% | 
% |
% +------------------------------------------------------------------------+

\renewcommand\ccRefPageBegin{\ccParDims\cgalColumnLayout\begin{ccAdvanced}}
\renewcommand\ccRefPageEnd{\ccParDims\cgalColumnLayout\end{ccAdvanced}}
\begin{ccRefConcept}{PartitionIsValidTraits_2}

\ccDefinition
  
Requirements of a traits class that is used 
by \ccc{partition_is_valid_2}, \ccc{convex_partition_is_valid_2},
and \ccc{y_monotone_partition_is_valid_2} for testing if a given set of 
polygons are nonoverlapping and if their union is a polygon that is the 
same as a polygon represented by a given sequence of points.  Note that the 
traits class for \ccc{partition_is_valid_2} may have to satisfy additional
requirements if each partition polygon is to be tested for having a
particular property; see, for example, the descriptions of the 
function \ccc{is_convex_2}
and the concept YMonotonePartitionTraits\_2 for the additional requirements
for testing for convexity and $y$-monotonicity, respectively.

\ccTypes

\ccNestedType{Point_2}{The point type on which the partitioning algorithm operates.}

\ccNestedType{Polygon_2}{The polygon type created by the partitioning 
function. This type should provide a nested type \ccc{Vertex_const_iterator} 
that is the type of the non-mutable iterator over the polygon vertices.}%

\ccNestedType{Is_valid}{A model of the concept PolygonIsValid}

\ccNestedType{Less_xy_2}{
Predicate object type that compares \ccc{Point_2}s lexicographically.
Must provide \ccc{bool operator()(Point_2 p, Point_2 q)} where \ccc{true}
is returned iff $p <_{xy} q$.
We have $p<_{xy}q$, iff $p_x < q_x$ or $p_x = q_x$ and $p_y < q_y$,
where $p_x$ and $p_y$ denote the $x$ and $y$ coordinates of point $p$, 
respectively.
}

\ccNestedType{Leftturn_2}{
Predicate object type that provides 
\ccc{bool operator()(Point_2 p,Point_2 q,Point_2 r)}, which
returns \ccc{true} iff \ccc{r} lies to the left of the 
oriented line through \ccc{p} and \ccc{q}.}

\ccNestedType{Orientation_2}{Predicate object type that provides
\ccc{CGAL::Orientation operator()(Point_2 p, Point_2 q, Point_2 r)} that
returns \ccStyle{CGAL::LEFTTURN}, if $r$ lies to the left of the oriented 
line $l$ defined by $p$ and $q$, returns \ccStyle{CGAL::RIGHTTURN} if $r$ 
lies to the right of $l$, and returns \ccStyle{CGAL::COLLINEAR} if $r$ lies
on $l$.}



\ccCreation
\ccCreationVariable{traits}  %% choose variable name

Only a copy constructor is required.

\ccConstructor{PartitionIsValidTraits_2(PartitionIsValidTraits_2& tr)}{}

\ccOperations

The following functions that create instances of the above predicate object
types must exist.

\ccMethod{Orientation_2 is_valid_object();}{}

\ccMethod{Less_xy_2 less_xy_2_object();}{}

\ccMethod{Leftturn_2 leftturn_2_object();}{}

\ccMethod{Orientation_2 orientation_2_object();}{}


\ccHasModels

\ccRefIdfierPage{CGAL::Partition_is_valid_traits_2<Traits, PolygonIsValid>}

\ccSeeAlso

\ccRefIdfierPage{CGAL::approx_convex_partition_2} \\
\ccRefIdfierPage{CGAL::greene_approx_convex_partition_2} \\
\ccRefIdfierPage{CGAL::optimal_convex_partition_2} \\
\ccRefIdfierPage{CGAL::y_monotone_partition_2}

\end{ccRefConcept}
\renewcommand\ccRefPageBegin{\ccParDims\cgalColumnLayout}
\renewcommand\ccRefPageEnd{\ccParDims\cgalColumnLayout}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

