% +------------------------------------------------------------------------+
% | Reference manual page: Mode.tex
% +------------------------------------------------------------------------+
% | 09.04.2002   Author
% | Package: Package
% | 
\RCSdef{\RCSModeRev}{$Id$}
\RCSdefDate{\RCSModeDate}{$Date$}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefEnum}{Mode}  %% add template arg's if necessary

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[enum]{} %% add further index entries

\ccDefinition
  
All classes in the \cgal\ kernel provide input and output operators for
IOStreams.  The basic task of such an operator is to produce a
representation of an object that can be written as a sequence of
characters on devices as a console, a file, or a pipe. The enum \ccRefName\
distinguish between three different printing formats.

In  \ccc{ASCII} mode, numbers 
e.g.\ the coordinates of a point or
the coefficients of a line, are written
in a machine independent format. 
In {\sc BINARY} mode, data are written
in a binary format, e.g.\ a double is represented
as a sequence of four byte. The format depends on the machine.
 The mode  {\sc PRETTY}
serves mainly for debugging as the type of the geometric
object is written, as well as the data defining the object. For example
for a point at the origin with Cartesian double coordinates, the output
would be \ccc{PointC2(0.0, 0.0)}.  At the moment \cgal\ does not
provide input operations for pretty printed data. By default a stream
is in {\sc Ascii} mode.



\ccGlobalEnum{enum Mode { ASCII = 0, BINARY, PRETTY };}

\ccRefLabel{ASCII}
\ccRefLabel{BINARY}
\ccRefLabel{PRETTY}
\ccHtmlCrossLink{ASCII}
\ccHtmlCrossLink{BINARY}
\ccHtmlCrossLink{PRETTY}
%\ccHtmlIndexC[enum_tags]{ASCII}
%\ccHtmlIndexC[enum_tags]{BINARY}
%\ccHtmlIndexC[enum_tags]{PRETTY}

\ccSeeAlso
\ccRefIdfierPage{CGAL::set_mode} \\
\ccRefIdfierPage{CGAL::set_ascii_mode} \\
\ccRefIdfierPage{CGAL::set_binary_mode}  \\
\ccRefIdfierPage{CGAL::set_pretty_mode}  \\
\ccRefIdfierPage{CGAL::get_mode} \\
\ccRefIdfierPage{CGAL::is_ascii} \\
\ccRefIdfierPage{CGAL::is_binary} \\
\ccRefIdfierPage{CGAL::is_pretty} \\


%\ccExample

%A short example program.
%Instead of a short program fragment, a full running program can be
%included using the 
%\verb|\ccIncludeExampleCode{Package/Mode_prog.C}| 
%macro. The program example would be part of the source code distribution and
%also part of the automatic test suite.

%\begin{ccExampleCode}
%void your_example_code() {
%}
%\end{ccExampleCode}

%% \ccIncludeExampleCode{Package/Mode_prog.C}

\end{ccRefEnum}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

