%% ==============================================================
%% Specification: All Furthest Neighbors
%% --------------------------------------------------------------
%% file  : spec_all_furthest_neighbors.awi
%% author: Michael Hoffmann
%% $Id$
%% ==============================================================

\cgalColumnLayout

\begin{ccRefFunction}{all_furthest_neighbors_2}
  \ccIndexSubitem[t]{neighbor}{all furthest}
  \ccIndexMainItem[t]{all furthest neighbors}
  \ccIndexSubitem[t]{furthest}{all neighbors}
  
  \ccDefinition The function \ccRefName\ computes all furthest
  neighbors for the vertices of a convex polygon $P$, i.e. for each
  vertex $v$ of $P$ a vertex $f_v$ of $P$ such that the distance
  between $v$ and $f_v$ is maximized.

  \ccInclude{CGAL/all_furthest_neighbors_2.h}

  \def\ccLongParamLayout{\ccTrue} 
  
  \ccGlobalFunction{ template < class RandomAccessIC, class
    OutputIterator, class Traits > OutputIterator
    all_furthest_neighbors_2( RandomAccessIC points_begin,
    RandomAccessIC points_end, OutputIterator o, Traits t =
    Default_traits);}
  
  computes all furthest neighbors for the vertices of the convex
  polygon described by the range [\ccc{points_begin},
  \ccc{points_end}), writes their indices (relative to
  \ccc{points_begin}) to \ccc{o}\footnote{i.e. the furthest neighbor
    of \ccc{points_begin[}i\ccc{]} is \ccc{points_begin[}$i$-th number
    written to \ccc{o}\ccc{]}} and returns the past-the-end iterator
  of this sequence.
  
  \ccPrecond The points denoted by the non-empty range
  [\ccc{points_begin}, \ccc{points_end}) form the boundary of a convex
  polygon $P$ (oriented clock-- or counterclockwise).
  
  The geometric types and operations to be used for the computation
  are specified by the traits class parameter \ccc{t}. This parameter
  can be omitted if \ccc{RandomAccessIC} refers to a point type from
  the 2D-Kernel. In this case, a default traits class
  (\ccc{All_furthest_neighbors_default_traits_2<R>}) is used.
  
  \ccRequire
  \begin{enumerate}
  \item If \ccc{t} is specified explicitly, \ccc{Traits} is a model
    for \ccc{All_furthest_neighbors_traits_2}.
  \item Value type of \ccc{RandomAccessIC} is \ccc{Traits::Point_2} or
    -- if \ccc{t} is not specified explicitly -- \ccc{Point_2<R>} for
    some representation class \ccc{R}.
  \item \ccc{OutputIterator} accepts \ccc{int} as value type.
  \end{enumerate}
  
  \ccSeeAlso
  \ccRefConceptPage{All_furthest_neighbors_traits_2}\\
  \ccRefIdfierPage{CGAL::All_furthest_neighbors_default_traits_2<R>}\\
  \ccRefIdfierPage{CGAL::monotone_matrix_search}
 
  \ccImplementation The implementation uses monotone matrix
  search\cite{akmsw-gamsa-87}. Its runtime complexity is linear in the
  number of vertices of $P$.
  
  \ccExample The following code generates a random convex polygon
  \ccc{p} with ten vertices, computes all furthest neighbors and
  writes the sequence of their indices (relative to
  \ccc{points_begin}) to \ccc{cout} (e.g. a sequence of
  \ccc{4788911224} means the furthest neighbor of
  \ccc{points_begin[0]} is \ccc{points_begin[4]}, the furthest
  neighbor of \ccc{points_begin[1]} is \ccc{points_begin[7]} etc.).
  
  \ccIncludeVerbatim{Optimisation_ref/all_furthest_neighbors_2_example_noheader.C}
\end{ccRefFunction}

\begin{ccRefClass}{All_furthest_neighbors_default_traits_2<R>}
  \ccCreationVariable{t}\ccTagFullDeclarations
  
  \ccDefinition The class \ccClassName\ provides the types and
  operations needed to compute all furthest neighbors for the vertices
  of a convex polygon.
  
  \ccRequirements
  The template parameter \ccc{R} is a model for \ccc{Kernel}.

  \ccIsModel 
  \ccRefConceptPage{All_furthest_neighbors_traits_2}

  \ccTypes
  
  \ccNestedType{Point_2}{typedef to \ccc{R::Point_2}.}
  
  \ccNestedType{FT}{typedef to \ccc{R::FT}.}
  
  \ccNestedType{Distance}{AdaptableBinaryFunction class: \ccc{Point_2}
    $\times$ \ccc{Point_2} $\rightarrow$ \ccc{FT} computing the
    squared Euclidean distance between two points.}

  \ccOperations
  
  \ccMemberFunction{Distance distance_object();}{returns the
    function object for computing distances.}
  
  \ccMemberFunction{template < class RandomAccessIC > bool is_convex(
    RandomAccessIC points_begin, RandomAccessIC points_end)
    const;}{returns true, iff the points [\ccc{points_begin},
    \ccc{points_end}) form a convex chain.}
  
  \ccSeeAlso
  \ccRefIdfierPage{CGAL::all_furthest_neighbors_2}

  \ccHeading{Notes}
  \begin{itemize}
  \item \ccClassName\ccc{::is_convex} is used for precondition
    checking only.
  \end{itemize}
\end{ccRefClass}

\begin{ccRefConcept}{All_furthest_neighbors_traits_2}
  \ccCreationVariable{t}\ccTagFullDeclarations
  
  \ccDefinition The concept \ccRefName\ defines types and operations
  needed to compute all furthest neighbors for the vertices of a
  convex polygon using the function \ccc{all_furthest_neighbors_2}.
  
  \ccTypes
  
  \ccNestedType{Point_2}{class used for representing the input
    points.}
  
  \ccNestedType{FT}{class used for doing computations on point
    coordinates; it has to be a model for \ccc{FieldNumberType}.}
  
  \ccNestedType{Distance}{AdaptableBinaryFunction class: \ccc{Point_2}
    $\times$ \ccc{Point_2} $\rightarrow$ \ccc{FT} computing the
    squared Euclidean distance between two points.}

  \ccOperations
  
  \ccMemberFunction{Distance distance_object();}{returns the
    function object for computing distances.}
  
  \ccMemberFunction{template < class RandomAccessIC > bool is_convex(
    RandomAccessIC points_begin, RandomAccessIC points_end)
    const;}{returns true, iff the points [\ccc{points_begin},
    \ccc{points_end}) form a convex chain.}
  
  \ccHasModels 
  \ccRefIdfierPage{CGAL::All_furthest_neighbors_default_traits_2<R>}

  \ccSeeAlso
  \ccRefIdfierPage{CGAL::all_furthest_neighbors_2}

  \ccHeading{Notes}
  \begin{itemize}
  \item \ccClassName\ccc{::is_convex} is used for precondition
    checking only.
  \end{itemize}
\end{ccRefConcept}

%% --------------------------------------------------------------
%% EOF spec_all_furthest_neighbors.awi
%% --------------------------------------------------------------
