% +------------------------------------------------------------------------+
% | Reference manual page: BoxTraits_d.tex
% +------------------------------------------------------------------------+

\begin{ccRefConcept}{BoxIntersectionTraits_d}
\ccThree{inti}{BoxIntersectionmmmmnTraits_d::dimension();}{}
\ccTwo{BoxIntersectionTraits_d::Box_handle;}{}
\ccCreationVariable{traits}

\ccDefinition

The \ccRefName\ concept is used for the intersection algorithms for
sequences of iso-oriented boxes.  This concept defines the access
functions to the dimension, the \ccc{id}-number, and the boundaries of
the boxes manipulated in these algorithms.


\ccRefines

\ccc{Assignable}.

\ccHasModels

\ccRefIdfierPage{CGAL::Box_intersection_d::Box_traits_d<BoxHandle>}

\ccTypes


\ccNestedType{Box_handle}{box handle. Since we support in our algorithms
  passing the boxes by value as well as passing them as pointers, we
  use as box handle either \ccc{const B&}, \ccc{B*}, or \ccc{const B*}
  respectively, where \ccc{B} is the actual box type.
  The boxes are passed as function arguments using exactly this type.} 

\ccNestedType{NT}{number type to represent the box
  boundaries. Allowed are the builtin types \ccc{int}, \ccc{unsigned
  int}, \ccc{float}, and \ccc{double}.} 

\ccNestedType{ID}{type for the \ccc{id}-number,
  model of the \ccc{LessThanComparable} concept.}

\ccAccessFunctions

\ccFunction{int BoxIntersectionTraits_d::dimension();}{%
  returns the dimension of the box.}

\ccFunction{ID BoxIntersectionTraits_d::id(Box_handle box);}{%
  returns the unique \ccc{id}-number for the \ccc{box}.}

\ccThree{const int}{BoxIntersec}{}

\ccFunction{NT  BoxIntersectionTraits_d::min_coord( Box_handle box, int d);}{%
  returns the lower boundary of the \ccc{box} in dimension
  \ccc{d}, $0 \leq $\ccc{d}$ < $\ccc{dimension()}.}

\ccFunction{NT  BoxIntersectionTraits_d::max_coord( Box_handle box, int d);}{%
  returns the upper boundary of the \ccc{box} in dimension
  \ccc{d}, $0 \leq $\ccc{d}$ < $\ccc{dimension()}.}

\ccSeeAlso

\ccRefIdfierPage{CGAL::box_intersection_d}\\
\ccRefIdfierPage{CGAL::box_self_intersection_d}\\
\ccRefIdfierPage{CGAL::box_intersection_all_pairs_d}\\
\ccRefIdfierPage{CGAL::box_self_intersection_all_pairs_d}

\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+
