% =============================================================================
% The CGAL Developers' Manual
% Chapter: Mailing Lists and Addresses
% -----------------------------------------------------------------------------
% file   : addresses.tex
% authors: Susan Hert <hert@mpi-sb.mpg.de>
% -----------------------------------------------------------------------------
% $Id$
% $Date$
% =============================================================================

\chapter{Mailing Lists and Addresses}
\label{chap:addresses}
\ccChapterRelease{Chapter Version: 1.0}
\ccChapterAuthor{Susan Hert ({\tt hert@mpi-sb.mpg.de})}
\ccIndexMainItemBegin{email addresses}
\ccIndexMainItemBegin{mailing lists}

There are a number of mailing lists and email addresses that have been set
up to communicate with various subsets of the \cgal\ community.  The
addresses that should be of interest to \cgal\ developers are as follows:

\begin{description}
\item[\ccAnchor{mailto:cgal-develop-l@postino.mpi-sb.mpg.de}{{\tt cgal-develop-l@postino.mpi-sb.mpg.de}}]
     (a.k.a. \texttt{cgal-develop@cgal.org})
     \index{cgal_develop mailing list@{\tt cgal-develop} mailing list}
     This list is intended for discussing detailed matters
     about implementation and development issues.  All developers should
     subscribe to this list by sending a message to
     \ccAnchor{mailto:ameyer@mpi-sb.mpg.de}{ameyer@mpi-sb.mpg.de}.
     An \ccAnchor{http://postino.mpi-sb.mpg.de/cgi-bin/lyris.pl?enter=cgal-develop-l}{archive}
     of this mailing list is maintained%
     \begin{ccTexOnly}
     at \nonlinkedpath|http://postino.mpi-sb.mpg.de/cgi-bin/lyris.pl?enter=cgal-develop-l|
     \end{ccTexOnly}.  To enter this archive, use your email address and
     password (if you have one) or
     \texttt{member1@cgal.org} and the usual password.

\item[\ccAnchor{mailto:cgal-commits@lists.gforge.inria.fr}{{\tt cgal-commits@lists.gforge.inria.fr}}]
     \index{cgal-commits mailing list@{\tt cgal-commits} mailing list}
     This list is read-only.  It collects all automatic mails sent by
     the SVN server, one per commit, with the log messages and the URLS
     pointing to the corresponding diffs.
     Developers can subscribe to this list from
     \ccAnchor{https://gforge.inria.fr/mail/?group_id=52}{\cgal\ mailing lists page}.
     An \ccAnchor{http://lists.gforge.inria.fr/cgi-bin/mailman/private/cgal-commits}{archive}
     of this mailing list is maintained%
     \begin{ccTexOnly}
     at \nonlinkedpath|http://lists.gforge.inria.fr/cgi-bin/mailman/private/cgal-commits|
     \end{ccTexOnly}.  To enter this archive, use your email address and InriaGForge
     password.

\item[\ccAnchor{mailto:cgal-discuss-l@postino.mpi-sb.mpg.de}{{\tt cgal-discuss-l@postino.mpi-sb.mpg.de}}]
     \index{cgal-discuss-l mailing list@{\tt cgal-discuss-l} mailing list}
     Users of \cgal\ post questions and discuss issues
     related to \cgal\ on this list.  All developers should subscribe to this
     list so they can answer questions relevant to their packages and monitor
     the input from the users provided here.
     To subscribe to the list, send a message to
     \ccAnchor{mailto:cgal-discuss-l-request@postino.mpi-sb.mpg.de}%
     {\nonlinkedpath|cgal-discuss-l-request@postino.mpi-sb.mpg.de|}
     with the content ``\texttt{subscribe cgal-discuss-l}''.
     An \ccAnchor{http://postino.mpi-sb.mpg.de/cgi-bin/lyris.pl?enter=cgal-discuss-l}{archive}
     of this mailing list is maintained%
     \begin{ccTexOnly}
     at \nonlinkedpath|http://postino.mpi-sb.mpg.de/cgi-bin/lyris.pl?enter=cgal-discuss-l|
     \end{ccTexOnly}.

\item[\ccAnchor{mailto:cgal-announce-l@postino.mpi-sb.mpg.de}{{\tt cgal-announce-l@postino.mpi-sb.mpg.de}}]
     \index{cgal-announce-l mailing list@{\tt cgal-announce-l} mailing list}
     Announcements of new releases, bug fixes, special courses, etc. are posted
     to this list.  The list is moderated (meaning every message posted needs
     to be approved) to keep the traffic low.
     To subscribe to the list, send a message to
     \ccAnchor{mailto:cgal-announce-l-request@postino.mpi-sb.mpg.de}%
     {\nonlinkedpath|cgal-announce-l-request@postino.mpi-sb.mpg.de|}
     with the content ``\texttt{subscribe cgal-announce-l}''.
     An \ccAnchor{http://postino.mpi-sb.mpg.de/cgi-bin/lyris.pl?enter=cgal-announcw-l}{archive}
     of this mailing list is maintained%
     \begin{ccTexOnly}
     at \nonlinkedpath|http://postino.mpi-sb.mpg.de/cgi-bin/lyris.pl?enter=cgal-announce-l|
     \end{ccTexOnly}.

\item[\ccAnchor{mailto:cgal-editors-list@lists.gforge.inria.fr}{{\tt cgal-editors-list@lists.gforge.inria.fr}}]
     \index{editor address@{\tt editor} address}
     % (a.k.a. \texttt{editor@cgal.org})
     This is the email address to which you should
     send proposed design specifications (Chapter~\ref{chap:specification})
     for approval by the editorial
     board (Section~\ref{sec:editorial_board}). Anyone can do that
     at any time about any \cgal\ design issues.

     This list is also
     \ccAnchor{http://lists.gforge.inria.fr/cgi-bin/mailman/listinfo/cgal-editors-list}{archived}%
     \lcTex{
     at \path|http://lists.gforge.inria.fr/cgi-bin/mailman/listinfo/cgal-editors-list|}, and members of the list should use their own
     email addresses and passwords (if you have one) to enter the archive.

     This list was previously hosted at postino, where it was
     \ccAnchor{http://postino.mpi-sb.mpg.de/cgi-bin/lyris.pl?enter=cgal-editor-l}{archived}%
     \lcTex{
     at \path|http://postino.mpi-sb.mpg.de/cgi-bin/lyris.pl?enter=cgal-editor-l|}, and members of the list should use their own
     email addresses and passwords (if you have one) to enter the archive.
\end{description}

The mailing lists at \texttt{lists.gforge.inria.fr} are currently maintained by
\ccAnchor{mailto:Sylvain.Pion@sophia.inria.fr}{Sylvain Pion}.
The mailing lists at \texttt{postino.mpi-sb.mpg.de}
are currently
maintained by \ccAnchor{mailto:ameyer@mpi-sb.mpg.de}{Andreas Meyer}.
\ccIndexMainItemEnd{email addresses}
\ccIndexMainItemEnd{mailing lists}
