\lcTex{\chapter*{Preface}}
\lcHtml{\chapter{Preface}}

\cgal\ is a {\em Computational Geometry Algorithms Library} written in \CC, 
developed by a consortium consisting of
\ccAnchor{http://www.inf.ethz.ch/}{ETH Z\"urich} (Switzerland), 
\ccAnchor{http://www.inf.fu-berlin.de/}{Freie Universit{\"a}t Berlin} (Germany), 
\ccAnchor{http://www.inria.fr/Equipes/PRISME-eng.html}{{\sc Inria} 
Sophia-Antipolis} (France),
\ccAnchor{http://www.informatik.uni-halle.de/}{Martin-Luther-Universit{\"a}t 
Halle-Wittenberg} (Germany),
\ccAnchor{http://www.mpi-sb.mpg.de/}{Max-Planck Institut f{\"u}r Informatik},
Saarbr\"ucken (Germany),
\ccAnchor{http://info.risc.uni-linz.ac.at/}{{\sc Risc}} Linz (Austria)
\ccAnchor{http://www.math.tau.ac.il/}{Tel-Aviv University} (Israel), and
\ccAnchor{http://www.cs.uu.nl/}{Utrecht University} (The Netherlands). 
You can find more information on the project on the 
\ccAnchor{http://www.cs.uu.nl/CGAL/}{\cgal\ home page}
\ccTexHtml{at URL {\tt http://www.cgal.org}}{}.

Should you have any questions, comments, remarks or criticism concerning 
\cgal, please send a message to 
\ccTexHtml{{\tt contact@cgal.org}}{<A HREF="mailto:contact@cgal.org">&#60;contact@cgal.org&#62;</A>}.


\section*{Editorial Committee}

Andreas Fabri ({\sc Inria} Sophia-Antipolis) \\
Bernd G\"artner (ETH Z\"urich) \\
Susan Hert (Max-Planck Institut f\"ur Informatik)\\
Shai Hirsch (Tel-Aviv University) \\
Michael Hoffmann (ETH Z\"urich) \\
Lutz Kettner (University of North Carolina at Chapel Hill) \\
Dmitrii Pasechnik (Delft University) \\
Sylvain Pion ({\sc Inria} Sophia-Antipolis)\\
Remco Veltkamp (Utrecht University)\\
Mariette Yvinec ({\sc Inria} Sophia-Antipolis)\\

\section*{Authors}

Herv\'e Br\"onnimann ({\sc Inria} Sophia-Antipolis). \\
Stefan Schirra (Max-Planck Institut f\"ur Informatik).\\
Michael Seel (Max-Planck Institut f\"ur Informatik)

\section*{Design and Implementation History}

This higher-dimensional kernel is the result of a long evolving
development. A first version of the kernel was offered as a LEDA
extension package ddgeo by Kurt Mehlhorn and Michael Seel. The
original design was driven by the realization of a d-dimensional
convex hull data type developed at the Max-Planck Institut f\"ur
Informatik.

The code base was discussed and reviewed within the CGAL kernel group
(of the low-dimensional kernel).  This led to the identification of
the concept interfaces and in parallel to adaptations according to the
evolvement of the low-dimensional kernel.  The kernel was revised
based on suggestions by Herv\'e Br\"onnimann, Michael Hoffmann, and
Stefan Schirra. It is currently maintained by Michael Seel.

\section*{Acknowledgement}

This work was supported by ESPRIT IV Long Term Research Projects
No.~21957 (CGAL) and No.~28155 (GALIA).


