% +------------------------------------------------------------------------+
% | Reference manual page: surface_mesher.tex
% +------------------------------------------------------------------------+
% | 01.12.2005   Author
% | Package: Package
% | 
\RCSdef{\RCSsurfacemesherRev}{$Revision$}
\RCSdefDate{\RCSsurfacemesherDate}{$Date$}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefFunction}{make_surface_mesh<C2T3, Oracle,
Criteria, Tag>}  %% add template arg's if necessary

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[function]{} %% add further index entries

\ccDefinition
  
The function \ccRefName\ computes a two dimensional mesh 
approximating  a surface.

The template parameter \ccc{Oracle} describes the type of the 
surface  to be meshed. 
The plugged in class 
has to be a model of the concept \ccc{SurfaceOracle}.

The output mesh satifies the requirements specified by the user
in an object of the class \ccc{Criteria}.
The class \ccc{Criteria} has to be
a model of the concept \ccc{SurfaceMeshCriteria}.

 The class \ccc{C2T3}
is required to be a model of the concept
\ccc{PureComplex_2InTriangulation_3}.
The object \ccc{c2t3} of type \ccc{C2T3} which is passed by reference
is used to maintain  the current surface mesh and stores
the final mesh at the end of the procedure.
Each object of type \ccc{C2T3} has a pointer to 
a three dimensional  Delaunay triangulation.
The vertex and cell base classes of this triangulation
have  to be  models  of the concepts 
\ccc{SurfaceMeshVertexBase_3} and 
\ccc{SurfaceMeshCellBase_3}, respectively.

The Delaunay refinement
process is started with an initial set of points which is the union 
of two sets: the
set of vertices in the initial  triangulation pointed to by 
\ccc{c2t3} and a set of
points output by the method \ccc{surf.initial_points()}.
This initial set of points is required to include at least one point
on each connected components of the surface to meshed.

The fourth template parameter is a tag whose type influences the behaviour of the
meshing algorithm. The function \ccRefName\  has specialized versions
for the following  tag types~: \\
\ccc{Manifold_tag}: the output mesh is guaranteed to be a manifold
surface without boundary.\\
\ccc{Manifold_with_boundary_tag}~:the output mesh is guaranteed to be
manifold but may have boundaries.\\
\ccc{Non_manifold_tag} : the algorithm relies on the given criteria and
guarantees nothing else.



\ccInclude{CGAL/make_surface_mesh.h}

\ccGlobalFunction{template <class C2T3,
                            class Oracle,
                            class Criteria,
                            class Tag >
void make_surface_mesh(C2T3& c2t3,
                       Oracle surf,
                       Criteria criteria,
                       Tag = Non_manifold_tag());}


 

%\ccIsModel

%Concept

\ccSeeAlso
%\ccc{Complex2InTriangulation3} \\
\ccc{PureComplex_2InTriangulation_3} \\
\ccc{SurfaceMeshCellBase_3} \\
\ccc{SurfaceMeshVertexBase_3} \\
\ccc{SurfaceOracle} \\
\ccc{SurfaceMeshCriteria} \\



%\ccExample

%A short example program.
%Instead of a short program fragment, a full running program can be
%included using the 
%\verb|\ccIncludeExampleCode{Package/surface_mesher.C}| 
%macro. The program example would be part of the source code distribution and
%also part of the automatic test suite.

%\begin{ccExampleCode}
%void your_example_code() {
%}
%\end{ccExampleCode}

%% \ccIncludeExampleCode{Package/make_surface_mesh.C}

\end{ccRefFunction}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

