% +------------------------------------------------------------------------+
% | Reference manual page: Surface_mesh_standard_criteria.tex
% +------------------------------------------------------------------------+
% | 08.12.2005   Author
% | Package: Package
% | 
\RCSdef{\RCSSurfacemeshstandardcriteriaRev}{$Revision$}
\RCSdefDate{\RCSSurfacemeshstandardcriteriaDate}{$Date$}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefClass}{Surface_mesh_standard_criteria<FT>}  %% add template arg's if necessary

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[class]{} %% add further index entries

\ccDefinition
  
The class \ccRefName\  implements  the most commonly used combination
of meshing criteria. It involves mainly three criteria which are
in order~: \\
- a lower bound on the minimum angle of a facet. \\
- an upper bound on the radius of surface Delaunay balls.
 A surface Delaunay ball is a  ball circumscribed to a mesh facet 
and  centered on the surface. Such a ball exists for each facet
of the current mesh.
Indeed  the current surface mesh, 
is  the restricted Delaunay triangulation of the current sampling
which is just the set of facets in the Delaunay triangulation of
the sampling  which do have a Delaunay surfacic ball. \\
- an upper bound on the center-center distances of mesh facets.
  The center-center distances of a mesh facet 
  is the distances between the facet circumcenter and the 
 centers of its  surface Delaunay balls. 


\ccInclude{Surface_mesh_standard_criteria.h}

\ccIsModel

\ccc{SurfaceMeshCriteria}

%\ccTypess

%\ccTypedef{FT}{some nested types}

\ccCreation
\ccCreationVariable{criteria}  %% choose variable name

\ccConstructor{Surface_mesh_standard_criteria();}{default constructor.}
\ccConstructor{Surface_mesh_standard_criteria(FT angle_bound, 
                                              FT radius_bound
                                              FT distance_bound);}
{returns a \ccRefName\ with \ccc{angle_bound}, \ccc{radius_bound},
\ccc{distance_bound} as repective bounds for the minimum angle,
the radius of the surface Delaunay balls 
and the center-center distances.}


%\ccOperations

%\ccMethod{void foo();}{some member functions}

\ccSeeAlso

\ccc{surface_mesher<C2t3,Oracle,Criteria,Tag>}


%\ccExample

%A short example program.
%Instead of a short program fragment, a full running program can be
%included using the 
%\verb|\ccIncludeExampleCode{Package/Surface_mesh_standard_criteria.C}| 
%macro. The program example would be part of the source code distribution and
%also part of the automatic test suite.

%\begin{ccExampleCode}
%void your_example_code() {
%}
%\end{ccExampleCode}

%% \ccIncludeExampleCode{Package/Surface_mesh_standard_criteria.C}

\end{ccRefClass}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

