% +------------------------------------------------------------------------+
% | Reference manual page: Apollonius_graph_euclidean_traits_2.tex
% +------------------------------------------------------------------------+
% | 12.04.2000   Author
% | Package: Package
% | 
%\RCSdef{\RCSRegulartriangulationtraitsRev}{$Id$}
%\RCSdefDate{\RCSRegulartriangulationtraitsDate}{$Date$}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefClass}{Apollonius_graph_traits_2<K,Method_tag>}
%% add template arg's if necessary

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[class]{} %% add further index entries
\ccDefinition
  
The class \ccRefName\ provides a model for the
\ccc{ApolloniusGraphTraits_2} concept.
This class has two template parameters. The first template parameter
must be a model of the \ccc{Kernel} concept. The second template
parameter corresponds to how predicates are evaluated. There are two
predefined possible values for \ccc{Method_tag}, namely
\ccc{CGAL::Sqrt_field_tag} and \ccc{CGAL::Ring_tag}. The first one
must be used when the number type used in the representation supports
the exact evaluation of signs of expressions involving all four basic
operations and square roots, whereas the second one requires the exact
evaluation of signs of ring-type expressions, i.e., expressions
involving only additions, subtractions and multiplications. The
default value for \ccc{Method_tag} is \ccc{CGAL::Ring_tag}.
%
The way the predicates are evaluated is discussed in
\cite{cgal:ke-ppawv-02,cgal:ke-rctac-03}.


\ccInclude{CGAL/Apollonius_graph_traits_2.h}

\ccIsModel
\ccc{ApolloniusGraphTraits_2}

\ccCreationVariable{traits}
\ccCreation
\ccThree{Apollonius_graph_traits_2<K,Method_tag>}
{traits = other}{}
\ccThreeToTwo
%
\ccConstructor{ Apollonius_graph_traits_2<K,Method_tag>();}
              {Default constructor.}
\ccGlue
\ccConstructor{
Apollonius_graph_traits_2<K,Method_tag>(Apollonius_graph_traits_2<K,Method_tag> other);}
{Copy constructor.}
\ccGlue
\ccMethod{Apollonius_graph_traits_2<K,Method_tag>
operator=(Apollonius_graph_traits_2<K,Method_tag>
other);}{Assignment operator.}


\ccSeeAlso
\ccc{Kernel}\\
\ccc{ApolloniusGraphTraits_2} \\
\ccc{CGAL::Ring_tag}\\
\ccc{CGAL::Sqrt_field_tag}\\
\ccc{CGAL::Apollonius_graph_2<Gt,Agds>}\\
\ccc{CGAL::Apollonius_graph_filtered_traits_2<CK,CM,EK,EM,FK,FM>}

\end{ccRefClass}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

