\ccRefPageBegin

\begin{ccRefConcept}{GeneralPolygonSetTraits_2}

\ccThree{GeneralPolygonSetTraits_2}{General_polygon_with_holes_2}{}
\ccThreeToTwo

\ccDefinition
% ===========
This concept defines the minimal set of geometric predicates needed to
perform the Boolean-set operations. It refines the $x$-monotone
arrangement-traits concept. In addition to the \ccc{Point_2} and
\ccc{X_monotone_curve_2} types defined in the generalized concept, it defines
a type that represents a general polygon and another one that represents
general polygon with holes. It also requires operations that operate on these
types.

\ccRefines
\ccc{ArrangementXMonotoneTraits_2}

\ccTypes
% ======

\ccNestedType{Polygon_2}{represents a general polygon.}
\ccGlue
\ccNestedType{Polygon_with_holes_2}{represents a general polygon
  with holes.}

\ccNestedType{Curve_const_iterator}
{A const iterator of curves. Its value type is const
\ccc{X_monotone_curve_2}.}

\ccHeading{Functor Types}
% =======================

\ccThree{Construct_polygon_2}{}{\hspace*{\ccwComment}}
\ccThreeToTwo

\ccNestedType{Construct_polygon_2}
{a functor that constructs a general polygon from a range of
$x$-monotone curves. It uses the operator\\
 \ccc{void operator() (InputIterator begin, Input iterator end,
                       Polygon_2 & pgn)}, \\
 parameterized by the \ccc{InputIterator} type.}

\ccNestedType{Construct_curves_2}
{a functor that returns a pair that consists of the begin and
 past-the-end iterators of the $x$ monotone curves of the boundary of
 a given general polygon. It uses the operator\\
 \ccc{std:pair<Curve_const_iterator,
               Curve_const_iterator>
  operator() (const Polygon_2 & pgn)}.}

\ccCreation
\ccCreationVariable{traits}
% =========================

\ccConstructor{GeneralPolygonSetTraits_2();}{default constructor.}
\ccGlue
\ccConstructor{GeneralPolygonSetTraits_2(GeneralPolygonSetTraits_2 other);}
{copy constructor}
\ccGlue
\ccMethod{GeneralPolygonSetTraits_2  operator=(other);}{assignment operator.}


\ccHeading{Accessing Functor Objects}
%====================================

\ccMethod{Construct_polygon_2 construct_polygon_2_object();}
{returns a functor that constructs a general polygon.}

\ccMethod{Construct_curves_2 construct_curves_2_object();}
{returns a functor that obtains the curves of a general polygon.}

\ccHeading{Functor Types}
%========================
\ccNestedType{Is_valid_2}
{provides the operators~: \\
 \ccc{Boolean operator() (Polygon_2 & pgn)} \\
 which returns \ccc{true} if the \ccc{pgn} is valid, and \ccc{false}
 otherwise; and~: \\
 \ccc{Boolean operator(Polygon_with_holes_2 & pgn_with_holes) ()} \\
 which returns \ccc{true} if the polygon with holes \ccc{pgn_with_holes} 
 is valid, and \ccc{false} otherwise.
 A polygon of type \ccc{Polygon_2} is valid, if it is strictly simple.
 A polygon of type \ccc{Polygon_with_holes_2} is valid, if its outer 
 boundary is simple and oriented counterclockwise, each one of its holes 
 is simple, oriented clockwise, and contained inside the outer boundary, 
 and the outer boundary and the outer boundary of the holes are pairwise 
 disjoint, except perhaps at the vertices. This functionality is used to
 verify precondition of some of the operations.}

\ccHasModels
%===========
\ccc{CGAL::Gps_segment_traits_2<Kernel,Container,ArrSegmentTraits>}\\
\ccc{CGAL::Gps_circle_segment_traits_2<Kernel>}\\
\ccc{CGAL::Gps_traits_2<ArrTraits,GeneralPolygon>}

\ccSeeAlso
% ========
\ccSeeAlso
  \ccc{Arrangement_2}\lcTex{(\ccRefPage{Arrangement_2})}\\
  \ccc{ArrangementXMonotoneTraits_2}\lcTex{(\ccRefPage{ArrangementXMonotoneTraits_2})}

\end{ccRefConcept}

\ccRefPageEnd
