\ccRefPageBegin

\def\ccLongParamLayout{\ccFalse}
\begin{ccRefConcept}{GeneralPolygonWithHoles_2}

\ccTypes
% ======
\ccThree{GeneralPolygonWithHoles}{Hole_const_iterator~}{}
\ccThreeToTwo

% \ccNestedType{Size}{number of holes size type.}

\ccNestedType{General_polygon_2}{general-polygon type used to
represent the outer boundary and each hole.}

\ccNestedType{Hole_const_iterator}{bidirectional iterator
  over the polygonal holes. Its value type is
  \ccc{General_polygon_2}.}

\ccDefinition
% ===========
A model of this concept represents a general polygon with holes. The
concept requires the ability to access the general polygon that
represents the outer boundary and the general polygons that represent
the holes.

% \lcTex{\ccwParamIndent=0mm}
\ccThree{GeneralPolygonWithHoles_2}{polygon.outer_boundary()~~~}{}
\ccThreeToTwo

\ccCreation
\ccCreationVariable{polygon}

\ccConstructor{GeneralPolygonWithHoles_2();}{default constructor.}
\ccGlue
\ccConstructor{GeneralPolygonWithHoles_2(GeneralPolygonWithHoles_2 other);}
{copy constructor.}
\ccGlue
\ccMethod{GeneralPolygonWithHoles_2 operator=(other);}{assignment operator.}

\ccConstructor{template <class InputIterator>
GeneralPolygonWithHoles_2(General_polygon_2 & outer,
                          InputIterator begin, InputIterator end);}
{constructs a general polygon with holes using a given general polygon
as the outer boundary and a given range of holes. The holes must be
pairwise disjoint in their interiors.}

\ccAccessFunctions
% ================

\ccMethod{Hole_const_iterator holes_begin() const;}
{returns the begin iterator of the holes.}
\ccGlue
\ccMethod{Hole_const_iterator holes_end() const;}
{returns the past-the-end iterator of the holes.}

\ccMethod{const General_polygon_2 & outer_boundary() const;}
{returns the general polygon that represents the outer boundary.
\ccPrecond{The polygon must not be unbounded.}}

\ccPredicates
% ===========
\ccMethod{bool is_unbounded();}
{returns \ccc{true} if the outer boundary exists, and \ccc{false}
otherwise.}

\ccHasModels
%===========
\ccc{CGAL::General_polygon_with_holes_2<General_polygon>}

\end{ccRefConcept}

\ccRefPageEnd
