%%
%%  *** CGAL Installation Guide ***
%%
%% file:     appendix.tex
%%
%% authors:  Michael Hoffmann, Dima Pasechnik and Wieger Wesselink
%%
%% $Id$
%%


\section{Compiler Workarounds}
\index{compilers!workarounds}\index{workaround flags}

A number of boolean flags are used to workaround compiler bugs and
limitations. They all  start
with the prefix \texttt{CGAL\_CFG}. These flags are used to work
around compiler bugs and limitations. For example, the flag
\texttt{CGAL\_CFG\_NO\_CPP0X\_LONG\_LONG} denotes that the compiler does not
know the type \texttt{long long}.

For each compiler a file \texttt{<CGAL/compiler\_config.h>}
\index{files!\texttt{compiler\_config.h}} is defined, with the correct
settings of all flags. This file is generated automatically by 
\cmake, and it is located in the \texttt{include} directory of
where you run \cmake. For an in-source configuration this means
\texttt{CGAL-3.x/include}.

The test programs used to generate the \texttt{compiler\_config.h}
file can be found in \texttt{config/testfiles}.
\index{directories!config/testfiles@\texttt{config/testfiles}} Both
\texttt{compiler\_config.h} and the test programs contain a short
description of the problem. In case of trouble with one of the
\texttt{CGAL\_CFG} flags, it is a good idea to take a look at it.

The file \texttt{CGAL/compiler\_config.h} is included from
\texttt{<CGAL/config.h>}.\index{files!\texttt{config.h}}
which is included by all \cgal\ header files.

\section{Compiler Optimizations\label{sec:compiler-optimisations}}
\index{compilers!optimization}
\index{optimization compiler flags}

By default \cmake\ generates makefiles for Release mode, with 
optimization flags switched on, and vcproj files for Release
and Debug modes.



\section{Scripts}

\subsection{\texttt{cgal\_create\_cmake\_script\label{sec:create_cgal_cmake_script}}}
\TTindex{cgal\_create\_cmake\_script}\index{scripts!\texttt{cgal\_create\_cmake\_script}}

The Bourne-shell script \texttt{cgal\_create\_cmake\_script} is contained in the
\cgaldir\texttt{/scripts} directory. It can be used to create
\texttt{CmakeLists.txt} files for compiling \cgal\ applications. Executing
\texttt{cgal\_create\_cmake\_script} in an application directory creates a
\texttt{CMakeLists.txt} containing rules for every \texttt{*.cpp} file
there. Currently, that script only works for applications that only need
the CGAL and CGALCore libraries.


%%
%% EOF
%%


