\ccHtmlNoClassLinks
\begin{ccRefFunction}{operator<<}
\label{ref_arr_operator_leftshift}

\ccDefinition

%%%%

Inserts an arrangement into a given output stream using the
output format defined by the \ccc{Arr_text_formatter} class --- that is,
only the basic geometric and topological features of the arrangement are
written, without any auxiliary data that may be attached to the
\dcel\ features.

\ccInclude{CGAL/IO/Arr_iostream.h}

\ccGlobalFunction{template<typename Traits, typename Dcel>
            std::ostream& operator<< (std::ostream& os,
                                      const Arrangement_2<Traits,Dcel>& arr);}

%%%%

Inserts an arrangement into a given Postscript stream.
Only the basic geometric and topological features of the arrangement are
written. Auxiliary data that might be attached to the \dcel\ features is
lost.

\ccInclude{CGAL/IO/Arr_postscript_file_stream.h}

\ccGlobalFunction{template<typename Traits, typename Dcel>
            Arr_postscript_file_stream& operator<< (std::ostream& os,
                                      const Arrangement_2<Traits,Dcel>& arr);}

%%%%

Inserts a polyline into a given Postscript stream.
Only the basic geometric and topological features of the polylines are
written. Auxiliary data that might be attached is lost.
    
\ccInclude{CGAL/IO/Polyline_postscript_file_stream.h}

\ccGlobalFunction{template<typename SegmentTraits>
            Postscript_file_stream& operator<< (std::ostream& os,
                                  const Polyline_2<SegmentTraits>& polyline);}
%%%%

Inserts an arrangement-with-history into a given
output stream using the default output format.

\ccInclude{CGAL/IO/Arr_with_history_iostream.h}

\ccGlobalFunction{template<typename Traits, typename Dcel>
            std::ostream& operator<< (std::ostream& os,
                         const Arrangement_with_history_2<Traits,Dcel>& arr);}

\ccSeeAlso
  \ccc{read}\lcTex{(\ccRefPage{CGAL::read})}\\
  \ccc{write}\lcTex{(\ccRefPage{CGAL::write})}\\
  \lcTex{\ccc{operator>>} page~\pageref{ref_arr_operator_rightshift}}
  \lcRawHtml{<I><A HREF="Function_operator--.html">operator&gt;&gt;</A></I>}

\end{ccRefFunction}
\ccRefPageEnd
