\ccRefPageBegin

\begin{ccRefFunction}{insert_x_monotone_curve}

\ccDefinition

The function \ccRefName\ inserts a given $x$-monotone curve into a
given arrangement. The given curve is inserted into the arrangement as
follows. First, its left endpoint is located. Then, its zone is computed
starting from its left endpoint location. The zone computation terminates
when the right endpoint is reached. A given point-location object is used
for locating the left endpoint of the given curve in the exising
arrangemnt. By default, the function uses the ``walk along line''
point-location strategy --- namely an instance of the class
\ccc{Arr_walk_along_line_point_location<Arrangement_2<Traits,Dcel> >}.

\ccInclude{CGAL/Arrangement_2.h}

\ccGlobalFunction{template<typename Traits, typename Dcel,
                           typename PointLocation>
            void insert_x_monotone_curve (Arrangement_2<Traits,Dcel>& arr,
                         const typename Traits::X_monotone_curve_2& xc,
                         const PointLocation& pl = walk_pl);}
Inserts the $x$-monotone curve \ccc{xc} into the arrangement \ccc{arr}. It
uses the point-location object \ccc{pl} to locate the left endpoint of
\ccc{xc} in \ccc{arr}.
\ccPrecond{f provided, \ccc{pl} must be attached to the given arrangement
\ccc{arr}.}

%%%%

\ccGlobalFunction{template<typename Traits, typename Dcel>
            void insert_x_monotone_curve (Arrangement_2<Traits,Dcel>& arr,
                         const typename Traits::X_monotone_curve_2& xc,
                         const Object& obj);}
Inserts the $x$-monotone curve \ccc{xc} into the arrangement \ccc{arr}. 
The object \ccc{obj}, which either wraps a \ccc{Vertex_const_handle}, a
\ccc{Halfedge_const_handle}, or a \ccc{Face_const_handle}, represents the
location of \ccc{xc}'s left endpoint in the arrangement. The zone of
\ccc{xc} is computed strating from the feature represented by \ccc{obj}.
As in the case above, the sone computation terminates, when the right
endpoint is reached.  Thus, point-location is not required.

\ccRequirements
\begin{itemize}
\item The instantiated \ccc{Traits} class must model the
  \ccc{ArrangementXMonotoneTraits_2} concept.
\item The point-location object \ccc{pl}, must model the
  \ccc{ArrangementPointLocation_2} concept.
\end{itemize}
			 
\end{ccRefFunction}

\ccRefPageEnd
