% Reference manual page: ArrangementTraits.tex
% Package: Arrangement_2

\ccRefPageBegin
\begin{ccRefConcept}{ArrangementTraits_2}

\ccDefinition
% ===========
The concept \ccRefName{} allows the construction of arrangement
of {\sl general} planar curves. Models of this concept are used
by the free \ccc{insert()} functions of the arrangement package and
by the \ccc{Arrangement_with_history_2} class.

A model of this concept must define the nested \ccc{Curve_2} type, which
represents a general planar curve that is not necessarily $x$-monotone
and is not necessarily connected. Such curves are eventually subdivided into
$x$-monotone subcurves and isolated points (represented by the \ccc{Point_2}
and \ccc{X_monotone_curve_2} types, defined in the basic traits concept).

\ccRefines
\ccc{ArrangementXMonotoneTraits_2}

\ccTypes
% ======
\ccNestedType{Curve_2}{represents a general planar curve.}

\ccHeading{Functor Types}
% =======================
\ccThree{Compare_y_at_x_2}{}{\hspace*{14cm}}
\ccThreeToTwo

\ccNestedType{Make_x_monotone_2}
{provides the operator (parameterized by the \ccc{OutputIterator} type)~:
 \begin{itemize}
 \item \ccc{OutputIterator operator() (Curve_2 c, OutputIterator oi)}\\
 which subdivides the input curve \ccc{c} into $x$-monotone subcurves and
 isolated points, and inserts the results into a container through the
 given output iterator. The value type of \ccc{OutputIterator} is
 \ccc{CGAL::Object}, where each \ccc{Object} wraps either an
 \ccc{X_monotone_curve_2} instance or a \ccc{Point_2} instance. The
 operator returns a past-the-end iterator for the output sequence.
 \end{itemize}}

\ccThree{Construct_x_monotone_curve_2~~~}{}{\hspace*{7cm}}
\ccThreeToTwo

\ccCreationVariable{traits}
% \ccCreation
% =========

\ccHeading{Accessing Functor Objects}
% ===================================
\ccMethod{Make_x_monotone_2 make_x_monotone_2_object();}{}

\ccHasModels
% ==========
\ccc{CGAL::Arr_segment_traits_2<Kernel>}\\
\ccc{CGAL::Arr_non_caching_segment_traits_2<Kernel>}\\
\ccc{CGAL::Arr_polyline_traits_2<SegmentTraits>}\\
\ccc{CGAL::Arr_circle_segment_traits_2<Kernel>}\\
\ccc{CGAL::Arr_conic_traits_2<RatKernel,AlgKernel,NtTraits>}\\
\ccc{CGAL::Arr_rational_arc_traits_2<AlgKernel,NtTraits>}\\
\ccc{CGAL::Arr_curve_data_traits_2<Tr,XData,Mrg,CData,Cnv>}\\
\ccc{CGAL::Arr_consolidated_curve_data_traits_2<Traits,Data>}

\ccSeeAlso
% ========
\ccc{ArrangementBasicTraits_2}\lcTex{ 
      (\ccRefPage{ArrangementBasicTraits_2})}\\
\ccc{ArrangementXMonotoneTraits_2}\lcTex{ 
      (\ccRefPage{ArrangementXMonotoneTraits_2})}\\
\ccc{ArrangementLandmarkTraits_2}\lcTex{ 
      (\ccRefPage{ArrangementLandmarkTraits_2})}

\end{ccRefConcept}

\ccRefPageEnd
