\chapter{Introduction}
\input{common_intro.tex}

{This} part of the reference manual covers the kernel.
The kernel contains objects of constant size, such as point, vector, 
direction, line, ray, segment, triangle, iso-oriented rectangle and 
tetrahedron. 
With each type comes a set of functions which can be applied to an object 
of this type.  
You will typically find access functions (e.g.\ to the coordinates of a point), 
tests of the position of a point relative to the object, a function returning 
the bounding box, the length, or the area of an object, and so on.
The \cgal\ kernel further contains basic operations such as affine
transformations, detection and computation of intersections, and distance 
computations.

\section{Robustness}
The correctness proof of nearly all geometric algorithms presented
in theory papers assumes exact computation with real numbers.
This leads to a fundamental problem with the implementation of geometric
algorithms.
Naively, often the exact real arithmetic is replaced by inexact floating-point 
arithmetic in the implementation.
This often leads to acceptable results for many input data.
However, even for the implementation of the simplest geometric 
algorithms this simplification occasionally does not work.
Rounding errors introduced by an inaccurate arithmetic may lead to 
inconsistent decisions, causing unexpected failures for some correct 
input data.
There are many approaches to this problem, one of them is to compute
exactly (compute so accurate that all decisions made by the algorithm
are exact) which is possible in many cases but more expensive
than standard floating-point arithmetic.
C.~M.~Hoffmann~\cite{h-gsm-89,h-pargc-89} illustrates some 
of the problems arising in the implementation of geometric algorithms
and discusses some approaches to solve them. 
A more recent overview is given in \cite{s-rpgc-99}.
The exact computation paradigm is discussed by Yap and Dub\'e 
\cite{yd-ecp-95} and Yap \cite{y-tegc-97}.

In \cgal\ you can choose the underlying number types and arithmetic.  
You can use different types of arithmetic simultaneously and the choice can 
be easily changed, e.g.\ for testing.  
So you can choose between implementations with fast but occasionally inexact 
arithmetic and implementations guaranteeing exact computation and exact 
results.  
Of course you have to pay for the exactness in terms of execution time 
and storage space.  
See the section on number types in the Support Library
for more details on number types and their capabilities and performance.

\section{CGAL and LEDA}

\ccAnchor{http://www.algorithmic-solutions.com/}{\leda}
\ccTexHtml{\footnote{\tt http://www.algorithmic-solutions.com/}}{}
is a {\em Library of Efficient Data types and Algorithms} partially developed 
at the {\em Max-Planck Institut f\"ur Informatik}, Saarbr\"ucken,
and the {\em University of Trier}, Germany.
\cgal\ is independent of \leda, but the two work well together.  In particular
the exact number types provided by \leda\ are a way to deal with the robustness
issues of the geometric algorithms of \cgal.
