% +------------------------------------------------------------------------+
% | Reference manual page: LargestEmptyIsoRectangleTraits_2.tex
% +------------------------------------------------------------------------+
% | 06.04.2000   Author
% | Package: Package
% | 
\RCSdef{\RCSSnapRoundingTraits_2Rev}{$Revision$}
\RCSdefDate{\RCSSnapRoundingTraits_2Date}{$Date$}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+

\begin{ccRefConcept}{SnapRoundingTraits_2}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries

\ccDefinition
  
The concept \ccRefName\ lists the set of requirements that must be fulfilled by
an instance of the \ccc{Traits} template-parameter of
the function \ccc{snap_rounding_2<Traits,InputIterator,OutputContainer>}.
This concept provides the types of the geometric primitives used in
this class and some function object types for the required
predicates on those primitives.

\ccTypes
\ccNestedType{Point_2}{The point type.}
\ccGlue
\ccNestedType{Segment_2}{The segment type.}
\ccGlue
\ccNestedType{X_curve}{The x-monotone curve type.}
\ccGlue
\ccNestedType{Iso_rectangle_2}{The iso-rectangle type.}

\ccNestedType{Compare_x_2}{Predicate object. Must provide
the operator
\ccc{Comparison_result operator()(Point_2 p, Point_2 q)}
which returns 
\ccc{SMALLER, EQUAL} or \ccc{LARGER} according to the
$x$-ordering of points \ccc{p} and \ccc{q}.}
\ccGlue
\ccNestedType{Compare_y_2}{Predicate object. Must provide
the operator
\ccc{Comparison_result operator()(Point_2 p, Point_2 q)}
which returns
\ccc{SMALLER, EQUAL} or \ccc{ LARGER}
according to the
$y$-ordering of points \ccc{p} and \ccc{q}.}
\ccGlue

\ccNestedType{Snap_2}{Rounds a point to a center of a pixel (unit square)
in the grid used by the Snap Rounding algorithm. Note that no conversion
to an integer grid is done yet. Must have the syntax
\ccc{void operator()(Point_2 p,FT pixel_size,FT &x,FT &y)} where $p$ is the
input point, \ccc{pixel_size} is the size of the pixel of the grid,
and $x$ and $y$ are the $x$ and $y$-coordinates of the rounded point
respectively.}

\ccNestedType{Integer_grid_point_2}{Convert coordinates
into an integer representation where one unit is equal to pixel size.
For instance, if a point has the coordinates $(3.7,5.3)$ and the pixel
size is $0.5$, then the new point will have the coordinates of $(7,10)$.
Note, however, that the number type remains the same here, although
integers are represented.
Must have the syntax \ccc{Point_2 operator()(Point_2 p,NT pixel_size)}
where $p$ is the converted point and \ccc{pixel_size} is the size of the pixel
of the grid.}

\ccNestedType{Minkowski_sum_with_pixel_2}{Returns the vertices of a polygon,
which is the Minkowski sum of a segment and a square centered at the origin
with edge size \ccc{pixel edge}.
Must have the syntax
\ccc{void operator()(std::list<Point_2>& vertices_list, Segment_2 s,
NT unit_square)}
where {\ccc vertices\_list} is the list of the vertices of the Minkowski sum
polygon, $s$ is the input segment and {\ccc unit\_square} is the edge size of
the pixel.}

\ccCreation
\ccCreationVariable{traits}  %% choose variable name
This concept refines the standard concepts DefaultConstructible, Assignable and
CopyConstructible.

% \ccConstructor{SnapRoundingTraits_2();}{Default constructor.}
% \ccGlue
% \ccConstructor{SnapRoundingTraits_2(SnapRoundingTraits_2);}
% {Copy constructor}
% \ccMethod{SnapRoundingTraits_2 operator=(SnapRoundingTraits_2 gtr);}
% {Assignment operator.}

\ccOperations

The following functions construct the required function objects occasionally
referred as functors listed above.
% Each of these objects provide a necessary operation to carry out the
% snap-rounding procedure.

\ccThree{Minkowski_sum_with_pixel_2}{minkowski_sum_with_pixel_2_object();}{}
\ccMethod{Construct_iso_rectangle_2 construct_iso_rectangle_2_object();}{}

\ccMethod{Compare_x_2 compare_x_2_object();}{}                               
\ccGlue
\ccMethod{Compare_y_2 compare_y_2_object();}{}
\ccGlue
\ccMethod{Snap_2 snap_2_object();}{}
\ccGlue
\ccMethod{Integer_grid_point_2 integer_grid_point_2_object();}{}
\ccGlue
\ccMethod{Minkowski_sum_with_pixel_2 minkowski_sum_with_pixel_2_object();}{}
\ccGlue


\ccHasModels
\ccc{CGAL::Snap_rounding_traits<Kernel>}

\ccSeeAlso
\ccc{CGAL::Snap_rounding_2<Traits>}

\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

