% +------------------------------------------------------------------------+
% | Reference manual page: MarchingTetrahedraObserver_3.tex
% +------------------------------------------------------------------------+
% | 27.09.2005   Nico Kruithof
% | Package: Skin_surface
% | 
\RCSdef{\RCSMarchingtetrahedraobserverRev}{$Id$}
\RCSdefDate{\RCSMarchingtetrahedraobserverDate}{$Date$}
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefConcept}{MarchingTetrahedraObserver_3}
\label{pageMarchingTetrahedraObserver}

  Required types and member functions for the \ccRefName\ concept.
  This concept is used to customize the behavior of the marching
  tetrahedra algorithm.

  After the construction of a vertex or a triangle of the mesh, the
  functions \ccc{after_vertex_insertion} and
  \ccc{after_facet_insertion} are called respectively.

%\ccRefines
%\ccc{CopyConstructable}, \ccc{Assignable}.

\ccTypes

\ccThree{Triangulation_cell}{handle to the Cell type of
  the triangulation}{}
\ccThreeToTwo

\ccNestedType{Triangulation_cell_handle}{handle to the Cell type of
  the triangulation}
\ccNestedType{Polyhedron_vertex_handle}{handle to the Vertex type of
  the polyhedron}
\ccGlue
\ccNestedType{Polyhedron_facet_handle}{handle to the Facet type of the
  polyhedron}


\ccCreation
\ccCreationVariable{observer}

\ccConstructor{MarchingTetrahedraObserver_3();}{}
\ccGlue
\ccConstructor{MarchingTetrahedraObserver_3( const
  MarchingTetrahedraObserver_3& traits2);}{ copy constructor.}

\ccOperations

\ccMethod{void after_vertex_insertion(Triangulation_cell_handle ch,
  int i, int j, Polyhedron_vertex_handle vh);}{ this function is
  called after the insertion of a new vertex to the mesh.
  \ccPrecond{\ccc{ch} is finite.}}
\ccMethod{void after_facet_insertion(Triangulation_cell_handle ch,
  Polyhedron_facet_handle fh);}{this function is called after the
  insertion of a vertex to the mesh. 
  \ccPrecond{\ccc{ch} is finite.}}

\ccHasModels

\ccRefIdfierPage{CGAL::Marching_tetrahedra_observer_default_3<MarchingTetrahedraTraits_3>}
\ccRefIdfierPage{CGAL::Marching_tetrahedra_observer_skin_surface_3<MarchingTetrahedraTraits_3>}
\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+

