% +------------------------------------------------------------------------+
% | Reference manual page: Volume.tex
% +------------------------------------------------------------------------+
% | 14.05.2004   Peter Hachenberger
% | Package: Nef_3
% | 
\RCSdef{\RCSVolumeRev}{$Id$}
\RCSdefDate{\RCSVolumeDate}{$Date$}
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefClass}[Nef_polyhedron_3<Traits>::]{Volume}

\ccDefinition

A volume is a full-dimensional connected point set in $\mathbb{R}^3$. It is
bounded by several shells, i.e. a connected part of the boundary incident
to a single volume. An entry element to each shell is provided by the 
iterator range (\ccc{shells_begin()}/\ccc{shells_end()}). A 
\ccc{Shell_entry_iterator} is assignable to \ccc{SFace_handle}.

\ccInclude{CGAL/Nef_polyhedron_3.h}

\ccTypes
\ccThree{Shell_entry_const_iterator}{shells_begin() const;}{}
\ccThreeToTwo

The following types are the same as in \ccc{Nef_polyhedron_3<Traits>}.

\ccNestedType{Mark}{type of mark.}

\ccNestedType{Object_list}{list of Object handles.}

\ccNestedType{Volume_const_handle}{const handle to Volume.}
\ccGlue
\ccNestedType{Shell_entry_const_iterator}
{const iterator over the entries to all shells adjacent to a volume.}

\ccCreation
\ccCreationVariable{c}

There is no need for a user to create a \ccc{Volume} explicitly. The
class \ccc{Nef_polyhedron_3<Traits>} manages the needed volumes internally.

%\ccConstructor{Volume();}{ default constructor.}

\ccOperations

\ccThree{Shell_entry_const_iterator}{h.halfedge()const}{}

\ccMethod{const Mark& mark() const;}{the mark of \ccVar\ .}

\ccMethod{Shell_entry_const_iterator  shells_begin() const;}
{const iterator over the entries to all shells adjacent to \ccVar\ .}

\ccMethod{Shell_entry_const_iterator  shells_end() const;}
{past-the-end iterator.}

\ccSeeAlso

\ccRefIdfierPage{CGAL::Nef_polyhedron_3<Traits>::SFace}

\ccTagDefaults
\end{ccRefClass}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+
