% +------------------------------------------------------------------------+
% | Reference manual page: Nef_polyhedron_3.tex
% +------------------------------------------------------------------------+
% | 26.02.2004   Peter Hachenberger
% | Package: Nef_3
% | 
\RCSdef{\RCSNefThreeRev}{$Id$}
\RCSdefDate{\RCSNefThreeDate}{$Date$}
% +------------------------------------------------------------------------+

\begin{ccRefClass}{Nef_polyhedron_3<Traits>}

\ccDefinition

A 3D Nef polyhedron is a subset of the 3-dimensional space that is the
result of forming complements and intersections starting from a finite
set \ccc{H} of 3-dimensional halfspaces. Nef polyhedra are closed
under all binary set operations, i.e., intersection, union,
difference, complement, and under the topological operations boundary,
closure, and interior.

A 3D Nef polyhedron can be represented by the local pyramids of the minimal
elements of its incidence structure. Without going into to much detail, a local
pyramid essentially reflects the topologic and geometric situation at a certain
location in a point set. For finite polyhedra the minimal elements 
of the incidence structure are vertices only. This means, that it suffices to 
model the topological and geometric situation of the vertices. For 
3D Nef polyhedra, the local pyramid of a vertex is represented by 
a planar Nef polyhedra embedded on a sphere.

A \ccc{Nef_polyhedron_3} consists of vertices \emph{V}, a sphere map for each
vertex in \emph{V}, edges \emph{E}, facets \emph{F}, volumes \emph{C}, a mark
for every item, and an incidence relation on them. Each edge and each facet
is represented by two halfedges or two halffacets, respectively.

\ccInclude{CGAL/Nef_polyhedron_3.h}

\ccParameters

\begin{tabbing}
\ccc{template <} \=\ccc{class Nef_polyhedronTraits_3,}\\
                 \>\ccc{class Nef_polyhedronItems_3 = CGAL::Default_items<Nef_polyhedronTraits_3>,}\\
                 \>\ccc{class Nef_polyhedronMarks = bool >}\\
    \ccc{class Nef_polyhedron_3;}
\end{tabbing}

The first parameter requires one of the following exact kernels:
\ccc{Homogeneous}, \ccc{Simple_homogeneous}, \ccc{Extended_homogeneous} 
parametrized with \ccc{Gmpz}, \ccc{leda_integer} or any other number type
modeling \Z, or \ccc{Cartesian}, \ccc{Simple_cartesian}, 
\ccc{Extended_cartesian} parametrized with \ccc{Gmpq}, \ccc{leda_rational},
\ccc{Quotient<Gmpz>} or any other number type modeling \Q.

The second parameter and the third parameter are for future considerations.
Neither \ccc{Nef_polyhedronItems_3} nor \ccc{Nef_polyhedronMarks} is
specifed, yet. Do not use any other than the default types for these two 
template parameters.

\ccTypes

\ccTwo{Nef_polyhedron_3<Traits>::SHalfedge_const_iterator;}{}

\ccNestedType{Traits}{traits class selected for \ccc{Nef_polyhedronTraits_3}.}
\ccGlue
\ccNestedType{Mark}{All object (vertices, edges, etc.) are attributed by a Mark. 
  Mark equals bool.} 

\ccNestedType{size_type}{size type of \ccc{Nef_polyhedron_3}.}

\ccNestedType{Vertex_const_handle}{non-mutable handle to a vertex.}
\ccGlue
\ccNestedType{Halfedge_const_handle}{non-mutable handle to a halfedge.}
\ccGlue
\ccNestedType{Halffacet_const_handle}{non-mutable handle to a halffacet.}
\ccGlue
\ccNestedType{Volume_const_handle}{non-mutable handle to a volume.}
\ccGlue
\ccNestedType{SVertex_const_handle}{non-mutable handle to a svertex.}
\ccGlue
\ccNestedType{SHalfedge_const_handle}{non-mutable handle to a shalfedge.}
\ccGlue
\ccNestedType{SHalfloop_const_handle}{non-mutable handle to a shalfloop.}
\ccGlue
\ccNestedType{SFace_const_handle}{non-mutable handle to a sface.}

\ccNestedType{Vertex_const_iterator}{non-mutable iterator over all vertices.}
\ccGlue
\ccNestedType{Halfedge_const_iterator}{non-mutable iterator over all halfeges.}
\ccGlue
\ccNestedType{Halffacet_const_iterator}{non-mutable iterator over all halffacets.}
\ccGlue
\ccNestedType{Volume_const_iterator}{non-mutable iterator over all volumes.}
\ccGlue
\ccNestedType{SVertex_const_iterator}{non-mutable iterator over all svertices.}
\ccGlue
\ccNestedType{SHalfedge_const_iterator}{non-mutable iterator over all shalfedges.}
\ccGlue
\ccNestedType{SHalfloop_const_iterator}{non-mutable iterator over all shalfloops.}
\ccGlue
\ccNestedType{SFace_const_iterator}{non-mutable iterator over all sfaces.}

\ccTwo{Nef_polyhedron_3<Traits>::Object_handle;;;}{}

\ccNestedType{SHalfedge_around_svertex_const_circulator}{non-mutable circulator of shalfedges around a svertex (cw).}
\ccGlue
\ccNestedType{SHalfedge_around_sface_const_circulator}{non-mutable circulator of shalfedges around a sface (ccw).}
\ccGlue
\ccNestedType{SHalfedge_aroud_facet_const_circulator}{non-mutable circulator of shalfedges around a halffacet (ccw).}
\ccGlue
\ccNestedType{SFace_cycle_const_iterator}{non-mutable iterator over the cylces of a sface.}
\ccGlue
\ccNestedType{Halffacet_cycle_const_iterator}{non-mutable iterator over the cylces of a halffacet.}
\ccGlue
\ccNestedType{Shell_entry_const_iterator}{non-mutable iterator providing an entry to each shell. }

\ccNestedType{Object_handle}{a generic handle to an object. 
  The kind of object \ccc{(vertex, halfedge, halffacet, volume, 
    svertex, shalfedge, shalfloop, sface)} can 
  be determined and the object can be assigned to a corresponding
  constant handle by one of the following functions:\\
  \ccc{bool assign(Vertex_const_handle& h, Object_handle)}\\
  \ccc{bool assign(Halfedge_const_handle& h, Object_handle)}\\
  \ccc{bool assign(Halffacet_const_handle& h, Object_handle)}\\
  \ccc{bool assign(Volume_const_handle& h, Object_handle)}\\
  \ccc{bool assign(SVertex_const_handle& h, Object_handle)}\\
  \ccc{bool assign(SHalfedge_const_handle& h, Object_handle)}\\
  \ccc{bool assign(SHalfloop_const_handle& h, Object_handle)}\\
  \ccc{bool assign(SFace_const_handle& h, Object_handle)}\\
  where each function returns \ccc{true} iff the assignment to
  \ccc{h} could be accomplished. }

\ccNestedType{Point_3}{location of vertices.}
\ccGlue
\ccNestedType{Segment_3}{segment represented by a halfedge.}
\ccGlue
\ccNestedType{Vector_3}{direction of a halfedge.}
\ccGlue
\ccNestedType{Plane_3}{plane of a halffacet lies in.}
\ccGlue
\ccNestedType{Aff_transformation_3}{affine transformation.}

\ccNestedType{Polylines_tag}{tag for calling polyline constructor.}

\ccEnum{enum Boundary { EXCLUDED,  INCLUDED }}{construction selection.}
\ccGlue
\ccEnum{enum Content { EMPTY,  COMPLETE }}{construction selection.}
\ccGlue
\ccEnum{enum Intersection_mode { CLOSED_HALFSPACE, OPEN_HALFSPACE,
    PLANE_ONLY }}{intersection selection.}
\ccNestedType{Nef_polyhedron_S2}{a sphere map.}
\ccGlue
\ccNestedType{Polyhedron}{a polyhedral surface.}


\ccCreation
\ccCreationVariable{N}

\ccThree{Nef_polyhedron_3<Traits>;}{N}{}
\ccThreeToTwo

\ccConstructor{Nef_polyhedron_3(Content space = EMPTY);} {
  creates a Nef polyhedron and initializes it to the empty 
  set if \ccc{plane == EMPTY}
  and to the whole space if \ccc{space == COMPLETE}.}

\ccConstructor{Nef_polyhedron_3(const Plane_3& p, 
                                Boundary b = INCLUDED);}{ creates a
  Nef polyhedron containing the halfspace on the negative side of
  \ccc{p} including \ccc{p} if \ccc{b==INCLUDED}, excluding \ccc{p} if
  \ccc{b==EXCLUDED}.}

\ccConstructor{Nef_polyhedron_3(Polyhedron& P);}{
  creates a Nef polyhedron, which represents the same point set as 
  the polyhedral surface \ccc{P} does.}

\ccConstructor{Nef_polyhedron_3(Input_iterator begin, Input_iterator end);}
              {creates a Nef polyhedron consisting of a single polygon
              spanned by the list of points in the iterator range
              \ccc{[begin,end)}. If the points do not on a common
              supporting plane, the constructor tries to triangulate
              the polygon into multiple facets.If the construction does
              not succeed, the empty set is created.}

\ccConstructor{template <class Forward_iterator>
Nef_polyhedron_3(Forward_iterator it, Forward_iterator end,
Polylines_tag)}{The iterator range [it, end) defines a set point
ranges, each of which defines a polyline.}

%\ccConstructor{Nef_polyhedron_3(const char* filename);}{
%  loads a Nef polyhedron from \ccc{filename}.}


\ccHeading{Access Member Functions}

\ccThree{Nef_polyhedron_3<Traits>}{N.number_of_halffacets();}{}

\ccMethod{bool is_simple() const;}{returns true, if \ccVar\ is a 2-manifold.}
\ccGlue
\ccMethod{bool is_valid() const;}{checks the integrity of \ccVar\ .}

%\ccThree{Size_type}{N.number_of_halffacets();}{}

\ccMethod{Size_type number_of_vertices() const;}
{returns the number of vertices.}
\ccGlue
\ccMethod{Size_type number_of_halfedges() const;}
{return the number of halfedges.} 
\ccGlue
\ccMethod{Size_type number_of_edges() const;}
{returns the number of halfedge pairs.}     
\ccGlue
\ccMethod{Size_type number_of_halffacets() const;}
{returns the number of halffacets.}   
\ccGlue
\ccMethod{Size_type number_of_facets() const;}
{returns the number of halffacet pairs.}    
\ccGlue
\ccMethod{Size_type number_of_volumes() const;}
{returns the number of volumes.}   

\ccMethod{Vertex_const_iterator   vertices_begin() const;}{iterator over all vertices.}
\ccGlue
\ccMethod{Vertex_const_iterator   vertices_end()   const;}{past-the-end iterator.}
\ccMethod{Halfedge_const_iterator halfedges_begin()const;}{iterator over all halfedges.}
\ccGlue
\ccMethod{Halfedge_const_iterator halfedges_end()  const;}{past-the-end iterator.}
\ccMethod{Halffacet_const_iterator halffacets_begin() const;}{iterator over all halffacets.}
\ccGlue
\ccMethod{Halffacet_const_iterator halffacets_end() const;}{past-the-end iterator.}
\ccMethod{Volume_const_iterator   volumes_begin() const;}{iterator over all volumes.}
\ccGlue
\ccMethod{Volume_const_iterator   volumes_end()   const;}{past-the-end iterator.}

The following macros are provided: \ccc{CGAL_forall_vertices(v,N)},
\ccc{CGAL_forall_halfedges(e,N)}, \ccc{CGAL_forall_edges(e,N)},
\ccc{CGAL_forall_halffacets(f,N)}, \ccc{CGAL_forall_facets(f,N)},
\ccc{CGAL_forall_volumes(c,N)} where \ccc{N} is a \ccc{Nef_polyhedron_3}.

\ccMethod{Object_handle locate(const Point_3& p) const;}
{returns a generic handle to the object (vertex, edge, facet or volume) which contains the point p in its relative interior.}
%\ccMethod{bool contains(Object_handle h) const;}{}
%\ccMethod{bool contained_in_boundary(Object_handle h) const;}{}

\ccMethod{Nef_polyhedron_S2 get_sphere_map(Vertex_const_iterator v) const;}
{returns the neighborhood of a vertex modeled by a \ccc{Nef_polyhedron_S2}.}

\ccHeading{Point Set Predicates}

\ccThree{Nef_polyhedron_3<Traits>}{N.intersection(N1);}{}

\ccMethod{bool is_empty() const;}{returns true, if \ccVar\ is the 
                                  empty point set.}
\ccGlue
\ccMethod{bool is_space() const;}{returns true, if \ccVar\ is the 
                                  complete 3D space.}

\ccMethod{bool operator==(const Nef_polyhedron_3<Traits>& N1) const;}
{returns true, if \ccVar\ and N1 comprise the same point sets.}
\ccGlue
\ccMethod{bool operator!=(const Nef_polyhedron_3<Traits>& N1) const;}
{returns true, if \ccVar\ and N1 comprise different point sets. }
\ccGlue
\ccMethod{bool operator<(const Nef_polyhedron_3<Traits>& N1) const;}
{returns true, if \ccVar\ is a proper subset of N1. }
\ccGlue
\ccMethod{bool operator>(const Nef_polyhedron_3<Traits>& N1) const;}
{returns true, if \ccVar\ is a proper superset of N1. }
\ccGlue
\ccMethod{bool operator<=(const Nef_polyhedron_3<Traits>& N1) const;}
{returns true, if \ccVar\ is a subset of N1. }
\ccGlue
\ccMethod{bool operator>=(const Nef_polyhedron_3<Traits>& N1) const;}
{returns true, if \ccVar\ is a superset of N1. }

\ccHeading{Unary Set Operations}

\ccMethod{Nef_polyhedron_3<Traits> complement() const;}
{returns the complement of \ccVar\ .}
\ccGlue
\ccMethod{Nef_polyhedron_3<Traits> interior() const;}
{returns the interior of \ccVar\ .}
\ccGlue
\ccMethod{Nef_polyhedron_3<Traits> boundary() const;}
{returns the boundary of \ccVar\ .}
\ccGlue
\ccMethod{Nef_polyhedron_3<Traits> closure() const;}
{returns the closure of \ccVar\ .}
\ccGlue
\ccMethod{Nef_polyhedron_3<Traits> regularization() const;}
{returns the regularization, i.e. the closure of the interior, of \ccVar\ .}

\ccMethod{Nef_polyhedron_3<Traits> operator!() const;}
{returns the complement of \ccVar\ .}

\ccHeading{Binary Set Operations}

\ccMethod{Nef_polyhedron_3<Traits> intersection(const Nef_polyhedron_3<Traits>& N1) const;}
{return the intersection of \ccVar\ and N1.}
\ccGlue
\ccMethod{Nef_polyhedron_3<Traits> join(const Nef_polyhedron_3<Traits>& N1) const;}
{return the union of \ccVar\ and N1. (Note that ''union'' is a C++ keyword and cannot be used for this operation.)}
\ccGlue
\ccMethod{Nef_polyhedron_3<Traits> difference(const Nef_polyhedron_3<Traits>& N1) const;}
{return the difference between \ccVar\ and N1.}
\ccGlue
\ccMethod{Nef_polyhedron_3<Traits> symmetric_difference(const Nef_polyhedron_3<Traits>& N1) const;}
{return the symmetric difference of \ccVar\ and N1.}
\ccGlue
\ccMethod{Nef_polyhedron_3<Traits> intersection(const Plane_3& p, Intersection_mode im) const;}
  {returns intersection of \ccVar\ with
  plane (\ccc{im=PLANE_ONLY}), open halfspace (\ccc{im=OPEN_HALFSPACE}), or closed
  halfspace (\ccc{im=CLOSED_HALFSPACE}). In the latter two cases, the
  halfspaces are on the negative side of the plane \ccc{p}. The function is
  written for the use with standard kernels, where halfspaces are not
  part of the domain. The function does not work in combination with
  an extended kernels or with an unbounded polyhedron.}

\ccMethod{Nef_polyhedron_3<Traits> operator*(const Nef_polyhedron_3<Traits>& N1) const;}
{return the intersection of \ccVar\ and N1.}
\ccGlue
\ccMethod{Nef_polyhedron_3<Traits> operator+(const Nef_polyhedron_3<Traits>& N1) const;}
{return the union of \ccVar\ and N1.}
\ccGlue
\ccMethod{Nef_polyhedron_3<Traits> operator-(const Nef_polyhedron_3<Traits>& N1) const;}
{return the difference between \ccVar\ and N1.}
\ccGlue
\ccMethod{Nef_polyhedron_3<Traits> operator^(const Nef_polyhedron_3<Traits>& N1) const;}
{return the symmetric difference of \ccVar\ and N1.}

\ccMethod{void operator*=(const Nef_polyhedron_3<Traits>& N1);}{intersects \ccVar\ and N1.}
\ccGlue
\ccMethod{void operator+=(const Nef_polyhedron_3<Traits>& N1);}{unites \ccVar\ with N1.}
\ccGlue
\ccMethod{void operator-=(const Nef_polyhedron_3<Traits>& N1);}{subtracts N1 from \ccVar\ .}
\ccGlue
\ccMethod{void operator^=(const Nef_polyhedron_3<Traits>& N1);}{performs a symmetric intersection of \ccVar\ and N1.}

\ccHeading{Operations}

\ccThree{void}{N}{}
\ccThreeToTwo

\ccMethod{void clear(Content space = EMPTY);}
{make \ccVar\ the empty set if \ccc{space == EMPTY} and
 the complete 3D space if \ccc{space == COMPLETE}.}

\ccMethod{void transform(const Aff_transformation_3& aff);}{applies an affine transformation to \ccVar\ .}

%\ccMethod{void dump() const;}{}
\ccMethod{void convert_to_polyhedron(Polyhedron& P) const;}
{converts \ccVar\ into a Polyhedron.~\ccPrecond \ccVar\ is simple.}

\ccMethod{void visit_shell_objects(SFace_const_handle f, Visitor& V) const;}
{calls the visit function of V for every item which belongs to the same shell as sf.}

%\ccMethod{static bool is_standard(const Vertex_const_handle v);}{}
%\ccMethod{static bool is_standard(const Halffacet_const_handle v);}{}
%\ccMethod{static bool is_standard_kernel() { return Infi_box::standard_kernel();}{}
%\ccMethod{static bool is_extended_kernel() { return Infi_box::extended_kernel();}{}
%\ccMethod{static void set_size_of_infimaximal_box(const typename Infi_box::NT& size);}{}

\ccSeeAlso

\ccRefIdfierPage{CGAL::Nef_polyhedron_3<Traits>::Vertex}\\
\ccRefIdfierPage{CGAL::Nef_polyhedron_3<Traits>::Halfedge}\\
\ccRefIdfierPage{CGAL::Nef_polyhedron_3<Traits>::Halffacet}\\
\ccRefIdfierPage{CGAL::Nef_polyhedron_3<Traits>::Volume}\\
\ccRefIdfierPage{CGAL::Nef_polyhedron_3<Traits>::SHalfedge}\\
\ccRefIdfierPage{CGAL::Nef_polyhedron_3<Traits>::SHalfloop}\\
\ccRefIdfierPage{CGAL::Nef_polyhedron_3<Traits>::SFace}\\
\ccRefIdfierPage{CGAL::Nef_polyhedron_S2<Traits>}\\
\ccRefIdfierPage{CGAL::Polyhedron_3<Traits>}



\end{ccRefClass}

% +------------------------------------------------------------------------+
% EOF
% +------------------------------------------------------------------------+
