% +------------------------------------------------------------------------+
% | Reference manual page: PatchableMeshAdaptor_3.tex
% +------------------------------------------------------------------------+
% | 29.08.2005   Laurent Saboret, Pierre Alliez
% | Package: Parameterization
% |
\RCSdef{\RCSPatchableMeshAdaptorRev}{$Revision$}
\RCSdefDate{\RCSPatchableMeshAdaptorDate}{$Date$}
% |
%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefConcept}{PatchableMeshAdaptor_3}

%% \ccHtmlCrossLink{}     %% add further rules for cross referencing links
%% \ccHtmlIndexC[concept]{} %% add further index entries

\ccDefinition

PatchableMeshAdaptor\_3 inherits from concept MeshAdaptor\_3, thus is a concept for a 3D surface mesh.

PatchableMeshAdaptor\_3 adds the ability to support patches and virtual seams. Patches are a subset of a 3D mesh. Virtual seams are the ability to behave exactly as if the surface was "cut" following a certain path.

The main purpose of this feature is to allow the parameterization package to parameterize any 3D surface by decomposing it as a list of topological disks.


\ccHasModels

Adaptators for Polyhedron\_3 and TDS\_2 with 3D points are provided.

\ccRefIdfierPage{CGAL::Mesh_adaptor_polyhedron_3<Traits>} \\


\ccHeading{Design pattern}

PatchableMeshAdaptor\_3 is an Adaptor (see [GOF95]): it changes the interface of a 3D mesh to match the interface expected by class Mesh\_adaptor\_patch\_3.


\ccRefines

MeshAdaptor\_3 \\

In addition to the requirements described in the concept MeshAdaptor\_3,
PatchableMeshAdaptor\_3 provides the following:


\ccCreation
\ccCreationVariable{m}  %% define variable name used by \ccMethod below

Construction and destruction are undefined.


\ccOperations

\textbf{VERTEX INTERFACE:}

\ccMethod{int get_vertex_seaming (Vertex_const_handle vertex) const;}
{
Get/set vertex seaming flag. Default value is undefined.
}
\ccMethod{void set_vertex_seaming (Vertex_handle vertex, int seaming);}
{
}

\textbf{EDGE INTERFACE:}

\ccMethod{int get_halfedge_seaming (Vertex_const_handle source, Vertex_const_handle target) const;}
{
Get/set oriented edge's seaming flag, ie position of the oriented edge wrt to the UNIQUE main boundary
}
\ccMethod{void set_halfedge_seaming (Vertex_handle source, Vertex_handle target, int seaming);}
{
}


\textbf{CORNER INTERFACE:}

\ccMethod{Point_2 get_corners_uv (Vertex_const_handle vertex, Vertex_const_handle prev_vertex, Vertex_const_handle next_vertex) const;}
{
Get/set the 2D position (= (u,v) pair) of corners at the "right" of the prev\_vertex -$>$ vertex -$>$ next\_vertex line. Default value is undefined.
}
\ccMethod{void set_corners_uv (Vertex_handle vertex, Vertex_const_handle prev_vertex, Vertex_const_handle next_vertex, const Point_2 & uv);}
{
}
\ccMethod{bool are_corners_parameterized (Vertex_const_handle vertex, Vertex_const_handle prev_vertex, Vertex_const_handle next_vertex) const;}
{
Get/set "is parameterized" field of corners at the "right" of the prev\_vertex -$>$ vertex -$>$ next\_vertex line. Default value is undefined.
}
\ccMethod{void set_corners_parameterized (Vertex_handle vertex, Vertex_const_handle prev_vertex, Vertex_const_handle next_vertex, bool parameterized);}
{
}
\ccMethod{int get_corners_index (Vertex_const_handle vertex, Vertex_const_handle prev_vertex, Vertex_const_handle next_vertex) const;}
{
Get/set index of corners at the "right" of the prev\_vertex -$>$ vertex -$>$ next\_vertex line. Default value is undefined.
}
\ccMethod{void set_corners_index (Vertex_handle vertex, Vertex_const_handle prev_vertex, Vertex_const_handle next_vertex, int index);}
{
}
\ccMethod{int get_corners_tag (Vertex_const_handle vertex, Vertex_const_handle prev_vertex, Vertex_const_handle next_vertex) const;}
{
Get/set all purpose tag of corners at the "right" of the prev\_vertex -$>$ vertex -$>$ next\_vertex line. Default value is undefined.
}
\ccMethod{void set_corners_tag (Vertex_handle vertex, Vertex_const_handle prev_vertex, Vertex_const_handle next_vertex, int tag);}
{
}


\ccSeeAlso

\ccRefConceptPage{MeshAdaptor_3}


\ccExample

This example program instantiates a polyhedron and a polyhedron adaptor using the default
traits class and parameterizes the polyhedron.

\ccIncludeExampleCode{Parameterization/Polyhedron_parameterization5.C}


\end{ccRefConcept}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
% EOF
% +------------------------------------------------------------------------+

