\begin{ccRefConcept}{Matrix}\ccCreationVariable{M}

\ccDefinition

An instance of data type \ccc{Matrix} is a matrix of variables of
number type \ccc{NT}. The types \ccc{Matrix} and \ccc{Vector} together
realize many functions of basic linear algebra. \ccc{Matrix} offers
all simple matrix operations.
 
\ccSetOneOfTwoColumns{5.5cm}

\ccTypes

\ccNestedType{NT}{the number type of the components.}

\ccNestedType{Vector}{the vector type used. }

\ccNestedType{iterator}{the iterator type for accessing rows. }

\ccNestedType{const_iterator}{the const iterator type for accessing rows.}

\ccNestedType{Identity}{a tag class for identity initialization. }

\ccNestedType{Initialize}{a tag class for homogeneous initialization. }

\ccSetOneOfTwoColumns{4cm}

\ccCreation

\ccConstructor{Matrix(int n)}{creates an instance \ccc{M} of type
  \ccc{Matrix} of dimension $n \times n$ initialized to the zero
  matrix.  }

\ccConstructor{Matrix(int n, int m)}{creates an instance \ccc{M} of
  type \ccc{Matrix} of dimension $n \times m$ initialized to the zero
  matrix.  }

\ccConstructor{Matrix(int n, Identity, NT x = NT(1))}{creates an
  instance \ccc{M} of type \ccc{Matrix} of dimension $n \times n$
  initialized to the identity matrix (times \ccc{x}).  }

\ccConstructor{Matrix(int n, int m, Initialize, NT x)}{ creates an
  instance \ccc{M} of type \ccc{Matrix} of dimension $n \times m$
  initialized to the matrix with \ccc{x} entries.  }

\ccConstructor{template <class Forward_iterator>
  Matrix(Forward_iterator first, Forward_iterator last)}{ creates an
  instance \ccc{M} of type \ccc{Matrix}. Let $S$ be the ordered set of
  $m$ column-vectors of common dimension $n$ as given by the iterator
  range \ccc{[first,last)}.  \ccc{M} is initialized to an $n \times m$
  matrix with the columns as specified by $S$.  \ccRequire
  \ccc{Forward_iterator} has a value type \ccc{V} from which we
  require that it provides an iterator type \ccc{V::const_iterator},
  and the value type of \ccc{V::const_iterator} is \ccc{NT}.\\ Note
  that \ccc{Vector} or \ccc{std::vector<NT>} fulfill these
  requirements.  }

\ccConstructor{Matrix(std::vector<Vector> A)}{ creates an instance
  \ccc{M} of type \ccc{Matrix}. Let $A$ be an array of $m$
  column-vectors of common dimension $n$.  \ccc{M} is initialized to
  an $n \times m$ matrix with the columns as specified by $A$.  }

\ccSetTwoOfThreeColumns{1.7cm}{3.5cm}

\ccOperations

\ccMethod{int row_dimension() ;}{ returns $n$, the number of rows of
  \ccc{M}.}

\ccMethod{int column_dimension() ;}{ returns $m$, the number of
  columns of \ccc{M}.}

\ccMethod{std::pair<int,int> dimension() ;}{ returns $(m,n)$, the
  dimension pair of \ccc{M}.}

\ccMethod{Vector row(int i) ;}{ returns the $i$-th row of \ccc{M} (an
  $m$ - vector).  \ccPrecond $0 \le i \le n - 1$.}

\ccMethod{Vector column(int i) ;}{ returns the $i$-th column of
  \ccc{M} (an $n$ - vector).  \ccPrecond $0 \le i \le m - 1$. }

\ccMethod{NT& operator()(int i, int j) ;}{returns $M_{ i,j }$.
  \ccPrecond $0\le i\le n - 1$ and $0\le j\le m - 1$.}

\ccMethod{void swap_columns(int i, int j) ;}{swaps columns $i$ and
  $j$.  }

\ccMethod{void swap_rows(int i, int j) ;}{swaps rows $i$ and $j$.  }

\ccMethod{bool operator==(const Matrix& M1) ;}{Test for equality.  }

\ccMethod{bool operator!=(const Matrix& M1) ;}{Test for inequality.  }

\ccHeading{Arithmetic Operators} 
\ccSetTwoOfThreeColumns{2cm}{3cm}

\newcommand{\dimeq}{ \ccc{M.row_dimension() == M1.row_dimension()} and
  \ccc{M.column_dimension() == M1.column_dimension()} }
 
\ccMethod{Matrix operator+ (const Matrix& M1);}{
 Addition. \ccPrecond \dimeq.}

\ccMethod{Matrix operator- (const Matrix& M1);}{ Subtraction.
  \ccPrecond \dimeq.}

\ccMethod{Matrix operator-();}{Negation.  }

\ccMethod{Matrix operator*(const Matrix& M1) ;}{ Multiplication.
  \ccPrecond \ccc{M.column_dimension() = M1.row_dimension()}.  }

\ccMethod{Vector operator*(const Vector& vec) ;}{ Multiplication with
  vector. \ccPrecond \ccc{M.column_dimension() = vec.dimension()}. }


\ccFunction{ Matrix operator*(const Matrix& M, const NT& x) ;}{
  Multiplication of every entry with \ccc{x}.}

\ccFunction{ Matrix operator*(const NT& x, const Matrix& M) ;}{
  Multiplication of every entry with \ccc{x}.}

\end{ccRefConcept}


