% +------------------------------------------------------------------------+
% | Reference manual page: Polyhedron_traits_with_normals_3.tex
% +------------------------------------------------------------------------+
% | 17.03.1999   Lutz Kettner
% | Package: Polyhedron
% | 
\RCSdef{\RCSPolyhedrontraitswithnormalsRev}{$Revision$}
\RCSdefDate{\RCSPolyhedrontraitswithnormalsDate}{$Date$}
% +------------------------------------------------------------------------+

\ccRefPageBegin

%%RefPage: end of header, begin of main body
% +------------------------------------------------------------------------+


\begin{ccRefClass}{Polyhedron_traits_with_normals_3<Kernel>}

\ccDefinition
  
The class \ccRefName\ is a model of the \ccc{PolyhedronTraits_3}
concept. It defines the geometric types and primitive operations used
in the polyhedral surface data structure
\ccc{CGAL::Polyhedron_3<PolyhedronTraits_3>}. \ccRefName\ uses the
normal vector from \ccc{Kernel} for the plane equation in facets. It
keeps a local copy of the kernel which makes it suitable for kernels
with local state.

\ccInclude{CGAL/Polyhedron_traits_with_normals_3.h}

\ccIsModel

\ccRefConceptPage{PolyhedronTraits_3}

\ccTypes
\ccThree{typedef Kernel::Construct_opposite_vector_3;}
    {Construct_opposite_plane_3;;}{}
\ccTwo{Polyhedron_traits_with_normals_3<Kernel> traits ( Kernel kernel);;;;}{}

\ccNestedType{Kernel}{the \ccc{Kernel} model.}
\ccGlue
\ccTypedef{typedef Kernel::Point_3 Point_3;}{}
\ccGlue
\ccTypedef{typedef Kernel::Vector_3 Plane_3;}{}

\ccTypedef{typedef Kernel::Construct_opposite_vector_3 
    Construct_opposite_plane_3;}{}

\ccCreation
\ccCreationVariable{traits}  %% choose variable name

\ccConstructor{Polyhedron_traits_with_normals_3();}{default constructor, uses 
    \ccc{Kernel()} as local reference to the kernel.}

\ccConstructor{Polyhedron_traits_with_normals_3( const Kernel& kernel);}
    {stores \ccc{kernel} as local reference.}

\ccOperations

\ccMethod{Construct_opposite_plane_3 construct_opposite_plane_3_object();}{
    forwarded to \ccc{kernel}.}

\ccSeeAlso

\ccRefIdfierPage{CGAL::Polyhedron_traits_3<Kernel>}

\ccExample

We use this traits class to instantiate a polyhedral surface with a
normal vector and no plane equation for each facet. We compute the
normal vector assuming exact arithmetic (integers in this example)
and convex planar facets.

\ccIncludeExampleCode{Polyhedron/polyhedron_prog_normals.C}

\end{ccRefClass}

% +------------------------------------------------------------------------+
%%RefPage: end of main body, begin of footer
\ccRefPageEnd
% EOF
% +------------------------------------------------------------------------+

