\begin{ccRefConcept}{Solution_1}

\ccDefinition

The concept \ccc{Solution_1} is meant to store a coordinate ($x$, or $y$) of
a point on curve. 

\ccRefines
 \ccc{DefaultConstructible, Assignable, LessThanComparable, CompactifiedNumber}

The concept \ccc{CompactifiedNumber} has not been introduced so far. Michael
Hemmer will introduce it as basic tool as soon as possible. For
now we assume that a number of this type is either finite, and if not,
we can ask, wether it represents $\pm\infty$.

There are reasons why we introduce \ccc{Solution_1} over 
\ccc{AlgebraicReal_1}\footnote{Not yet introduced so far}:
\begin{itemize}
\item It may suffices to use a simpler number type ($Q[\sqrt{2}]$).
\item Keep concept minimal, \ccc{AlgebraicReal_1} will quite certainly
contain more than needed here.
\item \ccc{AlgebraicReal_1} won't be a refinement of \ccc{CompaticiedNumber}.
\ccc{double} is.
\end{itemize}

\begin{ccAdvanced}

\ccTypes

\ccTypedef{typedef typename Solution_1::Boundary Boundary;}{A NT being able
to represent values between two Solution\_1}

\ccCreationVariable{sol1}

\ccAccessFunctions

Is this type meant to be really abstract (only RealEmbeddable) or 
do we want to have access
to certain entries? In general, it should be possible to use an appropriate
NT here, i.e., a NT that fits the needs of the CA/CPA.

TODO: Defining polynomial?

TODO: For some purposes (e.g., drawing, seperation) it is useful to have the 
following methods:

\ccMethod{Boundary between(Solution_1 s);}{
  returns a rational between \ccc{sol1} and \ccc{s}
  \ccPrecond{sol1 != s}
}

\ccMethod{std::pair<Boundary,Boundary> approximate(int prec);}{
  Refines the representation to the given precision (binary digits 
  after point). Internally the precision can already be higher.
} 

The advanced methods can be seen as a refined concept for enabling drawing. 
Maybe, we can have it orthogonal to the normal concept.

\end{ccAdvanced}

Remark: Note that this concept only deals with the interface to upper
layers. There might be additional requirements for number types to 
implement a model of this concept.

\ccHasModels
\ccc{double, NiX::Compactified< NiX::Algebraic_real >}

\end{ccRefConcept}
