%%  \cleardoublepage

{
\begin{thebibliography}{AMC+}

\bibitem[Avnaim]{Protocgal}
F.~Avnaim.
\newblock {C}++{G}{A}{L}: {A} {C}++ library for geometric algorithms.
\newblock 1994.

\bibitem[Avnaim et al.]{ABDPY}
F.~Avnaim, J.-D. Boissonnat, O.~Devillers, and F.~Preparata an~d M.~Yvinec.
\newblock Evaluation of a new method to compute signs of determinants.
\newblock In {\em Communication at the 11th Annu. ACM Sympos. Comput. Geom.},
  1995.

\bibitem[Br\"ungger et al.]{XYZ}
Br\"ungger, De Lorenzi, Marzetta, Matthias M\"uller, Nievergelt, Schorn,
and  Sleumer.
\newblock \ccAnchor{http://wwwjn.inf.ethz.ch/geobench/XYZGeoBench.html}{XYZ: EXperimental GeometrY Zurich}.

\bibitem[Burnikel et al.]{BKMNSU95_prec}
C.~Burnikel, J.~K\"onemann, K.~Mehlhorn, S.~N\"aher, S.~Schirra, and C.~Uhrig.
\newblock Exact geometric computation in {LEDA}.
\newblock In {\em Proceedings of the 11{th} ACM Symposium on Computational
  Geometry}, pages C18--C19, 1995.

\bibitem[Burnikel et al.]{reals_TR}
C.~Burnikel, K.~Mehlhorn, and S.~Schirra.
\newblock The {LEDA} class {\tt real} number.
\newblock Technical Report MPI-I-96-1-001, Max-Planck-Institut f\"ur
  Informatik, 1996.

\bibitem[Fabri et al.]{FGKSS}
A.~Fabri, G.J.~Giezeman, L.~Kettner, S.~Schirra, and S.~Sch\"onherr.
\newblock The {\sc Cgal} Kernel: A Basis for Geometric Computation.
\newblock {\em Proc.\ of the 1st ACM Workshop on Applied Computational 
Geometry}, 1996.  {\em Lecture Notes in Computer Science}, Vol.~1148, 1996.
\bibitem[Fortune]{fortune_survey}
S.~Fortune.
\newblock Progress in computational geometry.
\newblock In R.~Martin, editor, {\em Directions in Geometric Computing}, pages
  81 -- 128. Information Geometers Ltd., 1993.

\bibitem[Giezeman]{PlaGeo}
G.-J. Giezeman.
\newblock Pla{G}eo, a library for planar geometry, and {S}pa{G}eo, a library
  for spatial geometry.
\newblock 1994.


\bibitem[Gmp]{Gmp}
Torbj\"orn Granlund, TMG Dataconsult
\newblock The 
\ccAnchor{ftp://prep.ai.mit.edu/pub/gnu/gmp-M.N.tar.gz+}{GNU}
 Multiple Precision Arithmetic Library.
\newblock Edition 2.0.2, June 1996 


\bibitem[Hoffmann1]{Ho_GSM}
C.M. Hoffmann.
\newblock {\em Geometric and Solid Modeling}.
\newblock Morgan Kaufman, San Francisco, 1990.
\newblock Chapter~4.

\bibitem[Hoffmann2]{Ho_prec89}
C.M. Hoffmann.
\newblock The problem of accuracy and robustness in geometric computation.
\newblock {\em IEEE Computer}, pages 31--41, March 1989.

\bibitem[WACG]{wacg}
M.C. Lin, D. Manocha, (Eds.) 
\newblock {\em Applied Computational Geometry. Towards Geometric Engineering}. 
FCRC '96 Workshop, WACG '96, Philadelphia, PA, May 27 28, 1996. 
Springer LNCS 1148.

\bibitem[Mehlhorn et al.]{leda_cacm}
K.~Mehlhorn and S.~N\"aher.
\newblock \ccAnchor{http://www.mpi-sb.mpg.de/LEDA/leda.html}{LEDA}
A platform for combinatorial and geometric computing.
\newblock {\em Communications of the ACM}, 38(1):96--102, 1995.

\bibitem[Mehlhorn et al.]{leda-manual}
K.~Mehlhorn, S.~N\"aher and C.~Uhrig.
\newblock The \ccAnchor{http://www.mpi-sb.mpg.de/LEDA/leda.html}{LEDA} User Manual.

\bibitem[Schirra]{Udine_notes}
S.~Schirra, {\em Precision and Robustness in Geometric Computation},
\newblock Lecture Notes of Advanced School on Algorithmic Foundations of
Geographic Information Systems, Udine, Sept.~1996. 
\newblock (to appear).

\bibitem[Serpette et al.]{BigNum}
B.~Serpette, J.~Vuillemin, and J.C. Herv\protect{\'e}.
\newblock Big{N}um, a portable and efficient package for arbitrary-precision
  arithmetic.
\newblock Technical Report Research Report 2, Digital Paris Research
  Laboratory, 1989.

\bibitem[Yap1]{yap:crc}
C.~K. Yap.
\newblock Robust geometric computation.
\newblock In J.~E. Goodman and J.~O'Rourke, editors, {\em CRC Handbook in
  Computational Geometry}. CRC Press, 1996.
\newblock (to appear).

\bibitem[Yap2]{Yap_exact_CCCG}
C.K. Yap.
\newblock Towards exact geometric computation.
\newblock In {\em Proc.\ of the 5th Canadian Conference on Computational
  Geometry}, pages 405--419, 1993.

\bibitem[Yap and Dub\'e]{YD_ecp_prec}
C.~K. Yap and T.~Dub{\protect \'e}.
\newblock The exact computation paradigm.
\newblock In D.Z. Du and F.~Hwang, editors, {\em Computing in {E}uclidean
  Geometry}, pages 452--492. World Scientific Press, 1995.
\newblock 2nd edition.

\end{thebibliography}
}
