\begin{ccRefClass}{Filtered_kernel<CK>}

% was: \begin{ccRefClass}{Filtered_kernel<CK, EK, FK, C2E, C2F>}

\KernelRefLayout\gdef\ccTagOperatorLayout{\ccFalse}

\ccDefinition

\ccClassTemplateName is a kernel that uses the filtering technique based
on interval arithmetic from \cite{cgal:bbp-iayed-01} to achieve
exact and efficient predicates.  In addition, a few selected important
predicates are implemented using the formally proved, semi-static, filtering
techniques from \cite{cgal:mp-fcafg-05}.

The geometric constructions are exactly those
of the kernel \ccc{CK}, which means that they are not necessarily exact.
%The global functions are also currently not changed, i.e. they are those
%of \ccc{CK}.

% This is achieved by converting the geometric objects of \ccc{CK} arguments of
% each predicate to the filtering kernel \ccc{FK} using \ccc{C2F}, then applying
% the corresponding predicate from \ccc{FK}, which should throw an exception in
% case it cannot determine the result exactly.  In this case the exception is
% caught and the corresponding predicate from the kernel \ccc{EK} is called to
% obtain the exact result (after having converted the arguments using
% \ccc{C2E}).

% \ccc{CK}, \ccc{EK}, \ccc{FK} must be models of the concept \ccc{Kernel}.

% At the moment, the parameter \ccc{FK} supports only the four kernels of
% CGAL instantiated with \ccc{Interval_nt_advanced}.

% The default parameters are \ccc{EK = Simple_cartesian<MP_Float>},
%   \ccc{FK = Simple_cartesian<Interval_nt_advanced>},
%   \ccc{C2E = Cartesian_converter<CK, EK>},
%   \ccc{C2F = Cartesian_converter<CK, FK, To_interval<CK::RT>}.

\ccInclude{CGAL/Filtered_kernel.h}

\ccParameters

The first parameter, \ccc{CK}, is the "Construction Kernel", namely the kernel
from which are taken the types of the geometric objects as well as the
geometric constructions.

The second parameter, \ccc{UseStaticFilters}, is a Boolean value which
activates or not an additional layer of semi-static filters.  It defaults to
\ccc{true} (activated), unless the \ccc{CGAL_NO_STATIC_FILTERS} macro is
defined.  This option is mostly for debugging and testing, there should be no
production use for deactivating static filters.

\ccIsModel
\ccc{Kernel}

\ccTypes

\ccTypedef{typedef EK Exact_kernel;}{The type of the exact kernel.}
\ccGlue
\ccTypedef{typedef FK Approximate_kernel;}{The type of the approximate "filtering" kernel.}

\ccConstants

\ccVariable{static const bool Has_static_filters;}{A Boolean value corresponding to the
second template argument.  Tells whether static filters are provided.}

\ccExample

The following example shows how to produce a kernel whose geometric
objects and constructions are those of \ccc{Simple_cartesian<double>}
but the predicates are exact. 

\begin{verbatim}
#include <CGAL/Simple_cartesian.h>
#include <CGAL/Filtered_kernel.h>

typedef CGAL::Simple_cartesian<double> CK;
typedef CGAL::Filtered_kernel<CK> K;

\end{verbatim}

\ccImplementation
The implementation uses \ccc{CGAL::Filtered_predicate<EP, FP, C2E, C2F>} over
each predicate of the kernel traits interface.  Additionally, faster static
filters may be used for a few selected critical predicates.

\end{ccRefClass}
